### 2017-07-03 Manuscript_11May.Rmd
Add files via upload

---
title             : "Comparing MTurk and the US Population’s Occupational Diversity"
shorttitle        : "MTurk's Occupational Diversity"

author: 
  - name          : "Christopher M. Castille"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    email         : "chris_castille@mac.com"
  - name          : "Bodour H. Mahmoud"
    affiliation   : "2"
  - name          : "Rachel L. Williamson"
    affiliation   : "3"
  - name          : "John E. Buckner"
    affiliation   : "4"
  - name          : "James De Leôn"
    affiliation   : "5"
affiliation:
  - id            : "1"
    institution   : "Nicholls State University"
  - id            : "2"
    institution   : "Villanova University"
  - id            : "3"
    institution   : "University of Georgia"
  - id            : "4"
    institution   : "AlixPartners"
  - id            : "5"
    institution   : "APT Metrics"

author_note: >
  All correspondence should be sent to the lead author at chris_castille@mac.com.

abstract: >
  We compare the occupational diversity of two convenient MTurk samples against the broader US economy from which they have been indirectly sampled. We focus on occupational diversity given a chief concern that findings from OB/HR investigations relying on MTurk might not generalize to the broader US economy . Additionally, as researchers may hope to target specific populations (e.g., sales professionals) understanding the extent to which these professionals are represented in the MTurk population would be helpful. Therefore, we compare the occupational diversity of MTurk against that described by the Bureau of Labor Statistics, testing the null hypothesis that these populations are equivalent in terms of occupational diversity. Across both samples, which were obtained from studies conducted in 2015, we found differences suggesting that the MTurk population is generally overrepresented by white collar professionals (though this is an imperfect trend) and generally underrepresented by blue collar workers.
keywords          : "MTurk, Occupational Diversity"
wordcount         : "3000"

bibliography      : ["references.bib"]

figsintext        : no
figurelist        : no
tablelist         : yes
footnotelist      : no
lineno            : no

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---

```{r message = FALSE, warning = FALSE}
library("papaja")
require(devtools)
install_github("crsh/papaja")
```
#Introduction
  Amazon’s Mechanical Turk (MTurk), an online labor market created by Amazon, has recently become popular among social scientists interested in collecting inexpensive, high-quality data from a diverse population (@aguinis2012conducting @behrend2011viability @bergman2016have @paolacci2014inside @shank2016using). Leveraging the strengths of this tool, MTurk has been used by social scientists to replicate well-known phenomena (e.g., reaction times, priming, task switching; @crump2013evaluating; memory, @simons2012common) and by organizational behavior (OB) researchers to expand the OB literature (e.g., @yarkoni2015interactions).

  Yet, in spite of the growing enthusiasm surrounding the use of MTurk, it represents merely another convenient sampling methodology that comes with a few constraints, such as repeated participation or motivation due to compensation (@landers2015inconvenient @woo2015amazon) and other yet-to-be-identified constraints. Here, we examine one potentially important constraint for using MTurk to conduct OB research: the occupational diversity of MTurk. Given that a fundamental goal of most OB research is that workers are sampled from an appropriate organizational setting (e.g., @pathak2008methodology), understanding the occupational diversity of MTurk will improve our understanding of the boundary conditions or limits to the generalizability of MTurk research findings. By examining the occupational diversity of MTurk, our work addresses a call for research that describes the kinds of individuals who participate in MTurk studies (@griggs2016these).

#Review of the Literature
##What is MTurk?
  MTurk is an internet marketplace where people seeking laborers have access to a population of workers willing to do tasks requiring a human intelligence for a small fee (@behrend2011viability). Billed as a “marketplace for work that requires human intelligence”, MTurk allows “requesters” to post Human Intelligence Tasks (HITs), which serve as self-contained jobs in which “workers” can participate. Via MTurk, researchers seeking participants often post survey studies for workers to voluntarily complete (@goodman2013data). Workers are given a short description about a project, including details about various tasks, estimated time investment, and payment, and may selectively choose which projects to complete. Here, researchers seeking participants often post survey studies for workers to voluntarily complete (@goodman2013data).

##Why is MTurk Valuable for Researchers Studying Working Populations?
  MTurk offers practical advantages that may not be available via other more traditional methods of data collection, such as sampling from specific organizations (@paolacci2010running). The platform allows for easier subject pool access at an affordable cost and for subject prescreening (@mason2012conducting). Additionally, it allows for subject anonymity, subject identifiability in longitudinal studies, and offers a simple and supportive infrastructure (@paolacci2010running). More importantly, its diversity is a key strength that sets it apart from other commonly studied populations (e.g., university students, community samples), making it an attractive subject pool for researchers to draw upon (@buhrmester2011amazon; Erikson & Simpson, 2010; @paolacci2010running). For instance, @behrend2011viability found that MTurk workers are more diverse on variables such as age, ethnicity, education, employment status, job experience, profession, nationality, and personality. The diversity of MTurk allows OB researchers to overcome concerns regarding the generalizability of their findings (e.g., @paolacci2010running), which has been a key concern facing OB research (@chiao2010weirdest).

  However, while researchers have praised MTurk for its diversity, few organizational behavior researchers have considered how MTurk might be less diverse than expected in a key respect: occupational diversity. To our knowledge, no study has compared the occupational diversity of MTurk to the broader US population. While @behrend2011viability work suggests that MTurk’s occupational diversity is greater than the university population, our work expands on their research by comparing MTurk’s occupational diversity to the broader US population. If the occupational diversity of the broader US population is indeed reflected in MTurk, findings from MTurk should better generalize across occupations. Alternatively, if MTurk’s occupational diversity over- or under-represent certain occupations, generalizability of findings from MTurk should be more limited.

  *Research Question: Is the occupational diversity of the MTurk population representative of the broader US economy?*

# Methods
##US Population Occupational Summary Statistics
  Occupational Employment Statistics (OES) were obtained from the United States Bureau of Labor Statistics (BLS) (2015). Occupation diversity was measured by calculating the percentage of job holders falling under a particular occupational category. We adopted the Intermediate Aggregation and Standard Occupational Classification (SOC) used by the Bureau of Labor Statistics (BLS) for this study (see table 1). Percentages describe the percentage of workers in the US economy who work in occupations that fall under this broader occupational category.

#- - - - - - - - - - - - - 
#insert table 1 about here
#- - - - - - - - - - - - -

```{r,BLS, include=FALSE, results='asis'}
#Load packages
library(readr)
library(readxl)
library(data.table)

#Load datasets. Note: these datasets were not taken direclty from their respective sources (i.e., BLS or Qualtrics survey, respectively). The BLS dataset is a table describing the broader occupational categories, number of employees working in jobs that fall under one of these categories, and the relative frequency of jobs falling under said occupational category. The LATech dataset comes from a separate investigaiton using MTurk whereby individuals who were flagged for inattentive responding were removed from the dataset. The UGA dataset is a full dataset in the sense that it contains all individuals whose data are relevant for our investigation (i.e., participants hold a job that falls under a SOC classification) or not (i.e., they either do not work or work in a job falling outside the SOC classification system).

#Build the BLS Table.
##BLS data
BLS <- read_excel("~/Documents/Research/Research on MTurk/MTurk's Occupational Diversity/Datasets/BLS Data from 2015.xlsx")
###Rename rows and aggregate.
BLS[1, 1] = "11-13 Management, Business, and Financial Occupations"
BLS[2, 1] = "11-13 Management, Business, and Financial Occupations"
BLS[3, 1] = "15-19 Computer, Engineering, and Science Occupations"
BLS[4, 1] = "15-19 Computer, Engineering, and Science Occupations"
BLS[5, 1] = "15-19 Computer, Engineering, and Science Occupations"
BLS[6, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
BLS[7, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
BLS[8, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
BLS[9, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
BLS[10, 1] = "29 Healthcare Practitioners and Technical Occupations"
BLS[11, 1] = "31-39 Service Occupations"
BLS[12, 1] = "31-39 Service Occupations"
BLS[13, 1] = "31-39 Service Occupations"
BLS[14, 1] = "31-39 Service Occupations"
BLS[15, 1] = "31-39 Service Occupations"
BLS[16, 1] = "41 Sales and Related Occupations"
BLS[17, 1] = "43 Office and Administrative Support Occupations"
BLS[18, 1] = "45 Farming, Fishing, and Forestry Occupations"
BLS[19, 1] = "47 Construction and Extraction Occupation"
BLS[20, 1] = "49 Installation, Maintenance, and Repair Occupations"
BLS[21, 1] = "51 Production Occupation"
BLS[22, 1] = "53 Transportation and Material Moving Occupation"
BLS[23, 1] = "55 Military Specific Occupations"
names(BLS) <- c("Var1","Var2","Var3")
BLS <- aggregate(.~Var1,BLS,sum)
###Data on the size of the military taken from the department of defense (http://us-military-branches.insidegov.com). 
BLS[13, 2] = "1350236"
names(BLS) <- c("Intermediate Aggregation Title", "Freq","RFreq")
BLS$Freq <- as.numeric(BLS$Freq)
tab <- transform(BLS, relative = prop.table(Freq))
BLS <- tab[c(1,4)]
names(BLS) <- c("Intermediate Aggregation Title","e")
```

```{r Sample Data, include=FALSE, results='asis', echo=FALSE}
##LATech data
LATech <- read_csv("/Users/ccasti02/Documents/Research/Research on MTurk/MTurk's Occupational Diversity/Datasets/Chris's Data from 2015.csv")
###Delete unneeded data.
LATech <- LATech[c(1:3)]
###Edit data. Some participants provided incorrect codes or no codes.
LATech[703, 3] = "43-6011.00"
LATech[704, 3] = "43-6011.00"
LATech[705, 3] = "43-6011.00"
LATech[706, 3] = "43-6011.00"
LATech[707, 3] = "43-6011.00"
LATech[755, 3] = "43-9199.00"
LATech[756, 3] = "11-3051.01"
LATech[757, 3] = "43-3031.00"
LATech[758, 3] = "17-2199.00"
LATech[759, 3] = "13-2099.00"
LATech[760, 3] = "33-3051.01"
LATech[761, 3] = "23-1011.00"
LATech[762, 3] = "27-3099.00"
LATech[763, 3] = "17-2199.00"
LATech[765, 3] = "43-9061.00"
LATech[766, 3] = "39-5012.00"
LATech[768, 3] = "19-4061.00"
LATech[769, 3] = "41-4011.00"
LATech[770, 3] = "43-4171.00"
LATech[771, 3] = "15-1134.00"
LATech[772, 3] = "37-2012.00"
LATech[773, 3] = "41-1011.00"
LATech[775, 3] = "25-0000.00"
LATech[776, 3] = "25-0000.00"
LATech[779, 3] = "13-1111.00"
LATech[781, 3] = "29-1171.00"
LATech[782, 3] = "37-2012.00"
LATech[785, 3] = "35-2014.00"
LATech[786, 3] = "29-1123.00"
LATech[784, 3] = "25-0000.00"
###Remove unemployed cases.
completeFun <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}
LATech <- completeFun(LATech, "O*NET Job Code")

###Abbreviate data, consolidate into intermediate categories, and bind.
LO <- LATech[c(3)]
LO <- read.fwf(textConnection(LO$`O*NET Job Code`), 2)
names(LO) <- c("Int.Agg.Cat")
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 11] <- "11-13 Management, Business, and Financial Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 13] <- "11-13 Management, Business, and Financial Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 15] <- "15-19 Computer, Engineering, and Science Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 17] <- "15-19 Computer, Engineering, and Science Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 19] <- "15-19 Computer, Engineering, and Science Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 21] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 23] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 25] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 27] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 29] <- "29 Healthcare Practitioners and Technical Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 31] <- "31-39 Service Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 33] <- "31-39 Service Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 35] <- "31-39 Service Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 37] <- "31-39 Service Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 39] <- "31-39 Service Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 41] <- "41 Sales and Related Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 43] <- "43 Office and Administrative Support Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 45] <- "45 Farming, Fishing, and Forestry Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 47] <- "47 Construction and Extraction Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 49] <- "49 Installation, Maintenance, and Repair Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 51] <- "51 Production Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 53] <- "53 Transportation and Material Moving Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 55] <- "55 Military Specific Occupations"
LATech <- cbind(LATech,LO)
###Build relative frequency table.
tab <- as.data.frame(table(LATech$Int.Agg.Cat, exclude=NULL))
tab <- transform(tab, relative = prop.table(Freq))
names(tab) <- c("Intermediate Aggregation Title","n","f")
#Table for poster.
table <- merge(BLS,tab, by="Intermediate Aggregation Title", all=TRUE)

##UGA data
UGA <- read_excel("/Users/ccasti02/Documents/Research/Research on MTurk/MTurk's Occupational Diversity/Datasets/Rachel's Data from 2015.xlsx")
UGA <- UGA[c(2,21)]
###Edit data. Some individuals could be classified under O*NET, but weren't in this previous investigation. Keep in mind that only the first two numbers really matter, so if there are errors (and they be random) then they should wash out at the high level of the hierarchy. 
####Manually recode self-reported job titles.
#Recode self-reports into SOC codes
UGA$ONETCode[UGA$JobTitle=="campus supervisor"] <- "11-9033.00"
UGA$ONETCode[UGA$JobTitle=="ETl Hardlines"] <- "37-2012.00"
UGA$ONETCode[UGA$JobTitle=="Calculations assistant"] <- "43-3031.00"
UGA$ONETCode[UGA$JobTitle=="community moderator"] <- "21-1099.00"
UGA$ONETCode[UGA$JobTitle=="senior engineer"] <- "17-2199.00"
UGA$ONETCode[UGA$JobTitle=="Attendant"] <- "53-2031.00"
UGA$ONETCode[UGA$JobTitle=="Student/Homemaker"] <- "37-2012.00"
UGA$ONETCode[UGA$JobTitle=="Operator"] <- "51-8013.00"
UGA$ONETCode[UGA$JobTitle=="Intake Coordinator"] <- "21-1011.00"
UGA$ONETCode[UGA$JobTitle=="none/homemaker"] <- "37-2012.00"
UGA$ONETCode[UGA$JobTitle=="HOMEMAKER"] <- "37-2012.00"
UGA$ONETCode[UGA$JobTitle=="Homemaker"] <- "37-2012.00"
UGA$ONETCode[UGA$JobTitle=="homemaker"] <- "37-2012.00"
UGA$ONETCode[UGA$JobTitle=="Home maker"] <- "37-2012.00"
UGA$ONETCode[UGA$JobTitle=="home maker"] <- "37-2012.00"
UGA$ONETCode[UGA$JobTitle=="Homemaker/Volunteer at Church"] <- "37-2012.00"
UGA$ONETCode[UGA$JobTitle=="Stay at home mother of two and wife/ maid :)"] <- "37-2012.00"
UGA$ONETCode[UGA$JobTitle=="Housewife"] <- "37-2012.00"
UGA$ONETCode[UGA$JobTitle=="homeworker"] <- "37-2012.00"
UGA$ONETCode[UGA$JobTitle=="Military"] <- "55-3019.00"
UGA$ONETCode[UGA$JobTitle=="military"] <- "55-3019.00"
UGA$ONETCode[UGA$JobTitle=="Navy Nuke"] <- "55-3019.00"
UGA$ONETCode[UGA$JobTitle=="SOLDIER"] <- "55-3019.00"
UGA$ONETCode[UGA$JobTitle=="Crew commander"] <- "55-3019.00"
UGA$ONETCode[UGA$JobTitle=="Administrator"] <- "21-1011.00"
UGA$ONETCode[UGA$JobTitle=="Engineering Administrator"] <- "21-1011.00"
UGA$ONETCode[UGA$JobTitle=="A bit of everything office wise"] <- "21-1011.00"
UGA$ONETCode[UGA$JobTitle=="postdoc"] <- "19-3022.00"
UGA$ONETCode[UGA$JobTitle=="Postdoctoral Fellow"] <- "19-3022.00"
UGA$ONETCode[UGA$JobTitle=="Postdoctoral Fellow"] <- "19-3022.00"
UGA$ONETCode[UGA$JobTitle=="Senior Research Fellow"] <- "19-3022.00"
UGA$ONETCode[UGA$JobTitle=="Associate Scientist"] <- "19-3022.00"
UGA$ONETCode[UGA$JobTitle=="Scientist"] <- "19-1042.00"
UGA$ONETCode[UGA$JobTitle=="scientist"] <- "19-1042.00"
UGA$ONETCode[UGA$JobTitle=="Associate Scientist"] <- "19-1042.00"
UGA$ONETCode[UGA$JobTitle=="Truck Driver"] <- "53-3032.00"
UGA$ONETCode[UGA$JobTitle=="Body piercer/owner"] <- "39-9099.00"
UGA$ONETCode[UGA$JobTitle=="Resource coordinator"] <- "13-1071.00"
UGA$ONETCode[UGA$JobTitle=="Administrative Research Assistant II"] <- "43-6014.00"
UGA$ONETCode[UGA$JobTitle=="Sr. Manager"] <- "11-9199.00"
UGA$ONETCode[UGA$JobTitle=="Bid Desk Specialist"] <- "43-9061.00"
UGA$ONETCode[UGA$JobTitle=="Senior Learning Leader (last position)"] <- "51-9061.00"
UGA$ONETCode[UGA$JobTitle=="Mad Scientist (Children's Entertainer/Educator)"] <- "27-2099.00"
UGA$ONETCode[UGA$JobTitle=="plan builder"] <- "47-4011.00"
UGA$ONETCode[UGA$JobTitle=="Therapy support staff"] <- "31-2012.00"
####Reclassify cases as "Unclear Occupational Category/Employed"
UGA$ONETCode[UGA$JobTitle=="Resource Room Director"] <- "99"
UGA$ONETCode[UGA$JobTitle=="currently self employed but I another job within t"] <- "99"
UGA$ONETCode[UGA$JobTitle=="Subject Matter Expert"] <- "99"
UGA$ONETCode[UGA$JobTitle=="Member"] <- "99"
UGA$ONETCode[UGA$JobTitle=="Idependent Contractor"] <- "99"
UGA$ONETCode[UGA$JobTitle=="Self Employed"] <- "99"
UGA$ONETCode[UGA$JobTitle=="Self-employed"] <- "99"
UGA$ONETCode[UGA$JobTitle=="Self-Employed"] <- "99"
UGA$ONETCode[UGA$JobTitle=="Self employed"] <- "99"
UGA$ONETCode[UGA$JobTitle=="self employed"] <- "99" ###Check this one..
UGA$ONETCode[UGA$JobTitle=="I'm currently self employed"] <- "99"
UGA$ONETCode[UGA$JobTitle=="self-employed"] <- "99"
UGA$ONETCode[UGA$JobTitle=="Casual Relief"] <- "99"
UGA$ONETCode[UGA$JobTitle=="no title given"] <- "99"
UGA$ONETCode[UGA$JobTitle=="TCSA"] <- "99"
UGA$ONETCode[UGA$JobTitle=="Independent Contrator"] <- "99"
UGA$ONETCode[UGA$JobTitle=="Independent Contractor"] <- "99"
UGA$ONETCode[UGA$JobTitle=="Independent contractor"] <- "99"
UGA$ONETCode[UGA$JobTitle=="Random jobs"] <- "99"
UGA$ONETCode[UGA$JobTitle=="Lead Organizer"] <- "99"
UGA$ONETCode[UGA$JobTitle=="Jr. Project Manager"] <- "99"
UGA$ONETCode[UGA$JobTitle=="Installer"] <- "99"
UGA$ONETCode[UGA$JobTitle=="Module Leader"] <- "99"
UGA$ONETCode[UGA$JobTitle=="paraprofphisonal"] <- "99"
####Delete the unemployed.
UGA<-UGA[!(UGA$JobTitle=="volunteer"),]
UGA<-UGA[!(UGA$JobTitle=="Volunteer"),]
UGA<-UGA[!(UGA$JobTitle=="unemployed"),]
UGA<-UGA[!(UGA$JobTitle=="Unemployed"),]
UGA<-UGA[!(UGA$JobTitle=="Unemployed/Stay at home daughter"),]
UGA<-UGA[!(UGA$JobTitle=="Stay at Home Mom, Piano Teacher, Mturker"),]
UGA<-UGA[!(UGA$JobTitle=="Currently uemployed, last position was customer se"),]
UGA<-UGA[!(UGA$JobTitle=="i used to be a crisis phone worker in a social ser"),]
UGA<-UGA[!(UGA$JobTitle=="unemployed/self employd"),]
UGA<-UGA[!(UGA$JobTitle=="I said I did not have one"),]
UGA<-UGA[!(UGA$JobTitle=="Not employed"),]
UGA<-UGA[!(UGA$JobTitle=="None"),]
UGA<-UGA[!(UGA$JobTitle=="None."),]
UGA<-UGA[!(UGA$JobTitle=="none"),]
UGA<-UGA[!(UGA$JobTitle=="not applicable"),]
UGA<-UGA[!(UGA$JobTitle=="not employed now"),]
UGA<-UGA[!(UGA$JobTitle=="na"),]
UGA<-UGA[!(UGA$JobTitle=="n/a"),]
UGA<-UGA[!(UGA$JobTitle=="n/a/"),]
UGA<-UGA[!(UGA$JobTitle=="N/A"),]
UGA<-UGA[!(UGA$JobTitle=="NA"),]
UGA<-UGA[!(UGA$JobTitle=="Not applicable. I freelance on MTurk and also writ"),]
UGA<-UGA[!(UGA$JobTitle=="Does not apply -- I pressed no on last question."),]
UGA<-UGA[!(UGA$JobTitle=="TURKER"),]
UGA<-UGA[!(UGA$JobTitle=="intern"),]
UGA<-UGA[!(UGA$JobTitle=="Intern"),]
UGA<-UGA[!(UGA$JobTitle=="Humane Education Intern"),]
UGA<-UGA[!(UGA$JobTitle=="student"),]
UGA<-UGA[!(UGA$JobTitle=="Student"),]
UGA<-UGA[!(UGA$JobTitle=="Graduate Student"),]
UGA<-UGA[!(UGA$JobTitle=="Ph. D Student"),]
UGA<-UGA[!(UGA$JobTitle=="Full Time Student"),]
UGA<-UGA[!(UGA$JobTitle=="Student Trainee (co-op)"),]
UGA<-UGA[!(UGA$JobTitle=="Medical student"),]
UGA<-UGA[!(UGA$JobTitle=="student manager"),]
UGA<-UGA[!(UGA$JobTitle=="Disabled"),]
UGA<-UGA[!(UGA$JobTitle=="Disabled/unable to work"),]
UGA<-UGA[!(UGA$JobTitle=="disabled"),]
UGA<-UGA[!(UGA$JobTitle=="Retired"),]
UGA<-UGA[!(UGA$JobTitle=="retired"),]
UGA<-UGA[!(UGA$JobTitle=="semi-retired"),]
UGA<-UGA[!(UGA$JobTitle=="RETIRED BUT WAS A MANAGER--PROJECT MGR, DEPARTMENT"),]
UGA<-UGA[!(UGA$JobTitle=="not employed"),]
UGA<-UGA[!(UGA$JobTitle=="I don't have a job"),]
UGA<-UGA[!(UGA$JobTitle=="parent at home"),]
UGA<-UGA[!(UGA$JobTitle=="stay at home mom"),]
UGA<-UGA[!(UGA$JobTitle=="stay at home parent"),]
UGA<-UGA[!(UGA$JobTitle=="Stay at home mom"),]
UGA<-UGA[!(UGA$JobTitle=="Mom"),]
UGA<-UGA[!(UGA$JobTitle=="Stay home mom"),]
UGA<-UGA[!(UGA$JobTitle=="Stat home mom"),]
UGA<-UGA[!(UGA$JobTitle=="Stat at home mom"),]
UGA<-UGA[!(UGA$JobTitle=="Slacker"),]
UGA <- completeFun(UGA, "ONETCode")
LO <- UGA[c(1)]
LO <- read.fwf(textConnection(LO$ONETCode), 2)
names(LO) <- c("Int.Agg.Cat")
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 11] <- "11-13 Management, Business, and Financial Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 13] <- "11-13 Management, Business, and Financial Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 15] <- "15-19 Computer, Engineering, and Science Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 17] <- "15-19 Computer, Engineering, and Science Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 19] <- "15-19 Computer, Engineering, and Science Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 21] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 23] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 25] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 27] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 29] <- "29 Healthcare Practitioners and Technical Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 31] <- "31-39 Service Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 33] <- "31-39 Service Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 35] <- "31-39 Service Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 37] <- "31-39 Service Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 39] <- "31-39 Service Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 41] <- "41 Sales and Related Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 43] <- "43 Office and Administrative Support Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 45] <- "45 Farming, Fishing, and Forestry Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 47] <- "47 Construction and Extraction Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 49] <- "49 Installation, Maintenance, and Repair Occupations"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 51] <- "51 Production Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 53] <- "53 Transportation and Material Moving Occupation"
LO$Int.Agg.Cat[LO$Int.Agg.Cat == 55] <- "55 Military Specific Occupations"
UGA <- cbind(UGA,LO)
###Build relative frequency table.
tab2 <- as.data.frame(table(UGA$Int.Agg.Cat, exclude=NULL))
tab2 <- transform(tab2, relative = prop.table(Freq))
names(tab2) <- c("Intermediate Aggregation Title","n","f")
tab2 <- merge(tab2,BLS, by="Intermediate Aggregation Title", all=TRUE)

#Chi-square function that quantifies the discrepancy between expected and observed proportions.
chi2 <- function(x) {
    o <- (x$n)
    e <- (x$e)
    n <- sum(x$n, na.rm=TRUE)
    ((o-(e)*(n))^2)/((e)*(n))
    }

#Confidence interval formula for proportions with assymptotic intervals. Intervals are assymptotic because proportions cannot be less than 0 or greater than 1, which becomes problematic as proportions near 0 or 1. 
require("binom")
CI <- binom.confint(table$n, sum(table$n), conf.level = 0.95, methods = "exact")
CI <- CI[c(5:6)]
table <- cbind(table,CI)
table <- table[,c(1,2,3,5,4,6)]
ch <- as.data.frame(chi2(table))
ch <- na.omit(ch)
names(table) <- c("Intermediate Aggregation Title","Exp(p)","n1","LCL1","Obs(p)1","UCL1")
CI2 <- binom.confint(tab2$n, sum(tab2$n), conf.level = 0.95, methods = "exact")
CI2 <- CI2[c(5:6)]
tab2 <- cbind(tab2,CI2)
tab2 <- tab2[,c(1,2,5,3,6,4)]
ch2 <- as.data.frame(chi2(tab2))
ch2 <- na.omit(ch2)
tab2 <- tab2[c(-6)]
names(tab2) <- c("Intermediate Aggregation Title","n2","LCL2","Obs(p)2","UCL2")
#Sum chi-square values.
sum(ch$`chi2(table)`, na.rm=TRUE)
sum(ch2$`chi2(tab2)`, na.rm=TRUE)
##Validate using chi-square function in r.
#Function for differences in relative percentages. This is not printed in the tables, but could be used to help readers see the disparity between expected and observed proportions.
f <- function(x) {
    f   <- (x$f)
    BLS <- (x$e)
    (f-BLS)
}
f1 <- as.data.frame(f(table))

#Print chi-square APA style.
require(devtools)
install_github("dgromer/apa")
require(apa)
##Sample 1#
Table2 <- merge(table,tab2, by="Intermediate Aggregation Title", all=TRUE)
observed1 <- Table2$n1
observed1 <- observed1[c(1:13)]
expected1 <- Table2$`Exp(p)`
expected1 <- expected1[c(1:13)]
c1 <- chisq_apa(chisq.test(x = observed1, p = expected1, correct = TRUE))

##Sample 2
observed2 <- Table2$n2
observed2 <- observed2[c(1:13)]
expected2 <- Table2$`Exp(p)`
expected2 <- expected2[c(1:13)]
c2 <- chisq_apa(chisq.test(x = observed2, p = expected2, correct = TRUE))

#Post-hoc power analysis.
##Convert chi-squares to correlation coefficient to allow meaningful statistic.
library(pwr)
###Study 1
X21 <-sum(ch$`chi2(table)`, na.rm=TRUE)
r1 <- sqrt((X21/sum(tab$n)))
pwr.chisq.test(w=r1,N=(sum(tab$n)),df=12,sig.level = .01)
###Study 2
X22 <- sum(ch2$`chi2(tab2)`, na.rm=TRUE)
r2 <- sqrt((X21/sum(tab2$n2)))
pwr.chisq.test(w=r2,N=(sum(tab2$n2)),df=12,sig.level = .01)
##Conclusion - both studies possess enough power to detect the disparities that we have observed; namely that the observed distribution of occupations in MTurk does not match the distribution of the larger economy. 
###When interpreting the differences, point out the magnitude of the disparity between expectations and observations.

```

##MTurk Occupational Summary Statistics
  Participants’ data were collected from two independently conducted studies (n~1~ = `r nrow(LATech)`; n~2~ = `r nrow(UGA)`). In one study (n~1~ =`r nrow(LATech)`), occupational data was self-reported by participants who were asked to described their job title. They were then brought to ONET online and asked to retrieve the  six-digit occupational classification code that most closely corresponded to their job title. In the second study (n~2~ = `r nrow(UGA)`), participants again self-reported their job title. However, the six-digit occupational classification codes were obtained by training research assistants to match the self-reported job titles to those in the ONET database. Using this data, we described the occupational diversity of each sample using relative frequencies of occupational category representation as described by Table 1.

##Analysis
  A chi-square test of goodness-of-fit was used to test whether proportions from MTurk samples deviated from expected proportions as derived from the BLS. Specifically, we tested whether MTurk’s occupational diversity deviated (p < .05) from that expected if we assume the BLS population parameters generalize to the MTurk population. This tests the null hypothesis that the populations are identical in terms of occupational diversity. To facilitate interpretation of our data, we also caluculated 95% confidence intervals for our sample proportions, which allows a visual inspection of whether or not the population value is within sampling error.

#Results
  Results shown in our table indicate that MTurk’s occupational frequency distribution does not consistently align with the US economy for both sample 1 ($\chi^2(12) = 368.58, p < .001$) and sample 2 ($\chi^2(12) = 486.07, p < .001$). Examining the 95% confidence intervals across both samples, certain occupations were consistently over- or under-represented. More specifically individuals sampled from MTurk occupied generally more white-collar jobs (e.g., Management, Business, and Financial Occupations; Computer, Engineering, and Science Occupations) and generally fewer blue-collar jobs (e.g., Construction and Extraction Occupations;  Installation, Maintenance, and Repair Occupations; Production Occupations) than what would be expected based on BLS data. For instance, 10.13% of workers in the US economy in 2015 worked in “Management, Business, and Financial Occupations.” By contrast, approximately 17% and 23% of workers from the MTurk samples fell under this classification. These trends were generally consistent across both study 1 and 2.

#- - - - - - - - - - - - - 
#insert table 2 about here
#- - - - - - - - - - - - -

#Discussion
  What started our investigation was a simple research question: is the occupational diversity of the MTurk population representative of the broader US population? Our data suggest that the answer is not consistently so: certain occupations are over-represented, some fall within expectations, and still others are under-represented. Thus, OB researchers using convenient sampling procedures that draw on the MTurk population should consider whether occupational features might play a role in their investigation, which is point that we will elaborate upon in greater detail. Simply put, our results suggest that MTurk’s (US) occupational diversity does not align with the broader US economy.

#Recommendations for Researchers Using MTurk
  Given that OB researchers will likely wish to continue using MTurk as a means of gathering diverse, convenient, and low-cost survey sample data, researchers should consider how differences in the occupational diversity observed amongst MTurk workers relative to the US population might impinge upon the generalizability of their findings (@newman2015external). Specifically, given the over-representation of workers from (1) Management, Business, and Financial, (2) Computer, Engineering, and Science, and (3) Education, Legal, Community Service, Arts, and Media occupations, we might safely assume that many of our findings from MTurk will generalize across jobs classified under these broader over-represented occupational categories. However, as many occupations were under-represented [e.g., (1) Service, (2) Construction and Extraction, (3) Installation, Maintenance, and Repair, (4) Production; and (5) Transportation and Material Moving], questions may arise as to whether findings will generalize to jobs falling under these broad classifications. 
  To address this issue, researchers should consider capturing occupational data and modeling theoretically derived moderators. Person-environment (P-E) fit theories should help guide researchers in proposing how certain occupational groupings might influence individual-level relationships, lending to more nuanced and contextualized results (@how2009dr). Further, O*NET might be useful in this regard as it provides researchers a means for quantifying key occupational differences (e.g., level of competition requirements, social skills requirements) and thereby testing P-E fit hypotheses pertaining to occupational group differences (see @judge2015person).

##Limitations and Future Research
  One key limitation is that we assumed that O*NET’s classification system perfectly captured all occupations during 2015. Additionally, as both studies involved convenient sampling procedures, it remains uncertain the extent to which these samples adequately reflect the larger MTurk population. Still, the consistency of our findings should be considered by future OB/HR researchers hoping to draw on MTurk for their research with the hopes of generalizing to the larger (or a specific) working US population. Additionally, as our studies were conducted in the US, it remains unclear how other MTurk populations might reflect (however imperfectly) their respective broader economy. Future larger scale studies should also consider lower levels of BLS occupational classification to examine the extent to which narrower occupations might not be represented by MTurk. Lastly, examining diversity in other respects (age, racio-ethnic, income, education, etc.) should also be considered. Though MTurk offers a practically feasible method of attaining high quality data, future research will be needed to understand the limitations of this tool.

  Given that our data were gathered and analyzed in 2015, it might be insightful to have our procedures replicated annually to examine how the demographics of MTurk, specifically occupational characteristics, change over time, especially as access to technology becomes even easier and more commonplace. Thus, we encourage researchers to continue examining the occupational diversity of MTurk relative to the US economy. We also encourage researchers to consider novel ways of approximating the occupational diversity of both the US economy and MTurk because the currently existing taxonomies that we have used (i.e., BLS-based) probably do not capture all occupations. Lastly, our results raise a new and interesting research question: Why might MTurk possess the occupational diversity makeup that it does (i.e., why are some occupations over-represented while others are under-represented)? Similarly, what factors (e.g., access to technology, interest in psychology) might make it easier for workers coming from certain occupations to participate in OB studies hosted on MTurk? Answering these questions might unearth more constraints that impinge on the findings of OB studies using MTurk.

#Conclusion
  We called into question the diversity of MTurk as a key strength and suggested one key area where diversity may be lacking: occupational diversity. Our results suggest that, compared to the broader US population, MTurk is not as diverse, both over- and underrepresenting certain occupations. Future research drawing on MTurk should consider how occupational differences might be theoretically relevant and incorporate these effects in analyses using MTurk sample data to help overcoming these shortcomings.

\newpage

# References
```{r}
require(papaja)
r_refs(file = "/Users/ccasti02/Documents/Research/Research on MTurk/MTurk's Occupational Diversity/r-references.bib")
my_citation <- cite_r(file = "/Users/ccasti02/Documents/Research/Research on MTurk/MTurk's Occupational Diversity/r-references.bib")

```
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

### 2017-07-03 Manuscript_11May.Rmd
Made changes to improve usability of the opening code.

@@
 ```{r message = FALSE, warning = FALSE}
-library("papaja")
+#The packages below will allow you to access "papaja", and if it fails, then try running all of the code at once. It should work then. 
 require(devtools)
 install_github("crsh/papaja")
+library("papaja")
 ```

### 2017-07-26 Manuscript_11May.tex
Bibliography added and pdf printed.

\documentclass[english,man]{apa6}

\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}

% Table formatting
\usepackage{longtable, booktabs}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}

\newenvironment{lltable}
  {\begin{landscape}\begin{center}\begin{ThreePartTable}}
  {\end{ThreePartTable}\end{center}\end{landscape}}

  \usepackage{ifthen} % Only add declarations when endfloat package is loaded
  \ifthenelse{\equal{\string man}{\string man}}{%
   \DeclareDelayedFloatFlavor{ThreePartTable}{table} % Make endfloat play with longtable
   % \DeclareDelayedFloatFlavor{ltable}{table} % Make endfloat play with lscape
   \DeclareDelayedFloatFlavor{lltable}{table} % Make endfloat play with lscape & longtable
  }{}%

% The following enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand\getlongtablewidth{%
 \begingroup
  \ifcsname LT@\roman{LT@tables}\endcsname
  \global\longtablewidth=0pt
  \renewcommand\LT@entry[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}%
  \@nameuse{LT@\roman{LT@tables}}%
  \fi
\endgroup}

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            pdfauthor={},
            pdftitle={Comparing MTurk and the US Population's Occupational Diversity},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setlength{\parindent}{0pt}
%\setlength{\parskip}{0pt plus 0pt minus 0pt}

\setlength{\emergencystretch}{3em}  % prevent overfull lines

\ifxetex
  \usepackage{polyglossia}
  \setmainlanguage{}
\else
  \usepackage[english]{babel}
\fi

% Manuscript styling
\captionsetup{font=singlespacing,justification=justified}
\usepackage{csquotes}
\usepackage{upgreek}

\usepackage{tikz} % Variable definition to generate author note

% fix for \tightlist problem in pandoc 1.14
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Essential manuscript parts
  \title{Comparing MTurk and the US Population's Occupational Diversity}

  \shorttitle{MTurk's Occupational Diversity}

  \author{Christopher M. Castille\textsuperscript{1}, Bodour H. Mahmoud\textsuperscript{2}, Rachel L. Williamson\textsuperscript{3}, John E. Buckner\textsuperscript{4}, \& James De Leôn\textsuperscript{5}}

  \def\affdep{{"", "", "", "", ""}}%
  \def\affcity{{"", "", "", "", ""}}%

  \affiliation{
    \vspace{0.5cm}
          \textsuperscript{1} Nicholls State University\\
          \textsuperscript{2} Villanova University\\
          \textsuperscript{3} University of Georgia\\
          \textsuperscript{4} AlixPartners\\
          \textsuperscript{5} APT Metrics  }

  \authornote{
    \newcounter{author}
    All correspondence should be sent to the lead author at
    \href{mailto:chris_castille@mac.com}{\nolinkurl{chris\_castille@mac.com}}.

                      Correspondence concerning this article should be addressed to Christopher M. Castille. E-mail: \href{mailto:chris_castille@mac.com}{\nolinkurl{chris\_castille@mac.com}}
                                                        }

  \abstract{We compare the occupational diversity of two convenient MTurk samples
against the broader US economy from which they have been indirectly
sampled. We focus on occupational diversity given a chief concern that
findings from OB/HR investigations relying on MTurk might not generalize
to the broader US economy . Additionally, as researchers may hope to
target specific populations (e.g., sales professionals) understanding
the extent to which these professionals are represented in the MTurk
population would be helpful. Therefore, we compare the occupational
diversity of MTurk against that described by the Bureau of Labor
Statistics, testing the null hypothesis that these populations are
equivalent in terms of occupational diversity. Across both samples,
which were obtained from studies conducted in 2015, we found differences
suggesting that the MTurk population is generally overrepresented by
white collar professionals (though this is an imperfect trend) and
generally underrepresented by blue collar workers.}
  \keywords{MTurk, Occupational Diversity \\

    \indent Word count: 3000
  }

\usepackage[titles]{tocloft}
\cftpagenumbersoff{table}
\renewcommand{\cfttabpresnum}{\itshape\tablename\enspace}
\renewcommand{\cfttabaftersnum}{.\space}
\setlength{\cfttabindent}{0pt}
\setlength{\cftafterloftitleskip}{0pt}
\settowidth{\cfttabnumwidth}{Table 10.\qquad}

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{example}{Example}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\begin{document}

\maketitle

\setcounter{secnumdepth}{0}

\section{Introduction}\label{introduction}

Amazon's Mechanical Turk (MTurk), an online labor market created by
Amazon, has recently become popular among social scientists interested
in collecting inexpensive, high-quality data from a diverse population
(Aguinis and Lawal (2012) Behrend, Sharek, Meade, and Wiebe (2011)
Bergman and Jean (2016) Paolacci and Chandler (2014) Shank (2016)).
Leveraging the strengths of this tool, MTurk has been used by social
scientists to replicate well-known phenomena (e.g., reaction times,
priming, task switching; Crump, McDonnell, and Gureckis (2013); memory,
Simons and Chabris (2012)) and by organizational behavior (OB)
researchers to expand the OB literature (e.g., Yarkoni, Ashar, and Wager
(2015)).

Yet, in spite of the growing enthusiasm surrounding the use of MTurk, it
represents merely another convenient sampling methodology that comes
with a few constraints, such as repeated participation or motivation due
to compensation (Landers and Behrend (2015) Woo, Keith, and Thornton
(2015)) and other yet-to-be-identified constraints. Here, we examine one
potentially important constraint for using MTurk to conduct OB research:
the occupational diversity of MTurk. Given that a fundamental goal of
most OB research is that workers are sampled from an appropriate
organizational setting (e.g., Pathak (2008)), understanding the
occupational diversity of MTurk will improve our understanding of the
boundary conditions or limits to the generalizability of MTurk research
findings. By examining the occupational diversity of MTurk, our work
addresses a call for research that describes the kinds of individuals
who participate in MTurk studies (Griggs et al. (2016)).

\section{Review of the Literature}\label{review-of-the-literature}

\subsection{What is MTurk?}\label{what-is-mturk}

MTurk is an internet marketplace where people seeking laborers have
access to a population of workers willing to do tasks requiring a human
intelligence for a small fee (Behrend et al. (2011)). Billed as a
\enquote{marketplace for work that requires human intelligence}, MTurk
allows \enquote{requesters} to post Human Intelligence Tasks (HITs),
which serve as self-contained jobs in which \enquote{workers} can
participate. Via MTurk, researchers seeking participants often post
survey studies for workers to voluntarily complete (Goodman, Cryder, and
Cheema (2013)). Workers are given a short description about a project,
including details about various tasks, estimated time investment, and
payment, and may selectively choose which projects to complete. Here,
researchers seeking participants often post survey studies for workers
to voluntarily complete (Goodman et al. (2013)).

\subsection{Why is MTurk Valuable for Researchers Studying Working
Populations?}\label{why-is-mturk-valuable-for-researchers-studying-working-populations}

MTurk offers practical advantages that may not be available via other
more traditional methods of data collection, such as sampling from
specific organizations (Paolacci, Chandler, and Ipeirotis (2010)). The
platform allows for easier subject pool access at an affordable cost and
for subject prescreening (Mason and Suri (2012)). Additionally, it
allows for subject anonymity, subject identifiability in longitudinal
studies, and offers a simple and supportive infrastructure (Paolacci et
al. (2010)). More importantly, its diversity is a key strength that sets
it apart from other commonly studied populations (e.g., university
students, community samples), making it an attractive subject pool for
researchers to draw upon (Buhrmester, Kwang, and Gosling (2011); Erikson
\& Simpson, 2010; Paolacci et al. (2010)). For instance, Behrend et al.
(2011) found that MTurk workers are more diverse on variables such as
age, ethnicity, education, employment status, job experience,
profession, nationality, and personality. The diversity of MTurk allows
OB researchers to overcome concerns regarding the generalizability of
their findings (e.g., Paolacci et al. (2010)), which has been a key
concern facing OB research (Chiao and Cheon (2010)).

However, while researchers have praised MTurk for its diversity, few
organizational behavior researchers have considered how MTurk might be
less diverse than expected in a key respect: occupational diversity. To
our knowledge, no study has compared the occupational diversity of MTurk
to the broader US population. While Behrend et al. (2011) work suggests
that MTurk's occupational diversity is greater than the university
population, our work expands on their research by comparing MTurk's
occupational diversity to the broader US population. If the occupational
diversity of the broader US population is indeed reflected in MTurk,
findings from MTurk should better generalize across occupations.
Alternatively, if MTurk's occupational diversity over- or
under-represent certain occupations, generalizability of findings from
MTurk should be more limited.

\emph{Research Question: Is the occupational diversity of the MTurk
population representative of the broader US economy?}

\section{Methods}\label{methods}

\subsection{US Population Occupational Summary
Statistics}\label{us-population-occupational-summary-statistics}

Occupational Employment Statistics (OES) were obtained from the United
States Bureau of Labor Statistics (BLS) (2015). Occupation diversity was
measured by calculating the percentage of job holders falling under a
particular occupational category. We adopted the Intermediate
Aggregation and Standard Occupational Classification (SOC) used by the
Bureau of Labor Statistics (BLS) for this study (see table 1).
Percentages describe the percentage of workers in the US economy who
work in occupations that fall under this broader occupational category.

\section{- - - - - - - - - - - - -}\label{section}

\section{insert table 1 about here}\label{insert-table-1-about-here}

\section{- - - - - - - - - - - - -}\label{section-1}

\subsection{MTurk Occupational Summary
Statistics}\label{mturk-occupational-summary-statistics}

Participants' data were collected from two independently conducted
studies (n\textsubscript{1} = 779; n\textsubscript{2} = 1108). In one
study (n\textsubscript{1} =779), occupational data was self-reported by
participants who were asked to described their job title. They were then
brought to ONET online and asked to retrieve the six-digit occupational
classification code that most closely corresponded to their job title.
In the second study (n\textsubscript{2} = 1108), participants again
self-reported their job title. However, the six-digit occupational
classification codes were obtained by training research assistants to
match the self-reported job titles to those in the ONET database. Using
this data, we described the occupational diversity of each sample using
relative frequencies of occupational category representation as
described by Table 1.

\subsection{Analysis}\label{analysis}

A chi-square test of goodness-of-fit was used to test whether
proportions from MTurk samples deviated from expected proportions as
derived from the BLS. Specifically, we tested whether MTurk's
occupational diversity deviated (p \textless{} .05) from that expected
if we assume the BLS population parameters generalize to the MTurk
population. This tests the null hypothesis that the populations are
identical in terms of occupational diversity. To facilitate
interpretation of our data, we also caluculated 95\% confidence
intervals for our sample proportions, which allows a visual inspection
of whether or not the population value is within sampling error.

\section{Results}\label{results}

Results shown in our table indicate that MTurk's occupational frequency
distribution does not consistently align with the US economy for both
sample 1 (\(\chi^2(12) = 368.58, p < .001\)) and sample 2
(\(\chi^2(12) = 486.07, p < .001\)). Examining the 95\% confidence
intervals across both samples, certain occupations were consistently
over- or under-represented. More specifically individuals sampled from
MTurk occupied generally more white-collar jobs (e.g., Management,
Business, and Financial Occupations; Computer, Engineering, and Science
Occupations) and generally fewer blue-collar jobs (e.g., Construction
and Extraction Occupations; Installation, Maintenance, and Repair
Occupations; Production Occupations) than what would be expected based
on BLS data. For instance, 10.13\% of workers in the US economy in 2015
worked in \enquote{Management, Business, and Financial Occupations.} By
contrast, approximately 17\% and 23\% of workers from the MTurk samples
fell under this classification. These trends were generally consistent
across both study 1 and 2.

\section{- - - - - - - - - - - - -}\label{section-2}

\section{insert table 2 about here}\label{insert-table-2-about-here}

\section{- - - - - - - - - - - - -}\label{section-3}

\section{Discussion}\label{discussion}

What started our investigation was a simple research question: is the
occupational diversity of the MTurk population representative of the
broader US population? Our data suggest that the answer is not
consistently so: certain occupations are over-represented, some fall
within expectations, and still others are under-represented. Thus, OB
researchers using convenient sampling procedures that draw on the MTurk
population should consider whether occupational features might play a
role in their investigation, which is point that we will elaborate upon
in greater detail. Simply put, our results suggest that MTurk's (US)
occupational diversity does not align with the broader US economy.

\section{Recommendations for Researchers Using
MTurk}\label{recommendations-for-researchers-using-mturk}

Given that OB researchers will likely wish to continue using MTurk as a
means of gathering diverse, convenient, and low-cost survey sample data,
researchers should consider how differences in the occupational
diversity observed amongst MTurk workers relative to the US population
might impinge upon the generalizability of their findings (Newman,
Joseph, and Feitosa (2015)). Specifically, given the over-representation
of workers from (1) Management, Business, and Financial, (2) Computer,
Engineering, and Science, and (3) Education, Legal, Community Service,
Arts, and Media occupations, we might safely assume that many of our
findings from MTurk will generalize across jobs classified under these
broader over-represented occupational categories. However, as many
occupations were under-represented {[}e.g., (1) Service, (2)
Construction and Extraction, (3) Installation, Maintenance, and Repair,
(4) Production; and (5) Transportation and Material Moving{]}, questions
may arise as to whether findings will generalize to jobs falling under
these broad classifications. To address this issue, researchers should
consider capturing occupational data and modeling theoretically derived
moderators. Person-environment (P-E) fit theories should help guide
researchers in proposing how certain occupational groupings might
influence individual-level relationships, lending to more nuanced and
contextualized results (How, Meade, Behrend, and Lance (2009)). Further,
O*NET might be useful in this regard as it provides researchers a means
for quantifying key occupational differences (e.g., level of competition
requirements, social skills requirements) and thereby testing P-E fit
hypotheses pertaining to occupational group differences (see Judge and
Zapata (2015)).

\subsection{Limitations and Future
Research}\label{limitations-and-future-research}

One key limitation is that we assumed that O*NET's classification system
perfectly captured all occupations during 2015. Additionally, as both
studies involved convenient sampling procedures, it remains uncertain
the extent to which these samples adequately reflect the larger MTurk
population. Still, the consistency of our findings should be considered
by future OB/HR researchers hoping to draw on MTurk for their research
with the hopes of generalizing to the larger (or a specific) working US
population. Additionally, as our studies were conducted in the US, it
remains unclear how other MTurk populations might reflect (however
imperfectly) their respective broader economy. Future larger scale
studies should also consider lower levels of BLS occupational
classification to examine the extent to which narrower occupations might
not be represented by MTurk. Lastly, examining diversity in other
respects (age, racio-ethnic, income, education, etc.) should also be
considered. Though MTurk offers a practically feasible method of
attaining high quality data, future research will be needed to
understand the limitations of this tool.

Given that our data were gathered and analyzed in 2015, it might be
insightful to have our procedures replicated annually to examine how the
demographics of MTurk, specifically occupational characteristics, change
over time, especially as access to technology becomes even easier and
more commonplace. Thus, we encourage researchers to continue examining
the occupational diversity of MTurk relative to the US economy. We also
encourage researchers to consider novel ways of approximating the
occupational diversity of both the US economy and MTurk because the
currently existing taxonomies that we have used (i.e., BLS-based)
probably do not capture all occupations. Lastly, our results raise a new
and interesting research question: Why might MTurk possess the
occupational diversity makeup that it does (i.e., why are some
occupations over-represented while others are under-represented)?
Similarly, what factors (e.g., access to technology, interest in
psychology) might make it easier for workers coming from certain
occupations to participate in OB studies hosted on MTurk? Answering
these questions might unearth more constraints that impinge on the
findings of OB studies using MTurk.

\section{Conclusion}\label{conclusion}

We called into question the diversity of MTurk as a key strength and
suggested one key area where diversity may be lacking: occupational
diversity. Our results suggest that, compared to the broader US
population, MTurk is not as diverse, both over- and underrepresenting
certain occupations. Future research drawing on MTurk should consider
how occupational differences might be theoretically relevant and
incorporate these effects in analyses using MTurk sample data to help
overcoming these shortcomings.

\newpage

\section{References}\label{references}

\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\hypertarget{ref-aguinis2012conducting}{}
Aguinis, H., \& Lawal, S. O. (2012). Conducting field experiments using
eLancing's natural environment. \emph{Journal of Business Venturing},
\emph{27}(4), 493--505.

\hypertarget{ref-behrend2011viability}{}
Behrend, T. S., Sharek, D. J., Meade, A. W., \& Wiebe, E. N. (2011). The
viability of crowdsourcing for survey research. \emph{Behavior Research
Methods}, \emph{43}(3), 800.

\hypertarget{ref-bergman2016have}{}
Bergman, M. E., \& Jean, V. A. (2016). Where have all the ``workers''
gone? A critical analysis of the unrepresentativeness of our samples
relative to the labor market in the industrial--organizational
psychology literature. \emph{Industrial and Organizational Psychology},
\emph{9}(01), 84--113.

\hypertarget{ref-buhrmester2011amazon}{}
Buhrmester, M., Kwang, T., \& Gosling, S. D. (2011). Amazon's mechanical
turk a new source of inexpensive, yet high-quality, data?
\emph{Perspectives on Psychological Science}, \emph{6}(1), 3--5.

\hypertarget{ref-chiao2010weirdest}{}
Chiao, J. Y., \& Cheon, B. K. (2010). The weirdest brains in the world.
\emph{Behavioral and Brain Sciences}, \emph{33}(2-3), 88--90.

\hypertarget{ref-crump2013evaluating}{}
Crump, M. J., McDonnell, J. V., \& Gureckis, T. M. (2013). Evaluating
amazon's mechanical turk as a tool for experimental behavioral research.
\emph{PloS One}, \emph{8}(3), e57410.

\hypertarget{ref-goodman2013data}{}
Goodman, J. K., Cryder, C. E., \& Cheema, A. (2013). Data collection in
a flat world: The strengths and weaknesses of mechanical turk samples.
\emph{Journal of Behavioral Decision Making}, \emph{26}(3), 213--224.

\hypertarget{ref-griggs2016these}{}
Griggs, T. L., Eby, L. T., Maupin, C. K., Conley, K. M., Williamson, R.
L., Griek, O. H. V., \& Clauson, M. G. (2016). Who are these workers,
anyway? \emph{Industrial and Organizational Psychology}, \emph{9}(01),
114--121.

\hypertarget{ref-how2009dr}{}
How, I., Meade, A. W., Behrend, T. S., \& Lance, C. E. (2009). Dr.
strangelove, or. \emph{Statistical and Methodological Myths and Urban
Legends: Doctrine, Verity and Fable in the Organizational and Social
Sciences}, 89.

\hypertarget{ref-judge2015person}{}
Judge, T. A., \& Zapata, C. P. (2015). The person--situation debate
revisited: Effect of situation strength and trait activation on the
validity of the big five personality traits in predicting job
performance. \emph{Academy of Management Journal}, \emph{58}(4),
1149--1179.

\hypertarget{ref-landers2015inconvenient}{}
Landers, R. N., \& Behrend, T. S. (2015). An inconvenient truth:
Arbitrary distinctions between organizational, mechanical turk, and
other convenience samples. \emph{Industrial and Organizational
Psychology}, \emph{8}(02), 142--164.

\hypertarget{ref-mason2012conducting}{}
Mason, W., \& Suri, S. (2012). Conducting behavioral research on
amazon's mechanical turk. \emph{Behavior Research Methods},
\emph{44}(1), 1--23.

\hypertarget{ref-newman2015external}{}
Newman, D. A., Joseph, D. L., \& Feitosa, J. (2015). External validity
and multi-organization samples: Levels-of-analysis implications of
crowdsourcing and college student samples. \emph{Industrial and
Organizational Psychology}, \emph{8}(02), 214--220.

\hypertarget{ref-paolacci2014inside}{}
Paolacci, G., \& Chandler, J. (2014). Inside the turk: Understanding
mechanical turk as a participant pool. \emph{Current Directions in
Psychological Science}, \emph{23}(3), 184--188.

\hypertarget{ref-paolacci2010running}{}
Paolacci, G., Chandler, J., \& Ipeirotis, P. G. (2010). Running
experiments on amazon mechanical turk.

\hypertarget{ref-pathak2008methodology}{}
Pathak, R. P. (2008). \emph{Methodology of educational research}.
Atlantic Publishers \& Dist.

\hypertarget{ref-shank2016using}{}
Shank, D. B. (2016). Using crowdsourcing websites for sociological
research: The case of amazon mechanical turk. \emph{The American
Sociologist}, \emph{47}(1), 47--55.

\hypertarget{ref-simons2012common}{}
Simons, D. J., \& Chabris, C. F. (2012). Common (mis) beliefs about
memory: A replication and comparison of telephone and mechanical turk
survey methods. \emph{PloS One}, \emph{7}(12), e51876.

\hypertarget{ref-woo2015amazon}{}
Woo, S. E., Keith, M., \& Thornton, M. A. (2015). Amazon mechanical turk
for industrial and organizational psychology: Advantages, challenges,
and practical recommendations. \emph{Industrial and Organizational
Psychology}, \emph{8}(02), 171--179.

\hypertarget{ref-yarkoni2015interactions}{}
Yarkoni, T., Ashar, Y. K., \& Wager, T. D. (2015). Interactions between
donor agreeableness and recipient characteristics in predicting
charitable donation and positive social evaluation. \emph{PeerJ},
\emph{3}, e1089.

\clearpage
\renewcommand{\listtablename}{Table captions}
\listoftables

\end{document}

### 2018-01-26 Manuscript.Rmd

--- 2017-07-03 Manuscript_11May.Rmd
@@
 #The packages below will allow you to access "papaja", and if it fails, then try running all of the code at once. It should work then. 
-require(devtools)
-install_github("crsh/papaja")
 library("papaja")
@@
 library(data.table)
+library(openxlsx)
 
@@
 The UGA dataset is a full dataset in the sense that it contains all individuals whose data are relevant for our investigation (i.e., participants hold a job that falls under a SOC classification) or not (i.e., they either do not work or work in a job falling outside the SOC classification system).
+#Build the BLS Table, but first establish a temp file.
 
-#Build the BLS Table.
-##BLS data
+# Download the file with download.file()
+# Here is the URL.
+download.file("https://www.bls.gov/oes/special.requests/oesm15nat.zip", "BLS2015.zip")
+unzip("BLS2015.zip")
+library(readxl)
+national_M2015_dl <- read_excel("oesm15nat/national_M2015_dl.xlsx")
+View(national_M2015_dl)
+
+#Edit the code below such that the newly downloaded data aligns with the code below. You'll need to include relative percentages.
+
 BLS <- read_excel("~/Documents/Research/Research on MTurk/MTurk's Occupational Diversity/Datasets/BLS Data from 2015.xlsx")

### 2018-09-17 Manuscript.Rmd
Replication Demographic Analysis

@@
 \setlength{\leftskip}{0.5in}
+
+###Replication Demographic Analaysis
+#Age Analysis T- Test
+#Load Dataset
+require(dplyr)
+require(readxl)
+BLS_age <- read_excel("age_demo.xlsx")
+
+#Define population mean. In this case it was already calculated in the dataset. 
+pop_mean <- as.numeric(age_demo[6 , 10])
+
+#Define sample mean
+MTurk17 <- read_excel("~/MTurk Diversity 2017 Data/2017 Data.xls")
+samp_mean <- as.numeric(MTurk17 %>%
+  summarise(MTurk_age = mean(What.is.your.age., na.rm = TRUE)))
+
+#Not able to get population standard deviation. Estimated using sample standard deviation.
+samp_sd <- as.numeric(MTurk17 %>%
+  summarise(sd_age = sd(What.is.your.age., na.rm = TRUE)))
+
+#Define sample size
+n <- as.numeric(667)
+
+#Run t test.
+t_value <- (samp_mean - pop_mean)/(samp_sd/sqrt(n))
+View(t_value)
+
+##Gender Analysis
+BLS_data <- read_excel("employment_demo.xlsx")
+
+#Get BLS gender data (expected value)
+BLS_women <- as.numeric(BLS_data[7,3])/100
+BLS_men <- 1.000 - BLS_women
+
+BLS_gender <- c(BLS_women, BLS_men, 0.0)
+
+#Get MTurk gender data (observed value)
+MTurk_gender <- MTurk17 %>%
+  count(What.is.your.gender.)
+
+#Define confidence intervals
+require(binom)
+gCI <- binom.confint(x = MTurk_gender$n, n = sum(MTurk_gender$n), conf.level = 0.95, methods = "exact")
+gCI <- gCI[ , 4:6]
+
+#Build Gender table with gender, expected value, n, LL, observed, UL
+gender_table <- cbind(MTurk_gender, gCI, BLS_gender)
+names(gender_table) <- c("gender", "n", "o", "LL_g", "UL_g", "e")
+gender_table <- gender_table[ 1, c(1, 2, 3, 4, 6, 5)]
+View(gender_table)
+
+#Gender chi square test
+
+chi2 <- function(x) {
+  o <- (x$n)
+  e <- (x$e)
+  n <- sum(x$n, na.rm=TRUE)
+  ((o-(e)*(n))^2)/((e)*(n))
+}
+
+gender_ch2 <- as.data.frame(chi2(gender_table))
+names(gender_ch2) <- c("chi2")
+row.names(gender_ch2) <- c("female")
+gender_ch2 <- na.omit(gender_ch2)
+View(gender_ch2)
+
+#Sum chi-square values.
+sum(gender_ch2$chi2, na.rm=TRUE)
+
+#Ethnicity Analysis 
+#Define obs_eth
+BLS_cauc <- as.numeric(BLS_data[7, 4])/100
+BLS_AfAm <- as.numeric(BLS_data[7,5])/100
+BLS_Asn <- as.numeric(BLS_data[7,6])/100
+BLS_Hisp <- as.numeric(BLS_data[7,7])/100
+BLS_eth <- c(BLS_AfAm, BLS_Asn, BLS_cauc, BLS_Hisp)
+
+sum(BLS_eth)
+
+#Get MTurk ethnicity data
+MTurk_eth <- MTurk17 %>%
+  count(MTurk17$With.which.ethnicity.do.you.most.identify.)
+
+#Define confidence intervals 
+ethCI <- binom.confint(x = MTurk_eth$n, n = sum(MTurk_eth$n), conf.level = 0/95, methods = "exact")
+ethCI <- ethCI[ , 4:6]
+
+#Build Ethnicity table 
+ethnicity_table <- cbind(MTurk_eth, ethCI, BLS_eth)
+names(ethnicity_table) <- c("ethnicity", "n", "o", "LL_eth", "UL_eth", "e")
+eth_table <- ethnicity_table[1:4 , c(1, 6, 2, 4, 3, 5)]
+View(eth_table)
+
+#Ethnicity chi squared test
+eth_ch2 <- as.data.frame(chi2(eth_table))
+names(eth_ch2) <- c("chi2")
+row.names(eth_ch2) <- c("African American", "Asian", "Caucasian", "Hispanic")
+eth_ch2 <- na.omit(eth_ch2)
+View(eth_ch2)
+
+#Sum chi-square values.
+sum(eth_ch2$chi2, na.rm=TRUE)

### 2018-09-17 Manuscript.Rmd
Replication Demographic Analaysis- Age, Gender, and Ethinicity

@@
 
-###Replication Demographic Analaysis
+##Replication Demographic Analaysis
+##Age Analysis
+```{r}
 #Age Analysis T- Test
@@
 View(t_value)
+```
 
+##Gender Analysis
+```{r}
 ##Gender Analysis
@@
 sum(gender_ch2$chi2, na.rm=TRUE)
+```
 
+##Ethnicity Analysis
+```{r}
 #Ethnicity Analysis 
@@
 sum(eth_ch2$chi2, na.rm=TRUE)
+```

### 2018-09-17 Manuscript.Rmd
Updated local.

--- 2018-01-26 Manuscript.Rmd
@@
 
-```{r,BLS, include=FALSE, results='asis'}
+```{r Load Data, include=FALSE, results='asis'}
 #Load packages
@@
 library(readxl)
-national_M2015_dl <- read_excel("oesm15nat/national_M2015_dl.xlsx")
-View(national_M2015_dl)
+BLS <- read_excel("oesm15nat/national_M2015_dl.xlsx")
+BLS <- BLS[c(2,4)]
 
-#Edit the code below such that the newly downloaded data aligns with the code below. You'll need to include relative percentages.
+# Include data on the size of the military (taken from the department of defense (http://us-military-branches.insidegov.com))
+BLS <- rbind(BLS, c("Military Specific Occupations", 1350236))
 
-BLS <- read_excel("~/Documents/Research/Research on MTurk/MTurk's Occupational Diversity/Datasets/BLS Data from 2015.xlsx")
+#Only keep intermediate category totals.
+BLS <- BLS[c(2,71,129,162,222,293,320,336,432,494,586,612,653,687,705,767,810,923,950,1054,1130,1298,1395,1),]
+
 ###Rename rows and aggregate.
@@
 BLS[23, 1] = "55 Military Specific Occupations"
-names(BLS) <- c("Var1","Var2","Var3")
+names(BLS) <- c("Var1","Var2")
+BLS$Var2 <- as.numeric(BLS$Var2)
 BLS <- aggregate(.~Var1,BLS,sum)
-###Data on the size of the military taken from the department of defense (http://us-military-branches.insidegov.com). 
-BLS[13, 2] = "1350236"
-names(BLS) <- c("Intermediate Aggregation Title", "Freq","RFreq")
-BLS$Freq <- as.numeric(BLS$Freq)
+
+#Add military occupation number to the overall. 
+BLS$Var2[14] <- BLS$Var2[13] + BLS$Var2[14]
+
+#Rename variables
+names(BLS) <- c("Intermediate Aggregation Title", "Freq")
+
+#Only keep occupational categories (no all).
+BLS <- BLS[-14,]
+
+#Compute relative frequencies. Call the object "tab".
 tab <- transform(BLS, relative = prop.table(Freq))
-BLS <- tab[c(1,4)]
+
+#Define new BLS. "e" is for "relative frequency". 
+BLS <- tab[c(1,3)]
 names(BLS) <- c("Intermediate Aggregation Title","e")
-```
 
-```{r Sample Data, include=FALSE, results='asis', echo=FALSE}
 ##LATech data
-LATech <- read_csv("/Users/ccasti02/Documents/Research/Research on MTurk/MTurk's Occupational Diversity/Datasets/Chris's Data from 2015.csv")
+LATech <- read_csv("Data/Chris's Data from 2015.csv")
 ###Delete unneeded data.
@@
 LATech[784, 3] = "25-0000.00"
+
 ###Remove unemployed cases.
@@
 }
+
 LATech <- completeFun(LATech, "O*NET Job Code")
@@
 LATech <- cbind(LATech,LO)
+
 ###Build relative frequency table.
@@
 names(tab) <- c("Intermediate Aggregation Title","n","f")
+
 #Table for poster.
@@
 ##UGA data
-UGA <- read_excel("/Users/ccasti02/Documents/Research/Research on MTurk/MTurk's Occupational Diversity/Datasets/Rachel's Data from 2015.xlsx")
+UGA <- read_excel("Data/Rachel's Data from 2015.xlsx")
 UGA <- UGA[c(2,21)]

### 2018-09-17 Manuscript.Rmd

@@
 \setlength{\leftskip}{0.5in}
+
+##Replication Demographic Analaysis
+##Age Analysis
+```{r}
+#Age Analysis T- Test
+#Load Dataset
+require(dplyr)
+require(readxl)
+BLS_age <- read_excel("age_demo.xlsx")
+
+#Define population mean. In this case it was already calculated in the dataset. 
+pop_mean <- as.numeric(age_demo[6 , 10])
+
+#Define sample mean
+MTurk17 <- read_excel("~/MTurk Diversity 2017 Data/2017 Data.xls")
+samp_mean <- as.numeric(MTurk17 %>%
+  summarise(MTurk_age = mean(What.is.your.age., na.rm = TRUE)))
+
+#Not able to get population standard deviation. Estimated using sample standard deviation.
+samp_sd <- as.numeric(MTurk17 %>%
+  summarise(sd_age = sd(What.is.your.age., na.rm = TRUE)))
+
+#Define sample size
+n <- as.numeric(667)
+
+#Run t test.
+t_value <- (samp_mean - pop_mean)/(samp_sd/sqrt(n))
+View(t_value)
+```
+
+##Gender Analysis
+```{r}
+##Gender Analysis
+BLS_data <- read_excel("employment_demo.xlsx")
+
+#Get BLS gender data (expected value)
+BLS_women <- as.numeric(BLS_data[7,3])/100
+BLS_men <- 1.000 - BLS_women
+
+BLS_gender <- c(BLS_women, BLS_men, 0.0)
+
+#Get MTurk gender data (observed value)
+MTurk_gender <- MTurk17 %>%
+  count(What.is.your.gender.)
+
+#Define confidence intervals
+require(binom)
+gCI <- binom.confint(x = MTurk_gender$n, n = sum(MTurk_gender$n), conf.level = 0.95, methods = "exact")
+gCI <- gCI[ , 4:6]
+
+#Build Gender table with gender, expected value, n, LL, observed, UL
+gender_table <- cbind(MTurk_gender, gCI, BLS_gender)
+names(gender_table) <- c("gender", "n", "o", "LL_g", "UL_g", "e")
+gender_table <- gender_table[ 1, c(1, 2, 3, 4, 6, 5)]
+View(gender_table)
+
+#Gender chi square test
+
+chi2 <- function(x) {
+  o <- (x$n)
+  e <- (x$e)
+  n <- sum(x$n, na.rm=TRUE)
+  ((o-(e)*(n))^2)/((e)*(n))
+}
+
+gender_ch2 <- as.data.frame(chi2(gender_table))
+names(gender_ch2) <- c("chi2")
+row.names(gender_ch2) <- c("female")
+gender_ch2 <- na.omit(gender_ch2)
+View(gender_ch2)
+
+#Sum chi-square values.
+sum(gender_ch2$chi2, na.rm=TRUE)
+```
+
+##Ethnicity Analysis
+```{r}
+#Ethnicity Analysis 
+#Define obs_eth
+BLS_cauc <- as.numeric(BLS_data[7, 4])/100
+BLS_AfAm <- as.numeric(BLS_data[7,5])/100
+BLS_Asn <- as.numeric(BLS_data[7,6])/100
+BLS_Hisp <- as.numeric(BLS_data[7,7])/100
+BLS_eth <- c(BLS_AfAm, BLS_Asn, BLS_cauc, BLS_Hisp)
+
+sum(BLS_eth)
+
+#Get MTurk ethnicity data
+MTurk_eth <- MTurk17 %>%
+  count(MTurk17$With.which.ethnicity.do.you.most.identify.)
+
+#Define confidence intervals 
+ethCI <- binom.confint(x = MTurk_eth$n, n = sum(MTurk_eth$n), conf.level = 0/95, methods = "exact")
+ethCI <- ethCI[ , 4:6]
+
+#Build Ethnicity table 
+ethnicity_table <- cbind(MTurk_eth, ethCI, BLS_eth)
+names(ethnicity_table) <- c("ethnicity", "n", "o", "LL_eth", "UL_eth", "e")
+eth_table <- ethnicity_table[1:4 , c(1, 6, 2, 4, 3, 5)]
+View(eth_table)
+
+#Ethnicity chi squared test
+eth_ch2 <- as.data.frame(chi2(eth_table))
+names(eth_ch2) <- c("chi2")
+row.names(eth_ch2) <- c("African American", "Asian", "Caucasian", "Hispanic")
+eth_ch2 <- na.omit(eth_ch2)
+View(eth_ch2)
+
+#Sum chi-square values.
+sum(eth_ch2$chi2, na.rm=TRUE)
+```

### 2018-09-21 Manuscript.Rmd
Edited ethnicity analysis to only include ethnicities which data are available from BLS.

@@
   count(MTurk17$With.which.ethnicity.do.you.most.identify.)
+MTurk_eth <- MTurk_eth[c(1:4), ]
 
@@
 ```
+###Education Analysis 
+```{r}
+#Education Analysis 
+#Clean BLS Data. Get totals.  
+BLS_education_original <- read_excel("education_demo.xlsx")
+BLS_education <- as.data.frame(BLS_education_original[8:14, ])
+BLS_education <- BLS_education[1, c(-2, -3, -6)]
+names(BLS_education) <- c("category", "High school graduates, no college(1)", "Some college, no degree", "Associate degree", "Bachelor's degree only", "Advanced degree")
+
+#Combine categories as necessary. Get proportions.  
+highschool_ged <- c(as.numeric(BLS_education$`High school graduates, no college(1)`) + as.numeric(BLS_education$`Some college, no degree`))
+two_year_deg <- as.numeric(BLS_education$`Associate degree`)
+four_year_deg <- as.numeric(BLS_education$`Bachelor's degree only`)
+advanaced_deg <- as.numeric(BLS_education$`Advanced degree`)
+BLS_education <- c(highschool_ged, two_year_deg, four_year_deg, advanaced_deg)
+names(BLS_education) <- c("high school/GED" , "2 year degree", "4 year degree", "advanced degree")
+BLS_total <- as.numeric(sum(BLS_education))
+
+#Function to find proportion for each iteration of the vector. 
+e_prop <- function(x) {
+  e <- x/BLS_total
+}
+
+#Use vapply and the above function to get expected proportions from BLS data
+BLS_edu <- sapply(BLS_education, prop_func)
+
+#Clean MTurk Data
+MTurk_education <- MTurk17 %>%
+  count(MTurk17$What.level.of.education.have.you.completed.)
+colnames(MTurk_education) <- c("education level", "n")
+advanced_deg <- as.numeric(MTurk_education[4,2]) + as.numeric(MTurk_education[5,2])
+MTurk_education <- rbind(MTurk_education, advanced_deg)
+MTurk_education[6,1] <- "advanced degree"
+MTurk_edu <- MTurk_education[c(-4, -5), ]
+
+#Define confidence intervals 
+eduCI <- binom.confint(x = MTurk_edu$n, n = sum(MTurk_edu$n), conf.level = 0/95, methods = "exact")
+eduCI <- eduCI[ , 4:6]
+
+#Build Education table 
+education_table <- cbind(MTurk_edu, eduCI, BLS_edu)
+names(education_table) <- c("education level", "n", "o", "LL_eth", "UL_eth", "e")
+education_table <- education_table[ , c(1, 6, 2, 4, 3, 5)]
+View(education_table)
+
+#Education chi squared test
+edu_ch2 <- as.data.frame(chi2(education_table))
+names(edu_ch2) <- c("chi2")
+row.names(edu_ch2) <- c("high school/GED" , "2 year degree", "4 year degree", "advanced degree")
+edu_ch2 <- na.omit(edu_ch2)
+View(edu_ch2)
+
+#Sum chi-square values.
+sum(edu_ch2$chi2, na.rm=TRUE)
+```

### 2018-09-21 Manuscript.Rmd
Updated code to work with my computer. I also included directions / requests for effect size indicators.

--- 2018-09-17 Manuscript.Rmd
@@
 
+##Replication Demographic Analaysis
+##Age Analysis
+```{r}
+#Age Analysis T- Test
+#Load Dataset
+require(dplyr)
+require(readxl)
+age_demo <- read_excel("age_demo.xlsx")
+
+#Define population mean. In this case it was already calculated in the dataset. 
+pop_mean <- as.numeric(age_demo[6 , 10])
+
+#Define sample mean
+MTurk17 <- read_excel("2017 Data.xls")
+samp_mean <- as.numeric(MTurk17 %>%
+  summarise(MTurk_age = mean(What.is.your.age., na.rm = TRUE)))
+
+#Not able to get population standard deviation. Estimated using sample standard deviation.
+samp_sd <- as.numeric(MTurk17 %>%
+  summarise(sd_age = sd(What.is.your.age., na.rm = TRUE)))
+
+#Define sample size
+n <- as.numeric(667)
+
+#Run t test.
+t_value <- (samp_mean - pop_mean)/(samp_sd/sqrt(n))
+t_value
+
+#So MTurk is much younger than the population on average. We need to convert this to an effect size (Cohen's D). 
+```
+
+##Gender Analysis
+```{r}
+##Gender Analysis
+BLS_data <- read_excel("employment_demo.xlsx")
+
+#Get BLS gender data (expected value)
+BLS_women <- as.numeric(BLS_data[7,3])/100
+BLS_men <- 1.000 - BLS_women
+
+BLS_gender <- c(BLS_women, BLS_men, 0.0)
+
+#Get MTurk gender data (observed value)
+MTurk_gender <- MTurk17 %>%
+  count(What.is.your.gender.)
+
+#Define confidence intervals
+require(binom)
+gCI <- binom.confint(x = MTurk_gender$n, n = sum(MTurk_gender$n), conf.level = 0.95, methods = "exact")
+gCI <- gCI[ , 4:6]
+
+#Build Gender table with gender, expected value, n, LL, observed, UL
+gender_table <- cbind(MTurk_gender, gCI, BLS_gender)
+names(gender_table) <- c("gender", "n", "o", "LL_g", "UL_g", "e")
+gender_table <- gender_table[ 1, c(1, 2, 3, 4, 6, 5)]
+View(gender_table)
+
+#Gender chi square test
+
+chi2 <- function(x) {
+  o <- (x$n)
+  e <- (x$e)
+  n <- sum(x$n, na.rm=TRUE)
+  ((o-(e)*(n))^2)/((e)*(n))
+}
+
+gender_ch2 <- as.data.frame(chi2(gender_table))
+names(gender_ch2) <- c("chi2")
+row.names(gender_ch2) <- c("female")
+gender_ch2 <- na.omit(gender_ch2)
+View(gender_ch2)
+
+#Sum chi-square values.
+sum(gender_ch2$chi2, na.rm=TRUE)
+
+#So it appears that MTurk is largely dominated by females. We need to have an effect size describing this phenomena (e.g., a likelihood ratio).
+```
+
+##Ethnicity Analysis
+```{r}
+#Ethnicity Analysis 
+#Define obs_eth
+BLS_cauc <- as.numeric(BLS_data[7, 4])/100
+BLS_AfAm <- as.numeric(BLS_data[7,5])/100
+BLS_Asn <- as.numeric(BLS_data[7,6])/100
+BLS_Hisp <- as.numeric(BLS_data[7,7])/100
+BLS_eth <- c(BLS_AfAm, BLS_Asn, BLS_cauc, BLS_Hisp)
+
+sum(BLS_eth)
+
+#Get MTurk ethnicity data
+MTurk_eth <- MTurk17 %>%
+  count(MTurk17$With.which.ethnicity.do.you.most.identify.)
+
+#Define confidence intervals 
+ethCI <- binom.confint(x = MTurk_eth$n, n = sum(MTurk_eth$n), conf.level = 0/95, methods = "exact")
+ethCI <- ethCI[ , 4:6]
+
+#Build Ethnicity table 
+ethnicity_table <- cbind(MTurk_eth, ethCI, BLS_eth)
+names(ethnicity_table) <- c("ethnicity", "n", "o", "LL_eth", "UL_eth", "e")
+eth_table <- ethnicity_table[1:4 , c(1, 6, 2, 4, 3, 5)]
+View(eth_table)
+
+#Ethnicity chi squared test
+eth_ch2 <- as.data.frame(chi2(eth_table))
+names(eth_ch2) <- c("chi2")
+row.names(eth_ch2) <- c("African American", "Asian", "Caucasian", "Hispanic")
+eth_ch2 <- na.omit(eth_ch2)
+View(eth_ch2)
+
+#Sum chi-square values.
+sum(eth_ch2$chi2, na.rm=TRUE)
+```
+
 #Discussion
@@
 \setlength{\leftskip}{0.5in}
-
-##Replication Demographic Analaysis
-##Age Analysis
-```{r}
-#Age Analysis T- Test
-#Load Dataset
-require(dplyr)
-require(readxl)
-BLS_age <- read_excel("age_demo.xlsx")
-
-#Define population mean. In this case it was already calculated in the dataset. 
-pop_mean <- as.numeric(age_demo[6 , 10])
-
-#Define sample mean
-MTurk17 <- read_excel("~/MTurk Diversity 2017 Data/2017 Data.xls")
-samp_mean <- as.numeric(MTurk17 %>%
-  summarise(MTurk_age = mean(What.is.your.age., na.rm = TRUE)))
-
-#Not able to get population standard deviation. Estimated using sample standard deviation.
-samp_sd <- as.numeric(MTurk17 %>%
-  summarise(sd_age = sd(What.is.your.age., na.rm = TRUE)))
-
-#Define sample size
-n <- as.numeric(667)
-
-#Run t test.
-t_value <- (samp_mean - pop_mean)/(samp_sd/sqrt(n))
-View(t_value)
-```
-
-##Gender Analysis
-```{r}
-##Gender Analysis
-BLS_data <- read_excel("employment_demo.xlsx")
-
-#Get BLS gender data (expected value)
-BLS_women <- as.numeric(BLS_data[7,3])/100
-BLS_men <- 1.000 - BLS_women
-
-BLS_gender <- c(BLS_women, BLS_men, 0.0)
-
-#Get MTurk gender data (observed value)
-MTurk_gender <- MTurk17 %>%
-  count(What.is.your.gender.)
-
-#Define confidence intervals
-require(binom)
-gCI <- binom.confint(x = MTurk_gender$n, n = sum(MTurk_gender$n), conf.level = 0.95, methods = "exact")
-gCI <- gCI[ , 4:6]
-
-#Build Gender table with gender, expected value, n, LL, observed, UL
-gender_table <- cbind(MTurk_gender, gCI, BLS_gender)
-names(gender_table) <- c("gender", "n", "o", "LL_g", "UL_g", "e")
-gender_table <- gender_table[ 1, c(1, 2, 3, 4, 6, 5)]
-View(gender_table)
-
-#Gender chi square test
-
-chi2 <- function(x) {
-  o <- (x$n)
-  e <- (x$e)
-  n <- sum(x$n, na.rm=TRUE)
-  ((o-(e)*(n))^2)/((e)*(n))
-}
-
-gender_ch2 <- as.data.frame(chi2(gender_table))
-names(gender_ch2) <- c("chi2")
-row.names(gender_ch2) <- c("female")
-gender_ch2 <- na.omit(gender_ch2)
-View(gender_ch2)
-
-#Sum chi-square values.
-sum(gender_ch2$chi2, na.rm=TRUE)
-```
-
-##Ethnicity Analysis
-```{r}
-#Ethnicity Analysis 
-#Define obs_eth
-BLS_cauc <- as.numeric(BLS_data[7, 4])/100
-BLS_AfAm <- as.numeric(BLS_data[7,5])/100
-BLS_Asn <- as.numeric(BLS_data[7,6])/100
-BLS_Hisp <- as.numeric(BLS_data[7,7])/100
-BLS_eth <- c(BLS_AfAm, BLS_Asn, BLS_cauc, BLS_Hisp)
-
-sum(BLS_eth)
-
-#Get MTurk ethnicity data
-MTurk_eth <- MTurk17 %>%
-  count(MTurk17$With.which.ethnicity.do.you.most.identify.)
-
-#Define confidence intervals 
-ethCI <- binom.confint(x = MTurk_eth$n, n = sum(MTurk_eth$n), conf.level = 0/95, methods = "exact")
-ethCI <- ethCI[ , 4:6]
-
-#Build Ethnicity table 
-ethnicity_table <- cbind(MTurk_eth, ethCI, BLS_eth)
-names(ethnicity_table) <- c("ethnicity", "n", "o", "LL_eth", "UL_eth", "e")
-eth_table <- ethnicity_table[1:4 , c(1, 6, 2, 4, 3, 5)]
-View(eth_table)
-
-#Ethnicity chi squared test
-eth_ch2 <- as.data.frame(chi2(eth_table))
-names(eth_ch2) <- c("chi2")
-row.names(eth_ch2) <- c("African American", "Asian", "Caucasian", "Hispanic")
-eth_ch2 <- na.omit(eth_ch2)
-View(eth_ch2)
-
-#Sum chi-square values.
-sum(eth_ch2$chi2, na.rm=TRUE)
-```

### 2018-09-21 Manuscript.Rmd

--- 2018-09-21 Manuscript.Rmd
@@
 
-#Discussion
-  What started our investigation was a simple research question: is the occupational diversity of the MTurk population representative of the broader US population?
-Our data suggest that the answer is not consistently so: certain occupations are over-represented, some fall within expectations, and still others are under-represented.
-Thus, OB researchers using convenient sampling procedures that draw on the MTurk population should consider whether occupational features might play a role in their investigation, which is point that we will elaborate upon in greater detail.
-Simply put, our results suggest that MTurk’s (US) occupational diversity does not align with the broader US economy.
-
-#Recommendations for Researchers Using MTurk
-  Given that OB researchers will likely wish to continue using MTurk as a means of gathering diverse, convenient, and low-cost survey sample data, researchers should consider how differences in the occupational diversity observed amongst MTurk workers relative to the US population might impinge upon the generalizability of their findings (@newman2015external).
-Specifically, given the over-representation of workers from (1) Management, Business, and Financial, (2) Computer, Engineering, and Science, and (3) Education, Legal, Community Service, Arts, and Media occupations, we might safely assume that many of our findings from MTurk will generalize across jobs classified under these broader over-represented occupational categories.
-However, as many occupations were under-represented [e.g., (1) Service, (2) Construction and Extraction, (3) Installation, Maintenance, and Repair, (4) Production; and (5) Transportation and Material Moving], questions may arise as to whether findings will generalize to jobs falling under these broad classifications.
-  To address this issue, researchers should consider capturing occupational data and modeling theoretically derived moderators.
-Person-environment (P-E) fit theories should help guide researchers in proposing how certain occupational groupings might influence individual-level relationships, lending to more nuanced and contextualized results (@how2009dr).
-Further, O*NET might be useful in this regard as it provides researchers a means for quantifying key occupational differences (e.g., level of competition requirements, social skills requirements) and thereby testing P-E fit hypotheses pertaining to occupational group differences (see @judge2015person).
-
-##Limitations and Future Research
-  One key limitation is that we assumed that O*NET’s classification system perfectly captured all occupations during 2015.
-Additionally, as both studies involved convenient sampling procedures, it remains uncertain the extent to which these samples adequately reflect the larger MTurk population.
-Still, the consistency of our findings should be considered by future OB/HR researchers hoping to draw on MTurk for their research with the hopes of generalizing to the larger (or a specific) working US population.
-Additionally, as our studies were conducted in the US, it remains unclear how other MTurk populations might reflect (however imperfectly) their respective broader economy.
-Future larger scale studies should also consider lower levels of BLS occupational classification to examine the extent to which narrower occupations might not be represented by MTurk.
-Lastly, examining diversity in other respects (age, racio-ethnic, income, education, etc.) should also be considered.
-Though MTurk offers a practically feasible method of attaining high quality data, future research will be needed to understand the limitations of this tool.
-
-  Given that our data were gathered and analyzed in 2015, it might be insightful to have our procedures replicated annually to examine how the demographics of MTurk, specifically occupational characteristics, change over time, especially as access to technology becomes even easier and more commonplace.
-Thus, we encourage researchers to continue examining the occupational diversity of MTurk relative to the US economy.
-We also encourage researchers to consider novel ways of approximating the occupational diversity of both the US economy and MTurk because the currently existing taxonomies that we have used (i.e., BLS-based) probably do not capture all occupations.
-Lastly, our results raise a new and interesting research question: Why might MTurk possess the occupational diversity makeup that it does (i.e., why are some occupations over-represented while others are under-represented)?
-Similarly, what factors (e.g., access to technology, interest in psychology) might make it easier for workers coming from certain occupations to participate in OB studies hosted on MTurk?
-Answering these questions might unearth more constraints that impinge on the findings of OB studies using MTurk.
-
-#Conclusion
-  We called into question the diversity of MTurk as a key strength and suggested one key area where diversity may be lacking: occupational diversity.
-Our results suggest that, compared to the broader US population, MTurk is not as diverse, both over- and underrepresenting certain occupations.
-Future research drawing on MTurk should consider how occupational differences might be theoretically relevant and incorporate these effects in analyses using MTurk sample data to help overcoming these shortcomings.
-
-\newpage
-
-# References
-```{r}
-require(papaja)
-r_refs(file = "/Users/ccasti02/Documents/Research/Research on MTurk/MTurk's Occupational Diversity/r-references.bib")
-my_citation <- cite_r(file = "/Users/ccasti02/Documents/Research/Research on MTurk/MTurk's Occupational Diversity/r-references.bib")
-
-```
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
 ##Replication Demographic Analaysis
@@
 require(readxl)
-BLS_age <- read_excel("age_demo.xlsx")
+age_demo <- read_excel("age_demo.xlsx")
 
@@
 #Define sample mean
-MTurk17 <- read_excel("~/MTurk Diversity 2017 Data/2017 Data.xls")
+MTurk17 <- read_excel("2017 Data.xls")
 samp_mean <- as.numeric(MTurk17 %>%
@@
 t_value <- (samp_mean - pop_mean)/(samp_sd/sqrt(n))
-View(t_value)
+t_value
+
+#So MTurk is much younger than the population on average. We need to convert this to an effect size (Cohen's D). 
 ```
@@
 sum(gender_ch2$chi2, na.rm=TRUE)
+
+#So it appears that MTurk is largely dominated by females. We need to have an effect size describing this phenomena (e.g., a likelihood ratio).
 ```
@@
 ```
+
 ###Education Analysis 
@@
 ```
+
+#Discussion
+  What started our investigation was a simple research question: is the occupational diversity of the MTurk population representative of the broader US population?
+Our data suggest that the answer is not consistently so: certain occupations are over-represented, some fall within expectations, and still others are under-represented.
+Thus, OB researchers using convenient sampling procedures that draw on the MTurk population should consider whether occupational features might play a role in their investigation, which is point that we will elaborate upon in greater detail.
+Simply put, our results suggest that MTurk’s (US) occupational diversity does not align with the broader US economy.
+
+#Recommendations for Researchers Using MTurk
+  Given that OB researchers will likely wish to continue using MTurk as a means of gathering diverse, convenient, and low-cost survey sample data, researchers should consider how differences in the occupational diversity observed amongst MTurk workers relative to the US population might impinge upon the generalizability of their findings (@newman2015external).
+Specifically, given the over-representation of workers from (1) Management, Business, and Financial, (2) Computer, Engineering, and Science, and (3) Education, Legal, Community Service, Arts, and Media occupations, we might safely assume that many of our findings from MTurk will generalize across jobs classified under these broader over-represented occupational categories.
+However, as many occupations were under-represented [e.g., (1) Service, (2) Construction and Extraction, (3) Installation, Maintenance, and Repair, (4) Production; and (5) Transportation and Material Moving], questions may arise as to whether findings will generalize to jobs falling under these broad classifications.
+  To address this issue, researchers should consider capturing occupational data and modeling theoretically derived moderators.
+Person-environment (P-E) fit theories should help guide researchers in proposing how certain occupational groupings might influence individual-level relationships, lending to more nuanced and contextualized results (@how2009dr).
+Further, O*NET might be useful in this regard as it provides researchers a means for quantifying key occupational differences (e.g., level of competition requirements, social skills requirements) and thereby testing P-E fit hypotheses pertaining to occupational group differences (see @judge2015person).
+
+##Limitations and Future Research
+  One key limitation is that we assumed that O*NET’s classification system perfectly captured all occupations during 2015.
+Additionally, as both studies involved convenient sampling procedures, it remains uncertain the extent to which these samples adequately reflect the larger MTurk population.
+Still, the consistency of our findings should be considered by future OB/HR researchers hoping to draw on MTurk for their research with the hopes of generalizing to the larger (or a specific) working US population.
+Additionally, as our studies were conducted in the US, it remains unclear how other MTurk populations might reflect (however imperfectly) their respective broader economy.
+Future larger scale studies should also consider lower levels of BLS occupational classification to examine the extent to which narrower occupations might not be represented by MTurk.
+Lastly, examining diversity in other respects (age, racio-ethnic, income, education, etc.) should also be considered.
+Though MTurk offers a practically feasible method of attaining high quality data, future research will be needed to understand the limitations of this tool.
+
+  Given that our data were gathered and analyzed in 2015, it might be insightful to have our procedures replicated annually to examine how the demographics of MTurk, specifically occupational characteristics, change over time, especially as access to technology becomes even easier and more commonplace.
+Thus, we encourage researchers to continue examining the occupational diversity of MTurk relative to the US economy.
+We also encourage researchers to consider novel ways of approximating the occupational diversity of both the US economy and MTurk because the currently existing taxonomies that we have used (i.e., BLS-based) probably do not capture all occupations.
+Lastly, our results raise a new and interesting research question: Why might MTurk possess the occupational diversity makeup that it does (i.e., why are some occupations over-represented while others are under-represented)?
+Similarly, what factors (e.g., access to technology, interest in psychology) might make it easier for workers coming from certain occupations to participate in OB studies hosted on MTurk?
+Answering these questions might unearth more constraints that impinge on the findings of OB studies using MTurk.
+
+#Conclusion
+  We called into question the diversity of MTurk as a key strength and suggested one key area where diversity may be lacking: occupational diversity.
+Our results suggest that, compared to the broader US population, MTurk is not as diverse, both over- and underrepresenting certain occupations.
+Future research drawing on MTurk should consider how occupational differences might be theoretically relevant and incorporate these effects in analyses using MTurk sample data to help overcoming these shortcomings.
+
+\newpage
+
+# References
+```{r}
+require(papaja)
+r_refs(file = "/Users/ccasti02/Documents/Research/Research on MTurk/MTurk's Occupational Diversity/r-references.bib")
+my_citation <- cite_r(file = "/Users/ccasti02/Documents/Research/Research on MTurk/MTurk's Occupational Diversity/r-references.bib")
+
+```
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+=======

### 2018-09-21 Manuscript.Rmd
Commit in order to pull from GitHub

--- 2018-09-21 Manuscript.Rmd
@@
 
-```{r Load Data, include=FALSE, results='asis'}
+```{r,BLS, include=FALSE, results='asis'}
 #Load packages
@@
 
-# Include data on the size of the military (taken from the department of defense (http://us-military-branches.insidegov.com))
-BLS <- rbind(BLS, c("Military Specific Occupations", 1350236))
+#Include data on the size of the military (taken from the department of defense (http://us-military-branches.insidegov.com))
+BLS <- rbind(BLS, c("Military specific occupations", 1350236))
 
-#Only keep intermediate category totals.
-BLS <- BLS[c(2,71,129,162,222,293,320,336,432,494,586,612,653,687,705,767,810,923,950,1054,1130,1298,1395,1),]
+#Only major occupation groups are included in BLS
+BLS <- 
+BLS[c(2,71,129,162,222,293,320,336,432,494,586,612,653,687,705,767,810,923,950,1054,1130,1298,1395,1),]
 
@@
 
-#Add military occupation number to the overall. 
+#Add military occupation number to the overall
 BLS$Var2[14] <- BLS$Var2[13] + BLS$Var2[14]
@@
 BLS <- tab[c(1,3)]
-names(BLS) <- c("Intermediate Aggregation Title","e")
+names(BLS) <- c("Intermediate Aggregation Title", "e")
 
 ##LATech data
-LATech <- read_csv("Data/Chris's Data from 2015.csv")
+LATech <- read_csv("Chris's Data from 2015.csv")
 ###Delete unneeded data.
@@
 LATech[784, 3] = "25-0000.00"
-
 ###Remove unemployed cases.
@@
 }
-
 LATech <- completeFun(LATech, "O*NET Job Code")
@@
 LATech <- cbind(LATech,LO)
-
 ###Build relative frequency table.
@@
 names(tab) <- c("Intermediate Aggregation Title","n","f")
-
 #Table for poster.
@@
 ##UGA data
-UGA <- read_excel("Data/Rachel's Data from 2015.xlsx")
+UGA <- read_excel("Rachel's Data from 2015.xlsx")
 UGA <- UGA[c(2,21)]
@@
 
-##Replication Demographic Analaysis
-##Age Analysis
-```{r}
-#Age Analysis T- Test
-#Load Dataset
-require(dplyr)
-require(readxl)
-age_demo <- read_excel("age_demo.xlsx")
-
-#Define population mean. In this case it was already calculated in the dataset. 
-pop_mean <- as.numeric(age_demo[6 , 10])
-
-#Define sample mean
-MTurk17 <- read_excel("2017 Data.xls")
-samp_mean <- as.numeric(MTurk17 %>%
-  summarise(MTurk_age = mean(What.is.your.age., na.rm = TRUE)))
-
-#Not able to get population standard deviation. Estimated using sample standard deviation.
-samp_sd <- as.numeric(MTurk17 %>%
-  summarise(sd_age = sd(What.is.your.age., na.rm = TRUE)))
-
-#Define sample size
-n <- as.numeric(667)
-
-#Run t test.
-t_value <- (samp_mean - pop_mean)/(samp_sd/sqrt(n))
-t_value
-
-#So MTurk is much younger than the population on average. We need to convert this to an effect size (Cohen's D). 
-```
-
-##Gender Analysis
-```{r}
-##Gender Analysis
-BLS_data <- read_excel("employment_demo.xlsx")
-
-#Get BLS gender data (expected value)
-BLS_women <- as.numeric(BLS_data[7,3])/100
-BLS_men <- 1.000 - BLS_women
-
-BLS_gender <- c(BLS_women, BLS_men, 0.0)
-
-#Get MTurk gender data (observed value)
-MTurk_gender <- MTurk17 %>%
-  count(What.is.your.gender.)
-
-#Define confidence intervals
-require(binom)
-gCI <- binom.confint(x = MTurk_gender$n, n = sum(MTurk_gender$n), conf.level = 0.95, methods = "exact")
-gCI <- gCI[ , 4:6]
-
-#Build Gender table with gender, expected value, n, LL, observed, UL
-gender_table <- cbind(MTurk_gender, gCI, BLS_gender)
-names(gender_table) <- c("gender", "n", "o", "LL_g", "UL_g", "e")
-gender_table <- gender_table[ 1, c(1, 2, 3, 4, 6, 5)]
-View(gender_table)
-
-#Gender chi square test
-
-chi2 <- function(x) {
-  o <- (x$n)
-  e <- (x$e)
-  n <- sum(x$n, na.rm=TRUE)
-  ((o-(e)*(n))^2)/((e)*(n))
-}
-
-gender_ch2 <- as.data.frame(chi2(gender_table))
-names(gender_ch2) <- c("chi2")
-row.names(gender_ch2) <- c("female")
-gender_ch2 <- na.omit(gender_ch2)
-View(gender_ch2)
-
-#Sum chi-square values.
-sum(gender_ch2$chi2, na.rm=TRUE)
-
-#So it appears that MTurk is largely dominated by females. We need to have an effect size describing this phenomena (e.g., a likelihood ratio).
-```
-
-##Ethnicity Analysis
-```{r}
-#Ethnicity Analysis 
-#Define obs_eth
-BLS_cauc <- as.numeric(BLS_data[7, 4])/100
-BLS_AfAm <- as.numeric(BLS_data[7,5])/100
-BLS_Asn <- as.numeric(BLS_data[7,6])/100
-BLS_Hisp <- as.numeric(BLS_data[7,7])/100
-BLS_eth <- c(BLS_AfAm, BLS_Asn, BLS_cauc, BLS_Hisp)
-
-sum(BLS_eth)
-
-#Get MTurk ethnicity data
-MTurk_eth <- MTurk17 %>%
-  count(MTurk17$With.which.ethnicity.do.you.most.identify.)
-
-#Define confidence intervals 
-ethCI <- binom.confint(x = MTurk_eth$n, n = sum(MTurk_eth$n), conf.level = 0/95, methods = "exact")
-ethCI <- ethCI[ , 4:6]
-
-#Build Ethnicity table 
-ethnicity_table <- cbind(MTurk_eth, ethCI, BLS_eth)
-names(ethnicity_table) <- c("ethnicity", "n", "o", "LL_eth", "UL_eth", "e")
-eth_table <- ethnicity_table[1:4 , c(1, 6, 2, 4, 3, 5)]
-View(eth_table)
-
-#Ethnicity chi squared test
-eth_ch2 <- as.data.frame(chi2(eth_table))
-names(eth_ch2) <- c("chi2")
-row.names(eth_ch2) <- c("African American", "Asian", "Caucasian", "Hispanic")
-eth_ch2 <- na.omit(eth_ch2)
-View(eth_ch2)
-
-#Sum chi-square values.
-sum(eth_ch2$chi2, na.rm=TRUE)
-```
-
 #Discussion

### 2018-09-28 Manuscript.Rmd
Added brackets to citations

--- 2018-09-21 Manuscript.Rmd
@@
 #Introduction
-  Amazon’s Mechanical Turk (MTurk), an online labor market created by Amazon, has recently become popular among social scientists interested in collecting inexpensive, high-quality data from a diverse population (@aguinis2012conducting @behrend2011viability @bergman2016have @paolacci2014inside @shank2016using).
-Leveraging the strengths of this tool, MTurk has been used by social scientists to replicate well-known phenomena (e.g., reaction times, priming, task switching; @crump2013evaluating; memory, @simons2012common) and by organizational behavior (OB) researchers to expand the OB literature (e.g., @yarkoni2015interactions).
+  Amazon’s Mechanical Turk (MTurk), an online labor market created by Amazon, has recently become popular among social scientists interested in collecting inexpensive, high-quality data from a diverse population [@aguinis2012conducting @behrend2011viability @bergman2016have @paolacci2014inside @shank2016using].
+Leveraging the strengths of this tool, MTurk has been used by social scientists to replicate well-known phenomena [e.g., reaction times, priming, task switching; @crump2013evaluating; memory, @simons2012common] and by organizational behavior (OB) researchers to expand the OB literature [e.g., @yarkoni2015interactions].
 
-  Yet, in spite of the growing enthusiasm surrounding the use of MTurk, it represents merely another convenient sampling methodology that comes with a few constraints, such as repeated participation or motivation due to compensation (@landers2015inconvenient @woo2015amazon) and other yet-to-be-identified constraints.
+  Yet, in spite of the growing enthusiasm surrounding the use of MTurk, it represents merely another convenient sampling methodology that comes with a few constraints, such as repeated participation or motivation due to compensation [@landers2015inconvenient @woo2015amazon] and other yet-to-be-identified constraints.
 Here, we examine one potentially important constraint for using MTurk to conduct OB research: the occupational diversity of MTurk.
-Given that a fundamental goal of most OB research is that workers are sampled from an appropriate organizational setting (e.g., @pathak2008methodology), understanding the occupational diversity of MTurk will improve our understanding of the boundary conditions or limits to the generalizability of MTurk research findings.
-By examining the occupational diversity of MTurk, our work addresses a call for research that describes the kinds of individuals who participate in MTurk studies (@griggs2016these).
+Given that a fundamental goal of most OB research is that workers are sampled from an appropriate organizational setting [e.g., @pathak2008methodology], understanding the occupational diversity of MTurk will improve our understanding of the boundary conditions or limits to the generalizability of MTurk research findings.
+By examining the occupational diversity of MTurk, our work addresses a call for research that describes the kinds of individuals who participate in MTurk studies [@griggs2016these].
 
@@
 ##What is MTurk?
-  MTurk is an internet marketplace where people seeking laborers have access to a population of workers willing to do tasks requiring a human intelligence for a small fee (@behrend2011viability).
+  MTurk is an internet marketplace where people seeking laborers have access to a population of workers willing to do tasks requiring a human intelligence for a small fee [@behrend2011viability].
 Billed as a “marketplace for work that requires human intelligence”, MTurk allows “requesters” to post Human Intelligence Tasks (HITs), which serve as self-contained jobs in which “workers” can participate.
-Via MTurk, researchers seeking participants often post survey studies for workers to voluntarily complete (@goodman2013data).
+Via MTurk, researchers seeking participants often post survey studies for workers to voluntarily complete [@goodman2013data].
 Workers are given a short description about a project, including details about various tasks, estimated time investment, and payment, and may selectively choose which projects to complete.
-Here, researchers seeking participants often post survey studies for workers to voluntarily complete (@goodman2013data).
+Here, researchers seeking participants often post survey studies for workers to voluntarily complete [@goodman2013data].
 
 ##Why is MTurk Valuable for Researchers Studying Working Populations?
-  MTurk offers practical advantages that may not be available via other more traditional methods of data collection, such as sampling from specific organizations (@paolacci2010running).
-The platform allows for easier subject pool access at an affordable cost and for subject prescreening (@mason2012conducting).
-Additionally, it allows for subject anonymity, subject identifiability in longitudinal studies, and offers a simple and supportive infrastructure (@paolacci2010running).
-More importantly, its diversity is a key strength that sets it apart from other commonly studied populations (e.g., university students, community samples), making it an attractive subject pool for researchers to draw upon (@buhrmester2011amazon; Erikson & Simpson, 2010; @paolacci2010running).
+  MTurk offers practical advantages that may not be available via other more traditional methods of data collection, such as sampling from specific organizations [@paolacci2010running].
+The platform allows for easier subject pool access at an affordable cost and for subject prescreening [@mason2012conducting].
+Additionally, it allows for subject anonymity, subject identifiability in longitudinal studies, and offers a simple and supportive infrastructure [@paolacci2010running].
+More importantly, its diversity is a key strength that sets it apart from other commonly studied populations (e.g., university students, community samples), making it an attractive subject pool for researchers to draw upon [@buhrmester2011amazon; Erikson & Simpson, 2010; @paolacci2010running].
 For instance, @behrend2011viability found that MTurk workers are more diverse on variables such as age, ethnicity, education, employment status, job experience, profession, nationality, and personality.
-The diversity of MTurk allows OB researchers to overcome concerns regarding the generalizability of their findings (e.g., @paolacci2010running), which has been a key concern facing OB research (@chiao2010weirdest).
+The diversity of MTurk allows OB researchers to overcome concerns regarding the generalizability of their findings [e.g., @paolacci2010running], which has been a key concern facing OB research [@chiao2010weirdest].
 
@@
 BLS <- BLS[c(2,4)]
+
+#Include data on the size of the military (taken from the department of defense (http://us-military-branches.insidegov.com))
+BLS <- rbind(BLS, c("Military specific occupations", 1350236))
+
+#Only major occupation groups are included in BLS
+BLS <- 
+BLS[c(2,71,129,162,222,293,320,336,432,494,586,612,653,687,705,767,810,923,950,1054,1130,1298,1395,1),]
 
@@
 BLS <- tab[c(1,3)]
+names(BLS) <- c("Intermediate Aggregation Title", "e")
+
+##LATech data
+LATech <- read_csv("Chris's Data from 2015.csv")
+
+#Only keep occupational categories (no all).
+BLS <- BLS[-14,]
+
+#Compute relative frequencies. Call the object "tab".
+tab <- transform(BLS, relative = prop.table(Freq))
+
+#Define new BLS. "e" is for "relative frequency". 
+BLS <- tab[c(1,3)]
 names(BLS) <- c("Intermediate Aggregation Title","e")
@@
 LATech <- read_csv("Data/Chris's Data from 2015.csv")
+
 ###Delete unneeded data.
@@
 ##UGA data
+UGA <- read_excel("Rachel's Data from 2015.xlsx")
 UGA <- read_excel("Data/Rachel's Data from 2015.xlsx")
@@
 #Recommendations for Researchers Using MTurk
-  Given that OB researchers will likely wish to continue using MTurk as a means of gathering diverse, convenient, and low-cost survey sample data, researchers should consider how differences in the occupational diversity observed amongst MTurk workers relative to the US population might impinge upon the generalizability of their findings (@newman2015external).
+  Given that OB researchers will likely wish to continue using MTurk as a means of gathering diverse, convenient, and low-cost survey sample data, researchers should consider how differences in the occupational diversity observed amongst MTurk workers relative to the US population might impinge upon the generalizability of their findings [@newman2015external].
 Specifically, given the over-representation of workers from (1) Management, Business, and Financial, (2) Computer, Engineering, and Science, and (3) Education, Legal, Community Service, Arts, and Media occupations, we might safely assume that many of our findings from MTurk will generalize across jobs classified under these broader over-represented occupational categories.
@@
   To address this issue, researchers should consider capturing occupational data and modeling theoretically derived moderators.
-Person-environment (P-E) fit theories should help guide researchers in proposing how certain occupational groupings might influence individual-level relationships, lending to more nuanced and contextualized results (@how2009dr).
-Further, O*NET might be useful in this regard as it provides researchers a means for quantifying key occupational differences (e.g., level of competition requirements, social skills requirements) and thereby testing P-E fit hypotheses pertaining to occupational group differences (see @judge2015person).
+Person-environment (P-E) fit theories should help guide researchers in proposing how certain occupational groupings might influence individual-level relationships, lending to more nuanced and contextualized results [@how2009dr].
+Further, O*NET might be useful in this regard as it provides researchers a means for quantifying key occupational differences (e.g., level of competition requirements, social skills requirements) and thereby testing P-E fit hypotheses pertaining to occupational group differences [see @judge2015person].
 

### 2018-10-04 Manuscript.Rmd
Fixed education analysis error on line 618 (now line 616). Also took out a few lines where it was viewing the tables in order for code to run smoother.

--- 2018-09-21 Manuscript.Rmd
@@
 eth_table <- ethnicity_table[1:4 , c(1, 6, 2, 4, 3, 5)]
-View(eth_table)
 
@@
 eth_ch2 <- na.omit(eth_ch2)
-View(eth_ch2)
 
@@
 #Use vapply and the above function to get expected proportions from BLS data
-BLS_edu <- sapply(BLS_education, prop_func)
+BLS_edu <- sapply(BLS_education, e_prop)
 
@@
 education_table <- education_table[ , c(1, 6, 2, 4, 3, 5)]
-View(education_table)
 
@@
 edu_ch2 <- na.omit(edu_ch2)
-View(edu_ch2)
 

### 2018-11-05 Manuscript.Rmd

@@
 #- - - - - - - - - - - - - 
+##Chart 1
+```{r}
+#Bar Plot with error bars
+require(ggplot2)
+Values <- c(Table2[1:13, 5], Table2[1:13, 2])
+Group <- c("MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS")
+Occupations <- c(Table2[1:13, 1], Table2[1:13, 1])
+Occ_Nums <- sapply(strsplit(Occupations, " "), "[[", 1)
+barplot_data <- data.frame(as.character(Values), as.character(Occ_Nums),as.character(Group))
+names(barplot_data) <- c("Frequency", "Occupations","Group")
+dodge <- position_dodge(width = .9)
+
+#Define Error Bar limits.
+upperM <- as.vector(Table2[1:13, 6])
+upperB <- c(0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
+upper <-c(upperM, upperB)
+
+lowerM <- as.vector(Table2[1:13, 6])
+lowerB <- c(0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
+lower <- c(lowerM, lowerB)
+
+se <- data.frame(upper, lower)
+limits <- aes(ymax = se$upper, ymin = se$lower)
+
+require(ggplot2)
+ggplot(barplot_data, aes(Occ_Nums, Values, fill = Group)) + 
+  geom_errorbar(limits, position = dodge,
+                width = 0.10, size = 1.0) +
+  geom_col(position = dodge)  +
+  ggtitle("MTurk's Occupational Diveristy with Error Bars") +
+  labs(x = "Occupation", y = "Frequency") +
+  theme(legend.position = "top", plot.title = element_text(hjust = 0.5), 
+        text=element_text(family="serif"))+
+  coord_flip()
+```
 

### 2018-11-27 Manuscript.Rmd
Updated before integration with Kathryn's code.

--- 2018-10-04 Manuscript.Rmd
@@
 ---
-title             : "Comparing MTurk and the US Population’s Occupational Diversity"
+title             : "Comparing the Occupational and Demographic Diversity of Amazon's Mechanical Turk to the U.S. Labor Force"
 shorttitle        : "MTurk's Occupational Diversity"
@@
     corresponding : yes    # Define only one corresponding author
+    address       : "906 E. 1st St., Thibodaux, LA, 70301"
     email         : "chris_castille@mac.com"
+  - name          : "Kathryn Daigle"
+    affiliation   : "1"
+  - name          : "Sarah Avet"
+    affiliation   : "1"
+  - name          : "Rachel L. Williamson"
+    affiliation   : "2"
   - name          : "Bodour H. Mahmoud"
-    affiliation   : "2"
-  - name          : "Rachel L. Williamson"
     affiliation   : "3"
@@
     affiliation   : "4"
-  - name          : "James De Leôn"
-    affiliation   : "5"
 affiliation:
@@
   - id            : "2"
+    institution   : "Louisiana State University"
+  - id            : "3"
     institution   : "Villanova University"
-  - id            : "3"
-    institution   : "University of Georgia"
   - id            : "4"
     institution   : "AlixPartners"
-  - id            : "5"
-    institution   : "APT Metrics"
 
@@
 abstract: >
-  We compare the occupational diversity of two convenient MTurk samples against the broader US economy from which they have been indirectly sampled.
-We focus on occupational diversity given a chief concern that findings from OB/HR investigations relying on MTurk might not generalize to the broader US economy .
-Additionally, as researchers may hope to target specific populations (e.g., sales professionals) understanding the extent to which these professionals are represented in the MTurk population would be helpful.
-Therefore, we compare the occupational diversity of MTurk against that described by the Bureau of Labor Statistics, testing the null hypothesis that these populations are equivalent in terms of occupational diversity.
-Across both samples, which were obtained from studies conducted in 2015, we found differences suggesting that the MTurk population is generally overrepresented by white collar professionals (though this is an imperfect trend) and generally underrepresented by blue collar workers.
-keywords          : "MTurk, Occupational Diversity"
+  We compare the occupational diversity of three conveniently gathered MTurk samples (two in 2015, one in 2017) against the broader US labor force from which they have been indirectly sampled.
+We focus on occupational diversity given concerns regarding the the generalizability of findings into organizational life that have been drawn from studies utilizing MTurk.
+Additionally, as researchers may hope to target specific populations (e.g., sales professionals) understanding the extent to which these professionals are over- or under- represented in the MTurk population would inform decisions regarding the cost-effectiveness of sampling techniques.
+Across our samples, we found differences suggesting that the MTurk population is generally overrepresented by white collar professionals (though this is an imperfect trend).
+Other demographic trends were also explored regarding age, gender, and education.
+Overall, the MTurk population appears to fall short of an ideal representation of the broader labor force.
+
+header-includes:
+  - \raggedbottom
+
+keywords          : "MTurk, Occupational Diversity, Demographics"
+
 wordcount         : "3000"
@@
 
-figsintext        : no
+figsintext        : yes
 figurelist        : no
-tablelist         : yes
+tablelist         : no
 footnotelist      : no
-lineno            : no
+lineno            : yes
 
@@
 ---
+```{r Load Packages, include=FALSE}
+# Load packages
+library(papaja)         # Print in apa style
+library(readr)          # Reading data
+library(readxl)         # Reading data
+library(data.table)     # Reading data
+library(openxlsx)       # Reading data
+library(fifer)          # Post hoc chi-sqaure testing
+library(binom)          # Confidence intervals for proportions
+library(apa)            # Print results in apa format
+library(pwr)            # Power analysis tools
+library(RVAideMemoire)  # Conduct post-hoc test
+library(ggplot2)        # Graphing results
+library(scales)         # For printing frequencies as percentages
+library(tidyquant)      # Used in demographic analysis
+library(lsr)            # Useful for conducting one-sample t-tests and estiamting Cohen's D
+```
+# Introduction
+Amazon’s Mechanical Turk (MTurk), an online labor market created by Amazon, has recently become popular among social scientists interested in collecting inexpensive, high-quality data from a diverse population [@aguinisConductingFieldExperiments2012; @behrendViabilityCrowdsourcingSurvey2011; @bergmanWhereHaveAll2016; @paolacciTurkUnderstandingMechanical2014; @shankUsingCrowdsourcingWebsites2016].
+Leveraging the strengths of this tool, MTurk has been used by social scientists to replicate well-known phenomena [e.g., reaction times, priming, task switching, see @crumpEvaluatingAmazonMechanical2013; memory, see @simonsCommonMisBeliefs2012 and by organizational behavior (OB) researchers to expand the OB literature [e.g., @yarkoniInteractionsDonorAgreeableness2015].
 
-```{r message = FALSE, warning = FALSE}
-#The packages below will allow you to access "papaja", and if it fails, then try running all of the code at once. It should work then. 
-library("papaja")
-```
-#Introduction
-  Amazon’s Mechanical Turk (MTurk), an online labor market created by Amazon, has recently become popular among social scientists interested in collecting inexpensive, high-quality data from a diverse population (@aguinis2012conducting @behrend2011viability @bergman2016have @paolacci2014inside @shank2016using).
-Leveraging the strengths of this tool, MTurk has been used by social scientists to replicate well-known phenomena (e.g., reaction times, priming, task switching; @crump2013evaluating; memory, @simons2012common) and by organizational behavior (OB) researchers to expand the OB literature (e.g., @yarkoni2015interactions).
+Yet, in spite of the growing enthusiasm surrounding the use of MTurk, it represents merely another convenient sampling methodology that comes with a few constraints, such as repeated participation or motivation due to compensation [@landersInconvenientTruthArbitrary2015; @wooAmazonMechanicalTurk2015] and other yet-to-be-identified constraints.
+Here, we examine one potentially important constraint for using MTurk to conduct OB research: the occupational diversity of MTurk.
+Given that a fundamental goal of most OB research is that workers are sampled from an appropriate organizational setting, understanding the occupational diversity of MTurk will improve our understanding of the boundary conditions or limits to the generalizability of MTurk research findings.
+By examining the occupational diversity of MTurk, our work addresses a call for research that describes the kinds of individuals who participate in MTurk studies [@griggsWhoAreThese2016].
 
-  Yet, in spite of the growing enthusiasm surrounding the use of MTurk, it represents merely another convenient sampling methodology that comes with a few constraints, such as repeated participation or motivation due to compensation (@landers2015inconvenient @woo2015amazon) and other yet-to-be-identified constraints.
-Here, we examine one potentially important constraint for using MTurk to conduct OB research: the occupational diversity of MTurk.
-Given that a fundamental goal of most OB research is that workers are sampled from an appropriate organizational setting (e.g., @pathak2008methodology), understanding the occupational diversity of MTurk will improve our understanding of the boundary conditions or limits to the generalizability of MTurk research findings.
-By examining the occupational diversity of MTurk, our work addresses a call for research that describes the kinds of individuals who participate in MTurk studies (@griggs2016these).
+# Review of the Literature
 
-#Review of the Literature
-##What is MTurk?
-  MTurk is an internet marketplace where people seeking laborers have access to a population of workers willing to do tasks requiring a human intelligence for a small fee (@behrend2011viability).
+## What is MTurk?
+MTurk is an internet marketplace where people seeking laborers have access to a population of workers willing to do tasks requiring a human intelligence for a small fee [@landersInconvenientTruthArbitrary2015].
 Billed as a “marketplace for work that requires human intelligence”, MTurk allows “requesters” to post Human Intelligence Tasks (HITs), which serve as self-contained jobs in which “workers” can participate.
-Via MTurk, researchers seeking participants often post survey studies for workers to voluntarily complete (@goodman2013data).
+Via MTurk, researchers seeking participants often post survey studies for workers to voluntarily complete.
 Workers are given a short description about a project, including details about various tasks, estimated time investment, and payment, and may selectively choose which projects to complete.
-Here, researchers seeking participants often post survey studies for workers to voluntarily complete (@goodman2013data).
+Here, researchers seeking participants often post survey studies for workers to voluntarily complete.
 
-##Why is MTurk Valuable for Researchers Studying Working Populations?
-  MTurk offers practical advantages that may not be available via other more traditional methods of data collection, such as sampling from specific organizations (@paolacci2010running).
-The platform allows for easier subject pool access at an affordable cost and for subject prescreening (@mason2012conducting).
-Additionally, it allows for subject anonymity, subject identifiability in longitudinal studies, and offers a simple and supportive infrastructure (@paolacci2010running).
-More importantly, its diversity is a key strength that sets it apart from other commonly studied populations (e.g., university students, community samples), making it an attractive subject pool for researchers to draw upon (@buhrmester2011amazon; Erikson & Simpson, 2010; @paolacci2010running).
-For instance, @behrend2011viability found that MTurk workers are more diverse on variables such as age, ethnicity, education, employment status, job experience, profession, nationality, and personality.
-The diversity of MTurk allows OB researchers to overcome concerns regarding the generalizability of their findings (e.g., @paolacci2010running), which has been a key concern facing OB research (@chiao2010weirdest).
+## The Value of Studying Working Populations with MTurk
+
+MTurk offers practical advantages that may not be available via other more traditional methods of data collection, such as sampling from specific organizations .
+The platform allows for easier subject pool access at an affordable cost and for subject prescreening [@masonConductingBehavioralResearch2012].
+Additionally, it allows for subject anonymity, subject identifiability in longitudinal studies, and offers a simple and supportive infrastructure [@paolacciRunningExperimentsAmazon2010].
+More importantly, its diversity is a key strength that sets it apart from other commonly studied populations (e.g., university students, community samples), making it an attractive subject pool for researchers to draw upon [@buhrmesterAmazonMechanicalTurk2011; @erikssonWhatAmericansKnow2012; @paolacciRunningExperimentsAmazon2010].
+For instance, @behrendViabilityCrowdsourcingSurvey2011 found that MTurk workers are more diverse on variables such as age, ethnicity, education, employment status, job experience, profession, nationality, and personality.
+The diversity of MTurk allows OB researchers to overcome concerns regarding the generalizability of their findings [@paolacciRunningExperimentsAmazon2010], which has been a key concern facing OB research [@henrichWeirdestPeopleWorld2010].
 
@@
 To our knowledge, no study has compared the occupational diversity of MTurk to the broader US population.
-While @behrend2011viability work suggests that MTurk’s occupational diversity is greater than the university population, our work expands on their research by comparing MTurk’s occupational diversity to the broader US population.
+While @behrendViabilityCrowdsourcingSurvey2011 work suggests that MTurk’s occupational diversity is greater than the university population, our work expands on their research by comparing MTurk’s occupational diversity to the broader US population.
 If the occupational diversity of the broader US population is indeed reflected in MTurk, findings from MTurk should better generalize across occupations.
@@
 
-  *Research Question: Is the occupational diversity of the MTurk population representative of the broader US economy?*
+*Research Question 1: Is the occupational diversity of the MTurk population representative of the broader US labor force?*
+
+In addition to examining occupational diversity, we conducted exploratory analyses of other demographic disparities, focusing in on age, gender, ethnicity, and education as these are commonly studied in the social sciences.
+Therefore, a second research question was examined, but in an exploratory fashion.
+Answering this question required that we describe the diversity of the US labor force.
+Fortunately, the BLS provides summary statistics which describe the proportion of individuals falling into various demographic categories.
+
+*Research Question 2: Is the demographic diversity of the MTurk population representative of the broader US labor force?*
 
 # Methods
-##US Population Occupational Summary Statistics
-  Occupational Employment Statistics (OES) were obtained from the United States Bureau of Labor Statistics (BLS) (2015).
-Occupation diversity was measured by calculating the percentage of job holders falling under a particular occupational category.
-We adopted the Intermediate Aggregation and Standard Occupational Classification (SOC) used by the Bureau of Labor Statistics (BLS) for this study (see table 1).
-Percentages describe the percentage of workers in the US economy who work in occupations that fall under this broader occupational category.
 
-#- - - - - - - - - - - - - 
-#insert table 1 about here
-#- - - - - - - - - - - - -
+## US Population Occupational Summary Statistics (2015 and 2017)
 
-```{r Load Data, include=FALSE, results='asis'}
-#Load packages
-library(readr)
-library(readxl)
-library(data.table)
-library(openxlsx)
+Occupational Employment Statistics were obtained from the United States Bureau of Labor Statistics (BLS) both from years 2015 and 2017.
+These data are released annually in the spring and describe the previous year.
+Statistics from these reports allowed us to define expectations regarding the proportion of workers falling into a particular intermediate occupational category.
+We adopted the Intermediate Aggregation and Standard Occupational Classification (SOC) used by the Bureau of Labor Statistics (BLS) for this study to ease our analysis.
 
-#Load datasets.
+```{r Load and Clean Data, include=FALSE, warning = FALSE, message = FALSE, echo = FALSE}
+# Load datasets.
 Note: these datasets were not taken direclty from their respective sources (i.e., BLS or Qualtrics survey, respectively).
@@
 The UGA dataset is a full dataset in the sense that it contains all individuals whose data are relevant for our investigation (i.e., participants hold a job that falls under a SOC classification) or not (i.e., they either do not work or work in a job falling outside the SOC classification system).
-#Build the BLS Table, but first establish a temp file.
 
+# Build the BLS Table, but first establish a temp file. Unhastag to use.
 # Download the file with download.file()
-# Here is the URL.
-download.file("https://www.bls.gov/oes/special.requests/oesm15nat.zip", "BLS2015.zip")
-unzip("BLS2015.zip")
-library(readxl)
+# Here is the URL: 
+# download.file("https://www.bls.gov/oes/special.requests/oesm15nat.zip", "BLS2015.zip")
+# unzip("BLS2015.zip")
 BLS <- read_excel("oesm15nat/national_M2015_dl.xlsx")
@@
 
-#Only keep intermediate category totals.
+# Only keep intermediate category totals.
 BLS <- BLS[c(2,71,129,162,222,293,320,336,432,494,586,612,653,687,705,767,810,923,950,1054,1130,1298,1395,1),]
 
-###Rename rows and aggregate.
-BLS[1, 1] = "11-13 Management, Business, and Financial Occupations"
-BLS[2, 1] = "11-13 Management, Business, and Financial Occupations"
-BLS[3, 1] = "15-19 Computer, Engineering, and Science Occupations"
-BLS[4, 1] = "15-19 Computer, Engineering, and Science Occupations"
-BLS[5, 1] = "15-19 Computer, Engineering, and Science Occupations"
-BLS[6, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
-BLS[7, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
-BLS[8, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
-BLS[9, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
-BLS[10, 1] = "29 Healthcare Practitioners and Technical Occupations"
-BLS[11, 1] = "31-39 Service Occupations"
-BLS[12, 1] = "31-39 Service Occupations"
-BLS[13, 1] = "31-39 Service Occupations"
-BLS[14, 1] = "31-39 Service Occupations"
-BLS[15, 1] = "31-39 Service Occupations"
-BLS[16, 1] = "41 Sales and Related Occupations"
-BLS[17, 1] = "43 Office and Administrative Support Occupations"
-BLS[18, 1] = "45 Farming, Fishing, and Forestry Occupations"
-BLS[19, 1] = "47 Construction and Extraction Occupation"
-BLS[20, 1] = "49 Installation, Maintenance, and Repair Occupations"
-BLS[21, 1] = "51 Production Occupation"
-BLS[22, 1] = "53 Transportation and Material Moving Occupation"
-BLS[23, 1] = "55 Military Specific Occupations"
+# Rename rows and aggregate.
+BLS[1, 1] = "11-13 Management, Business, and Financial"
+BLS[2, 1] = "11-13 Management, Business, and Financial"
+BLS[3, 1] = "15-19 Computer, Engineering, and Science"
+BLS[4, 1] = "15-19 Computer, Engineering, and Science"
+BLS[5, 1] = "15-19 Computer, Engineering, and Science"
+BLS[6, 1] = "21-27 Education, Legal, Community Service, Arts, and Media"
+BLS[7, 1] = "21-27 Education, Legal, Community Service, Arts, and Media"
+BLS[8, 1] = "21-27 Education, Legal, Community Service, Arts, and Media"
+BLS[9, 1] = "21-27 Education, Legal, Community Service, Arts, and Media"
+BLS[10, 1] = "29 Healthcare Practitioners and Technical"
+BLS[11, 1] = "31-39 Service"
+BLS[12, 1] = "31-39 Service"
+BLS[13, 1] = "31-39 Service"
+BLS[14, 1] = "31-39 Service"
+BLS[15, 1] = "31-39 Service"
+BLS[16, 1] = "41 Sales and Related"
+BLS[17, 1] = "43 Office and Administrative Support"
+BLS[18, 1] = "45 Farming, Fishing, and Forestry"
+BLS[19, 1] = "47 Construction and Extraction"
+BLS[20, 1] = "49 Installation, Maintenance, and Repair"
+BLS[21, 1] = "51 Production"
+BLS[22, 1] = "53 Transportation and Material Moving"
+BLS[23, 1] = "55 Military Specific"
 names(BLS) <- c("Var1","Var2")
@@
 
-#Add military occupation number to the overall. 
+# Add military occupation number to the overall. 
 BLS$Var2[14] <- BLS$Var2[13] + BLS$Var2[14]
 
-#Rename variables
+# Rename variables
 names(BLS) <- c("Intermediate Aggregation Title", "Freq")
 
-#Only keep occupational categories (no all).
+# Only keep occupational categories (no all).
 BLS <- BLS[-14,]
 
-#Compute relative frequencies. Call the object "tab".
+# Compute relative frequencies. Call the object "tab".
 tab <- transform(BLS, relative = prop.table(Freq))
 
-#Define new BLS. "e" is for "relative frequency". 
+# Define new BLS. "e" is for "relative frequency". 
 BLS <- tab[c(1,3)]
@@
 
-##LATech data
+# LATech data
 LATech <- read_csv("Data/Chris's Data from 2015.csv")
-###Delete unneeded data.
+
+# Delete unneeded data.
 LATech <- LATech[c(1:3)]
-###Edit data. Some participants provided incorrect codes or no codes.
+
+# Edit data. Some participants provided incorrect codes or no codes.
 LATech[703, 3] = "43-6011.00"
@@
 
-###Remove unemployed cases.
+# Remove unemployed cases.
 completeFun <- function(data, desiredCols) {
@@
 
-###Abbreviate data, consolidate into intermediate categories, and bind.
+# Abbreviate data, consolidate into intermediate categories, and bind.
 LO <- LATech[c(3)]
@@
 names(LO) <- c("Int.Agg.Cat")
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 11] <- "11-13 Management, Business, and Financial Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 13] <- "11-13 Management, Business, and Financial Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 15] <- "15-19 Computer, Engineering, and Science Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 17] <- "15-19 Computer, Engineering, and Science Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 19] <- "15-19 Computer, Engineering, and Science Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 21] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 23] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 25] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 27] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 29] <- "29 Healthcare Practitioners and Technical Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 31] <- "31-39 Service Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 33] <- "31-39 Service Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 35] <- "31-39 Service Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 37] <- "31-39 Service Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 39] <- "31-39 Service Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 41] <- "41 Sales and Related Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 43] <- "43 Office and Administrative Support Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 45] <- "45 Farming, Fishing, and Forestry Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 47] <- "47 Construction and Extraction Occupation"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 49] <- "49 Installation, Maintenance, and Repair Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 51] <- "51 Production Occupation"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 53] <- "53 Transportation and Material Moving Occupation"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 55] <- "55 Military Specific Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 11] <- "11-13 Management, Business, and Financial"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 13] <- "11-13 Management, Business, and Financial"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 15] <- "15-19 Computer, Engineering, and Science"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 17] <- "15-19 Computer, Engineering, and Science"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 19] <- "15-19 Computer, Engineering, and Science"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 21] <- "21-27 Education, Legal, Community Service, Arts, and Media"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 23] <- "21-27 Education, Legal, Community Service, Arts, and Media"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 25] <- "21-27 Education, Legal, Community Service, Arts, and Media"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 27] <- "21-27 Education, Legal, Community Service, Arts, and Media"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 29] <- "29 Healthcare Practitioners and Technical"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 31] <- "31-39 Service"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 33] <- "31-39 Service"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 35] <- "31-39 Service"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 37] <- "31-39 Service"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 39] <- "31-39 Service"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 41] <- "41 Sales and Related"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 43] <- "43 Office and Administrative Support"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 45] <- "45 Farming, Fishing, and Forestry"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 47] <- "47 Construction and Extraction"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 49] <- "49 Installation, Maintenance, and Repair"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 51] <- "51 Production"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 53] <- "53 Transportation and Material Moving"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 55] <- "55 Military Specific"
 LATech <- cbind(LATech,LO)
 
-###Build relative frequency table.
+# Build relative frequency table.
 tab <- as.data.frame(table(LATech$Int.Agg.Cat, exclude=NULL))
@@
 
-#Table for poster.
+# Table for poster.
 table <- merge(BLS,tab, by="Intermediate Aggregation Title", all=TRUE)
 
-##UGA data
+# UGA data
 UGA <- read_excel("Data/Rachel's Data from 2015.xlsx")
 UGA <- UGA[c(2,21)]
-###Edit data.
+# Edit data.
 Some individuals could be classified under O*NET, but weren't in this previous investigation.
 Keep in mind that only the first two numbers really matter, so if there are errors (and they be random) then they should wash out at the high level of the hierarchy.
-####Manually recode self-reported job titles.
-#Recode self-reports into SOC codes
+
+# Manually recode self-reported job titles.
+# Recode self-reports into SOC codes
 UGA$ONETCode[UGA$JobTitle=="campus supervisor"] <- "11-9033.00"
@@
 UGA$ONETCode[UGA$JobTitle=="Self employed"] <- "99"
-UGA$ONETCode[UGA$JobTitle=="self employed"] <- "99" ###Check this one..
+UGA$ONETCode[UGA$JobTitle=="self employed"] <- "99" 
 UGA$ONETCode[UGA$JobTitle=="I'm currently self employed"] <- "99"
@@
 names(LO) <- c("Int.Agg.Cat")
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 11] <- "11-13 Management, Business, and Financial Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 13] <- "11-13 Management, Business, and Financial Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 15] <- "15-19 Computer, Engineering, and Science Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 17] <- "15-19 Computer, Engineering, and Science Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 19] <- "15-19 Computer, Engineering, and Science Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 21] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 23] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 25] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 27] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 29] <- "29 Healthcare Practitioners and Technical Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 31] <- "31-39 Service Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 33] <- "31-39 Service Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 35] <- "31-39 Service Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 37] <- "31-39 Service Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 39] <- "31-39 Service Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 41] <- "41 Sales and Related Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 43] <- "43 Office and Administrative Support Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 45] <- "45 Farming, Fishing, and Forestry Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 47] <- "47 Construction and Extraction Occupation"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 49] <- "49 Installation, Maintenance, and Repair Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 51] <- "51 Production Occupation"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 53] <- "53 Transportation and Material Moving Occupation"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 55] <- "55 Military Specific Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 11] <- "11-13 Management, Business, and Financial"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 13] <- "11-13 Management, Business, and Financial"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 15] <- "15-19 Computer, Engineering, and Science"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 17] <- "15-19 Computer, Engineering, and Science"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 19] <- "15-19 Computer, Engineering, and Science"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 21] <- "21-27 Education, Legal, Community Service, Arts, and Media"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 23] <- "21-27 Education, Legal, Community Service, Arts, and Media"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 25] <- "21-27 Education, Legal, Community Service, Arts, and Media"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 27] <- "21-27 Education, Legal, Community Service, Arts, and Media"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 29] <- "29 Healthcare Practitioners and Technical"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 31] <- "31-39 Service"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 33] <- "31-39 Service"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 35] <- "31-39 Service"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 37] <- "31-39 Service"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 39] <- "31-39 Service"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 41] <- "41 Sales and Related"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 43] <- "43 Office and Administrative Support"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 45] <- "45 Farming, Fishing, and Forestry"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 47] <- "47 Construction and Extraction"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 49] <- "49 Installation, Maintenance, and Repair"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 51] <- "51 Production"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 53] <- "53 Transportation and Material Moving"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 55] <- "55 Military Specific"
 UGA <- cbind(UGA,LO)
@@
 tab2 <- as.data.frame(table(UGA$Int.Agg.Cat, exclude=NULL))
+###Omit self-employed individuals.
+tab2 <- tab2[c(-14),]
 tab2 <- transform(tab2, relative = prop.table(Freq))
@@
 tab2 <- merge(tab2,BLS, by="Intermediate Aggregation Title", all=TRUE) 
-
-#Chi-square function that quantifies the discrepancy between expected and observed proportions.
-chi2 <- function(x) {
-    o <- (x$n)
-    e <- (x$e)
-    n <- sum(x$n, na.rm=TRUE)
-    ((o-(e)*(n))^2)/((e)*(n))
-    }
-
-#Confidence interval formula for proportions with assymptotic intervals.
-Intervals are assymptotic because proportions cannot be less than 0 or greater than 1, which becomes problematic as proportions near 0 or 1.
-require("binom")
+```
+```{r Main Analyses, include = FALSE, warning = FALSE, message = FALSE, echo = FALSE}
+# Build table for sample 1 with confidence intervals.
 CI <- binom.confint(table$n, sum(table$n), conf.level = 0.95, methods = "exact")
@@
 table <- table[,c(1,2,3,5,4,6)]
-ch <- as.data.frame(chi2(table))
-ch <- na.omit(ch)
-names(table) <- c("Intermediate Aggregation Title","Exp(p)","n1","LCL1","Obs(p)1","UCL1")
 CI2 <- binom.confint(tab2$n, sum(tab2$n), conf.level = 0.95, methods = "exact")
@@
 tab2 <- tab2[,c(1,2,5,3,6,4)]
-ch2 <- as.data.frame(chi2(tab2))
-ch2 <- na.omit(ch2)
-tab2 <- tab2[c(-6)]
-names(tab2) <- c("Intermediate Aggregation Title","n2","LCL2","Obs(p)2","UCL2")
-#Sum chi-square values.
-sum(ch$`chi2(table)`, na.rm=TRUE)
-sum(ch2$`chi2(tab2)`, na.rm=TRUE)
-##Validate using chi-square function in r.
-#Function for differences in relative percentages. This is not printed in the tables, but could be used to help readers see the disparity between expected and observed proportions.
-f <- function(x) {
-    f   <- (x$f)
-    BLS <- (x$e)
-    (f-BLS)
+table <- cbind(table,tab2)
+table <- table[,c(1:6,8:11)]
+names(table) <- c("Intermediate Aggregation Title","Expected","n1","LL1","Obs1","UL1","n2","LL2","Obs2","UL2")
+table$`Expected` <- round(table$`Expected`,4)
+table$LL1 <- round(table$LL1,3)
+table$LL2 <- round(table$LL2,3)
+table$`Obs1` <- round(table$`Obs1`,3)
+table$`Obs2` <- round(table$`Obs2`,3)
+table$UL1 <- round(table$UL1,3)
+table$UL2 <- round(table$UL2,3)
+
+# Run chi-square test for sample 1
+x1 <- chisq.test(table$n1, p = round(table$`Expected`,3))
+# Results are significant.
+Agresti (2007) notes that standardized residuals greater than 2 are indicative of association.
+Positive residuals indicate over-representation, while a negative residual indicates a negative association.
+The error bars in the figure also capture this information.
+x1[["stdres"]]
+# Significantly over-represented: (i) 11-13 Management, Business, and Financial (6.94), (ii) 15-19 Computer, Engineering, and Science (11.97), and (iii) 21-27 Education, Legal, Community Service, Arts, and Media (8.17).
+# Conforming with expectations: (i) 29 Healthcare Practitioners and Technical (0.58), (ii) 41 Sales and Related (-2.47), (iii) 43 Office and Administrative Support (1.15), (iv) 45 Farming, Fishing, and Forestry (-0.22), and (v) 55 Military Specific (-1.37).
+# Significantly under-represented: (i) 31-39 Service (-6.33), (ii) 47 Construction and Extraction (-3.40), (iii) 49 Installation, Maintenance, and Repair (-4.51), (iv) 51 Production (-5.47), and (v) 53 Transportion and Material Moving (-5.69).
+
+# Run chi-square test for sample 2
+x2 <- chisq.test(table$n2, p = round(table$`Expected`,3))
+# Results are significant. Run post-hoc pairwise comparisons. 
+x2[["stdres"]]
+# Significantly over-represented: (i) 11-13 Management, Business, and Financial (14.76), (ii) 15-19 Computer, Engineering, and Science (8.52), and (iii) 21-27 Education, Legal, Community Service, Arts, and Media (7.30).
+# Conforming with expectations: (i) 41 Sales and Related (-1.70), (ii) 43 Office and Administrative Support (1.17), (iii) 45 Farming, Fishing, and Forestry (0.43), and (iv) 55 Military Specific (-1.76).
+# Significantly under-represented: (i) 29 Healthcare Practitioners and Technical (-3.32), (ii) 31-39 Service (-5.57), (iii) 47 Construction and Extraction (-4.72), (iv) 49 Installation, Maintenance, and Repair (-5.98), (v) 51 Production (-5.44), and (vi) 53 Transportion and Material Moving (-7.29).
+
+# Function for rounding p-values.
+myround2 <- function(x, digits = 3){
+  if (x < 10^-digits) return(paste('<', 10^-digits))
+  paste('=', myround(x, digits))
 }
-f1 <- as.data.frame(f(table))
-
-#Print chi-square APA style.
-require(devtools)
-install_github("dgromer/apa")
-require(apa)
-##Sample 1#
-Table2 <- merge(table,tab2, by="Intermediate Aggregation Title", all=TRUE)
-observed1 <- Table2$n1
-observed1 <- observed1[c(1:13)]
-expected1 <- Table2$`Exp(p)`
-expected1 <- expected1[c(1:13)]
-c1 <- chisq_apa(chisq.test(x = observed1, p = expected1, correct = TRUE))
-
-##Sample 2
-observed2 <- Table2$n2
-observed2 <- observed2[c(1:13)]
-expected2 <- Table2$`Exp(p)`
-expected2 <- expected2[c(1:13)]
-c2 <- chisq_apa(chisq.test(x = observed2, p = expected2, correct = TRUE))
-
-#Post-hoc power analysis.
-##Convert chi-squares to correlation coefficient to allow meaningful statistic.
-library(pwr)
-###Study 1
-X21 <-sum(ch$`chi2(table)`, na.rm=TRUE)
-r1 <- sqrt((X21/sum(tab$n)))
-pwr.chisq.test(w=r1,N=(sum(tab$n)),df=12,sig.level = .01)
-###Study 2
-X22 <- sum(ch2$`chi2(tab2)`, na.rm=TRUE)
-r2 <- sqrt((X21/sum(tab2$n2)))
-pwr.chisq.test(w=r2,N=(sum(tab2$n2)),df=12,sig.level = .01)
-##Conclusion - both studies possess enough power to detect the disparities that we have observed; namely that the observed distribution of occupations in MTurk does not match the distribution of the larger economy.
-###When interpreting the differences, point out the magnitude of the disparity between expectations and observations.
-
 ```
 
-##MTurk Occupational Summary Statistics
-  Participants’ data were collected from two independently conducted studies (n~1~ = `r nrow(LATech)`; n~2~ = `r nrow(UGA)`).
-In one study (n~1~ =`r nrow(LATech)`), occupational data was self-reported by participants who were asked to described their job title.
+## MTurk Occupational Summary Statistics (2015)
+
+In 2015, participants’ data were collected from two independently conducted studies (n~1~ = `r nrow(LATech)`; n~2~ = `r nrow(UGA)`).
+In sample one (n~1~ =`r nrow(LATech)`), occupational data was self-reported by participants who were asked to described their job title.
 They were then brought to ONET online and asked to retrieve the  six-digit occupational classification code that most closely corresponded to their job title.
-In the second study (n~2~ = `r nrow(UGA)`), participants again self-reported their job title.
+In the sample two (n~2~ = `r nrow(UGA)`), participants again self-reported their job title.
 However, the six-digit occupational classification codes were obtained by training research assistants to match the self-reported job titles to those in the ONET database.
 Using this data, we described the occupational diversity of each sample using relative frequencies of occupational category representation as described by Table 1.
+Data were again collected in 2017 as part of a separate investigation.
+In this sample, participants were asked to self-report their occupational data in the manner consistent with sample 1.
+```{r Table 1, results="asis"}
+papaja::apa_table(table, 
+                  caption = "Proportions of individuals sampled from each intermediate occupational category in 2015.",
+                  landscape = TRUE,
+                  note = "n = sample; 1 or 2 = sample 1 or 2, accordingly; LL = lower 95% confidence limit; Obs = observed proportion; UL = upper 95% confidence limit.")
+```
+## Analysis
 
-##Analysis
 A chi-square test of goodness-of-fit was used to test whether proportions from MTurk samples deviated from expected proportions as derived from the BLS.
 Specifically, we tested whether MTurk’s occupational diversity deviated (p < .05) from that expected if we assume the BLS population parameters generalize to the MTurk population.
-This tests the null hypothesis that the populations are identical in terms of occupational diversity.
-To facilitate interpretation of our data, we also caluculated 95% confidence intervals for our sample proportions, which allows a visual inspection of whether or not the population value is within sampling error.
+Gender, ethnicity, and education were examined in the same fashion.
+Given that multiple groups were examined, significant tests were followed by a post-hoc test.
+More specifically, we examined the standardized residuals from our chi-square tests [see @agrestiIntroductionCategoricalData2007], which in this context defines occupations that were over-represented (values > +3), under-represented (values < -3), or consistent with expectations (< or = |3|).
+To facilitate interpretation, we also calculated 95% confidence intervals for our sample proportions and plotted these values (see Figure 1).
+Age differences were examined used a one-sample t-test.
+Overall, our approach tests several distinct yet related null hypotheses; namely that the MTurk and broader US labor force contain similar (i) proportions of individuals from defined clusters of occupational areas, (ii) gender, (iii) ethnic, (iv) education, and (v) are of comparable age.
+[^p]
 
-#Results
-  Results shown in our table indicate that MTurk’s occupational frequency distribution does not consistently align with the US economy for both sample 1 ($\chi^2(12) = 368.58, p < .001$) and sample 2 ($\chi^2(12) = 486.07, p < .001$).
-Examining the 95% confidence intervals across both samples, certain occupations were consistently over- or under-represented.
-More specifically individuals sampled from MTurk occupied generally more white-collar jobs (e.g., Management, Business, and Financial Occupations; Computer, Engineering, and Science Occupations) and generally fewer blue-collar jobs (e.g., Construction and Extraction Occupations;  Installation, Maintenance, and Repair Occupations; Production Occupations) than what would be expected based on BLS data.
-For instance, 10.13% of workers in the US economy in 2015 worked in “Management, Business, and Financial Occupations.” By contrast, approximately 17% and 23% of workers from the MTurk samples fell under this classification.
-These trends were generally consistent across both study 1 and 2.
+[^p]: Analyses applied to the 2015 data were conducted in 2016.
+However, the analyses for 2017 data, more specifically the use of a chi-square goodness of fit test, were pre-registered on the Open Science Framework.
+Post-hoc testing was not pre-registered nor were the analyses regarding the remaining demographic variables.
 
-#- - - - - - - - - - - - - 
-#insert table 2 about here
-#- - - - - - - - - - - - -
+# Results from 2015
 
-##Replication Demographic Analaysis
-##Age Analysis
-```{r}
-#Age Analysis T- Test
-#Load Dataset
-require(dplyr)
-require(readxl)
+Chi-square tests indicate that MTurk’s occupational diversity does not align with expectations in both sample 1 (*X*^2^(`r x1[["parameter"]]`) = `r x1$statistic`, *p* `r myround2(x1$p.value)`) and sample 2, (*X*^2^(`r x2[["parameter"]]`)= `r x2$statistic`, *p* `r myround2(x2$p.value)`).
+Examining the standardized residuals [see @agrestiIntroductionCategoricalData2007] in this context clarifies which occupations were over-represented (values > +2), under-represented (values < -2), or consistent with expectations (< or = |2|) (see also the error bars in Figure 1).
+We use these criteria to facilitate interpretation.
+
+Across both samples, over-represented occupations included (i) 11-13 Management, Business, and Financial (study 1 = `r x1[["stdres"]][1]`; study 2 = `r x2[["stdres"]][1]`), (ii) 15-19 Computer, Engineering, and Science (study 1 = `r x1[["stdres"]][2]`; study 2 = `r x2[["stdres"]][2]`), (iii) 21-27 Education, Legal, Community Service, Arts, and Media (study 1 = `r x1[["stdres"]][3]`; study 2 = `r x2[["stdres"]][3]`).
+Occupations that were consistently under-represented included (i) 31-39 Service (study 1 = `r x1[["stdres"]][5]`; study 2 = `r x2[["stdres"]][5]`), (ii) 47 Construction and Extraction (study 1 = `r x1[["stdres"]][9]`; study 2 = `r x2[["stdres"]][9]`), (iii) 49 Installation, Maintenance, and Repair (study 1 = `r x1[["stdres"]][10]`; study 2 = `r x2[["stdres"]][10]`), (iv) 51 Production (study 1 = `r x1[["stdres"]][11]`; study 2 = `r x2[["stdres"]][11]`), and (v) 53 Transportation and Material Moving (study 1 = `r x1[["stdres"]][12]`; study 2 = `r x2[["stdres"]][12]`).
+Lastly, occupations that consistently appeared in a proportion that conformed with expectations included (i) 43 Office and Administrative Support (study 1 = `r x1[["stdres"]][7]`; study 2 = `r x2[["stdres"]][7]`), (ii) 45 Farming, Fishing, and Forestry (study 1 = `r x1[["stdres"]][8]`; study 2 = `r x2[["stdres"]][8]`), and (iii) 55 Military Specific (study 1 = `r x1[["stdres"]][13]`; study 2 = `r x2[["stdres"]][13]`).
+Overall, these results suggests that the MTurk population contains a disproportionate share of white-collar occupations relative to blue-collar occupations.
+
+It is worth pointing out that conclusions regarding two occupational categories are inconsistent across our two samples.
+For occupational group 29 (Healthcare Practitioners and Technical), sample one suggests that these occupations are represented as expected (study 1 = `r x1[["stdres"]][4]`).
+However, this group was under-represented in sample 2 (study 2 = `r x2[["stdres"]][3]`).
+Given that the confidence intervals from our two samples overlap (albeit very weakly), we  tentatively conclude that this group is adequately represented.
+For occupational category 41 (Sales and Related), sample one suggested under-representation (study 1 = `r x1[["stdres"]][6]`) whereas sample two suggests that these occupations are represented as expected (study 2 = `r x2[["stdres"]][6]`).
+Again, as these confidence intervals overlap, we offer a tentative conclusion that this population is represented as expected.
+
+```{r, echo = FALSE, warning = FALSE, fig.cap = "Comparing the occupational diversity of two MTurk samples with expecations based on the Bureau of Labor Statistics"}
+# Bar Plot with error bars
+Values <- c(table[1:13,2], table[1:13, 5], table[1:13, 9])
+Group <- c("BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2")
+Occupations <- c(table[1:13, 1])
+Occ_Nums <- sapply(strsplit(Occupations, " "), "[[", 1)
+barplot_data <- data.frame(as.character(Values), as.character(Occupations),as.character(Group))
+names(barplot_data) <- c("Frequency", "Occupations","Group")
+dodge <- position_dodge(width = .9)
+
+# Define Error Bar limits.
+upperB <- c(0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
+upperM <- c(table[1:13, 6], table[1:13, 10])
+upper <-c(upperB, upperM)
+lowerB <- c(0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
+lowerM <- c(table[1:13, 4], table[1:13,8])
+lower <- c(lowerB, lowerM)
+se <- data.frame(upper, lower)
+
+# Merge data
+df <- cbind(se,barplot_data)
+
+# Plot data
+ggplot(barplot_data, aes(Occupations, Values, fill = Group, ymax = upper, ymin = lower)) + 
+  geom_bar(stat="identity", position = "dodge", width = 0.7) +
+  geom_bar(stat="identity", position = "dodge", 
+                colour = "black", width = 0.7, 
+                show.legend = TRUE) +
+  scale_y_continuous(breaks = seq(0, 0.30, 0.1), 
+                limits = c(0, 0.30), 
+                expand = c(0, 0)) +
+  scale_fill_manual(name = "Groups" , 
+                 values = c('grey30', 'grey60', 'grey 80'), 
+                 labels = c("BLS 2015", "Sample 1", "Sample 2")) +
+  geom_errorbar(position=position_dodge(width=0.7), 
+                     width=0.0, size=0.5, color="black") +
+  #ggtitle("Occupational Diversity of MTurk") +
+  labs(x = element_blank(), y = "Proportions") +
+  theme(legend.position = c(.8,.8), 
+        #plot.title = element_text(hjust = 0), 
+        text=element_text(family="serif")) +
+  coord_flip()
+```
+
+# Results from 2017
+
+```{r Exploratory Analysis with Demographics, echo = FALSE, include = FALSE}
+# Define Age data
 age_demo <- read_excel("age_demo.xlsx")
 
-#Define population mean. In this case it was already calculated in the dataset. 
+# Define population mean. In this case it was already calculated in the dataset. 
 pop_mean <- as.numeric(age_demo[6 , 10])
 
-#Define sample mean
+# Define sample 
 MTurk17 <- read_excel("2017 Data.xls")
-samp_mean <- as.numeric(MTurk17 %>%
-  summarise(MTurk_age = mean(What.is.your.age., na.rm = TRUE)))
 
-#Not able to get population standard deviation. Estimated using sample standard deviation.
-samp_sd <- as.numeric(MTurk17 %>%
-  summarise(sd_age = sd(What.is.your.age., na.rm = TRUE)))
+# Run one-samplet test and estimate Cohen's D.
+t <- oneSampleTTest(x = MTurk17$What.is.your.age., mu = pop_mean)
+tvalue <- t$t.statistic %>%
+  formatC(digits = 2, format = "f")
+if (t$p.value < 0.0005) {
+  pvalue <- " < 0.001"
+} else {
+  if (t$p.value < 0.005)
+      pvalue <- paste0(" = ",t$p.value %>% formatC(digits = 3, format = "f"))
+    else 
+      pvalue <- paste0(" = ",t$p.value %>% formatC(digits = 2, format = "f")) 
+  }
+df <- t$df
+d <- round((t$effect.size),2)
+# MTurk participants are significantly younger than labor force at large. Moderate effect according to Cohen's criteria.
 
-#Define sample size
-n <- as.numeric(667)
-
-#Run t test.
-t_value <- (samp_mean - pop_mean)/(samp_sd/sqrt(n))
-t_value
-
-#So MTurk is much younger than the population on average. We need to convert this to an effect size (Cohen's D). 
-```
-
-##Gender Analysis
-```{r}
-##Gender Analysis
+# Define Gender data
 BLS_data <- read_excel("employment_demo.xlsx")
 
-#Get BLS gender data (expected value)
+# Get BLS gender data (expected value)
 BLS_women <- as.numeric(BLS_data[7,3])/100
-BLS_men <- 1.000 - BLS_women
+BLS_other <- 1.000 - BLS_women
+BLS_gender <- c(BLS_women, BLS_other)
 
-BLS_gender <- c(BLS_women, BLS_men, 0.0)
-
-#Get MTurk gender data (observed value)
+# Get MTurk gender data (observed value)
+MTurk17$What.is.your.gender.[MTurk17$What.is.your.gender.=="Male"] <- "Other"
 MTurk_gender <- MTurk17 %>%
@@
 
-#Define confidence intervals
-require(binom)
+# Define confidence intervals
 gCI <- binom.confint(x = MTurk_gender$n, n = sum(MTurk_gender$n), conf.level = 0.95, methods = "exact")
@@
 
-#Build Gender table with gender, expected value, n, LL, observed, UL
+# Build Gender table with gender, expected value, n, LL, observed, UL
 gender_table <- cbind(MTurk_gender, gCI, BLS_gender)
 names(gender_table) <- c("gender", "n", "o", "LL_g", "UL_g", "e")
-gender_table <- gender_table[ 1, c(1, 2, 3, 4, 6, 5)]
-View(gender_table)
+gender_table <- gender_table[ , c(1, 6, 2, 4, 3, 5)]
 
-#Gender chi square test
+# Run chi-square test for gender
+x3 <- chisq.test(gender_table$n, p = round(gender_table$e,3))
 
-chi2 <- function(x) {
-  o <- (x$n)
-  e <- (x$e)
-  n <- sum(x$n, na.rm=TRUE)
-  ((o-(e)*(n))^2)/((e)*(n))
-}
+# Result is significant. So it appears that MTurk is largely dominated by females. We need to have an effect size describing this phenomena (e.g., a likelihood ratio).
 
-gender_ch2 <- as.data.frame(chi2(gender_table))
-names(gender_ch2) <- c("chi2")
-row.names(gender_ch2) <- c("female")
-gender_ch2 <- na.omit(gender_ch2)
-View(gender_ch2)
-
-#Sum chi-square values.
-sum(gender_ch2$chi2, na.rm=TRUE)
-
-#So it appears that MTurk is largely dominated by females. We need to have an effect size describing this phenomena (e.g., a likelihood ratio).
-```
-
-##Ethnicity Analysis
-```{r}
-#Ethnicity Analysis 
-#Define obs_eth
+# Get BLS ethnicity data
 BLS_cauc <- as.numeric(BLS_data[7, 4])/100
@@
 
-sum(BLS_eth)
+sum(BLS_eth) # Note: Estimates for the above race groups (White, Black or African American, and Asian) do not sum to (100) because data are not presented for all races.
+Persons whose ethnicity is identified as Hispanic or Latino may be of any race.
+We decided to omit the Hispanic category and compute an "other" category, which is the residual of the other racial categories.
+BLS_other <- 1.000 - sum(BLS_cauc, BLS_AfAm, BLS_Asn)
+BLS_eth <- c(BLS_AfAm, BLS_Asn, BLS_cauc, BLS_other)
 
-#Get MTurk ethnicity data
+#Get MTurk ethnicity data (observed value)
+MTurk17$With.which.ethnicity.do.you.most.identify.[MTurk17$With.which.ethnicity.do.you.most.identify.=="Hispanic"] <- "Other"
+MTurk17$With.which.ethnicity.do.you.most.identify.[MTurk17$With.which.ethnicity.do.you.most.identify.=="Indian"] <- "Other"
+MTurk17$With.which.ethnicity.do.you.most.identify.[MTurk17$With.which.ethnicity.do.you.most.identify.=="Native American"] <- "Other"
+MTurk17$With.which.ethnicity.do.you.most.identify.[MTurk17$With.which.ethnicity.do.you.most.identify.=="Other:"] <- "Other"
 MTurk_eth <- MTurk17 %>%
   count(MTurk17$With.which.ethnicity.do.you.most.identify.)
-MTurk_eth <- MTurk_eth[c(1:4), ]
 
 #Define confidence intervals 
-ethCI <- binom.confint(x = MTurk_eth$n, n = sum(MTurk_eth$n), conf.level = 0/95, methods = "exact")
+ethCI <- binom.confint(x = MTurk_eth$n, n = sum(MTurk_eth$n), conf.level = 0.95, methods = "exact")
 ethCI <- ethCI[ , 4:6]
@@
 names(ethnicity_table) <- c("ethnicity", "n", "o", "LL_eth", "UL_eth", "e")
-eth_table <- ethnicity_table[1:4 , c(1, 6, 2, 4, 3, 5)]
+ethnicity_table <- ethnicity_table[ , c(1, 6, 2, 4, 3, 5)]
 
-#Ethnicity chi squared test
-eth_ch2 <- as.data.frame(chi2(eth_table))
-names(eth_ch2) <- c("chi2")
-row.names(eth_ch2) <- c("African American", "Asian", "Caucasian", "Hispanic")
-eth_ch2 <- na.omit(eth_ch2)
+# Ethnicity chi squared test
+x4 <- chisq.test(ethnicity_table$n, p = round(ethnicity_table$e,3))
+# Result is significant. MTurk is under-represented by African Americans, Asians, and other ethnicities. However, it does appear to be slightly over-represented by Caucasians.
 
-#Sum chi-square values.
-sum(eth_ch2$chi2, na.rm=TRUE)
-```
-
-###Education Analysis 
-```{r}
-#Education Analysis 
-#Clean BLS Data. Get totals.  
+# Education Analysis 
+# Clean BLS Data. Get totals.  
 BLS_education_original <- read_excel("education_demo.xlsx")
@@
 
-#Combine categories as necessary. Get proportions.  
+# Combine categories as necessary. Get proportions.  
 highschool_ged <- c(as.numeric(BLS_education$`High school graduates, no college(1)`) + as.numeric(BLS_education$`Some college, no degree`))
@@
 
-#Function to find proportion for each iteration of the vector. 
+# Function to find proportion for each iteration of the vector. 
 e_prop <- function(x) {
@@
 
-#Use vapply and the above function to get expected proportions from BLS data
+# Use vapply and the above function to get expected proportions from BLS data
 BLS_edu <- sapply(BLS_education, e_prop)
 
-#Clean MTurk Data
+# Clean MTurk Data
 MTurk_education <- MTurk17 %>%
@@
 
-#Define confidence intervals 
-eduCI <- binom.confint(x = MTurk_edu$n, n = sum(MTurk_edu$n), conf.level = 0/95, methods = "exact")
+# Define confidence intervals 
+eduCI <- binom.confint(x = MTurk_edu$n, n = sum(MTurk_edu$n), conf.level = 0.95, methods = "exact")
 eduCI <- eduCI[ , 4:6]
@@
 #Education chi squared test
-edu_ch2 <- as.data.frame(chi2(education_table))
-names(edu_ch2) <- c("chi2")
-row.names(edu_ch2) <- c("high school/GED" , "2 year degree", "4 year degree", "advanced degree")
-edu_ch2 <- na.omit(edu_ch2)
-
-#Sum chi-square values.
-sum(edu_ch2$chi2, na.rm=TRUE)
+x5 <- chisq.test(education_table$n, p = round(education_table$e,3))
+# Result is  significant. MTurk contains an unexpected proportion of education.
 ```
 
-#Discussion
+## Exploratory Analyses of Other Demographics
+
+The average worker in 2017 was `r t[["mu"]]` years of age, which was significantly older than the average MTurk worker (M = `r round(t[["mean"]],2)`, SD = `r round(t[["sd"]],2)`, *t*(`r df`) = `r tvalue`, *p* `r pvalue`, *d* = `r d`).
+
+With regard to gender, the BLS provides a summary statistic only for the proportion of the labor force that identifies with the female gender, which in 2017 was `r percent(BLS_women)`.
+The difference compared to our MTurk sample, `r percent(gender_table$o[1])` of which were women, was significant `r chisq_apa(x3)` and suggests that MTurk is over-represented by females (standardized residual = `r  round(x3[["stdres"]][1],2)`).
+
+With regard to ethnicity, as the BLS provides estimates for race groups that do not sum to 100% (because subgroups identified as Hispanic or Latino may also be of any race), we elected to examine only the published proportions for Caucasians, African Americans, and Asians (an "other" category was created as the residual of these three categories).
+BLS summary statistics suggest that the labor force was composed of approximately `r percent(BLS_cauc)` Caucasians, `r percent(BLS_AfAm)` African Americans, and `r percent(BLS_Asn)` Asians.
+This distribution deviated significantly from our our MTurk sample `r chisq_apa(x4)`.
+Post-hoc testing revealed that African Americans (`r percent(ethnicity_table$o[1])`) were significantly under-represented  (standardized residual = `r round(x4[["stdres"]][1],2)`).
+Additionally, the "other" category `r percent(ethnicity_table$o[4])` was over-represented by MTurk (standardized residual = `r round(x4[["stdres"]][4],2)`).
+This overall pattern suggests that MTurk may over-represent historically disadvantaged populations, at least in the US.
+
+With regard to education, after aligning the measures used by the BLS with that used in our study, we found a significant overall deviation `r chisq_apa(x5)` from expectations.
+Specifically, the 2-year degree (MTurk = `r percent(education_table$o[1])`; BLS = `r percent(education_table$e[1])`) was under-represented by the MTurk population (standardized residual = `r round(x5[["stdres"]][1])`).
+By contrast, the remaining education levels were over-represented (4-year degree: MTurk = `r percent(education_table$o[2])`; BLS = `r percent(education_table$e[2])`; high school/GED: MTurk = `r percent(education_table$o[3])`; BLS = `r percent(education_table$e[3])`; advanced degree: MTurk =  `r percent(education_table$o[4])`; BLS = `r percent(education_table$e[4])`), as indicated by standardized residuals (`r round(x5[["stdres"]][2])`, `r round(x5[["stdres"]][3])`, `r round(x5[["stdres"]][4])`).
+If we view the over-representation of high school/GED holders as more in-line with expectations than our cutoffs indicate, then we can see a clearer over-representation of more highly educated workers on MTurk (i.e., 4-year degree and advanced degree holders).
+
+# Discussion
+
 What started our investigation was a simple research question: is the occupational diversity of the MTurk population representative of the broader US population?
-Our data suggest that the answer is not consistently so: certain occupations are over-represented, some fall within expectations, and still others are under-represented.
-Thus, OB researchers using convenient sampling procedures that draw on the MTurk population should consider whether occupational features might play a role in their investigation, which is point that we will elaborate upon in greater detail.
-Simply put, our results suggest that MTurk’s (US) occupational diversity does not align with the broader US economy.
+While our data suggest that the answer is not consistently so, it is nevertheless striking how the diversity of MTurk nevertheless mirrors that of the broader labor force (albeit, imperfectly).
+Though MTurk over-represents certain white-collar occupations and under-represent blue collar occupations, the overall pattern does mirror the broader labor force.
+This is important because of questions concerning the work settings from which these individuals are sampled.
+Nevertheless, while sampling from MTurk does give researchers an useful cross-section of labor force, this cross-section is not ideal and so adjustments may be needed [e.g., respondent weighting; @simonsCommonMisBeliefs2012], particularly when drawing inferences to the larger labor force.
 
-#Recommendations for Researchers Using MTurk
-  Given that OB researchers will likely wish to continue using MTurk as a means of gathering diverse, convenient, and low-cost survey sample data, researchers should consider how differences in the occupational diversity observed amongst MTurk workers relative to the US population might impinge upon the generalizability of their findings (@newman2015external).
+## Recommendations for Researchers Using MTurk
+
+Given that organizational researchers will likely wish to continue using MTurk as a means of gathering diverse, convenient, and low-cost survey sample data, researchers should consider how differences in the occupational diversity observed among MTurk workers relative to the US population might impinge upon the generalizability of their findings [@newmanExternalValidityMultiorganization2015].
 Specifically, given the over-representation of workers from (1) Management, Business, and Financial, (2) Computer, Engineering, and Science, and (3) Education, Legal, Community Service, Arts, and Media occupations, we might safely assume that many of our findings from MTurk will generalize across jobs classified under these broader over-represented occupational categories.
 However, as many occupations were under-represented [e.g., (1) Service, (2) Construction and Extraction, (3) Installation, Maintenance, and Repair, (4) Production; and (5) Transportation and Material Moving], questions may arise as to whether findings will generalize to jobs falling under these broad classifications.
+
 To address this issue, researchers should consider capturing occupational data and modeling theoretically derived moderators.
-Person-environment (P-E) fit theories should help guide researchers in proposing how certain occupational groupings might influence individual-level relationships, lending to more nuanced and contextualized results (@how2009dr).
-Further, O*NET might be useful in this regard as it provides researchers a means for quantifying key occupational differences (e.g., level of competition requirements, social skills requirements) and thereby testing P-E fit hypotheses pertaining to occupational group differences (see @judge2015person).
+Person-environment (P-E) fit theories should help guide researchers in proposing how certain occupational groupings might influence individual-level relationships, lending to more nuanced and contextualized results [@meadeDrStrangeLOVEHow2009].
+Further, O*NET might be useful in this regard as it provides researchers a means for quantifying key occupational differences (e.g., level of competition requirements, social skills requirements) and thereby testing P-E fit hypotheses pertaining to occupational group differences [see @judgePersonSituationDebate2015].
 
-##Limitations and Future Research
+## Limitations and Future Research
+
 One key limitation is that we assumed that O*NET’s classification system perfectly captured all occupations during 2015.
@@
 Still, the consistency of our findings should be considered by future OB/HR researchers hoping to draw on MTurk for their research with the hopes of generalizing to the larger (or a specific) working US population.
-Additionally, as our studies were conducted in the US, it remains unclear how other MTurk populations might reflect (however imperfectly) their respective broader economy.
+Additionally, as our studies were conducted in the US, it remains unclear how other MTurk populations might reflect (however imperfectly) their respective broader labor force.
 Future larger scale studies should also consider lower levels of BLS occupational classification to examine the extent to which narrower occupations might not be represented by MTurk.
-Lastly, examining diversity in other respects (age, racio-ethnic, income, education, etc.) should also be considered.
+Lastly, examining diversity in other respects (age, ethnic, income, education, etc.) should also be considered.
 Though MTurk offers a practically feasible method of attaining high quality data, future research will be needed to understand the limitations of this tool.
 
-  Given that our data were gathered and analyzed in 2015, it might be insightful to have our procedures replicated annually to examine how the demographics of MTurk, specifically occupational characteristics, change over time, especially as access to technology becomes even easier and more commonplace.
-Thus, we encourage researchers to continue examining the occupational diversity of MTurk relative to the US economy.
-We also encourage researchers to consider novel ways of approximating the occupational diversity of both the US economy and MTurk because the currently existing taxonomies that we have used (i.e., BLS-based) probably do not capture all occupations.
+Given that our data were gathered and analyzed in 2015 and 2017, it might be insightful to have our procedures replicated annually to examine how the demographics of MTurk, specifically occupational characteristics, change over time, especially as access to technology becomes even easier and more commonplace.
+Thus, we encourage researchers to continue examining the occupational diversity of MTurk relative to the US labor force.
+We also encourage researchers to consider novel ways of approximating the occupational diversity of both the US labor force and MTurk because the currently existing taxonomies that we have used (i.e., BLS-based) probably do not capture all occupations.
 Lastly, our results raise a new and interesting research question: Why might MTurk possess the occupational diversity makeup that it does (i.e., why are some occupations over-represented while others are under-represented)?
 Similarly, what factors (e.g., access to technology, interest in psychology) might make it easier for workers coming from certain occupations to participate in OB studies hosted on MTurk?
-Answering these questions might unearth more constraints that impinge on the findings of OB studies using MTurk.
-
-#Conclusion
-  We called into question the diversity of MTurk as a key strength and suggested one key area where diversity may be lacking: occupational diversity.
-Our results suggest that, compared to the broader US population, MTurk is not as diverse, both over- and underrepresenting certain occupations.
-Future research drawing on MTurk should consider how occupational differences might be theoretically relevant and incorporate these effects in analyses using MTurk sample data to help overcoming these shortcomings.
+Answering these questions might unearth more constraints that impinge on the findings of occupational studies using MTurk.
 
@@
 # References
-```{r}
-require(papaja)
-r_refs(file = "/Users/ccasti02/Documents/Research/Research on MTurk/MTurk's Occupational Diversity/r-references.bib")
-my_citation <- cite_r(file = "/Users/ccasti02/Documents/Research/Research on MTurk/MTurk's Occupational Diversity/r-references.bib")
 
+```{r Citations, warning = FALSE, echo = FALSE}
+r_refs(file = "r-references.bib")
 ```
+
 \setlength{\parindent}{-0.5in}
 \setlength{\leftskip}{0.5in}
-=======

### 2018-11-27 Manuscript.Rmd

--- 2018-10-04 Manuscript.Rmd
@@
 #- - - - - - - - - - - - - 
+##Barplot 1
+```{r}
+#Bar Plot with error bars
+require(ggplot2)
+Values <- c(Table2[1:13, 5], Table2[1:13, 2])
+Group <- c("MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS")
+Occupations <- c(Table2[1:13, 1], Table2[1:13, 1])
+Occ_Nums <- sapply(strsplit(Occupations, " "), "[[", 1)
+barplot_data <- data.frame(as.character(Values), as.character(Occ_Nums),as.character(Group))
+names(barplot_data) <- c("Frequency", "Occupations","Group")
+dodge <- position_dodge(width = .9)
+
+#Define Error Bar limits.
+upperM <- as.vector(Table2[1:13, 6])
+upperB <- c(0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
+upper <-c(upperM, upperB)
+
+lowerM <- as.vector(Table2[1:13, 6])
+lowerB <- c(0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
+lower <- c(lowerM, lowerB)
+
+se <- data.frame(upper, lower)
+limits <- aes(ymax = se$upper, ymin = se$lower)
+
+require(ggplot2)
+ggplot(barplot_data, aes(Occ_Nums, Values, fill = Group)) + 
+  geom_errorbar(limits, position = dodge,
+                width = 0.10, size = 1.0) +
+  geom_col(position = dodge)  +
+  ggtitle("MTurk's Occupational Diveristy with Error Bars") +
+  labs(x = "Occupation", y = "Frequency") +
+  theme(legend.position = "top", plot.title = element_text(hjust = 0.5), 
+        text=element_text(family="serif"))+
+  coord_flip()
+```
+##2015 Demographic Analysis 
+##Study 1 Age
+```{r}
+#Chris's 2015 age analysis 
+require(dplyr)
+
+#Load BLS Data
+BLS_age_15 <- read_excel("BLS.Age.2015.xlsx")
+
+#Define population mean. In this case it was already calculated in the dataset. 
+pop_mean_15 <- as.numeric(BLS_age_15[6, 10])
+
+#Define sample mean
+samp_mean_15 <- as.numeric(MTurk15 %>%
+                        summarise(MTurk_age = mean(age, na.rm = TRUE)))
+
+#Sample standard deviation.
+samp_sd_15 <- as.numeric(MTurk15 %>%
+                        summarise(sd_age = sd(age, na.rm = TRUE)))
+
+#Define sample size
+n_15 <- nrow(MTurk15)
+
+#Run t test.
+t_value_15 <- (samp_mean_15 - pop_mean_15)/(samp_sd_15/sqrt(n_15))
+
+```
+
+##Study 1 Gender
+```{r}
+#Gender Analysis 2015
+library(readxl)
+BLS_2015_doc <- read_excel("bls.gender.2015.xlsx")
+
+#Get BLS gender data (expected value)
+BLS_gender_15_data <- BLS_2015_doc[87:93,c(1,8,22, 28)]
+BLS_men_15 <- as.numeric(BLS_gender_15_data[6,3])/as.numeric(BLS_gender_15_data[5,3])
+BLS_women_15 <- as.numeric(BLS_gender_15_data[7,3])/as.numeric(BLS_gender_15_data[5,3])
+BLS_gender_15 <- c(BLS_women_15,BLS_men_15)
+names(BLS_gender_15) <- c("Female", "Male")
+
+#Get MTurk gender data (observed value)
+require(dplyr)
+MTurk_gender_15 <- MTurk15 %>%
+  count(gender)
+MTurk_gender_15 <- MTurk_gender_15[2:3,]
+
+#Define confidence intervals
+require(binom)
+gCI_15 <- binom.confint(x = MTurk_gender_15$n, n = sum(MTurk_gender_15$n), conf.level = 0.95, methods = "exact")
+gCI_15 <- gCI_15[ ,4:6]
+
+#Build Gender table with gender, expected value, n, LL, observed, UL
+gender_table_15 <- cbind(MTurk_gender_15, gCI_15, BLS_gender_15)
+names(gender_table_15) <- c("gender", "n", "o", "LL_g", "UL_g", "e")
+gender_table_15 <- gender_table_15[, c(1, 3, 2, 4, 6, 5)]
+
+#Gender chi square test
+
+chi2 <- function(x) {
+  o <- (x$n)
+  e <- (x$e)
+  n <- sum(x$n, na.rm=TRUE)
+  ((o-(e)*(n))^2)/((e)*(n))
+}
+
+gender_ch2_15 <- as.data.frame(chi2(gender_table_15))
+names(gender_ch2_15) <- c("chi2")
+gender_ch2_15 <- na.omit(gender_ch2_15)
+
+#Sum chi-square values.
+sum(gender_ch2_15$chi2, na.rm=TRUE)
+```
+
+##Study 1 Ethnicity
+```{r}
+#Ethnicity Analysis 
+#Define obs_eth
+BLS_ethnicity_15_data <- BLS_2015_doc[c(94, 97, 100), (c(1, 22))]
+names(BLS_ethnicity_15_data) <- c("ethnicity", "population")
+BLS_ethnicity_15_data$population <- as.numeric(BLS_ethnicity_15_data$population)
+BLS15_eth_prop <- sapply(BLS_ethnicity_15_data$population, function(x) {x/sum(BLS_ethnicity_15_data$population)})
+names(BLS15_eth_prop) <- c(BLS_ethnicity_15_data$ethnicity)
+
+#Get MTurk ethnicity data
+MTurk_eth_15 <- count(MTurk15, ethnicity)
+
+MTurk_eth_15 <- MTurk_eth_15[c(4, 2, 3), ]
+
+#Define confidence intervals 
+ethCI_15 <- binom.confint(x = MTurk_eth_15$n, n = sum(MTurk_eth_15$n), conf.level = 0/95, methods = "exact")
+ethCI_15 <- ethCI_15[ , 4:6]
+
+#Build Ethnicity table 
+ethnicity_table_15 <- cbind(MTurk_eth_15, ethCI_15, BLS15_eth_prop)
+names(ethnicity_table_15) <- c("ethnicity", "n", "o", "LL", "UL", "e")
+eth_table_15 <- ethnicity_table_15[ , c(1, 6, 2, 4, 3, 5)]
+
+#Ethnicity chi squared test
+eth_ch2_15 <- as.data.frame(chi2(eth_table_15))
+names(eth_ch2_15) <- c("chi2")
+row.names(eth_ch2_15) <- c(BLS_ethnicity_15_data$ethnicity)
+eth_ch2_15 <- na.omit(eth_ch2_15)
+
+#Sum chi-square values.
+sum(eth_ch2_15$chi2, na.rm=TRUE)
+```
+
+##Study 1 Education Level 
+```{r}
+#2015 Education Analysis 
+#Clean BLS Data. Data is split between men and women, so the first step is to total these values for the civilian noninstitutionalize population. 
+BLS_education_15_data <- BLS_2015_doc[587:610,c(1,13,24,37,51,61,67)]
+BLS_education_15_total <- as.numeric(BLS_education_15_data[4,2]) + as.numeric(BLS_education_15_data[20,2])
+
+#Combine categories as necessary.Add men and women together.
+less_than_highschoo_15 <- as.numeric(BLS_education_15_data[4,3]) + as.numeric(BLS_education_15_data[20,3])
+
+#high school/ged includes "some college, no degree"
+highschool_ged_15 <- as.numeric(BLS_education_15_data[4,4]) + as.numeric(BLS_education_15_data[20,4]) + as.numeric(BLS_education_15_data[4,5]) + as.numeric(BLS_education_15_data[20,5])
+
+two_year_deg_15 <- as.numeric(BLS_education_15_data[4,6]) + as.numeric(BLS_education_15_data[20,6])
+
+bachelors_or_higher_15 <- as.numeric(BLS_education_15_data[4,7]) + as.numeric(BLS_education_15_data[20,7])
+
+BLS_education_15 <- c(less_than_highschoo_15,highschool_ged_15, two_year_deg_15, bachelors_or_higher_15)
+names(BLS_education_15) <- c("less than high school degree", "high school/GED" , "2 year degree", "bachelor's or more")
+
+#Use vapply and the anonomous function to get expected proportions from BLS data
+BLS_edu_15 <- sapply(BLS_education_15, function(x){x/BLS_education_15_total})
+
+#Clean MTurk Data
+MTurk_education_15 <- MTurk15 %>%
+  count(MTurk15$`education level`)
+colnames(MTurk_education_15) <- c("education level", "n")
+advanced_deg_15 <- as.numeric(MTurk_education_15[6,2]) + as.numeric(MTurk_education_15[8,2]) + as.numeric(MTurk_education_15[3,2])
+no_highschool_dip <- as.numeric(MTurk_education_15[5,2]) + as.numeric(MTurk_education_15[7,2])
+MTurk_education_15 <- rbind(no_highschool_dip, MTurk_education_15, advanced_deg_15)
+MTurk_education_15[10,1] <- c("bachelor's or higher")
+MTurk_education_15[1,1] <- c("less than a high school diploma")
+MTurk_edu_15 <- MTurk_education_15[c(-2, -4, -6, -7, -8, -9), ]
+MTurk_edu_15 <- MTurk_edu_15[c(1, 3, 2, 4), ]
+
+#Define confidence intervals 
+eduCI_15 <- binom.confint(x = MTurk_edu_15$n, n = sum(MTurk_edu_15$n), conf.level = 0/95, methods = "exact")
+eduCI_15 <- eduCI_15[ , 4:6]
+
+#Build Education table 
+education_table_15 <- cbind(MTurk_edu_15, eduCI_15, BLS_edu_15)
+names(education_table_15) <- c("education level", "n", "o", "LL_eth", "UL_eth", "e")
+education_table_15 <- education_table_15[ , c(1, 6, 2, 4, 3, 5)]
+
+#Education chi squared test
+edu_ch2_15 <- as.data.frame(chi2(education_table_15))
+names(edu_ch2_15) <- c("chi2")
+row.names(edu_ch2_15) <- c("less than a highschool diploma","high school/GED" , "2 year degree", "bachelor's or higher")
+edu_ch2_15 <- na.omit(edu_ch2_15)
+
+#Sum chi-square values.
+sum(edu_ch2_15$chi2, na.rm=TRUE)
+```
+
+##Study 2 Age
+```{r}
+#Rachel's 2015 Demographic Analysis 
+library(readxl)
+MTurk15_R <- read_excel("Rachel's Data from 2015.xlsx")
+
+#packages to clean data for demogrphics
+library(stringr)
+install.packages(tidyr)
+library(tidyr)
+
+#Rachel's age analysis 
+#Load BLS Data
+BLS_age_15 <- read_excel("~/Desktop/BLS.Age.2015.xlsx")
+
+#Define population mean. In this case it was already calculated in the dataset. 
+pop_mean_15 <- as.numeric(BLS_age_15[6, 10])
+
+#Define sample mean
+samp_mean_15_R <- as.numeric(MTurk15_R %>% 
+                             summarise(MTurk_age = mean(Age, na.rm = TRUE)))
+
+#Sample standard deviation.
+samp_sd_15_R <- as.numeric(MTurk15_R %>% 
+                           summarise(sd_age = sd(Age, na.rm = TRUE)))
+
+#Define sample size
+n_15_R <- nrow(MTurk15_R)
+
+#Run t test.
+t_value_15_R <- (samp_mean_15_R - pop_mean_15)/(samp_sd_15_R/sqrt(n_15_R))
+```
+
+##Study 2 Gender
+```{r}
+#Rachel's gender analysis
+#clean data
+MTurk15_R$Gender <- str_replace(MTurk15_R$Gender, "1", "male")
+MTurk15_R$Gender <- str_replace(MTurk15_R$Gender, "2", "female")
+
+#get frequencies
+MTurk_gender_15_R <- MTurk15_R %>% 
+  count(Gender)
+MTurk_gender_15_R <- MTurk_gender_15_R[1:2,]
+
+#Define confidence intervals
+require(binom)
+gCI_15_R <- binom.confint(x = MTurk_gender_15_R$n, n = sum(MTurk_gender_15_R$n), conf.level = 0.95, methods = "exact")
+gCI_15_R <- gCI_15_R[ ,4:6]
+
+#Build Gender table with gender, expected value, n, LL, observed, UL
+gender_table_15_R <- cbind(MTurk_gender_15_R, gCI_15_R, BLS_gender_15)
+names(gender_table_15_R) <- c("gender", "n", "o", "LL_g", "UL_g", "e")
+gender_table_15_R <- gender_table_15_R[, c(1, 3, 2, 4, 6, 5)]
+
+#Gender chi square test
+gender_ch2_15_R <- as.data.frame(chi2(gender_table_15_R))
+names(gender_ch2_15_R) <- c("chi2")
+gender_ch2_15_R <- na.omit(gender_ch2_15_R)
+
+#Sum chi-square values.
+sum(gender_ch2_15_R$chi2, na.rm=TRUE)
+
+```
+
+##Study 2 Ethnicity
+```{r}
+#Rachel's ethnicity analysis
+MTurk15_R_white <- length(which(MTurk15_R$White == 1))
+MTurk15_R_AfnAmn <- length(which(MTurk15_R$AfnAmn == 1))
+MTurk15_R_AsnPI <- length(which(MTurk15_R$AsnPI == 1))
+
+MTurk15_R_eth <- as.data.frame(c(MTurk15_R_white, MTurk15_R_AfnAmn, MTurk15_R_AsnPI))
+MTurk15_R_eth <- cbind(BLS_ethnicity_15_data$ethnicity, MTurk15_R_eth)
+colnames(MTurk15_R_eth) <- c("ethnicity", "n")
+MTurk15_R_eth_tot <- MTurk15_R_white + MTurk15_R_AfnAmn + MTurk15_R_AsnPI
+
+#Get proportions for ethnicities
+MTurk15_R_eth <- MTurk15_R_eth %>% 
+  mutate(prop = sapply(MTurk15_R_eth$n, function(x) {x/MTurk15_R_eth_tot}))
+
+#Define confidence intervals 
+ethCI_15_R <- binom.confint(x = MTurk15_R_eth$n, n = sum(MTurk15_R_eth$n), conf.level = 0/95, methods = "exact")
+ethCI_15_R <- ethCI_15_R[ , 4:6]
+
+#Build Ethnicity table 
+ethnicity_table_15_R <- cbind(MTurk15_R_eth[1:2], ethCI_15_R, BLS15_eth_prop)
+names(ethnicity_table_15_R) <- c("ethnicity", "n", "o", "LL", "UL", "e")
+eth_table_15_R <- ethnicity_table_15_R[1:3, c(1, 6, 2, 4, 3, 5)]
+
+#Ethnicity chi squared test
+eth_ch2_15_R <- as.data.frame(chi2(eth_table_15_R))
+names(eth_ch2_15_R) <- c("chi2")
+row.names(eth_ch2_15_R) <- c(BLS_ethnicity_15_data$ethnicity)
+eth_ch2_15_R <- na.omit(eth_ch2_15_R)
+
+#Sum chi-square values.
+sum(eth_ch2_15_R$chi2, na.rm=TRUE)
+```
+
+##Study 2 Education Level 
+```{r}
+#Rachel's education level
+MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "1", "Less than high school")
+MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "2", "High school/GED")
+MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "3", "Some college")
+MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "4", "2 year deg")
+MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "5", "4 year deg")
+MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "6", "Master's")
+MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "7", "Doctoral")
+MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "8", "J.D.")
+MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "9", "M.D.")
+
+MTurk15_R_edu <- MTurk15_R %>%
+  count(Educ)
+
+no_highschool_dip_R <- length(which(MTurk15_R$Educ == "Less than high school"))
+highschool_ged_R <- length(which(MTurk15_R$Educ == "High school/GED", MTurk15_R$Educ == "Some college"))
+two_year_deg_R <- length(which(MTurk15_R$Educ == "2 year deg"))
+advanged_deg_15_R <- length(which(MTurk15_R$Educ == "4 year deg")) + length(which(MTurk15_R$Educ == "Master's")) + length(which(MTurk15_R$Educ == "Doctoral")) + length(which(MTurk15_R$Educ == "J.D.")) + length(which(MTurk15_R$Educ == "M.D."))
+
+MTurk15_R_edu <- as.data.frame(c(no_highschool_dip_R, highschool_ged, two_year_deg_R, advanged_deg_15_R))
+education_levels <- c("no high school", "high school dimploma/GED", "2 year degree", "Bachelors or higher")
+MTurk15_R_edu <- cbind(education_levels, MTurk15_R_edu)
+colnames(MTurk15_R_edu) <- c("education level", "n")
+
+#Define confidence intervals 
+eduCI_15_R <- binom.confint(x = MTurk15_R_edu$n, n = sum(MTurk15_R_edu$n), conf.level = 0/95, methods = "exact")
+eduCI_15_R <- eduCI_15_R[ , 4:6]
+
+#Build Education table 
+education_table_15_R <- cbind(MTurk15_R_edu, eduCI_15_R, BLS_edu_15)
+names(education_table_15_R) <- c("education level", "n", "o", "LL_eth", "UL_eth", "e")
+education_table_15_R <- education_table_15_R[ , c(1, 6, 2, 4, 3, 5)]
+
+#Education chi squared test
+edu_ch2_15_R <- as.data.frame(chi2(education_table_15_R))
+names(edu_ch2_15_R) <- c("chi2")
+row.names(edu_ch2_15_R) <- c("less than a highschool diploma","high school/GED" , "2 year degree", "bachelor's or higher")
+edu_ch2_15_R <- na.omit(edu_ch2_15_R)
+
+#Sum chi-square values.
+sum(edu_ch2_15_R$chi2, na.rm=TRUE)
+```
 
 ##Replication Demographic Analaysis
-##Age Analysis
+##2017 Occupational Analysis 
+```{r}
+#Load datasets.
+Note: these datasets were not taken direclty from their respective sources (i.e., BLS or Qualtrics survey, respectively).
+The BLS dataset is a table describing the broader occupational categories, number of employees working in jobs that fall under one of these categories, and the relative frequency of jobs falling under said occupational category.
+The LATech dataset comes from a separate investigaiton using MTurk whereby individuals who were flagged for inattentive responding were removed from the dataset.
+#Build the BLS Table, but first establish a temp file.
+
+##BLS Data
+library(readxl)
+BLS <- read_excel("2017 BLS Data-updated.xlsx")
+BLS <- BLS[c(8,10)]
+
+#Include data on the size of the military (taken from (https://www.bls.gov/ooh/military/military-careers.htm))
+BLS <- rbind(BLS, c("Military specific occupations", 1085286))
+
+#Only major occupation groups are included in BLS
+BLS <- 
+  BLS[c(2,71,127,159,219,290,316,332,428,490,581,607,648,682,700,760,803,916,943,1046,1122,1288,427267,1),]
+
+###Rename rows and aggregate.
+BLS[1, 1] = "11-13 Management, Business, and Financial Occupations"
+BLS[2, 1] = "11-13 Management, Business, and Financial Occupations"
+BLS[3, 1] = "15-19 Computer, Engineering, and Science Occupations"
+BLS[4, 1] = "15-19 Computer, Engineering, and Science Occupations"
+BLS[5, 1] = "15-19 Computer, Engineering, and Science Occupations"
+BLS[6, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
+BLS[7, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
+BLS[8, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
+BLS[9, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
+BLS[10, 1] = "29 Healthcare Practitioners and Technical Occupations"
+BLS[11, 1] = "31-39 Service Occupations"
+BLS[12, 1] = "31-39 Service Occupations"
+BLS[13, 1] = "31-39 Service Occupations"
+BLS[14, 1] = "31-39 Service Occupations"
+BLS[15, 1] = "31-39 Service Occupations"
+BLS[16, 1] = "41 Sales and Related Occupations"
+BLS[17, 1] = "43 Office and Administrative Support Occupations"
+BLS[18, 1] = "45 Farming, Fishing, and Forestry Occupations"
+BLS[19, 1] = "47 Construction and Extraction Occupation"
+BLS[20, 1] = "49 Installation, Maintenance, and Repair Occupations"
+BLS[21, 1] = "51 Production Occupation"
+BLS[22, 1] = "53 Transportation and Material Moving Occupation"
+BLS[23, 1] = "55 Military Specific Occupations"
+names(BLS) <- c("Var1","Var2")
+BLS$Var2 <- as.numeric(BLS$Var2)
+BLS <- aggregate(.~Var1,BLS,sum)
+
+#Add military occupation number to the overall
+BLS$Var2[14] <- BLS$Var2[13] + BLS$Var2[14]
+
+#Rename variables
+names(BLS) <- c("Intermediate Aggregation Title", "Freq")
+
+#Only keep occupational categories (no all). 
+BLS <- BLS[-14,]
+
+#Compute relative frequencies. Call the object "tab". 
+tab <- transform(BLS, relative = prop.table(Freq))
+
+#Define new BLS. "e" is for "relative frequency". 
+BLS <- tab[c(1,3)]
+names(BLS) <- c("Intermediate Aggregation Title", "e")
+
+##LATech data
+LATech <- read_excel("2017 Data.xls")
+
+###Delete unneeded data.
+LATech <- LATech[c(12, 20:21)]
+names(LATech) <- c("Self-Reported Job Title", "O*NET Occupation Title", "O*NET Job Code")
+
+###Edit data. Some participants provided incorrect codes or no codes.
+LATech[644, 3] = "41-9031.00"
+LATech[274,] = c("analyst", "analyst", "13-0000.00")
+
+###Remove unemployed cases.
+completeFun <- function(data, desiredCols) {
+  completeVec <- complete.cases(data[, desiredCols])
+  return(data[completeVec, ])
+}
+LATech <- completeFun(LATech, "O*NET Job Code")
+
+###Abbreviate data, consolidate into intermediate categories, and bind.
+LO <- LATech[c(3)]
+LO <- read.fwf(textConnection(LO$`O*NET Job Code`), 2)
+names(LO) <- c("Int.Agg.Cat")
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 11] <- "11-13 Management, Business, and Financial Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 13] <- "11-13 Management, Business, and Financial Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 15] <- "15-19 Computer, Engineering, and Science Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 17] <- "15-19 Computer, Engineering, and Science Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 19] <- "15-19 Computer, Engineering, and Science Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 21] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 23] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 25] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 27] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 29] <- "29 Healthcare Practitioners and Technical Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 31] <- "31-39 Service Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 33] <- "31-39 Service Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 35] <- "31-39 Service Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 37] <- "31-39 Service Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 39] <- "31-39 Service Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 41] <- "41 Sales and Related Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 43] <- "43 Office and Administrative Support Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 45] <- "45 Farming, Fishing, and Forestry Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 47] <- "47 Construction and Extraction Occupation"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 49] <- "49 Installation, Maintenance, and Repair Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 51] <- "51 Production Occupation"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 53] <- "53 Transportation and Material Moving Occupation"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 55] <- "55 Military Specific Occupations"
+LATech <- cbind(LATech,LO)
+
+###Build relative frequency table.
+tab <- as.data.frame(table(LO$Int.Agg.Cat, exclude=NULL))
+tab <- transform(tab, relative = prop.table(Freq))
+names(tab) <- c("Intermediate Aggregation Title","n","f")
+tab <- merge(tab,BLS, by="Intermediate Aggregation Title", all=TRUE)
+
+#Chi-square function that quantifies the discrepancy between expected and observed proportions.
+chi2 <- function(x) {
+  o <- (x$n)
+  e <- (x$e)
+  n <- sum(x$n, na.rm=TRUE)
+  ((o-(e)*(n))^2)/((e)*(n))
+}
+
+#Confidence interval formula for proportions with assymptotic intervals.
+Intervals are assymptotic because proportions cannot be less than 0 or greater than 1, which becomes problematic as proportions near 0 or 1.
+require("binom")
+CI <- binom.confint(tab$n, sum(tab$n), conf.level = 0.95, methods = "exact")
+CI <- CI[c(5:6)]
+table <- cbind(tab,CI)
+table <- table[,c(1,4,2,5,3,6)]
+ch <- as.data.frame(chi2(table))
+ch <- na.omit(ch)
+names(table) <- c("Intermediate Aggregation Title","Exp(p)","n1","LCL1","Obs(p)1","UCL1")
+
+#Sum chi-square values.
+sum(ch$`chi2(table)`, na.rm=TRUE)
+
+##Validate using chi-square function in r.
+#Function for differences in relative percentages. This is not printed in the tables, but could be used to help readers see the disparity between expected and observed proportions.
+f <- function(x) {
+  f   <- (x$f)
+  BLS <- (x$e)
+  (f-BLS)
+}
+f1 <- as.data.frame(f(table))
+
+#Print chi-square APA style.
+require(devtools)
+install_github("dgromer/apa")
+require(apa)
+##Sample 1#
+observed1 <- table$n1
+observed1 <- observed1[c(1:13)]
+expected1 <- table$`Exp(p)`
+expected1 <- expected1[c(1:13)]
+c1 <- chisq_apa(chisq.test(x = observed1, p = expected1, correct = TRUE))
+
+#Post-hoc power analysis.
+##Convert chi-squares to correlation coefficient to allow meaningful statistic.
+library(pwr)
+###Study 1
+X21 <-sum(ch$`chi2(table)`, na.rm=TRUE)
+r1 <- sqrt((X21/sum(tab$n)))
+pwr.chisq.test(w=r1,N=(sum(tab$n)),df=12,sig.level = .01)
+```
+
+##2017 Age Analysis
 ```{r}
@@
 
-##Gender Analysis
+##2017 Gender Analysis
 ```{r}
@@
 
-##Ethnicity Analysis
+##2017 Ethnicity Analysis
 ```{r}
@@
 
-###Education Analysis 
+##2017 Education Analysis 
 ```{r}
@@
 
-#Function to find proportion for each iteration of the vector. 
-e_prop <- function(x) {
-  e <- x/BLS_total
-}
-
 #Use vapply and the above function to get expected proportions from BLS data
-BLS_edu <- sapply(BLS_education, e_prop)
+BLS_edu <- sapply(BLS_education, function(x) {x/BLS_total})
 

### 2018-11-27 Manuscript.Rmd

--- 2018-11-27 Manuscript.Rmd
@@
 Occupations <- c(table[1:13, 1])
+=======
+#Results
+  Results shown in our table indicate that MTurk’s occupational frequency distribution does not consistently align with the US economy for both sample 1 ($\chi^2(12) = 368.58, p < .001$) and sample 2 ($\chi^2(12) = 486.07, p < .001$).
+Examining the 95% confidence intervals across both samples, certain occupations were consistently over- or under-represented.
+More specifically individuals sampled from MTurk occupied generally more white-collar jobs (e.g., Management, Business, and Financial Occupations; Computer, Engineering, and Science Occupations) and generally fewer blue-collar jobs (e.g., Construction and Extraction Occupations;  Installation, Maintenance, and Repair Occupations; Production Occupations) than what would be expected based on BLS data.
+For instance, 10.13% of workers in the US economy in 2015 worked in “Management, Business, and Financial Occupations.” By contrast, approximately 17% and 23% of workers from the MTurk samples fell under this classification.
+These trends were generally consistent across both study 1 and 2.
+
+#- - - - - - - - - - - - - 
+#insert table 2 about here
+#- - - - - - - - - - - - - 
+##Barplot 1
+```{r}
+#Bar Plot with error bars
+require(ggplot2)
+Values <- c(Table2[1:13, 5], Table2[1:13, 2])
+Group <- c("MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS")
+Occupations <- c(Table2[1:13, 1], Table2[1:13, 1])
 Occ_Nums <- sapply(strsplit(Occupations, " "), "[[", 1)
@@
 ```
+## 2015 Demographic Analysis 
+## Study 1 Age
+```{r}
+#Chris's 2015 age analysis 
+require(dplyr)
+
+#Load BLS Data
+BLS_age_15 <- read_excel("BLS.Age.2015.xlsx")
+
+#Define population mean. In this case it was already calculated in the dataset. 
+pop_mean_15 <- as.numeric(BLS_age_15[6, 10])
+
+#Define sample mean
+samp_mean_15 <- as.numeric(MTurk15 %>%
+                        summarise(MTurk_age = mean(age, na.rm = TRUE)))
+
+#Sample standard deviation.
+samp_sd_15 <- as.numeric(MTurk15 %>%
+                        summarise(sd_age = sd(age, na.rm = TRUE)))
+
+#Define sample size
+n_15 <- nrow(MTurk15)
+
+#Run t test.
+t_value_15 <- (samp_mean_15 - pop_mean_15)/(samp_sd_15/sqrt(n_15))
+
+```
+
+## Study 1 Gender
+```{r}
+#Gender Analysis 2015
+library(readxl)
+BLS_2015_doc <- read_excel("bls.gender.2015.xlsx")
+
+#Get BLS gender data (expected value)
+BLS_gender_15_data <- BLS_2015_doc[87:93,c(1,8,22, 28)]
+BLS_men_15 <- as.numeric(BLS_gender_15_data[6,3])/as.numeric(BLS_gender_15_data[5,3])
+BLS_women_15 <- as.numeric(BLS_gender_15_data[7,3])/as.numeric(BLS_gender_15_data[5,3])
+BLS_gender_15 <- c(BLS_women_15,BLS_men_15)
+names(BLS_gender_15) <- c("Female", "Male")
+
+#Get MTurk gender data (observed value)
+require(dplyr)
+MTurk_gender_15 <- MTurk15 %>%
+  count(gender)
+MTurk_gender_15 <- MTurk_gender_15[2:3,]
+
+#Define confidence intervals
+require(binom)
+gCI_15 <- binom.confint(x = MTurk_gender_15$n, n = sum(MTurk_gender_15$n), conf.level = 0.95, methods = "exact")
+gCI_15 <- gCI_15[ ,4:6]
+
+#Build Gender table with gender, expected value, n, LL, observed, UL
+gender_table_15 <- cbind(MTurk_gender_15, gCI_15, BLS_gender_15)
+names(gender_table_15) <- c("gender", "n", "o", "LL_g", "UL_g", "e")
+gender_table_15 <- gender_table_15[, c(1, 3, 2, 4, 6, 5)]
+
+#Gender chi square test
+
+chi2 <- function(x) {
+  o <- (x$n)
+  e <- (x$e)
+  n <- sum(x$n, na.rm=TRUE)
+  ((o-(e)*(n))^2)/((e)*(n))
+}
+
+gender_ch2_15 <- as.data.frame(chi2(gender_table_15))
+names(gender_ch2_15) <- c("chi2")
+gender_ch2_15 <- na.omit(gender_ch2_15)
+
+#Sum chi-square values.
+sum(gender_ch2_15$chi2, na.rm=TRUE)
+```
+
+## Study 1 Ethnicity
+```{r}
+#Ethnicity Analysis 
+#Define obs_eth
+BLS_ethnicity_15_data <- BLS_2015_doc[c(94, 97, 100), (c(1, 22))]
+names(BLS_ethnicity_15_data) <- c("ethnicity", "population")
+BLS_ethnicity_15_data$population <- as.numeric(BLS_ethnicity_15_data$population)
+BLS15_eth_prop <- sapply(BLS_ethnicity_15_data$population, function(x) {x/sum(BLS_ethnicity_15_data$population)})
+names(BLS15_eth_prop) <- c(BLS_ethnicity_15_data$ethnicity)
+
+#Get MTurk ethnicity data
+MTurk_eth_15 <- count(MTurk15, ethnicity)
+
+MTurk_eth_15 <- MTurk_eth_15[c(4, 2, 3), ]
+
+#Define confidence intervals 
+ethCI_15 <- binom.confint(x = MTurk_eth_15$n, n = sum(MTurk_eth_15$n), conf.level = 0/95, methods = "exact")
+ethCI_15 <- ethCI_15[ , 4:6]
+
+#Build Ethnicity table 
+ethnicity_table_15 <- cbind(MTurk_eth_15, ethCI_15, BLS15_eth_prop)
+names(ethnicity_table_15) <- c("ethnicity", "n", "o", "LL", "UL", "e")
+eth_table_15 <- ethnicity_table_15[ , c(1, 6, 2, 4, 3, 5)]
+
+#Ethnicity chi squared test
+eth_ch2_15 <- as.data.frame(chi2(eth_table_15))
+names(eth_ch2_15) <- c("chi2")
+row.names(eth_ch2_15) <- c(BLS_ethnicity_15_data$ethnicity)
+eth_ch2_15 <- na.omit(eth_ch2_15)
+
+#Sum chi-square values.
+sum(eth_ch2_15$chi2, na.rm=TRUE)
+```
+
+## Study 1 Education Level 
+```{r}
+#2015 Education Analysis 
+#Clean BLS Data. Data is split between men and women, so the first step is to total these values for the civilian noninstitutionalize population. 
+BLS_education_15_data <- BLS_2015_doc[587:610,c(1,13,24,37,51,61,67)]
+BLS_education_15_total <- as.numeric(BLS_education_15_data[4,2]) + as.numeric(BLS_education_15_data[20,2])
+```
 
 # Results from 2017
-
 ```{r Exploratory Analysis with Demographics, echo = FALSE, include = FALSE}
 # Define Age data
+# Combine categories as necessary.Add men and women together.
+less_than_highschoo_15 <- as.numeric(BLS_education_15_data[4,3]) + as.numeric(BLS_education_15_data[20,3])
+
+#high school/ged includes "some college, no degree"
+highschool_ged_15 <- as.numeric(BLS_education_15_data[4,4]) + as.numeric(BLS_education_15_data[20,4]) + as.numeric(BLS_education_15_data[4,5]) + as.numeric(BLS_education_15_data[20,5])
+
+two_year_deg_15 <- as.numeric(BLS_education_15_data[4,6]) + as.numeric(BLS_education_15_data[20,6])
+
+bachelors_or_higher_15 <- as.numeric(BLS_education_15_data[4,7]) + as.numeric(BLS_education_15_data[20,7])
+
+BLS_education_15 <- c(less_than_highschoo_15,highschool_ged_15, two_year_deg_15, bachelors_or_higher_15)
+names(BLS_education_15) <- c("less than high school degree", "high school/GED" , "2 year degree", "bachelor's or more")
+
+#Use vapply and the anonomous function to get expected proportions from BLS data
+BLS_edu_15 <- sapply(BLS_education_15, function(x){x/BLS_education_15_total})
+
+#Clean MTurk Data
+MTurk_education_15 <- MTurk15 %>%
+  count(MTurk15$`education level`)
+colnames(MTurk_education_15) <- c("education level", "n")
+advanced_deg_15 <- as.numeric(MTurk_education_15[6,2]) + as.numeric(MTurk_education_15[8,2]) + as.numeric(MTurk_education_15[3,2])
+no_highschool_dip <- as.numeric(MTurk_education_15[5,2]) + as.numeric(MTurk_education_15[7,2])
+MTurk_education_15 <- rbind(no_highschool_dip, MTurk_education_15, advanced_deg_15)
+MTurk_education_15[10,1] <- c("bachelor's or higher")
+MTurk_education_15[1,1] <- c("less than a high school diploma")
+MTurk_edu_15 <- MTurk_education_15[c(-2, -4, -6, -7, -8, -9), ]
+MTurk_edu_15 <- MTurk_edu_15[c(1, 3, 2, 4), ]
+
+#Define confidence intervals 
+eduCI_15 <- binom.confint(x = MTurk_edu_15$n, n = sum(MTurk_edu_15$n), conf.level = 0/95, methods = "exact")
+eduCI_15 <- eduCI_15[ , 4:6]
+
+#Build Education table 
+education_table_15 <- cbind(MTurk_edu_15, eduCI_15, BLS_edu_15)
+names(education_table_15) <- c("education level", "n", "o", "LL_eth", "UL_eth", "e")
+education_table_15 <- education_table_15[ , c(1, 6, 2, 4, 3, 5)]
+
+#Education chi squared test
+edu_ch2_15 <- as.data.frame(chi2(education_table_15))
+names(edu_ch2_15) <- c("chi2")
+row.names(edu_ch2_15) <- c("less than a highschool diploma","high school/GED" , "2 year degree", "bachelor's or higher")
+edu_ch2_15 <- na.omit(edu_ch2_15)
+
+#Sum chi-square values.
+sum(edu_ch2_15$chi2, na.rm=TRUE)
+```
+
+##Study 2 Age
+```{r}
+#Rachel's 2015 Demographic Analysis 
+library(readxl)
+MTurk15_R <- read_excel("Rachel's Data from 2015.xlsx")
+
+#packages to clean data for demogrphics
+library(stringr)
+install.packages(tidyr)
+library(tidyr)
+
+#Rachel's age analysis 
+#Load BLS Data
+BLS_age_15 <- read_excel("~/Desktop/BLS.Age.2015.xlsx")
+
+#Define population mean. In this case it was already calculated in the dataset. 
+pop_mean_15 <- as.numeric(BLS_age_15[6, 10])
+
+#Define sample mean
+samp_mean_15_R <- as.numeric(MTurk15_R %>% 
+                             summarise(MTurk_age = mean(Age, na.rm = TRUE)))
+
+#Sample standard deviation.
+samp_sd_15_R <- as.numeric(MTurk15_R %>% 
+                           summarise(sd_age = sd(Age, na.rm = TRUE)))
+
+#Define sample size
+n_15_R <- nrow(MTurk15_R)
+
+#Run t test.
+t_value_15_R <- (samp_mean_15_R - pop_mean_15)/(samp_sd_15_R/sqrt(n_15_R))
+```
+
+##Study 2 Gender
+```{r}
+#Rachel's gender analysis
+#clean data
+MTurk15_R$Gender <- str_replace(MTurk15_R$Gender, "1", "male")
+MTurk15_R$Gender <- str_replace(MTurk15_R$Gender, "2", "female")
+
+#get frequencies
+MTurk_gender_15_R <- MTurk15_R %>% 
+  count(Gender)
+MTurk_gender_15_R <- MTurk_gender_15_R[1:2,]
+
+#Define confidence intervals
+require(binom)
+gCI_15_R <- binom.confint(x = MTurk_gender_15_R$n, n = sum(MTurk_gender_15_R$n), conf.level = 0.95, methods = "exact")
+gCI_15_R <- gCI_15_R[ ,4:6]
+
+#Build Gender table with gender, expected value, n, LL, observed, UL
+gender_table_15_R <- cbind(MTurk_gender_15_R, gCI_15_R, BLS_gender_15)
+names(gender_table_15_R) <- c("gender", "n", "o", "LL_g", "UL_g", "e")
+gender_table_15_R <- gender_table_15_R[, c(1, 3, 2, 4, 6, 5)]
+
+#Gender chi square test
+gender_ch2_15_R <- as.data.frame(chi2(gender_table_15_R))
+names(gender_ch2_15_R) <- c("chi2")
+gender_ch2_15_R <- na.omit(gender_ch2_15_R)
+
+#Sum chi-square values.
+sum(gender_ch2_15_R$chi2, na.rm=TRUE)
+
+```
+
+##Study 2 Ethnicity
+```{r}
+#Rachel's ethnicity analysis
+MTurk15_R_white <- length(which(MTurk15_R$White == 1))
+MTurk15_R_AfnAmn <- length(which(MTurk15_R$AfnAmn == 1))
+MTurk15_R_AsnPI <- length(which(MTurk15_R$AsnPI == 1))
+
+MTurk15_R_eth <- as.data.frame(c(MTurk15_R_white, MTurk15_R_AfnAmn, MTurk15_R_AsnPI))
+MTurk15_R_eth <- cbind(BLS_ethnicity_15_data$ethnicity, MTurk15_R_eth)
+colnames(MTurk15_R_eth) <- c("ethnicity", "n")
+MTurk15_R_eth_tot <- MTurk15_R_white + MTurk15_R_AfnAmn + MTurk15_R_AsnPI
+
+#Get proportions for ethnicities
+MTurk15_R_eth <- MTurk15_R_eth %>% 
+  mutate(prop = sapply(MTurk15_R_eth$n, function(x) {x/MTurk15_R_eth_tot}))
+
+#Define confidence intervals 
+ethCI_15_R <- binom.confint(x = MTurk15_R_eth$n, n = sum(MTurk15_R_eth$n), conf.level = 0/95, methods = "exact")
+ethCI_15_R <- ethCI_15_R[ , 4:6]
+
+#Build Ethnicity table 
+ethnicity_table_15_R <- cbind(MTurk15_R_eth[1:2], ethCI_15_R, BLS15_eth_prop)
+names(ethnicity_table_15_R) <- c("ethnicity", "n", "o", "LL", "UL", "e")
+eth_table_15_R <- ethnicity_table_15_R[1:3, c(1, 6, 2, 4, 3, 5)]
+
+#Ethnicity chi squared test
+eth_ch2_15_R <- as.data.frame(chi2(eth_table_15_R))
+names(eth_ch2_15_R) <- c("chi2")
+row.names(eth_ch2_15_R) <- c(BLS_ethnicity_15_data$ethnicity)
+eth_ch2_15_R <- na.omit(eth_ch2_15_R)
+
+#Sum chi-square values.
+sum(eth_ch2_15_R$chi2, na.rm=TRUE)
+```
+
+##Study 2 Education Level 
+```{r}
+#Rachel's education level
+MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "1", "Less than high school")
+MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "2", "High school/GED")
+MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "3", "Some college")
+MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "4", "2 year deg")
+MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "5", "4 year deg")
+MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "6", "Master's")
+MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "7", "Doctoral")
+MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "8", "J.D.")
+MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "9", "M.D.")
+
+MTurk15_R_edu <- MTurk15_R %>%
+  count(Educ)
+
+no_highschool_dip_R <- length(which(MTurk15_R$Educ == "Less than high school"))
+highschool_ged_R <- length(which(MTurk15_R$Educ == "High school/GED", MTurk15_R$Educ == "Some college"))
+two_year_deg_R <- length(which(MTurk15_R$Educ == "2 year deg"))
+advanged_deg_15_R <- length(which(MTurk15_R$Educ == "4 year deg")) + length(which(MTurk15_R$Educ == "Master's")) + length(which(MTurk15_R$Educ == "Doctoral")) + length(which(MTurk15_R$Educ == "J.D.")) + length(which(MTurk15_R$Educ == "M.D."))
+
+MTurk15_R_edu <- as.data.frame(c(no_highschool_dip_R, highschool_ged, two_year_deg_R, advanged_deg_15_R))
+education_levels <- c("no high school", "high school dimploma/GED", "2 year degree", "Bachelors or higher")
+MTurk15_R_edu <- cbind(education_levels, MTurk15_R_edu)
+colnames(MTurk15_R_edu) <- c("education level", "n")
+
+#Define confidence intervals 
+eduCI_15_R <- binom.confint(x = MTurk15_R_edu$n, n = sum(MTurk15_R_edu$n), conf.level = 0/95, methods = "exact")
+eduCI_15_R <- eduCI_15_R[ , 4:6]
+
+#Build Education table 
+education_table_15_R <- cbind(MTurk15_R_edu, eduCI_15_R, BLS_edu_15)
+names(education_table_15_R) <- c("education level", "n", "o", "LL_eth", "UL_eth", "e")
+education_table_15_R <- education_table_15_R[ , c(1, 6, 2, 4, 3, 5)]
+
+#Education chi squared test
+edu_ch2_15_R <- as.data.frame(chi2(education_table_15_R))
+names(edu_ch2_15_R) <- c("chi2")
+row.names(edu_ch2_15_R) <- c("less than a highschool diploma","high school/GED" , "2 year degree", "bachelor's or higher")
+edu_ch2_15_R <- na.omit(edu_ch2_15_R)
+
+#Sum chi-square values.
+sum(edu_ch2_15_R$chi2, na.rm=TRUE)
+```
+
+## Replication Demographic Analaysis
+## 2017 Occupational Analysis 
+```{r}
+#Load datasets.
+Note: these datasets were not taken direclty from their respective sources (i.e., BLS or Qualtrics survey, respectively).
+The BLS dataset is a table describing the broader occupational categories, number of employees working in jobs that fall under one of these categories, and the relative frequency of jobs falling under said occupational category.
+The LATech dataset comes from a separate investigaiton using MTurk whereby individuals who were flagged for inattentive responding were removed from the dataset.
+#Build the BLS Table, but first establish a temp file.
+
+##BLS Data
+library(readxl)
+BLS <- read_excel("2017 BLS Data-updated.xlsx")
+BLS <- BLS[c(8,10)]
+
+#Include data on the size of the military (taken from (https://www.bls.gov/ooh/military/military-careers.htm))
+BLS <- rbind(BLS, c("Military specific occupations", 1085286))
+
+#Only major occupation groups are included in BLS
+BLS <- 
+  BLS[c(2,71,127,159,219,290,316,332,428,490,581,607,648,682,700,760,803,916,943,1046,1122,1288,427267,1),]
+
+###Rename rows and aggregate.
+BLS[1, 1] = "11-13 Management, Business, and Financial Occupations"
+BLS[2, 1] = "11-13 Management, Business, and Financial Occupations"
+BLS[3, 1] = "15-19 Computer, Engineering, and Science Occupations"
+BLS[4, 1] = "15-19 Computer, Engineering, and Science Occupations"
+BLS[5, 1] = "15-19 Computer, Engineering, and Science Occupations"
+BLS[6, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
+BLS[7, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
+BLS[8, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
+BLS[9, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
+BLS[10, 1] = "29 Healthcare Practitioners and Technical Occupations"
+BLS[11, 1] = "31-39 Service Occupations"
+BLS[12, 1] = "31-39 Service Occupations"
+BLS[13, 1] = "31-39 Service Occupations"
+BLS[14, 1] = "31-39 Service Occupations"
+BLS[15, 1] = "31-39 Service Occupations"
+BLS[16, 1] = "41 Sales and Related Occupations"
+BLS[17, 1] = "43 Office and Administrative Support Occupations"
+BLS[18, 1] = "45 Farming, Fishing, and Forestry Occupations"
+BLS[19, 1] = "47 Construction and Extraction Occupation"
+BLS[20, 1] = "49 Installation, Maintenance, and Repair Occupations"
+BLS[21, 1] = "51 Production Occupation"
+BLS[22, 1] = "53 Transportation and Material Moving Occupation"
+BLS[23, 1] = "55 Military Specific Occupations"
+names(BLS) <- c("Var1","Var2")
+BLS$Var2 <- as.numeric(BLS$Var2)
+BLS <- aggregate(.~Var1,BLS,sum)
+
+#Add military occupation number to the overall
+BLS$Var2[14] <- BLS$Var2[13] + BLS$Var2[14]
+
+#Rename variables
+names(BLS) <- c("Intermediate Aggregation Title", "Freq")
+
+#Only keep occupational categories (no all). 
+BLS <- BLS[-14,]
+
+#Compute relative frequencies. Call the object "tab". 
+tab <- transform(BLS, relative = prop.table(Freq))
+
+#Define new BLS. "e" is for "relative frequency". 
+BLS <- tab[c(1,3)]
+names(BLS) <- c("Intermediate Aggregation Title", "e")
+
+##LATech data
+LATech <- read_excel("2017 Data.xls")
+
+###Delete unneeded data.
+LATech <- LATech[c(12, 20:21)]
+names(LATech) <- c("Self-Reported Job Title", "O*NET Occupation Title", "O*NET Job Code")
+
+###Edit data. Some participants provided incorrect codes or no codes.
+LATech[644, 3] = "41-9031.00"
+LATech[274,] = c("analyst", "analyst", "13-0000.00")
+
+###Remove unemployed cases.
+completeFun <- function(data, desiredCols) {
+  completeVec <- complete.cases(data[, desiredCols])
+  return(data[completeVec, ])
+}
+LATech <- completeFun(LATech, "O*NET Job Code")
+
+###Abbreviate data, consolidate into intermediate categories, and bind.
+LO <- LATech[c(3)]
+LO <- read.fwf(textConnection(LO$`O*NET Job Code`), 2)
+names(LO) <- c("Int.Agg.Cat")
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 11] <- "11-13 Management, Business, and Financial Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 13] <- "11-13 Management, Business, and Financial Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 15] <- "15-19 Computer, Engineering, and Science Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 17] <- "15-19 Computer, Engineering, and Science Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 19] <- "15-19 Computer, Engineering, and Science Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 21] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 23] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 25] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 27] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 29] <- "29 Healthcare Practitioners and Technical Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 31] <- "31-39 Service Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 33] <- "31-39 Service Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 35] <- "31-39 Service Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 37] <- "31-39 Service Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 39] <- "31-39 Service Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 41] <- "41 Sales and Related Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 43] <- "43 Office and Administrative Support Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 45] <- "45 Farming, Fishing, and Forestry Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 47] <- "47 Construction and Extraction Occupation"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 49] <- "49 Installation, Maintenance, and Repair Occupations"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 51] <- "51 Production Occupation"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 53] <- "53 Transportation and Material Moving Occupation"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 55] <- "55 Military Specific Occupations"
+LATech <- cbind(LATech,LO)
+
+###Build relative frequency table.
+tab <- as.data.frame(table(LO$Int.Agg.Cat, exclude=NULL))
+tab <- transform(tab, relative = prop.table(Freq))
+names(tab) <- c("Intermediate Aggregation Title","n","f")
+tab <- merge(tab,BLS, by="Intermediate Aggregation Title", all=TRUE)
+
+#Chi-square function that quantifies the discrepancy between expected and observed proportions.
+chi2 <- function(x) {
+  o <- (x$n)
+  e <- (x$e)
+  n <- sum(x$n, na.rm=TRUE)
+  ((o-(e)*(n))^2)/((e)*(n))
+}
+
+#Confidence interval formula for proportions with assymptotic intervals.
+Intervals are assymptotic because proportions cannot be less than 0 or greater than 1, which becomes problematic as proportions near 0 or 1.
+require("binom")
+CI <- binom.confint(tab$n, sum(tab$n), conf.level = 0.95, methods = "exact")
+CI <- CI[c(5:6)]
+table <- cbind(tab,CI)
+table <- table[,c(1,4,2,5,3,6)]
+ch <- as.data.frame(chi2(table))
+ch <- na.omit(ch)
+names(table) <- c("Intermediate Aggregation Title","Exp(p)","n1","LCL1","Obs(p)1","UCL1")
+
+#Sum chi-square values.
+sum(ch$`chi2(table)`, na.rm=TRUE)
+
+##Validate using chi-square function in r.
+#Function for differences in relative percentages. This is not printed in the tables, but could be used to help readers see the disparity between expected and observed proportions.
+f <- function(x) {
+  f   <- (x$f)
+  BLS <- (x$e)
+  (f-BLS)
+}
+f1 <- as.data.frame(f(table))
+
+#Print chi-square APA style.
+require(devtools)
+install_github("dgromer/apa")
+require(apa)
+##Sample 1#
+observed1 <- table$n1
+observed1 <- observed1[c(1:13)]
+expected1 <- table$`Exp(p)`
+expected1 <- expected1[c(1:13)]
+c1 <- chisq_apa(chisq.test(x = observed1, p = expected1, correct = TRUE))
+
+#Post-hoc power analysis.
+##Convert chi-squares to correlation coefficient to allow meaningful statistic.
+library(pwr)
+###Study 1
+X21 <-sum(ch$`chi2(table)`, na.rm=TRUE)
+r1 <- sqrt((X21/sum(tab$n)))
+pwr.chisq.test(w=r1,N=(sum(tab$n)),df=12,sig.level = .01)
+```
+
+## 2017 Age Analysis
+```{r}
+#Age Analysis T- Test
+#Load Dataset
+require(dplyr)
+require(readxl)
 age_demo <- read_excel("age_demo.xlsx")
@@
 # Define Gender data
+=======
+#Define sample size
+n <- as.numeric(667)
+
+#Run t test.
+t_value <- (samp_mean - pop_mean)/(samp_sd/sqrt(n))
+t_value
+
+#So MTurk is much younger than the population on average. We need to convert this to an effect size (Cohen's D). 
+```
+
+## 2017 Gender Analysis
+```{r}
+##Gender Analysis
 BLS_data <- read_excel("employment_demo.xlsx")
@@
 # Get BLS ethnicity data
+=======
+##2017 Ethnicity Analysis
+```{r}
+#Ethnicity Analysis 
+#Define obs_eth
 BLS_cauc <- as.numeric(BLS_data[7, 4])/100
@@
 # Clean BLS Data. Get totals.  
+## 2017 Education Analysis 
+```{r}
+#Education Analysis 
+#Clean BLS Data. Get totals.  
 BLS_education_original <- read_excel("education_demo.xlsx")
@@
 
+#Use vapply and the above function to get expected proportions from BLS data
+BLS_edu <- sapply(BLS_education, function(x) {x/BLS_total})
+
 # Clean MTurk Data
@@
 
-#Build Education table 
+# Build Education table 
 education_table <- cbind(MTurk_edu, eduCI, BLS_edu)
@@
 
-#Education chi squared test
+# Education chi squared test
 x5 <- chisq.test(education_table$n, p = round(education_table$e,3))

### 2018-11-28 Manuscript.Rmd
Added data source for 2015

--- 2018-11-27 Manuscript.Rmd
@@
 ```{r}
+#2015 Study 1 data
+MTurk15 <- read.csv("~/MTurkOccDiversity/Demographics.csv", stringsAsFactors = FALSE)
+names(MTurk15) <- c("country", "country text", "age", "gender", "years of current employment", "education level", "is english your primary language", "job title", "job title 2", "part time or full time", "sector", "employment status", "is MTurk primary income", "income currency", "approx annual income", "work hours per week", "ethnicity", "none")
+
 #Chris's 2015 age analysis 
 require(dplyr)
+require(readxl)
 

### 2018-11-30 Manuscript.Rmd
Updated code to pull out errors or redundancies.

--- 2018-11-27 Manuscript.Rmd
@@
 ```
+
 ## Analysis
@@
 
-```{r, echo = FALSE, warning = FALSE, fig.cap = "Comparing the occupational diversity of two MTurk samples with expecations based on the Bureau of Labor Statistics"}
-# Bar Plot with error bars
-Values <- c(table[1:13,2], table[1:13, 5], table[1:13, 9])
-Group <- c("BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2")
-Occupations <- c(table[1:13, 1])
-=======
-#Results
+# Results
   Results shown in our table indicate that MTurk’s occupational frequency distribution does not consistently align with the US economy for both sample 1 ($\chi^2(12) = 368.58, p < .001$) and sample 2 ($\chi^2(12) = 486.07, p < .001$).
@@
 
-#- - - - - - - - - - - - - 
-#insert table 2 about here
-#- - - - - - - - - - - - - 
-##Barplot 1
-```{r}
+```{r Barplot, echo = FALSE, warning = FALSE, fig.cap = "Comparing the occupational diversity of two MTurk samples with expecations based on the Bureau of Labor Statistics"}
 #Bar Plot with error bars
 require(ggplot2)
-Values <- c(Table2[1:13, 5], Table2[1:13, 2])
-Group <- c("MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS")
-Occupations <- c(Table2[1:13, 1], Table2[1:13, 1])
+Values <- c(table[1:13,2], table[1:13, 5], table[1:13, 9])
+Group <- c("BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2")
+Occupations <- c(table[1:13, 1])
 Occ_Nums <- sapply(strsplit(Occupations, " "), "[[", 1)
@@
 ```{r}
-#Chris's 2015 age analysis 
-require(dplyr)
-
 #Load BLS Data
@@
 pop_mean_15 <- as.numeric(BLS_age_15[6, 10])
+
+# Get dems
+MTurk15 <- read_csv("Demographics.csv")
 
@@
 # Get BLS ethnicity data
-=======
+```
+
 ##2017 Ethnicity Analysis
@@
 # Result is significant. MTurk is under-represented by African Americans, Asians, and other ethnicities. However, it does appear to be slightly over-represented by Caucasians.
+```
 
@@
 \newpage
-
 # References
-
 ```{r Citations, warning = FALSE, echo = FALSE}
@@
 ```
-
 \setlength{\parindent}{-0.5in}

### 2018-11-30 Manuscript.Rmd

@@
 ```
-
 ## Analysis
@@
 ```{r}
+#2015 Study 1 data
+MTurk15 <- read.csv("~/MTurkOccDiversity/Demographics.csv", stringsAsFactors = FALSE)
+names(MTurk15) <- c("country", "country text", "age", "gender", "years of current employment", "education level", "is english your primary language", "job title", "job title 2", "part time or full time", "sector", "employment status", "is MTurk primary income", "income currency", "approx annual income", "work hours per week", "ethnicity", "none")
+
+#Chris's 2015 age analysis 
+require(dplyr)
+require(readxl)
+
 #Load BLS Data

### 2018-11-30 Manuscript.Rmd

@@
 ```{r}
-#2015 Study 1 data
-MTurk15 <- read.csv("~/MTurkOccDiversity/Demographics.csv", stringsAsFactors = FALSE)
-names(MTurk15) <- c("country", "country text", "age", "gender", "years of current employment", "education level", "is english your primary language", "job title", "job title 2", "part time or full time", "sector", "employment status", "is MTurk primary income", "income currency", "approx annual income", "work hours per week", "ethnicity", "none")
-
 #Chris's 2015 age analysis 
 require(dplyr)
-require(readxl)
 

### 2018-12-01 Manuscript.Rmd
Updated with author note.

--- 2018-11-30 Manuscript.Rmd
@@
     affiliation   : "2"
+  - name          : "John E. Buckner"
+    affiliation   : "3"
   - name          : "Bodour H. Mahmoud"
-    affiliation   : "3"
-  - name          : "John E. Buckner"
     affiliation   : "4"
+  - name          : "James DeLeon"
+    affiliation   : "5"
 affiliation:
@@
   - id            : "3"
+    institution   : "AlixPartners"
+  - id            : "4"
     institution   : "Villanova University"
-  - id            : "4"
-    institution   : "AlixPartners"
+  - id            : "5"
+    institution   : "APTMetrics"
 
@@
   All correspondence should be sent to the lead author at chris_castille@mac.com.
+We would like to thank Bryan Bunn and Maximillian Sinn for taking the time to offer a friendly review of this manuscript.
 
@@
 library(lsr)            # Useful for conducting one-sample t-tests and estiamting Cohen's D
+library(stringr)        # Package helps us analyze Rachel's data
+library(tidyr)          # Package helps us analyze Rachel's data 
 ```
@@
 
-## US Population Occupational Summary Statistics (2015 and 2017)
+## US Population Occupational Summary Statistics
 
@@
 
-```{r Load and Clean Data, include=FALSE, warning = FALSE, message = FALSE, echo = FALSE}
+```{r Load and Clean 2015 Data, include=FALSE, warning = FALSE, message = FALSE, echo = FALSE}
 # Load datasets.
@@
 UGA$ONETCode[UGA$JobTitle=="Therapy support staff"] <- "31-2012.00"
-####Reclassify cases as "Unclear Occupational Category/Employed"
+
+# Reclassify cases as "Unclear Occupational Category/Employed"
 UGA$ONETCode[UGA$JobTitle=="Resource Room Director"] <- "99"
@@
 UGA$ONETCode[UGA$JobTitle=="paraprofphisonal"] <- "99"
-####Delete the unemployed.
+
+# Delete the unemployed.
 UGA<-UGA[!(UGA$JobTitle=="volunteer"),]
@@
 UGA <- cbind(UGA,LO)
-###Build relative frequency table.
+
+# Build relative frequency table.
 tab2 <- as.data.frame(table(UGA$Int.Agg.Cat, exclude=NULL))
-###Omit self-employed individuals.
+
+# Omit self-employed individuals.
 tab2 <- tab2[c(-14),]
@@
 ```
-```{r Main Analyses, include = FALSE, warning = FALSE, message = FALSE, echo = FALSE}
+```{r Main Analyses for 2015, include = FALSE, warning = FALSE, message = FALSE, echo = FALSE}
 # Build table for sample 1 with confidence intervals.
@@
 # Run chi-square test for sample 1
-x1 <- chisq.test(table$n1, p = round(table$`Expected`,3))
+x15.1 <- chisq.test(table$n1, p = round(table$`Expected`,3))
 # Results are significant.
@@
 The error bars in the figure also capture this information.
-x1[["stdres"]]
+x15.1[["stdres"]]
 # Significantly over-represented: (i) 11-13 Management, Business, and Financial (6.94), (ii) 15-19 Computer, Engineering, and Science (11.97), and (iii) 21-27 Education, Legal, Community Service, Arts, and Media (8.17).
@@
 # Run chi-square test for sample 2
-x2 <- chisq.test(table$n2, p = round(table$`Expected`,3))
+x15.2 <- chisq.test(table$n2, p = round(table$`Expected`,3))
 # Results are significant. Run post-hoc pairwise comparisons. 
-x2[["stdres"]]
+x15.2[["stdres"]]
 # Significantly over-represented: (i) 11-13 Management, Business, and Financial (14.76), (ii) 15-19 Computer, Engineering, and Science (8.52), and (iii) 21-27 Education, Legal, Community Service, Arts, and Media (7.30).
@@
 ```
-
-## MTurk Occupational Summary Statistics (2015)
-
-In 2015, participants’ data were collected from two independently conducted studies (n~1~ = `r nrow(LATech)`; n~2~ = `r nrow(UGA)`).
-In sample one (n~1~ =`r nrow(LATech)`), occupational data was self-reported by participants who were asked to described their job title.
+```{r Load and Clean 2017 Data, include = FALSE, warning = FALSE, message = FALSE, echo = FALSE}
+# BLS Data from 2017
+BLS17 <- read_excel("Data/oesm17nat/national_M2017_dl.xlsx")
+BLS17 <- BLS17[c(2,4)]
+
+# Include data on the size of the military (taken from (https://www.BLS17.gov/ooh/military/military-careers.htm))
+BLS17 <- rbind(BLS17, c("Military specific occupations", 1085286))
+
+# Only major occupation groups are included in BLS17
+BLS17 <- 
+  BLS17[c(2,71,127,159,219,290,316,332,428,490,581,607,648,682,700,760,803,916,943,1046,1122,1288,1383,1),]
+
+# Rename rows and aggregate.
+BLS17[1, 1] = "11-13 Management, Business, and Financial"
+BLS17[2, 1] = "11-13 Management, Business, and Financial"
+BLS17[3, 1] = "15-19 Computer, Engineering, and Science"
+BLS17[4, 1] = "15-19 Computer, Engineering, and Science"
+BLS17[5, 1] = "15-19 Computer, Engineering, and Science"
+BLS17[6, 1] = "21-27 Education, Legal, Community Service, Arts, and Media"
+BLS17[7, 1] = "21-27 Education, Legal, Community Service, Arts, and Media"
+BLS17[8, 1] = "21-27 Education, Legal, Community Service, Arts, and Media"
+BLS17[9, 1] = "21-27 Education, Legal, Community Service, Arts, and Media"
+BLS17[10, 1] = "29 Healthcare Practitioners and Technical"
+BLS17[11, 1] = "31-39 Service"
+BLS17[12, 1] = "31-39 Service"
+BLS17[13, 1] = "31-39 Service"
+BLS17[14, 1] = "31-39 Service"
+BLS17[15, 1] = "31-39 Service"
+BLS17[16, 1] = "41 Sales and Related"
+BLS17[17, 1] = "43 Office and Administrative Support"
+BLS17[18, 1] = "45 Farming, Fishing, and Forestry"
+BLS17[19, 1] = "47 Construction and Extraction"
+BLS17[20, 1] = "49 Installation, Maintenance, and Repair"
+BLS17[21, 1] = "51 Production"
+BLS17[22, 1] = "53 Transportation and Material Moving"
+BLS17[23, 1] = "55 Military Specific"
+names(BLS17) <- c("Var1","Var2")
+BLS17$Var2 <- as.numeric(BLS17$Var2)
+BLS17 <- aggregate(.~Var1,BLS17,sum)
+
+# Add military occupation number to the overall
+BLS17$Var2[14] <- BLS17$Var2[13] + BLS17$Var2[14]
+
+# Rename variables
+names(BLS17) <- c("Intermediate Aggregation Title", "Freq")
+
+# Only keep occupational categories (no all). 
+BLS17 <- BLS17[-14,]
+
+# Compute relative frequencies. Call the object "tab". 
+tab <- transform(BLS17, relative = prop.table(Freq))
+
+# Define new BLS17. "e" is for "relative frequency". 
+BLS17 <- tab[c(1,3)]
+names(BLS17) <- c("Intermediate Aggregation Title", "e")
+
+# C217 data
+C217 <- read_excel("2017 Data.xls")
+
+# Delete unneeded data.
+C217 <- C217[c(12, 20:21)]
+names(C217) <- c("Self-Reported Job Title", "O*NET Occupation Title", "O*NET Job Code")
+
+# Edit data. Some participants provided incorrect codes or no codes.
+C217[153, 3] = "43-3011.00" 
+C217[412, 3] = "43-5081.03" # Provided two codes; picked the first code.
+C217[612, 3] = "43-3031.00"
+C217[644, 3] = "41-9031.00"
+C217[274,] = c("analyst", "analyst", "13-0000.00")
+
+# Remove unemployed cases.
+C217 <- completeFun(C217, "O*NET Job Code")
+
+# Abbreviate data, consolidate into intermediate categories, and bind.
+LO <- C217[c(3)]
+LO <- read.fwf(textConnection(LO$`O*NET Job Code`), 2)
+names(LO) <- c("Int.Agg.Cat")
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 11] <- "11-13 Management, Business, and Financial"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 13] <- "11-13 Management, Business, and Financial"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 15] <- "15-19 Computer, Engineering, and Science"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 17] <- "15-19 Computer, Engineering, and Science"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 19] <- "15-19 Computer, Engineering, and Science"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 21] <- "21-27 Education, Legal, Community Service, Arts, and Media"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 23] <- "21-27 Education, Legal, Community Service, Arts, and Media"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 25] <- "21-27 Education, Legal, Community Service, Arts, and Media"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 27] <- "21-27 Education, Legal, Community Service, Arts, and Media"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 29] <- "29 Healthcare Practitioners and Technical"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 31] <- "31-39 Service"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 33] <- "31-39 Service"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 35] <- "31-39 Service"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 37] <- "31-39 Service"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 39] <- "31-39 Service"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 41] <- "41 Sales and Related"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 43] <- "43 Office and Administrative Support"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 45] <- "45 Farming, Fishing, and Forestry"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 47] <- "47 Construction and Extraction"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 49] <- "49 Installation, Maintenance, and Repair"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 51] <- "51 Production"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 53] <- "53 Transportation and Material Moving"
+LO$Int.Agg.Cat[LO$Int.Agg.Cat == 55] <- "55 Military Specific"
+C217 <- cbind(C217,LO)
+
+# Build relative frequency table.
+tab <- as.data.frame(table(LO$Int.Agg.Cat, exclude=NULL))
+tab <- transform(tab, relative = prop.table(Freq))
+names(tab) <- c("Intermediate Aggregation Title","n","f")
+tab <- merge(tab,BLS17, by="Intermediate Aggregation Title", all=TRUE) 
+```
+```{r Main Analyses for 2017, include = FALSE, warning = FALSE, message = FALSE, echo = FALSE}
+# Build table for sample 3 with confidence intervals.
+CI <- binom.confint(tab$n, sum(tab$n), conf.level = 0.95, methods = "exact")
+CI <- CI[c(5:6)]
+table3 <- cbind(tab,CI)
+table3 <- table3[,c(1,4,2,5,3,6)]
+names(table3) <- c("Intermediate Aggregation Title","Expected","n3","LL3","Obs3","UL3")
+table3$`Expected` <- round(table3$`Expected`,4)
+table3$LL3 <- round(table3$LL3,3)
+table3$`Obs3` <- round(table3$`Obs3`,3)
+table3$UL3 <- round(table3$UL3,3)
+
+# Run chi-square test for sample 3
+x17.1 <- chisq.test(table3$n3, p = round(table3$`Expected`,3))
+# Results are significant.
+Agresti (2007) notes that standardized residuals greater than 2 are indicative of association.
+Positive residuals indicate over-representation, while a negative residual indicates a negative association.
+The error bars in the figure also capture this information.
+x17.1[["stdres"]]
+# Significantly over-represented: (i) 11-13 Management, Business, and Financial (8.23), (ii) 15-19 Computer, Engineering, and Science (9.56), and (iii) 21-27 Education, Legal, Community Service, Arts, and Media (6.30).
+# Conforming with expectations: (i) 29 Healthcare Practitioners and Technical (-2.52), (ii) 41 Sales and Related (-2.23), (iii) 43 Office and Administrative Support (2.36), (iv) 45 Farming, Fishing, and Forestry (1.42), (v) 49 Installation and Maintenance (-2.10), and (vi) 55 Military Specific (-1.02).
+# Significantly under-represented: (i) 31-39 Service (-6.05), (ii) 47 Construction and Extraction (-4.68), (iii) 51 Production (-4.47), and (iv) 53 Transportion and Material Moving (-5.57).
+```
+
+## MTurk Occupational Summary Statistics
+
+In 2015, participants’ data were collected from two independently conducted studies (n~1~ = `r nrow(LATech)`; n~2~ = `r nrow(UGA)`) for purposes that were not directly related to the purpose of this study (i.e., investigating psychological phenomena in organizational life).
+Data collected in 2017 (n~3~ = `r nrow(C217)`) can be similarly described.
+For two samples (2015; n~1~ =`r nrow(LATech)`; 2017; n~3~ =`r nrow(C217)`), occupational data were self-reported by participants who were asked to described their job title.
 They were then brought to ONET online and asked to retrieve the six-digit occupational classification code that most closely corresponded to their job title.
-In the sample two (n~2~ = `r nrow(UGA)`), participants again self-reported their job title.
+In another sample (n~2~ = `r nrow(UGA)`), participants again self-reported their job title.
 However, the six-digit occupational classification codes were obtained by training research assistants to match the self-reported job titles to those in the ONET database.
-Using this data, we described the occupational diversity of each sample using relative frequencies of occupational category representation as described by Table 1.
-Data were again collected in 2017 as part of a separate investigation.
-In this sample, participants were asked to self-report their occupational data in the manner consistent with sample 1.
+Using this data, we described the occupational diversity of each sample using relative frequencies of occupational category representation.
+Table 1 contains statistics for 2015.
+Table 2 contains statistics for 2017.
+
 ```{r Table 1, results="asis"}
@@
 ```
-
-## Analysis
-
-A chi-square test of goodness-of-fit was used to test whether proportions from MTurk samples deviated from expected proportions as derived from the BLS.
+```{r Table 2, results="asis"}
+papaja::apa_table(table3, 
+                  caption = "Proportions of individuals sampled from each intermediate occupational category in 2017",
+                  landscape = TRUE,
+                  note = "n = sample; 3 = sample 3, accordingly; LL = lower 95% confidence limit; Obs = observed proportion; UL = upper 95% confidence limit.")
+```
+
+## Analytical Approach
+
+A chi-square test of goodness-of-fit was used to determine whether observed proportions from MTurk samples deviated from expected proportions as derived from the BLS.
 Specifically, we tested whether MTurk’s occupational diversity deviated (p < .05) from that expected if we assume the BLS population parameters generalize to the MTurk population.
 Gender, ethnicity, and education were examined in the same fashion.
-Given that multiple groups were examined, significant tests were followed by a post-hoc test.
-More specifically, we examined the standardized residuals from our chi-square tests [see @agrestiIntroductionCategoricalData2007], which in this context defines occupations that were over-represented (values > +3), under-represented (values < -3), or consistent with expectations (< or = |3|).
-To facilitate interpretation, we also calculated 95% confidence intervals for our sample proportions and plotted these values (see Figure 1).
+Given that multiple occupational and ethnic groups were examined, significant tests were followed by a post-hoc test.
+More specifically, we examined the standardized residuals from our chi-square tests [see @agrestiIntroductionCategoricalData2007], which in this context defines occupations that in our view were over-represented (values > +3), under-represented (values < -3), or consistent with expectations (< or = |3|).
+To facilitate interpretation, we also calculated 95% confidence intervals for our sample proportions and plotted these values (see Figure 1 for 2015 and Figure 2 for 2017).
 Age differences were examined used a one-sample t-test.
-Overall, our approach tests several distinct yet related null hypotheses; namely that the MTurk and broader US labor force contain similar (i) proportions of individuals from defined clusters of occupational areas, (ii) gender, (iii) ethnic, (iv) education, and (v) are of comparable age.
+Overall, our approach tests several distinct yet related null hypotheses; namely that the MTurk and broader US labor force contain similar proportions of individuals from (i) occupational areas, (ii) gender, (iii) ethnic, (iv) education, and (v) are of comparable age.
 [^p]
 
-[^p]: Analyses applied to the 2015 data were conducted in 2016.
-However, the analyses for 2017 data, more specifically the use of a chi-square goodness of fit test, were pre-registered on the Open Science Framework.
-Post-hoc testing was not pre-registered nor were the analyses regarding the remaining demographic variables.
-
-# Results from 2015
-
-Chi-square tests indicate that MTurk’s occupational diversity does not align with expectations in both sample 1 (*X*^2^(`r x1[["parameter"]]`) = `r x1$statistic`, *p* `r myround2(x1$p.value)`) and sample 2, (*X*^2^(`r x2[["parameter"]]`)= `r x2$statistic`, *p* `r myround2(x2$p.value)`).
-Examining the standardized residuals [see @agrestiIntroductionCategoricalData2007] in this context clarifies which occupations were over-represented (values > +2), under-represented (values < -2), or consistent with expectations (< or = |2|) (see also the error bars in Figure 1).
-We use these criteria to facilitate interpretation.
-
-Across both samples, over-represented occupations included (i) 11-13 Management, Business, and Financial (study 1 = `r x1[["stdres"]][1]`; study 2 = `r x2[["stdres"]][1]`), (ii) 15-19 Computer, Engineering, and Science (study 1 = `r x1[["stdres"]][2]`; study 2 = `r x2[["stdres"]][2]`), (iii) 21-27 Education, Legal, Community Service, Arts, and Media (study 1 = `r x1[["stdres"]][3]`; study 2 = `r x2[["stdres"]][3]`).
-Occupations that were consistently under-represented included (i) 31-39 Service (study 1 = `r x1[["stdres"]][5]`; study 2 = `r x2[["stdres"]][5]`), (ii) 47 Construction and Extraction (study 1 = `r x1[["stdres"]][9]`; study 2 = `r x2[["stdres"]][9]`), (iii) 49 Installation, Maintenance, and Repair (study 1 = `r x1[["stdres"]][10]`; study 2 = `r x2[["stdres"]][10]`), (iv) 51 Production (study 1 = `r x1[["stdres"]][11]`; study 2 = `r x2[["stdres"]][11]`), and (v) 53 Transportation and Material Moving (study 1 = `r x1[["stdres"]][12]`; study 2 = `r x2[["stdres"]][12]`).
-Lastly, occupations that consistently appeared in a proportion that conformed with expectations included (i) 43 Office and Administrative Support (study 1 = `r x1[["stdres"]][7]`; study 2 = `r x2[["stdres"]][7]`), (ii) 45 Farming, Fishing, and Forestry (study 1 = `r x1[["stdres"]][8]`; study 2 = `r x2[["stdres"]][8]`), and (iii) 55 Military Specific (study 1 = `r x1[["stdres"]][13]`; study 2 = `r x2[["stdres"]][13]`).
-Overall, these results suggests that the MTurk population contains a disproportionate share of white-collar occupations relative to blue-collar occupations.
-
-It is worth pointing out that conclusions regarding two occupational categories are inconsistent across our two samples.
-For occupational group 29 (Healthcare Practitioners and Technical), sample one suggests that these occupations are represented as expected (study 1 = `r x1[["stdres"]][4]`).
-However, this group was under-represented in sample 2 (study 2 = `r x2[["stdres"]][3]`).
-Given that the confidence intervals from our two samples overlap (albeit very weakly), we  tentatively conclude that this group is adequately represented.
-For occupational category 41 (Sales and Related), sample one suggested under-representation (study 1 = `r x1[["stdres"]][6]`) whereas sample two suggests that these occupations are represented as expected (study 2 = `r x2[["stdres"]][6]`).
-Again, as these confidence intervals overlap, we offer a tentative conclusion that this population is represented as expected.
+[^p]: Analysis of the occupational diversity of MTurk was conducted on the 2015 samples and were not pre-registered.
+However, analysis of the occupational diversity of the 2017 sample were pre-registered on the Open Science Framework.
+It is worth pointing out hat ost-hoc testing was not pre-registered nor were the analyses regarding gender, ethnicity, education, and age.
 
 # Results
-  Results shown in our table indicate that MTurk’s occupational frequency distribution does not consistently align with the US economy for both sample 1 ($\chi^2(12) = 368.58, p < .001$) and sample 2 ($\chi^2(12) = 486.07, p < .001$).
-Examining the 95% confidence intervals across both samples, certain occupations were consistently over- or under-represented.
-More specifically individuals sampled from MTurk occupied generally more white-collar jobs (e.g., Management, Business, and Financial Occupations; Computer, Engineering, and Science Occupations) and generally fewer blue-collar jobs (e.g., Construction and Extraction Occupations;  Installation, Maintenance, and Repair Occupations; Production Occupations) than what would be expected based on BLS data.
-For instance, 10.13% of workers in the US economy in 2015 worked in “Management, Business, and Financial Occupations.” By contrast, approximately 17% and 23% of workers from the MTurk samples fell under this classification.
-These trends were generally consistent across both study 1 and 2.
-
-```{r Barplot, echo = FALSE, warning = FALSE, fig.cap = "Comparing the occupational diversity of two MTurk samples with expecations based on the Bureau of Labor Statistics"}
-#Bar Plot with error bars
-require(ggplot2)
+
+## Occupational Diversity (2015)
+
+Chi-square tests indicate that MTurk’s occupational diversity does not align with expectations in both sample 1 (*X*^2^(`r x15.1[["parameter"]]`) = `r x15.1$statistic`, *p* `r myround2(x15.1$p.value)`) and sample 2, (*X*^2^(`r x15.2[["parameter"]]`)= `r x15.2$statistic`, *p* `r myround2(x15.2$p.value)`).
+Therefore, both samples deviate from expectations.
+
+```{r Barplot 1, echo = FALSE, warning = FALSE, fig.cap = "Comparing the occupational diversity of two MTurk samples with expecations based on the Bureau of Labor Statistics"}
+# Bar Plot with error bars
 Values <- c(table[1:13,2], table[1:13, 5], table[1:13, 9])
 Group <- c("BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2")
-Occupations <- c(table[1:13, 1])
+Occupations <- c(as.character(table[1:13, 1]))
 Occ_Nums <- sapply(strsplit(Occupations, " "), "[[", 1)
@@
 ```
-## 2015 Demographic Analysis 
-## Study 1 Age
-```{r}
-#Load BLS Data
+
+Across both samples, over-represented occupations included (i) 11-13 Management, Business, and Financial (study 1 = `r x15.1[["stdres"]][1]`; study 2 = `r x15.2[["stdres"]][1]`), (ii) 15-19 Computer, Engineering, and Science (study 1 = `r x15.1[["stdres"]][2]`; study 2 = `r x15.2[["stdres"]][2]`), and (iii) 21-27 Education, Legal, Community Service, Arts, and Media (study 1 = `r x15.1[["stdres"]][3]`; study 2 = `r x15.2[["stdres"]][3]`).
+Occupations that were consistently under-represented included (i) 31-39 Service (study 1 = `r x15.1[["stdres"]][5]`; study 2 = `r x15.2[["stdres"]][5]`), (ii) 47 Construction and Extraction (study 1 = `r x15.1[["stdres"]][9]`; study 2 = `r x15.2[["stdres"]][9]`), (iii) 49 Installation, Maintenance, and Repair (study 1 = `r x15.1[["stdres"]][10]`; study 2 = `r x15.2[["stdres"]][10]`), (iv) 51 Production (study 1 = `r x15.1[["stdres"]][11]`; study 2 = `r x15.2[["stdres"]][11]`), and (v) 53 Transportation and Material Moving (study 1 = `r x15.1[["stdres"]][12]`; study 2 = `r x15.2[["stdres"]][12]`).
+Lastly, occupations that consistently appeared in a proportion that conformed with expectations included (i) 41 Sales and Relateed (study 1 = `r x15.1[["stdres"]][6]`; study 2 = `r x15.2[["stdres"]][6]`), (ii) 43 Office and Administrative Support (study 1 = `r x15.1[["stdres"]][7]`; study 2 = `r x15.2[["stdres"]][7]`), (iii) 45 Farming, Fishing, and Forestry (study 1 = `r x15.1[["stdres"]][8]`; study 2 = `r x15.2[["stdres"]][8]`), and (iv) 55 Military Specific (study 1 = `r x15.1[["stdres"]][13]`; study 2 = `r x15.2[["stdres"]][13]`).
+Overall, these results suggests that the MTurk population contains a disproportionate share of white-collar occupations relative to blue-collar occupations.
+For intermediate occupational group 29 (Healthcare Practitioners and Technical), sample one suggests that these occupations are represented as expected (study 1 = `r x15.1[["stdres"]][4]`).
+However, this group was under-represented in sample 2 (study 2 = `r x15.2[["stdres"]][3]`).
+Given that the confidence intervals from our two samples overlap (albeit very weakly), we tentatively conclude that this group appears adequately represented.
+
+## Demographic Diversity (2015) 
+```{r Exploratory Analysis with Demographics, warning = FALSE, echo = FALSE, include = FALSE}
+# Age
 BLS_age_15 <- read_excel("BLS.Age.2015.xlsx")
 
-#Define population mean. In this case it was already calculated in the dataset. 
+# Define population mean. In this case it was already calculated in the dataset. 
 pop_mean_15 <- as.numeric(BLS_age_15[6, 10])
 
-# Get dems
-MTurk15 <- read_csv("Demographics.csv")
-
-#Define sample mean
-samp_mean_15 <- as.numeric(MTurk15 %>%
-                        summarise(MTurk_age = mean(age, na.rm = TRUE)))
-
-#Sample standard deviation.
-samp_sd_15 <- as.numeric(MTurk15 %>%
-                        summarise(sd_age = sd(age, na.rm = TRUE)))
-
-#Define sample size
-n_15 <- nrow(MTurk15)
-
-#Run t test.
-t_value_15 <- (samp_mean_15 - pop_mean_15)/(samp_sd_15/sqrt(n_15))
-
-```
-
-## Study 1 Gender
-```{r}
-#Gender Analysis 2015
-library(readxl)
+# Chris's dems
+MTurk15 <- read_excel("Data/Chris's Data from 2015.xlsx")
+names(MTurk15) <- c("age", "gender", "years of current employment", "education level", "job title", "O*NET Job Title", "part time or full time", "sector", "employment status", "is MTurk primary income", "income currency", "approx annual income", "work hours per week", "ethnicity", "ethnicity 2")
+
+# Run one-samplet test and estimate Cohen's D for Chris's data.
+t15.1 <- oneSampleTTest(x = as.numeric(MTurk15$age), mu = pop_mean_15)
+tvalue15.1 <- t15.1$t.statistic %>%
+  formatC(digits = 2, format = "f")
+if (t15.1$p.value < 0.0005) {
+  pvalue <- " < 0.001"
+} else {
+  if (t15.1$p.value < 0.005)
+      pvalue <- paste0(" = ",t$p.value %>% formatC(digits = 3, format = "f"))
+    else 
+      pvalue <- paste0(" = ",t$p.value %>% formatC(digits = 2, format = "f")) 
+  }
+df15.1 <- t15.1$df
+d15.1 <- round((t15.1$effect.size),2)
+# MTurk participants from Chris's data are significantly younger than labor force at large. Moderate effect according to Cohen's criteria.
+
+# Run one-samplet test and estimate Cohen's D for Rachel's data.
+MTurk15_R <- read_excel("Data/Rachel's Data from 2015.xlsx")
+t15.2 <- oneSampleTTest(x = MTurk15_R$Age, mu = pop_mean_15)
+tvalue15.2 <- t15.2$t.statistic %>%
+  formatC(digits = 2, format = "f")
+if (t15.2$p.value < 0.0005) {
+  pvalue <- " < 0.001"
+} else {
+  if (t15.2$p.value < 0.005)
+      pvalue <- paste0(" = ",t$p.value %>% formatC(digits = 3, format = "f"))
+    else 
+      pvalue <- paste0(" = ",t$p.value %>% formatC(digits = 2, format = "f")) 
+  }
+df15.2 <- t15.2$df
+d15.2 <- round((t15.2$effect.size),2)
+# MTurk participants from Rachel's data are significantly younger than labor force at large. Moderate effect according to Cohen's criteria.
+
+# Gender
 BLS_2015_doc <- read_excel("bls.gender.2015.xlsx")
 
-#Get BLS gender data (expected value)
+# Get BLS gender data (expected value)
 BLS_gender_15_data <- BLS_2015_doc[87:93,c(1,8,22, 28)]
@@
 
-#Get MTurk gender data (observed value)
-require(dplyr)
+# Get MTurk gender data (observed value) (Chris's)
+MTurk15$gender[MTurk15$gender=="1"] <- "Male"
+MTurk15$gender[MTurk15$gender=="2"] <- "Female"
 MTurk_gender_15 <- MTurk15 %>%
-  count(gender)
-MTurk_gender_15 <- MTurk_gender_15[2:3,]
-
-#Define confidence intervals
-require(binom)
+  count(gender) %>%
+  drop_na()
+
+# Define confidence intervals
 gCI_15 <- binom.confint(x = MTurk_gender_15$n, n = sum(MTurk_gender_15$n), conf.level = 0.95, methods = "exact")
@@
 
-#Build Gender table with gender, expected value, n, LL, observed, UL
+# Build Gender table with gender, expected value, n, LL, observed, UL
 gender_table_15 <- cbind(MTurk_gender_15, gCI_15, BLS_gender_15)
@@
 
+# Run chi-square test for gender
+x15.3 <- chisq.test(gender_table_15$n, p = round(gender_table_15$e,3))
+
+# Result is significant. Chris's data suggest that MTurk is over-represented by females.
+
+# Rachel's gender analysis
+MTurk15_R$Gender <- str_replace(MTurk15_R$Gender, "1", "male")
+MTurk15_R$Gender <- str_replace(MTurk15_R$Gender, "2", "female")
+
+# Get frequencies
+MTurk_gender_15_R <- MTurk15_R %>% 
+  count(Gender) %>%
+  drop_na()
+
+# Define confidence intervals
+gCI_15_R <- binom.confint(x = MTurk_gender_15_R$n, n = sum(MTurk_gender_15_R$n), conf.level = 0.95, methods = "exact")
+gCI_15_R <- gCI_15_R[ ,4:6]
+
+# Build Gender table with gender, expected value, n, LL, observed, UL
+gender_table_15_R <- cbind(MTurk_gender_15_R, gCI_15_R, BLS_gender_15)
+names(gender_table_15_R) <- c("gender", "n", "o", "LL_g", "UL_g", "e")
+gender_table_15_R <- gender_table_15_R[, c(1, 3, 2, 4, 6, 5)]
+
 #Gender chi square test
-
-chi2 <- function(x) {
-  o <- (x$n)
-  e <- (x$e)
-  n <- sum(x$n, na.rm=TRUE)
-  ((o-(e)*(n))^2)/((e)*(n))
-}
-
-gender_ch2_15 <- as.data.frame(chi2(gender_table_15))
-names(gender_ch2_15) <- c("chi2")
-gender_ch2_15 <- na.omit(gender_ch2_15)
-
-#Sum chi-square values.
-sum(gender_ch2_15$chi2, na.rm=TRUE)
-```
-
-## Study 1 Ethnicity
-```{r}
-#Ethnicity Analysis 
-#Define obs_eth
-BLS_ethnicity_15_data <- BLS_2015_doc[c(94, 97, 100), (c(1, 22))]
+x15.4 <- chisq.test(gender_table_15_R$n, p = round(gender_table_15_R$e,3))
+
+# Result is significant. Rachel's data also suggests that MTurk is largely dominated by females.
+
+# Ethnicity
+# Get BLS data
+Total <- BLS_2015_doc[c(91), (c(1, 42))]
+Total <- Total[c(-1)]
+Total <- as.numeric(Total)
+BLS_ethnicity_15_data <- BLS_2015_doc[c(94, 97, 100), (c(1, 42))]
 names(BLS_ethnicity_15_data) <- c("ethnicity", "population")
-BLS_ethnicity_15_data$population <- as.numeric(BLS_ethnicity_15_data$population)
-BLS15_eth_prop <- sapply(BLS_ethnicity_15_data$population, function(x) {x/sum(BLS_ethnicity_15_data$population)})
+BLS15_eth_prop <- sapply(as.numeric(BLS_ethnicity_15_data$population), 
+                         function(x) 
+                           {x/Total})
 names(BLS15_eth_prop) <- c(BLS_ethnicity_15_data$ethnicity)
-
-#Get MTurk ethnicity data
+BLS15_eth_prop <- round(as.data.frame(t(BLS15_eth_prop)),3)
+BLS_cauc <- BLS15_eth_prop$White
+BLS_AfAm <- BLS15_eth_prop$Black
+BLS_Asn <- BLS15_eth_prop$Asian
+BLS15_eth_prop$Other <- 1-sum(BLS_cauc, BLS_AfAm, BLS_Asn)
+BLS15_eth_prop <- t(BLS15_eth_prop)
+
+# Get Chris's MTurk ethnicity data
+MTurk15$ethnicity[MTurk15$ethnicity==1] <- "White"
+MTurk15$ethnicity[MTurk15$ethnicity==2] <- "Black"
+MTurk15$ethnicity[MTurk15$ethnicity==3] <- "Asian"
+MTurk15$ethnicity[MTurk15$ethnicity==4] <- "Other"
+MTurk15$ethnicity[MTurk15$ethnicity==5] <- "Other"
+MTurk15$ethnicity[MTurk15$ethnicity==6] <- "Other"
+MTurk15$ethnicity[MTurk15$ethnicity==7] <- "Other"
 MTurk_eth_15 <- count(MTurk15, ethnicity)
-
-MTurk_eth_15 <- MTurk_eth_15[c(4, 2, 3), ]
-
-#Define confidence intervals 
-ethCI_15 <- binom.confint(x = MTurk_eth_15$n, n = sum(MTurk_eth_15$n), conf.level = 0/95, methods = "exact")
+MTurk_eth_15 <- MTurk_eth_15[c(4,2,1,3),]
+
+# Define confidence intervals 
+ethCI_15 <- binom.confint(x = MTurk_eth_15$n, n = sum(MTurk_eth_15$n), conf.level = 0.95, methods = "exact")
 ethCI_15 <- ethCI_15[ , 4:6]
 
-#Build Ethnicity table 
+# Build Ethnicity table 
 ethnicity_table_15 <- cbind(MTurk_eth_15, ethCI_15, BLS15_eth_prop)
@@
 
-#Ethnicity chi squared test
-eth_ch2_15 <- as.data.frame(chi2(eth_table_15))
-names(eth_ch2_15) <- c("chi2")
-row.names(eth_ch2_15) <- c(BLS_ethnicity_15_data$ethnicity)
-eth_ch2_15 <- na.omit(eth_ch2_15)
-
-#Sum chi-square values.
-sum(eth_ch2_15$chi2, na.rm=TRUE)
-```
-
-## Study 1 Education Level 
-```{r}
-#2015 Education Analysis 
-#Clean BLS Data. Data is split between men and women, so the first step is to total these values for the civilian noninstitutionalize population. 
-BLS_education_15_data <- BLS_2015_doc[587:610,c(1,13,24,37,51,61,67)]
-BLS_education_15_total <- as.numeric(BLS_education_15_data[4,2]) + as.numeric(BLS_education_15_data[20,2])
-```
-
-# Results from 2017
-```{r Exploratory Analysis with Demographics, echo = FALSE, include = FALSE}
-# Define Age data
-# Combine categories as necessary.Add men and women together.
-less_than_highschoo_15 <- as.numeric(BLS_education_15_data[4,3]) + as.numeric(BLS_education_15_data[20,3])
-
-#high school/ged includes "some college, no degree"
-highschool_ged_15 <- as.numeric(BLS_education_15_data[4,4]) + as.numeric(BLS_education_15_data[20,4]) + as.numeric(BLS_education_15_data[4,5]) + as.numeric(BLS_education_15_data[20,5])
-
-two_year_deg_15 <- as.numeric(BLS_education_15_data[4,6]) + as.numeric(BLS_education_15_data[20,6])
-
-bachelors_or_higher_15 <- as.numeric(BLS_education_15_data[4,7]) + as.numeric(BLS_education_15_data[20,7])
-
-BLS_education_15 <- c(less_than_highschoo_15,highschool_ged_15, two_year_deg_15, bachelors_or_higher_15)
-names(BLS_education_15) <- c("less than high school degree", "high school/GED" , "2 year degree", "bachelor's or more")
-
-#Use vapply and the anonomous function to get expected proportions from BLS data
+# Ethnicity chi squared test for Chris's data
+x15.5 <- chisq.test(eth_table_15$n, p = round(eth_table_15$e,3))
+
+# Result is significant. Run post-hoc pairwise comparisons. 
+x15.5[["stdres"]]
+# MTurk is under-represented by African Americans. It also appears to be over-represented by individuals coming from groups outside of three primary races (White, Black, Asian).
+
+# Rachel's ethnicity data.
+She measured demographics by asking individuals to select in a "which of the following ethnicities apply to you" kind of manner.
+This data had to be reshaped to identify individuals who only reported a single race.
+MTurk15_R_white <- MTurk15_R %>%
+  filter(White == 1) %>%
+  filter(is.na(AfnAmn)) %>%
+  filter(is.na(AsnPI)) %>%
+  filter(is.na(HispLat)) %>%
+  filter(is.na(NAorAI)) %>%
+  filter(is.na(Other)) %>%
+  filter(is.na(OthrTxt)) 
+MTurk15_R_white <- nrow(MTurk15_R_white)
+MTurk15_R_AfnAmn <- MTurk15_R %>%
+  filter(is.na(White)) %>%
+  filter(AfnAmn ==1) %>%
+  filter(is.na(AsnPI)) %>%
+  filter(is.na(HispLat)) %>%
+  filter(is.na(NAorAI)) %>%
+  filter(is.na(Other)) %>%
+  filter(is.na(OthrTxt))
+MTurk15_R_AfnAmn <- nrow(MTurk15_R_AfnAmn)
+MTurk15_R_AsnPI <- MTurk15_R %>%
+  filter(is.na(White)) %>%
+  filter(is.na(AfnAmn)) %>%
+  filter(AsnPI ==1) %>%
+  filter(is.na(HispLat)) %>%
+  filter(is.na(NAorAI)) %>%
+  filter(is.na(Other)) %>%
+  filter(is.na(OthrTxt))
+MTurk15_R_AsnPI <- nrow(MTurk15_R_AsnPI)
+MTurk15_R_Other <- nrow(MTurk15_R)-sum(MTurk15_R_white,MTurk15_R_AfnAmn,MTurk15_R_AsnPI)
+MTurk15_R_eth <- c(MTurk15_R_white, MTurk15_R_AfnAmn, MTurk15_R_AsnPI,MTurk15_R_Other)
+MTurk15_R_eth <- as.data.frame(cbind(BLS15_eth_prop, MTurk15_R_eth))
+MTurk15_R_eth <- round(MTurk15_R_eth, 3)
+colnames(MTurk15_R_eth) <- c("e","n")
+
+#Get proportions for ethnicities
+Total <- nrow(MTurk15_R)
+MTurk15_R_eth <- MTurk15_R_eth %>% 
+  mutate(prop = sapply(MTurk15_R_eth$n, function(x){x/Total}))
+
+#Define confidence intervals 
+ethCI_15_R <- binom.confint(x = MTurk15_R_eth$n, n = sum(MTurk15_R_eth$n), conf.level = 0.95, methods = "exact")
+ethCI_15_R <- ethCI_15_R[ , 4:6]
+
+#Build Ethnicity table 
+ethnicity_table_15_R <- cbind(MTurk15_R_eth, ethCI_15_R, BLS15_eth_prop)
+ethnicity_table_15_R$e[1] <- "White"
+ethnicity_table_15_R$e[2] <- "Black"
+ethnicity_table_15_R$e[3] <- "Asian"
+ethnicity_table_15_R$e[4] <- "Other"
+eth_table_15_R <- ethnicity_table_15_R[1:4, c(1, 2, 3, 5, 6, 7)]
+names(eth_table_15_R) <- c("ethnicity", "n", "o", "LL", "UL", "e")
+
+# Ethnicity chi squared test for Rachel's data
+x15.6 <- chisq.test(eth_table_15_R$n, p = round(eth_table_15_R$e,3))
+
+# Result is significant. Run post-hoc pairwise comparisons. 
+x15.6[["stdres"]]
+# Again, African Americans are under-represented by MTurk. It also appears to be over-represented by individuals coming from groups outside of three primary races (White, Black, Asian).
+
+# Education 
+# Clean BLS Data. 
+BLS_education_15_data <- BLS_2015_doc[491:514,c(1,13,24,37,51,61,67)]
+BLS_education_15_total <- as.numeric(BLS_education_15_data[5,2])
+less_than_highschool_15 <- as.numeric(BLS_education_15_data[5,3])
+highschool_ged_15 <- as.numeric(BLS_education_15_data[5,4])
+some_college_no_degree15 <- as.numeric(BLS_education_15_data[5,5])
+two_year_deg_15 <- as.numeric(BLS_education_15_data[5,6])
+bachelors_or_higher_15 <- as.numeric(BLS_education_15_data[5,7])
+BLS_education_15 <- c(less_than_highschool_15,highschool_ged_15, some_college_no_degree15, two_year_deg_15, bachelors_or_higher_15)
+names(BLS_education_15) <- c("Less than a high school diploma", "high school/GED" , "Some college, no degree", "Associate's degree", "Bachelor's degree and higher")
+
+# Use vapply and the anonomous function to get expected proportions from BLS data
 BLS_edu_15 <- sapply(BLS_education_15, function(x){x/BLS_education_15_total})
 
-#Clean MTurk Data
-MTurk_education_15 <- MTurk15 %>%
-  count(MTurk15$`education level`)
-colnames(MTurk_education_15) <- c("education level", "n")
-advanced_deg_15 <- as.numeric(MTurk_education_15[6,2]) + as.numeric(MTurk_education_15[8,2]) + as.numeric(MTurk_education_15[3,2])
-no_highschool_dip <- as.numeric(MTurk_education_15[5,2]) + as.numeric(MTurk_education_15[7,2])
-MTurk_education_15 <- rbind(no_highschool_dip, MTurk_education_15, advanced_deg_15)
-MTurk_education_15[10,1] <- c("bachelor's or higher")
-MTurk_education_15[1,1] <- c("less than a high school diploma")
-MTurk_edu_15 <- MTurk_education_15[c(-2, -4, -6, -7, -8, -9), ]
-MTurk_edu_15 <- MTurk_edu_15[c(1, 3, 2, 4), ]
-
-#Define confidence intervals 
-eduCI_15 <- binom.confint(x = MTurk_edu_15$n, n = sum(MTurk_edu_15$n), conf.level = 0/95, methods = "exact")
-eduCI_15 <- eduCI_15[ , 4:6]
-
-#Build Education table 
-education_table_15 <- cbind(MTurk_edu_15, eduCI_15, BLS_edu_15)
-names(education_table_15) <- c("education level", "n", "o", "LL_eth", "UL_eth", "e")
-education_table_15 <- education_table_15[ , c(1, 6, 2, 4, 3, 5)]
-
-#Education chi squared test
-edu_ch2_15 <- as.data.frame(chi2(education_table_15))
-names(edu_ch2_15) <- c("chi2")
-row.names(edu_ch2_15) <- c("less than a highschool diploma","high school/GED" , "2 year degree", "bachelor's or higher")
-edu_ch2_15 <- na.omit(edu_ch2_15)
-
-#Sum chi-square values.
-sum(edu_ch2_15$chi2, na.rm=TRUE)
-```
-
-##Study 2 Age
-```{r}
-#Rachel's 2015 Demographic Analysis 
-library(readxl)
-MTurk15_R <- read_excel("Rachel's Data from 2015.xlsx")
-
-#packages to clean data for demogrphics
-library(stringr)
-install.packages(tidyr)
-library(tidyr)
-
-#Rachel's age analysis 
-#Load BLS Data
-BLS_age_15 <- read_excel("~/Desktop/BLS.Age.2015.xlsx")
-
-#Define population mean. In this case it was already calculated in the dataset. 
-pop_mean_15 <- as.numeric(BLS_age_15[6, 10])
-
-#Define sample mean
-samp_mean_15_R <- as.numeric(MTurk15_R %>% 
-                             summarise(MTurk_age = mean(Age, na.rm = TRUE)))
-
-#Sample standard deviation.
-samp_sd_15_R <- as.numeric(MTurk15_R %>% 
-                           summarise(sd_age = sd(Age, na.rm = TRUE)))
-
-#Define sample size
-n_15_R <- nrow(MTurk15_R)
-
-#Run t test.
-t_value_15_R <- (samp_mean_15_R - pop_mean_15)/(samp_sd_15_R/sqrt(n_15_R))
-```
-
-##Study 2 Gender
-```{r}
-#Rachel's gender analysis
-#clean data
-MTurk15_R$Gender <- str_replace(MTurk15_R$Gender, "1", "male")
-MTurk15_R$Gender <- str_replace(MTurk15_R$Gender, "2", "female")
-
-#get frequencies
-MTurk_gender_15_R <- MTurk15_R %>% 
-  count(Gender)
-MTurk_gender_15_R <- MTurk_gender_15_R[1:2,]
-
-#Define confidence intervals
-require(binom)
-gCI_15_R <- binom.confint(x = MTurk_gender_15_R$n, n = sum(MTurk_gender_15_R$n), conf.level = 0.95, methods = "exact")
-gCI_15_R <- gCI_15_R[ ,4:6]
-
-#Build Gender table with gender, expected value, n, LL, observed, UL
-gender_table_15_R <- cbind(MTurk_gender_15_R, gCI_15_R, BLS_gender_15)
-names(gender_table_15_R) <- c("gender", "n", "o", "LL_g", "UL_g", "e")
-gender_table_15_R <- gender_table_15_R[, c(1, 3, 2, 4, 6, 5)]
-
-#Gender chi square test
-gender_ch2_15_R <- as.data.frame(chi2(gender_table_15_R))
-names(gender_ch2_15_R) <- c("chi2")
-gender_ch2_15_R <- na.omit(gender_ch2_15_R)
-
-#Sum chi-square values.
-sum(gender_ch2_15_R$chi2, na.rm=TRUE)
-
-```
-
-##Study 2 Ethnicity
-```{r}
-#Rachel's ethnicity analysis
-MTurk15_R_white <- length(which(MTurk15_R$White == 1))
-MTurk15_R_AfnAmn <- length(which(MTurk15_R$AfnAmn == 1))
-MTurk15_R_AsnPI <- length(which(MTurk15_R$AsnPI == 1))
-
-MTurk15_R_eth <- as.data.frame(c(MTurk15_R_white, MTurk15_R_AfnAmn, MTurk15_R_AsnPI))
-MTurk15_R_eth <- cbind(BLS_ethnicity_15_data$ethnicity, MTurk15_R_eth)
-colnames(MTurk15_R_eth) <- c("ethnicity", "n")
-MTurk15_R_eth_tot <- MTurk15_R_white + MTurk15_R_AfnAmn + MTurk15_R_AsnPI
-
-#Get proportions for ethnicities
-MTurk15_R_eth <- MTurk15_R_eth %>% 
-  mutate(prop = sapply(MTurk15_R_eth$n, function(x) {x/MTurk15_R_eth_tot}))
-
-#Define confidence intervals 
-ethCI_15_R <- binom.confint(x = MTurk15_R_eth$n, n = sum(MTurk15_R_eth$n), conf.level = 0/95, methods = "exact")
-ethCI_15_R <- ethCI_15_R[ , 4:6]
-
-#Build Ethnicity table 
-ethnicity_table_15_R <- cbind(MTurk15_R_eth[1:2], ethCI_15_R, BLS15_eth_prop)
-names(ethnicity_table_15_R) <- c("ethnicity", "n", "o", "LL", "UL", "e")
-eth_table_15_R <- ethnicity_table_15_R[1:3, c(1, 6, 2, 4, 3, 5)]
-
-#Ethnicity chi squared test
-eth_ch2_15_R <- as.data.frame(chi2(eth_table_15_R))
-names(eth_ch2_15_R) <- c("chi2")
-row.names(eth_ch2_15_R) <- c(BLS_ethnicity_15_data$ethnicity)
-eth_ch2_15_R <- na.omit(eth_ch2_15_R)
-
-#Sum chi-square values.
-sum(eth_ch2_15_R$chi2, na.rm=TRUE)
-```
-
-##Study 2 Education Level 
-```{r}
-#Rachel's education level
-MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "1", "Less than high school")
-MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "2", "High school/GED")
-MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "3", "Some college")
-MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "4", "2 year deg")
-MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "5", "4 year deg")
-MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "6", "Master's")
-MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "7", "Doctoral")
-MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "8", "J.D.")
-MTurk15_R$Educ <- str_replace(MTurk15_R$Educ, "9", "M.D.")
-
+# Clean Chris's MTurk Data [Note: Analysis abandoned because of scaling issues]
+#MTurk15$`education level`[MTurk15$`education level`==1] <- "Less than middle school"
+#MTurk15$`education level`[MTurk15$`education level`==2] <- "Middle school"
+#MTurk15$`education level`[MTurk15$`education level`==3] <- "High school/GED"
+#MTurk15$`education level`[MTurk15$`education level`==4] <- "2-year degree"
+#MTurk15$`education level`[MTurk15$`education level`==5] <- "4-year degree"
+#MTurk15$`education level`[MTurk15$`education level`==6] <- "Masters or equivalent"
+#MTurk15$`education level`[MTurk15$`education level`==7] <- "Ph.D. or equivalent"
+#MTurk_education_15 <- MTurk15 %>%
+#  count(MTurk15$`education level`)
+#colnames(MTurk_education_15) <- c("education level", "n")
+#no_highschool_M15 <- as.numeric(MTurk_education_15[4,2])
+#highschool_ged_M15 <- as.numeric(MTurk_education_15[3,2])
+#some_college_no_degree_M15 <- NA
+#two_year_deg_M15 <- as.numeric(MTurk_education_15[1,2])
+#bachelors_or_higher_M15 <- as.numeric(MTurk_education_15[6,2]) + as.numeric(MTurk_education_15[2,2]) + as.numeric(MTurk_education_15[5,2])
+#MTurk_education_15 <- as.data.frame(rbind(no_highschool_M15, highschool_ged_M15, some_college_no_degree_M15, two_year_deg_M15, bachelors_or_higher_M15))
+#names(MTurk_education_15) <- c("n")
+#MTurk_education_15$n <- as.numeric(MTurk_education_15$n)
+
+# Define confidence intervals 
+#eduCI_15 <- binom.confint(x = MTurk_education_15$n, n = sum(MTurk_education_15$n), conf.level = 0.95, methods = "exact")
+#eduCI_15 <- eduCI_15[ , 4:6]
+
+# Build Education table 
+#education_table_15 <- cbind(MTurk_edu_15, eduCI_15, BLS_edu_15)
+#names(education_table_15) <- c("education level", "n", "o", "LL_eth", "UL_eth", "e")
+#education_table_15 <- education_table_15[ , c(1, 6, 2, 4, 3, 5)]
+
+# Rachel's education level
+MTurk15_R$Educ[MTurk15_R$Educ==1] <- "Less than high school"
+MTurk15_R$Educ[MTurk15_R$Educ==2] <- "High school/GED"
+MTurk15_R$Educ[MTurk15_R$Educ==3] <- "Some college"
+MTurk15_R$Educ[MTurk15_R$Educ==4] <- "2 year deg"
+MTurk15_R$Educ[MTurk15_R$Educ==5] <- "4 year deg"
+MTurk15_R$Educ[MTurk15_R$Educ==6] <- "Master's"
+MTurk15_R$Educ[MTurk15_R$Educ==7] <- "Doctoral"
+MTurk15_R$Educ[MTurk15_R$Educ==8] <- "J.D."
+MTurk15_R$Educ[MTurk15_R$Educ==9] <- "M.D."
+MTurk15_R$Age <- as.numeric(MTurk15_R$Age)
 MTurk15_R_edu <- MTurk15_R %>%
+  filter(Age >= 25) %>%
   count(Educ)
 
-no_highschool_dip_R <- length(which(MTurk15_R$Educ == "Less than high school"))
-highschool_ged_R <- length(which(MTurk15_R$Educ == "High school/GED", MTurk15_R$Educ == "Some college"))
-two_year_deg_R <- length(which(MTurk15_R$Educ == "2 year deg"))
-advanged_deg_15_R <- length(which(MTurk15_R$Educ == "4 year deg")) + length(which(MTurk15_R$Educ == "Master's")) + length(which(MTurk15_R$Educ == "Doctoral")) + length(which(MTurk15_R$Educ == "J.D.")) + length(which(MTurk15_R$Educ == "M.D."))
-
-MTurk15_R_edu <- as.data.frame(c(no_highschool_dip_R, highschool_ged, two_year_deg_R, advanged_deg_15_R))
-education_levels <- c("no high school", "high school dimploma/GED", "2 year degree", "Bachelors or higher")
-MTurk15_R_edu <- cbind(education_levels, MTurk15_R_edu)
+no_highschool_dip_R <- MTurk15_R_edu[6,2]
+highschool_ged_R <- MTurk15_R_edu[4,2]
+two_year_deg_R <- MTurk15_R_edu[1,2]
+advanged_deg_15_R <- MTurk15_R_edu[2,2] + MTurk15_R_edu[8,2] + MTurk15_R_edu[3,2] + MTurk15_R_edu[5,2] + MTurk15_R_edu[7,2]
+some_college_no_degree_15_R <- MTurk15_R_edu[9,2]
+MTurk15_R_edu <- c(no_highschool_dip_R, highschool_ged_R, some_college_no_degree_15_R, two_year_deg_R, advanged_deg_15_R)
+education_levels <- c("no high school", "high school dimploma/GED", "some college", "2 year degree", "Bachelors or higher")
+MTurk15_R_edu <- as.data.frame(cbind(education_levels, MTurk15_R_edu))
 colnames(MTurk15_R_edu) <- c("education level", "n")
-
-#Define confidence intervals 
-eduCI_15_R <- binom.confint(x = MTurk15_R_edu$n, n = sum(MTurk15_R_edu$n), conf.level = 0/95, methods = "exact")
+MTurk15_R_edu$n <- as.numeric(MTurk15_R_edu$n)
+
+# Define confidence intervals 
+eduCI_15_R <- binom.confint(x = MTurk15_R_edu$n, n = sum(MTurk15_R_edu$n), conf.level = 0.95, methods = "exact")
 eduCI_15_R <- eduCI_15_R[ , 4:6]
 
-#Build Education table 
+# Build Education table 
 education_table_15_R <- cbind(MTurk15_R_edu, eduCI_15_R, BLS_edu_15)
@@
 education_table_15_R <- education_table_15_R[ , c(1, 6, 2, 4, 3, 5)]
-
-#Education chi squared test
-edu_ch2_15_R <- as.data.frame(chi2(education_table_15_R))
-names(edu_ch2_15_R) <- c("chi2")
-row.names(edu_ch2_15_R) <- c("less than a highschool diploma","high school/GED" , "2 year degree", "bachelor's or higher")
-edu_ch2_15_R <- na.omit(edu_ch2_15_R)
-
-#Sum chi-square values.
-sum(edu_ch2_15_R$chi2, na.rm=TRUE)
+education_table_15_R$e <- round(education_table_15_R$e,2)
+
+# Chi-square test
+x15.7 <- chisq.test(education_table_15_R$n, p = round(education_table_15_R$e,3))
+
+# Result is significant. Run post-hoc pairwise comparisons. 
+x15.7[["stdres"]]
+# Under-represented: (i) no high school (-9.06) and (ii) some college (-11.51).
+# Expected: (i) 2 year degree (2.12).
+# Over-represented: (i) some college (5.60) and (ii) bachelors or higher (9.77). 
 ```
-
-## Replication Demographic Analaysis
-## 2017 Occupational Analysis 
-```{r}
-#Load datasets.
-Note: these datasets were not taken direclty from their respective sources (i.e., BLS or Qualtrics survey, respectively).
-The BLS dataset is a table describing the broader occupational categories, number of employees working in jobs that fall under one of these categories, and the relative frequency of jobs falling under said occupational category.
-The LATech dataset comes from a separate investigaiton using MTurk whereby individuals who were flagged for inattentive responding were removed from the dataset.
-#Build the BLS Table, but first establish a temp file.
-
-##BLS Data
-library(readxl)
-BLS <- read_excel("2017 BLS Data-updated.xlsx")
-BLS <- BLS[c(8,10)]
-
-#Include data on the size of the military (taken from (https://www.bls.gov/ooh/military/military-careers.htm))
-BLS <- rbind(BLS, c("Military specific occupations", 1085286))
-
-#Only major occupation groups are included in BLS
-BLS <- 
-  BLS[c(2,71,127,159,219,290,316,332,428,490,581,607,648,682,700,760,803,916,943,1046,1122,1288,427267,1),]
-
-###Rename rows and aggregate.
-BLS[1, 1] = "11-13 Management, Business, and Financial Occupations"
-BLS[2, 1] = "11-13 Management, Business, and Financial Occupations"
-BLS[3, 1] = "15-19 Computer, Engineering, and Science Occupations"
-BLS[4, 1] = "15-19 Computer, Engineering, and Science Occupations"
-BLS[5, 1] = "15-19 Computer, Engineering, and Science Occupations"
-BLS[6, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
-BLS[7, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
-BLS[8, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
-BLS[9, 1] = "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
-BLS[10, 1] = "29 Healthcare Practitioners and Technical Occupations"
-BLS[11, 1] = "31-39 Service Occupations"
-BLS[12, 1] = "31-39 Service Occupations"
-BLS[13, 1] = "31-39 Service Occupations"
-BLS[14, 1] = "31-39 Service Occupations"
-BLS[15, 1] = "31-39 Service Occupations"
-BLS[16, 1] = "41 Sales and Related Occupations"
-BLS[17, 1] = "43 Office and Administrative Support Occupations"
-BLS[18, 1] = "45 Farming, Fishing, and Forestry Occupations"
-BLS[19, 1] = "47 Construction and Extraction Occupation"
-BLS[20, 1] = "49 Installation, Maintenance, and Repair Occupations"
-BLS[21, 1] = "51 Production Occupation"
-BLS[22, 1] = "53 Transportation and Material Moving Occupation"
-BLS[23, 1] = "55 Military Specific Occupations"
-names(BLS) <- c("Var1","Var2")
-BLS$Var2 <- as.numeric(BLS$Var2)
-BLS <- aggregate(.~Var1,BLS,sum)
-
-#Add military occupation number to the overall
-BLS$Var2[14] <- BLS$Var2[13] + BLS$Var2[14]
-
-#Rename variables
-names(BLS) <- c("Intermediate Aggregation Title", "Freq")
-
-#Only keep occupational categories (no all). 
-BLS <- BLS[-14,]
-
-#Compute relative frequencies. Call the object "tab". 
-tab <- transform(BLS, relative = prop.table(Freq))
-
-#Define new BLS. "e" is for "relative frequency". 
-BLS <- tab[c(1,3)]
-names(BLS) <- c("Intermediate Aggregation Title", "e")
-
-##LATech data
-LATech <- read_excel("2017 Data.xls")
-
-###Delete unneeded data.
-LATech <- LATech[c(12, 20:21)]
-names(LATech) <- c("Self-Reported Job Title", "O*NET Occupation Title", "O*NET Job Code")
-
-###Edit data. Some participants provided incorrect codes or no codes.
-LATech[644, 3] = "41-9031.00"
-LATech[274,] = c("analyst", "analyst", "13-0000.00")
-
-###Remove unemployed cases.
-completeFun <- function(data, desiredCols) {
-  completeVec <- complete.cases(data[, desiredCols])
-  return(data[completeVec, ])
-}
-LATech <- completeFun(LATech, "O*NET Job Code")
-
-###Abbreviate data, consolidate into intermediate categories, and bind.
-LO <- LATech[c(3)]
-LO <- read.fwf(textConnection(LO$`O*NET Job Code`), 2)
-names(LO) <- c("Int.Agg.Cat")
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 11] <- "11-13 Management, Business, and Financial Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 13] <- "11-13 Management, Business, and Financial Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 15] <- "15-19 Computer, Engineering, and Science Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 17] <- "15-19 Computer, Engineering, and Science Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 19] <- "15-19 Computer, Engineering, and Science Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 21] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 23] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 25] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 27] <- "21-27 Education, Legal, Community Service, Arts, and Media Occupation"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 29] <- "29 Healthcare Practitioners and Technical Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 31] <- "31-39 Service Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 33] <- "31-39 Service Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 35] <- "31-39 Service Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 37] <- "31-39 Service Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 39] <- "31-39 Service Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 41] <- "41 Sales and Related Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 43] <- "43 Office and Administrative Support Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 45] <- "45 Farming, Fishing, and Forestry Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 47] <- "47 Construction and Extraction Occupation"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 49] <- "49 Installation, Maintenance, and Repair Occupations"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 51] <- "51 Production Occupation"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 53] <- "53 Transportation and Material Moving Occupation"
-LO$Int.Agg.Cat[LO$Int.Agg.Cat == 55] <- "55 Military Specific Occupations"
-LATech <- cbind(LATech,LO)
-
-###Build relative frequency table.
-tab <- as.data.frame(table(LO$Int.Agg.Cat, exclude=NULL))
-tab <- transform(tab, relative = prop.table(Freq))
-names(tab) <- c("Intermediate Aggregation Title","n","f")
-tab <- merge(tab,BLS, by="Intermediate Aggregation Title", all=TRUE)
-
-#Chi-square function that quantifies the discrepancy between expected and observed proportions.
-chi2 <- function(x) {
-  o <- (x$n)
-  e <- (x$e)
-  n <- sum(x$n, na.rm=TRUE)
-  ((o-(e)*(n))^2)/((e)*(n))
-}
-
-#Confidence interval formula for proportions with assymptotic intervals.
-Intervals are assymptotic because proportions cannot be less than 0 or greater than 1, which becomes problematic as proportions near 0 or 1.
-require("binom")
-CI <- binom.confint(tab$n, sum(tab$n), conf.level = 0.95, methods = "exact")
-CI <- CI[c(5:6)]
-table <- cbind(tab,CI)
-table <- table[,c(1,4,2,5,3,6)]
-ch <- as.data.frame(chi2(table))
-ch <- na.omit(ch)
-names(table) <- c("Intermediate Aggregation Title","Exp(p)","n1","LCL1","Obs(p)1","UCL1")
-
-#Sum chi-square values.
-sum(ch$`chi2(table)`, na.rm=TRUE)
-
-##Validate using chi-square function in r.
-#Function for differences in relative percentages. This is not printed in the tables, but could be used to help readers see the disparity between expected and observed proportions.
-f <- function(x) {
-  f   <- (x$f)
-  BLS <- (x$e)
-  (f-BLS)
-}
-f1 <- as.data.frame(f(table))
-
-#Print chi-square APA style.
-require(devtools)
-install_github("dgromer/apa")
-require(apa)
-##Sample 1#
-observed1 <- table$n1
-observed1 <- observed1[c(1:13)]
-expected1 <- table$`Exp(p)`
-expected1 <- expected1[c(1:13)]
-c1 <- chisq_apa(chisq.test(x = observed1, p = expected1, correct = TRUE))
-
-#Post-hoc power analysis.
-##Convert chi-squares to correlation coefficient to allow meaningful statistic.
-library(pwr)
-###Study 1
-X21 <-sum(ch$`chi2(table)`, na.rm=TRUE)
-r1 <- sqrt((X21/sum(tab$n)))
-pwr.chisq.test(w=r1,N=(sum(tab$n)),df=12,sig.level = .01)
+The average worker in 2015 was `r t15.1[["mu"]]` years of age, which was significantly older than the average MTurk worker across both samples (n~1~: M = `r round(t15.1[["mean"]],2)`, SD = `r round(t15.1[["sd"]],2)`, *t*(`r t15.1[["df"]]`) = `r round(t15.1[["t.statistic"]],2)`, *p* `r myround2(t15.1[["p.value"]])`, *d* = `r t15.1[["effect.size"]]`; n~2~: M = `r round(t15.2[["mean"]],2)`, SD = `r round(t15.1[["sd"]],2)`, *t*(`r t15.2[["df"]]`) = `r round(t15.1[["t.statistic"]],2)`, *p* `r myround2(t15.1[["p.value"]])`, *d* = `r t15.1[["effect.size"]]`).
+
+With regard to gender, the BLS suggests that labor force was slightly male-dominated (Male = `r percent(gender_table_15$e[2])`; Female = `r percent(gender_table_15$e[1])`).
+The opposite was the case for both MTurk samples (n~1~: Male = `r percent(gender_table_15$o[2])`; Female = `r percent(gender_table_15$o[1])`; n~2~: Male = `r percent(gender_table_15_R$o[2])`; Female = `r percent(gender_table_15_R$o[1])`).
+These differences were statistically significant in both cases (n~1~: *X*^2^(`r x15.3[["parameter"]]`) = `r x15.3$statistic`, *p* `r myround2(x15.3$p.value)`; n~2~:*X*^2^(`r x15.4[["parameter"]]`) = `r x15.4$statistic`, *p* `r myround2(x15.4$p.value)`, suggests that MTurk is over-represented by females (standardized residuals: n~1~ = `r  round(x15.3[["stdres"]][1],2)`; n~2~ = `r round(x15.4[["stdres"]][1],2)`).
+
+With regard to ethnicity, we examined only the published proportions for Caucasians, African Americans, and Asians.[^p] BLS summary statistics suggest that the labor force was composed of approximately `r percent(BLS_cauc)` Caucasians, `r percent(BLS_AfAm)` African Americans, and `r percent(BLS_Asn)` Asians.
+This distribution deviated significantly from both of our MTurk samples (n~1~: *X*^2^(`r x15.5[["parameter"]]`) = `r x15.5$statistic`, *p* `r myround2(x15.5$p.value)`; n~2~:*X*^2^(`r x15.6[["parameter"]]`) = `r x15.6$statistic`, *p* `r myround2(x15.6$p.value)`.
+Post-hoc testing revealed that African Americans (n~1~ = `r percent(eth_table_15$o[3])`; n~2~ `r percent(eth_table_15_R$o[3])`) were significantly under-represented (standardized residuals: n~1~ = `r round(x15.5[["stdres"]][2],2)`; n~2~ = `r round(x15.6[["stdres"]][2],2)`).
+Additionally, the "other" category (n~1~ = `r percent(eth_table_15$o[4])`; n~2~ `r percent(eth_table_15_R$o[4])`) was over-represented by MTurk (standardized residuals: n~1~ = `r round(x15.5[["stdres"]][4],2)`; n~2~ = `r round(x15.6[["stdres"]][4],2)`).
+The remaining categories were represented in a manner that was consistent with expectations.
+
+[^p]: An "other" category was created as the remainder of these three categories.
+
+With regard to education, due to a scaling issue with sample 1, we were only able to examine sample 2.[^p] We detected a significant overall deviation from expectations (n~2~:*X*^2^(`r x15.7[["parameter"]]`) = `r x15.7$statistic`, *p* `r myround2(x15.7$p.value)`).
+Specifically, both the "no high school" (MTurk = `r percent(education_table_15_R$o[1])`; BLS = `r percent(education_table_15_R$e[1])`; standardized residual = `r round(x15.7[["stdres"]][1],2)`) and the "high school diploma/GED" groups (MTurk = `r percent(education_table_15_R$o[2])`; BLS = `r percent(education_table_15_R$e[2])`; standardized residual = `r round(x15.7[["stdres"]][2],2)`) were under-represented in the MTurk sample.
+Two education levels were over-represented (4-year degree: MTurk = `r percent(education_table_15_R$o[3])`, BLS = `r percent(education_table_15_R$e[3])`, standardized residual = `r round(x15.7[["stdres"]][3])`; advanced degree: MTurk = `r percent(education_table_15_R$o[5])`; BLS = `r percent(education_table_15_R$e[5])`, standardized residual = `r round(x15.7[["stdres"]][5],2)`).
+The "2 year degree" conformed to expectations (MTurk = `r percent(education_table_15_R$o[4])`, BLS = `r percent(education_table_15_R$e[4])`, standardized residual = `r round(x15.7[["stdres"]][4],2)`).
+This overall pattern suggests that MTurk may contain more highly educated individuals than the general population.
+
+[^p]: Additionally, to be consistent with the BLS, only individuals of age 25 or older were analyzed.
+
+## Occupational Diversity (2017)
+
+Chi-square tests indicate that MTurk’s occupational diversity does not align with expectations in (*X*^2^(`r x17.1[["parameter"]]`) = `r x17.1$statistic`, *p* `r myround2(x17.1$p.value)`).
+
+```{r Barplot 2, echo = FALSE, warning = FALSE, fig.cap = "Comparing the occupational diversity of two MTurk samples with expecations based on the Bureau of Labor Statistics"}
+# Bar Plot with error bars
+Values <- c(table3[1:13,2], table3[1:13, 5])
+Group <- c("BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "Sample 3", "Sample 3", "Sample 3", "Sample 3", "Sample 3", "Sample 3", "Sample 3", "Sample 3", "Sample 3", "Sample 3", "Sample 3", "Sample 3", "Sample 3")
+Occupations <- c(as.character(table[1:13, 1]))
+Occ_Nums <- sapply(strsplit(Occupations, " "), "[[", 1)
+barplot_data <- data.frame(as.character(Values), as.character(Occupations),as.character(Group))
+names(barplot_data) <- c("Frequency", "Occupations","Group")
+dodge <- position_dodge(width = .9)
+
+# Define Error Bar limits.
+upperB <- c(0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
+upperM <- c(table3[1:13, 6])
+upper <-c(upperB, upperM)
+lowerB <- c(0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
+lowerM <- c(table3[1:13, 4])
+lower <- c(lowerB, lowerM)
+se <- data.frame(upper, lower)
+
+# Merge data
+df <- cbind(se,barplot_data)
+
+# Plot data
+ggplot(barplot_data, aes(Occupations, Values, fill = Group, ymax = upper, ymin = lower)) + 
+  geom_bar(stat="identity", position = "dodge", width = 0.7) +
+  geom_bar(stat="identity", position = "dodge", 
+                colour = "black", width = 0.7, 
+                show.legend = TRUE) +
+  scale_y_continuous(breaks = seq(0, 0.30, 0.1), 
+                limits = c(0, 0.30), 
+                expand = c(0, 0)) +
+  scale_fill_manual(name = "Groups" , 
+                 values = c('grey30', 'grey60'), 
+                 labels = c("BLS 2017", "Sample 3")) +
+  geom_errorbar(position=position_dodge(width=0.7), 
+                     width=0.0, size=0.5, color="black") +
+  #ggtitle("Occupational Diversity of MTurk") +
+  labs(x = element_blank(), y = "Proportions") +
+  theme(legend.position = c(.8,.8), 
+        #plot.title = element_text(hjust = 0), 
+        text=element_text(family="serif")) +
+  coord_flip()
 ```
 
-## 2017 Age Analysis
-```{r}
+Many of our findings from the 2017 sample mirrored those from 2015.
+Over-represented occupations again included (i) 11-13 Management, Business, and Financial (`r x17.1[["stdres"]][1]`), (ii) 15-19 Computer, Engineering, and Science (`r x17.1[["stdres"]][2]`), and (iii) 21-27 Education, Legal, Community Service, Arts, and Media (`r x17.1[["stdres"]][3]`).
+Occupations that were under-represented again included (i) 31-39 Service (`r x17.1[["stdres"]][5]`), (ii) 47 Construction and Extraction (`r x17.1[["stdres"]][9]`), (iii) 51 Production (`r x17.1[["stdres"]][11]`), and (iv) 53 Transportation and Material Moving (`r x17.1[["stdres"]][12]`).
+Lastly, occupations that appeared in a proportion that conformed with expectations included (i) 41 Sales and Related (`r x17.1[["stdres"]][6]`), (ii) 43 Office and Administrative Support (`r x17.1[["stdres"]][7]`), (iii) 45 Farming, Fishing, and Forestry (`r x17.1[["stdres"]][8]`), and (iv) 55 Military Specific (`r x17.1[["stdres"]][13]`).
+Again, these results suggests that the MTurk population contains a disproportionate share of white-collar occupations relative to blue-collar occupations.
+However, certain results deviated from the 2015 samples: (i) 49 Installation, Maintenance, and Repair (`r x17.1[["stdres"]][10]`) and (ii) 29 (Healthcare Practitioners and Technical).
+Both groups conformed with expectations in our 2017 sample.
+
+## Demographic Diversity (2017)
+
+```{r 2017 Demographic Analyses, echo = FALSE, include = FALSE}
 #Age Analysis T- Test
 #Load Dataset
-require(dplyr)
-require(readxl)
 age_demo <- read_excel("age_demo.xlsx")
@@
 
-# Define Gender data
-=======
-#Define sample size
-n <- as.numeric(667)
-
-#Run t test.
-t_value <- (samp_mean - pop_mean)/(samp_sd/sqrt(n))
-t_value
-
-#So MTurk is much younger than the population on average. We need to convert this to an effect size (Cohen's D). 
-```
-
-## 2017 Gender Analysis
-```{r}
-##Gender Analysis
+## Gender Analysis
 BLS_data <- read_excel("employment_demo.xlsx")
@@
 # Run chi-square test for gender
-x3 <- chisq.test(gender_table$n, p = round(gender_table$e,3))
-
-# Result is significant. So it appears that MTurk is largely dominated by females. We need to have an effect size describing this phenomena (e.g., a likelihood ratio).
-
-# Get BLS ethnicity data
-```
-
-##2017 Ethnicity Analysis
-```{r}
-#Ethnicity Analysis 
-#Define obs_eth
-BLS_cauc <- as.numeric(BLS_data[7, 4])/100
-BLS_AfAm <- as.numeric(BLS_data[7,5])/100
-BLS_Asn <- as.numeric(BLS_data[7,6])/100
-BLS_Hisp <- as.numeric(BLS_data[7,7])/100
-BLS_eth <- c(BLS_AfAm, BLS_Asn, BLS_cauc, BLS_Hisp)
-
-sum(BLS_eth) # Note: Estimates for the above race groups (White, Black or African American, and Asian) do not sum to (100) because data are not presented for all races.
-Persons whose ethnicity is identified as Hispanic or Latino may be of any race.
-We decided to omit the Hispanic category and compute an "other" category, which is the residual of the other racial categories.
-BLS_other <- 1.000 - sum(BLS_cauc, BLS_AfAm, BLS_Asn)
-BLS_eth <- c(BLS_AfAm, BLS_Asn, BLS_cauc, BLS_other)
-
-#Get MTurk ethnicity data (observed value)
+x17.3 <- chisq.test(gender_table$n, p = round(gender_table$e,3))
+
+# Result is significant.
+
+# Ethnicity Analysis [Note: Numbers taken from Table 1 of this webpage: https://www.bls.gov/opub/reports/race-and-ethnicity/2017/home.htm)]
+BLS_cauc_17 <- as.numeric(120176/153337)
+BLS_AfAm_17 <- as.numeric(18587/153337)
+BLS_Asn_17 <- as.numeric(9448/153337)
+BLS_other_17 <- as.numeric(1-sum(BLS_cauc_17,BLS_AfAm_17,BLS_Asn_17))
+BLS_eth <- c(BLS_AfAm_17, BLS_Asn_17, BLS_cauc_17, BLS_other_17)
+
+# Get MTurk ethnicity data (observed value)
 MTurk17$With.which.ethnicity.do.you.most.identify.[MTurk17$With.which.ethnicity.do.you.most.identify.=="Hispanic"] <- "Other"
@@
 
-#Define confidence intervals 
+# Define confidence intervals 
 ethCI <- binom.confint(x = MTurk_eth$n, n = sum(MTurk_eth$n), conf.level = 0.95, methods = "exact")
@@
 
-#Build Ethnicity table 
+# Build Ethnicity table 
 ethnicity_table <- cbind(MTurk_eth, ethCI, BLS_eth)
@@
 # Ethnicity chi squared test
-x4 <- chisq.test(ethnicity_table$n, p = round(ethnicity_table$e,3))
-# Result is significant. MTurk is under-represented by African Americans, Asians, and other ethnicities. However, it does appear to be slightly over-represented by Caucasians.
-```
-
-# Education Analysis 
-# Clean BLS Data. Get totals.
-## 2017 Education Analysis 
-```{r}
+x17.4 <- chisq.test(ethnicity_table$n, p = round(ethnicity_table$e,3))
+
+# Result is significant. Run post-hoc pairwise comparisons. 
+x17.4[["stdres"]]
+
+# MTurk is under-represented by African Americans, Asians, and other ethnicities. However, it does appear to be slightly over-represented by Caucasians.
+
 #Education Analysis 
@@
 
-# Clean MTurk Data
-MTurk_education <- MTurk17 %>%
-  count(MTurk17$What.level.of.education.have.you.completed.)
-colnames(MTurk_education) <- c("education level", "n")
-advanced_deg <- as.numeric(MTurk_education[4,2]) + as.numeric(MTurk_education[5,2])
-MTurk_education <- rbind(MTurk_education, advanced_deg)
-MTurk_education[6,1] <- "advanced degree"
-MTurk_edu <- MTurk_education[c(-4, -5), ]
+# Clean MTurk Data [Note: Due to scaling issues, we cannot analyze the education data for 2017]
+#MTurk_education <- MTurk17 %>%
+#  count(MTurk17$What.level.of.education.have.you.completed.)
+#colnames(MTurk_education) <- c("education level", "n")
+#advanced_deg <- as.numeric(MTurk_education[4,2]) + as.numeric(MTurk_education[5,2])
+#MTurk_education <- rbind(MTurk_education, advanced_deg)
+#MTurk_education[6,1] <- "advanced degree"
+#MTurk_edu <- MTurk_education[c(-4, -5), ]
 
 # Define confidence intervals 
-eduCI <- binom.confint(x = MTurk_edu$n, n = sum(MTurk_edu$n), conf.level = 0.95, methods = "exact")
-eduCI <- eduCI[ , 4:6]
+#eduCI <- binom.confint(x = MTurk_edu$n, n = sum(MTurk_edu$n), conf.level = 0.95, methods = "exact")
+#eduCI <- eduCI[ , 4:6]
 
 # Build Education table 
-education_table <- cbind(MTurk_edu, eduCI, BLS_edu)
-names(education_table) <- c("education level", "n", "o", "LL_eth", "UL_eth", "e")
-education_table <- education_table[ , c(1, 6, 2, 4, 3, 5)]
+#education_table <- cbind(MTurk_edu, eduCI, BLS_edu)
+#names(education_table) <- c("education level", "n", "o", "LL_eth", "UL_eth", "e")
+#education_table <- education_table[ , c(1, 6, 2, 4, 3, 5)]
 
 # Education chi squared test
-x5 <- chisq.test(education_table$n, p = round(education_table$e,3))
+#x17.5 <- chisq.test(education_table$n, p = round(education_table$e,3))
 # Result is  significant. MTurk contains an unexpected proportion of education.
 ```
-
-## Exploratory Analyses of Other Demographics
-
-The average worker in 2017 was `r t[["mu"]]` years of age, which was significantly older than the average MTurk worker (M = `r round(t[["mean"]],2)`, SD = `r round(t[["sd"]],2)`, *t*(`r df`) = `r tvalue`, *p* `r pvalue`, *d* = `r d`).
-
-With regard to gender, the BLS provides a summary statistic only for the proportion of the labor force that identifies with the female gender, which in 2017 was `r percent(BLS_women)`.
-The difference compared to our MTurk sample, `r percent(gender_table$o[1])` of which were women, was significant `r chisq_apa(x3)` and suggests that MTurk is over-represented by females (standardized residual = `r  round(x3[["stdres"]][1],2)`).
-
-With regard to ethnicity, as the BLS provides estimates for race groups that do not sum to 100% (because subgroups identified as Hispanic or Latino may also be of any race), we elected to examine only the published proportions for Caucasians, African Americans, and Asians (an "other" category was created as the residual of these three categories).
-BLS summary statistics suggest that the labor force was composed of approximately `r percent(BLS_cauc)` Caucasians, `r percent(BLS_AfAm)` African Americans, and `r percent(BLS_Asn)` Asians.
-This distribution deviated significantly from our our MTurk sample `r chisq_apa(x4)`.
-Post-hoc testing revealed that African Americans (`r percent(ethnicity_table$o[1])`) were significantly under-represented  (standardized residual = `r round(x4[["stdres"]][1],2)`).
-Additionally, the "other" category `r percent(ethnicity_table$o[4])` was over-represented by MTurk (standardized residual = `r round(x4[["stdres"]][4],2)`).
-This overall pattern suggests that MTurk may over-represent historically disadvantaged populations, at least in the US.
-
-With regard to education, after aligning the measures used by the BLS with that used in our study, we found a significant overall deviation `r chisq_apa(x5)` from expectations.
-Specifically, the 2-year degree (MTurk = `r percent(education_table$o[1])`; BLS = `r percent(education_table$e[1])`) was under-represented by the MTurk population (standardized residual = `r round(x5[["stdres"]][1])`).
-By contrast, the remaining education levels were over-represented (4-year degree: MTurk = `r percent(education_table$o[2])`; BLS = `r percent(education_table$e[2])`; high school/GED: MTurk = `r percent(education_table$o[3])`; BLS = `r percent(education_table$e[3])`; advanced degree: MTurk =  `r percent(education_table$o[4])`; BLS = `r percent(education_table$e[4])`), as indicated by standardized residuals (`r round(x5[["stdres"]][2])`, `r round(x5[["stdres"]][3])`, `r round(x5[["stdres"]][4])`).
-If we view the over-representation of high school/GED holders as more in-line with expectations than our cutoffs indicate, then we can see a clearer over-representation of more highly educated workers on MTurk (i.e., 4-year degree and advanced degree holders).
+The average worker in 2017 was `r t[["mu"]]` years of age, which again was significantly older than the average MTurk worker (M = `r round(t[["mean"]],2)`, SD = `r round(t[["sd"]],2)`, *t*(`r t[["df"]]`) = `r round(t[["t.statistic"]],2)`, *p* `r myround2(t[["p.value"]])`, *d* = `r round(t[["effect.size"]],2)`).
+
+With regard to gender, the BLS suggests that labor force was slightly male-dominated (Male = `r percent(gender_table$e[2])`; Female = `r percent(gender_table$e[1])`).
+Again, the opposite was the case for the MTurk sample (Male = `r percent(gender_table$o[2])`; Female = `r percent(gender_table$o[2])`.
+This difference was statistically significant in (*X*^2^(`r x17.3[["parameter"]]`) = `r round(x17.3$statistic,2)`, *p* `r myround2(x17.3$p.value)`), again suggesting that MTurk is over-represented by females (standardized residual = `r  round(x17.3[["stdres"]][1],2)`).
+
+With regard to ethnicity, again we examined only the published proportions for Caucasians, African Americans, and Asians.
+BLS summary statistics suggest that the labor force was composed of approximately `r percent(BLS_cauc_17)` Caucasians, `r percent(BLS_AfAm_17)` African Americans, and `r percent(BLS_Asn_17)` Asians.
+Again, this distribution deviated significantly from our our MTurk sample (*X*^2^(`r x17.4[["parameter"]]`) = `r round(x17.4$statistic,2)`, *p* `r myround2(x17.4$p.value)`.
+Post-hoc testing revealed that, again, African Americans (MTurk = `r percent(ethnicity_table$o[1])`) were significantly under-represented (BLS = `r percent(ethnicity_table$e[1])`; standardized residual = `r round(x17.4[["stdres"]][1],2)`).
+Additionally, the "other" category `r percent(ethnicity_table$o[4])` was over-represented by MTurk (standardized residual = `r round(x17.4[["stdres"]][4],2)`).
+The remaining categories conformed to expectations.[^p]
+
+[^p]: Again, education was not analyzed due to a scaling issue.
 
@@
 Answering these questions might unearth more constraints that impinge on the findings of occupational studies using MTurk.
-
 \newpage
+
 # References

### 2018-12-09 Manuscript.Rmd
Remove fifer and upload packrat.

@@
 library(openxlsx)       # Reading data
-library(fifer)          # Post hoc chi-sqaure testing
 library(binom)          # Confidence intervals for proportions
@@
 library(tidyr)          # Package helps us analyze Rachel's data 
+library(packrat)        # Enhance reproducibility
 ```

### 2018-12-22 Manuscript.Rmd

@@
 ---
-title             : "Comparing the Occupational and Demographic Diversity of Amazon's Mechanical Turk to the U.S. Labor Force"
+title             : "Comparing the Occupational and Demographic Diversity of the Labor Force that is Accessible via MTurk (United States)"
 shorttitle        : "MTurk's Occupational Diversity"
@@
     affiliation   : "1"
-  - name          : "Rachel L. Williamson"
+  - name          : "Rachel Williamson Smith"
     affiliation   : "2"
-  - name          : "John E. Buckner"
+  - name          : "James DeLeon"
     affiliation   : "3"
@@
     affiliation   : "4"
-  - name          : "James DeLeon"
+  - name          : "John E. Buckner"
     affiliation   : "5"
+
 affiliation:
@@
   - id            : "3"
-    institution   : "AlixPartners"
+    institution   : "APTMetrics"
   - id            : "4"
@@
   - id            : "5"
-    institution   : "APTMetrics"
+    institution   : "AlixPartners"
 
 author_note: >
-  All correspondence should be sent to the lead author at chris_castille@mac.com.
-We would like to thank Bryan Bunn and Maximillian Sinn for taking the time to offer a friendly review of this manuscript.
+  We have sought to make this project fully reproducible.
+All project materials can be found on the Open Science Framework (https://osf.io/r7mjt/), where elements of this study were pre-registered (https://osf.io/fdgew/).
+A previous version of this manuscript was presented at the 2017 annual conference for the Society for Industrial & Organizational Psychology, Inc., in Orlando, FL.
+It should also be noted that data collection for one of the 2015 samples was funded by the Graduate School Dean's Award Program at the University of Georgia.
 
 abstract: >
-  We compare the occupational diversity of three conveniently gathered MTurk samples (two in 2015, one in 2017) against the broader US labor force from which they have been indirectly sampled.
-We focus on occupational diversity given concerns regarding the the generalizability of findings into organizational life that have been drawn from studies utilizing MTurk.
-Additionally, as researchers may hope to target specific populations (e.g., sales professionals) understanding the extent to which these professionals are over- or under- represented in the MTurk population would inform decisions regarding the cost-effectiveness of sampling techniques.
-Across our samples, we found differences suggesting that the MTurk population is generally overrepresented by white collar professionals (though this is an imperfect trend).
-Other demographic trends were also explored regarding age, gender, and education.
-Overall, the MTurk population appears to fall short of an ideal representation of the broader labor force.
+  Scholars interested in studying behavioral phenomena of relevance for organizational settings have increasingly relied upon Amazon's Mechanical Turk.
+MTurk offers opportunities for examining a wide range of occupational settings, greatly expanding the ability of scholars' ability to generate generalizable inferences from sample data.
+However, little research has compared the occupational makeup of the labor force that is accessible via MTurk to the broader labor force from which they are indirectly sampled.
+This is crucial to understand given the importance of the work context for organizational scholarship.
+Here, we compare the occupational diversity of three conveniently gathered MTurk samples (two in 2015, one in 2017) against the broader broader labor force from which they have been indirectly sampled in the United States.
+Across our samples, we consistently found differences suggesting that the MTurk population is generally overrepresented by certain white-collar professions (e.g., Management, Business, and Financial; Computer, Engineering, and Science; Education, Legal, Community Service, Arts, and Media) and underrepresented by blue-collar professions (e.g., Production; Transportation and Material Moving).
+Other demographic trends mirrored broader demographic trends identified with prior MTurk research with regard to age (younger), gender (female-biased), ethnicity (e.g., African Americans underrepresented), and education (generally overeducated).
+Overall, our conclusions mirror add to the published literature by indicating that the labor force that is accessible via MTurk does not reflect the broader labor force.
 
@@
 
-wordcount         : "3000"
+wordcount         : "3919"
 
@@
 
-figsintext        : yes
+figsintext        : no
 figurelist        : no
@@
 class             : "man"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_docx
 ---
@@
 library(papaja)         # Print in apa style
+library(dplyr)          # Manipulating data
+library(citr)           # Citation assistance
 library(readr)          # Reading data
 library(readxl)         # Reading data
-library(data.table)     # Reading data
 library(openxlsx)       # Reading data
@@
 library(tidyquant)      # Used in demographic analysis
-library(lsr)            # Useful for conducting one-sample t-tests and estiamting Cohen's D
-library(stringr)        # Package helps us analyze Rachel's data
-library(tidyr)          # Package helps us analyze Rachel's data 
-library(packrat)        # Enhance reproducibility
+library(lsr)            # Useful for conducting one-sample t-tests and estimating Cohen's D
+library(stringr)        # Package helps us analyze the UGA data
+library(tidyr)          # Package helps us analyze the UGA data 
+library(rIP)            # Facilitates screening data for bots
+library(DataCombine)    # Adding rows to tables to allow easier reading
 ```
 # Introduction
-Amazon’s Mechanical Turk (MTurk), an online labor market created by Amazon, has recently become popular among social scientists interested in collecting inexpensive, high-quality data from a diverse population [@aguinisConductingFieldExperiments2012; @behrendViabilityCrowdsourcingSurvey2011; @bergmanWhereHaveAll2016; @paolacciTurkUnderstandingMechanical2014; @shankUsingCrowdsourcingWebsites2016].
-Leveraging the strengths of this tool, MTurk has been used by social scientists to replicate well-known phenomena [e.g., reaction times, priming, task switching, see @crumpEvaluatingAmazonMechanical2013; memory, see @simonsCommonMisBeliefs2012 and by organizational behavior (OB) researchers to expand the OB literature [e.g., @yarkoniInteractionsDonorAgreeableness2015].
-
-Yet, in spite of the growing enthusiasm surrounding the use of MTurk, it represents merely another convenient sampling methodology that comes with a few constraints, such as repeated participation or motivation due to compensation [@landersInconvenientTruthArbitrary2015; @wooAmazonMechanicalTurk2015] and other yet-to-be-identified constraints.
-Here, we examine one potentially important constraint for using MTurk to conduct OB research: the occupational diversity of MTurk.
-Given that a fundamental goal of most OB research is that workers are sampled from an appropriate organizational setting, understanding the occupational diversity of MTurk will improve our understanding of the boundary conditions or limits to the generalizability of MTurk research findings.
-By examining the occupational diversity of MTurk, our work addresses a call for research that describes the kinds of individuals who participate in MTurk studies [@griggsWhoAreThese2016].
-
-# Review of the Literature
-
-## What is MTurk?
-MTurk is an internet marketplace where people seeking laborers have access to a population of workers willing to do tasks requiring a human intelligence for a small fee [@landersInconvenientTruthArbitrary2015].
-Billed as a “marketplace for work that requires human intelligence”, MTurk allows “requesters” to post Human Intelligence Tasks (HITs), which serve as self-contained jobs in which “workers” can participate.
-Via MTurk, researchers seeking participants often post survey studies for workers to voluntarily complete.
-Workers are given a short description about a project, including details about various tasks, estimated time investment, and payment, and may selectively choose which projects to complete.
-Here, researchers seeking participants often post survey studies for workers to voluntarily complete.
-
-## The Value of Studying Working Populations with MTurk
-
-MTurk offers practical advantages that may not be available via other more traditional methods of data collection, such as sampling from specific organizations .
-The platform allows for easier subject pool access at an affordable cost and for subject prescreening [@masonConductingBehavioralResearch2012].
-Additionally, it allows for subject anonymity, subject identifiability in longitudinal studies, and offers a simple and supportive infrastructure [@paolacciRunningExperimentsAmazon2010].
-More importantly, its diversity is a key strength that sets it apart from other commonly studied populations (e.g., university students, community samples), making it an attractive subject pool for researchers to draw upon [@buhrmesterAmazonMechanicalTurk2011; @erikssonWhatAmericansKnow2012; @paolacciRunningExperimentsAmazon2010].
-For instance, @behrendViabilityCrowdsourcingSurvey2011 found that MTurk workers are more diverse on variables such as age, ethnicity, education, employment status, job experience, profession, nationality, and personality.
-The diversity of MTurk allows OB researchers to overcome concerns regarding the generalizability of their findings [@paolacciRunningExperimentsAmazon2010], which has been a key concern facing OB research [@henrichWeirdestPeopleWorld2010].
-
-However, while researchers have praised MTurk for its diversity, few organizational behavior researchers have considered how MTurk might be less diverse than expected in a key respect: occupational diversity.
-To our knowledge, no study has compared the occupational diversity of MTurk to the broader US population.
-While @behrendViabilityCrowdsourcingSurvey2011 work suggests that MTurk’s occupational diversity is greater than the university population, our work expands on their research by comparing MTurk’s occupational diversity to the broader US population.
-If the occupational diversity of the broader US population is indeed reflected in MTurk, findings from MTurk should better generalize across occupations.
-Alternatively, if MTurk’s occupational diversity over- or under-represent certain occupations, generalizability of findings from MTurk should be more limited.
-
-*Research Question 1: Is the occupational diversity of the MTurk population representative of the broader US labor force?*
-
-In addition to examining occupational diversity, we conducted exploratory analyses of other demographic disparities, focusing in on age, gender, ethnicity, and education as these are commonly studied in the social sciences.
-Therefore, a second research question was examined, but in an exploratory fashion.
-Answering this question required that we describe the diversity of the US labor force.
-Fortunately, the BLS provides summary statistics which describe the proportion of individuals falling into various demographic categories.
-
-*Research Question 2: Is the demographic diversity of the MTurk population representative of the broader US labor force?*
+
+Amazon’s Mechanical Turk (MTurk), an online labor market created by Amazon, has been popular among social scientists interested in collecting inexpensive, high-quality data from a diverse population for well [@aguinisConductingFieldExperiments2012; @ahlerMicroTaskMarketLemons2018; @bergmanWhereHaveAll2016; @behrendViabilityCrowdsourcingSurvey2011; @kennedyShapeSolutionsMTurk2018; @landersInconvenientTruthArbitrary2015; @paolacciTurkUnderstandingMechanical2014].
+The platform allows for easier subject pool access at an affordable cost and for subject prescreening [@masonConductingBehavioralResearch2012], subject anonymity or identifiability (which is important for longitudinal studies), and offers a simple and supportive infrastructure [@paolacciRunningExperimentsAmazon2010].
+Leveraging the strengths of this tool, MTurk has been used to replicate a variety of well-known phenomena in the social sciences [e.g., reaction times, priming, task switching, see @crumpEvaluatingAmazonMechanical2013; memory, see @simonsCommonMisBeliefs2012].
+
+Scholars who study organizational phenomena (e.g., organizational behaviorists, industrial and organizational psychologists, management scholars) have also adopted MTurk.
+@keithSystemsPerspectiveAmazon2017 recently reported that published organizational science studies utilizing MTurk increased by 800% between 2012 and 2015.
+When comparing crowdsourcing tools like MTurk with traditional methods of studying organizational phenomena [e.g., gaining consent from both institutional review boards and local organizations; see @ilgenConductingIndustrialOrganizational2001], several benefits are particularly salient, such as rapidly gaining access to multiple organizational settings and enhanced external validity.
+Such benefits can greatly reduce the cost of studying organizational phenomena, leveling the research playing field [@goodmanDataCollectionFlat2013].
+
+As enthusiasm surrounding the use of MTurk in the organizational sciences has grown, so have scholars' concerns over its use [e.g., @cheungAmazonMechanicalTurk2017; @landersInconvenientTruthArbitrary2015; @keithSystemsPerspectiveAmazon2017; @wooAmazonMechanicalTurk2015].
+One problematic area relates to an assumption underlying research into organizational phenomena that draws on MTurk; namely, that the MTurk workers themselves represent a broad cross-section of the labor force population.
+This assumption is key to a commonly cited benefit of using crowdsourcing tools like MTurk; that is, increased generalizability [e.g., @aguinisConductingFieldExperiments2012; @behrendViabilityCrowdsourcingSurvey2011; @highhouseNewFruitFly2015; @keithSystemsPerspectiveAmazon2017; @roulinDonThrowBaby2015].
+In other words, organizational scholars may assume that MTurk can be used to indirectly and *adequately* sample from the broader working population.
+Unfortunately, little research has compared MTurk worker demographics to that of the broader labor force.
+If MTurk does not adequately reflect the broader labor force, then the generalizability of research drawing on MTurk will have its own set of constraints [@keithSystemsPerspectiveAmazon2017; @landersInconvenientTruthArbitrary2015].
+
+Here, we compare the working subpopulation of the U.S.
+MTurk workforce to the broader labor force from which they were indirectly sampled.
+Given the importance of context in organizational research [@johnsEssentialImpactContext2006; @judgeBrightDarkSides2007; @newmanExternalValidityMultiorganization2015], we focus specifically on the extent to which the labor force that is sampled via MTurk adequately represents the broader labor force.
+Our study, which fits into the broader body of literature regarding who we study and the generalizability of claims made in the social sciences [e.g., @paolacciRunningExperimentsAmazon2010; @henrichWeirdestPeopleWorld2010], thus contributes to the wealth of knowledge that exists on the demographics of the MTurk population.
+It also informs future research on the study of organizational phenomena via MTurk.
+
+# Examining the Occupational and Demographic Makeup of the U.S. Labor Force that is Sampled Indirectly from Amazon's Mechanical Turk
+
+Over half of the MTurk population is employed [@behrendViabilityCrowdsourcingSurvey2011; @keithSystemsPerspectiveAmazon2017; @levayDemographicPoliticalComposition2016].
+If the total MTurk population contains over 100,000 people [@difallahDemographicsDynamicsMechanical2018], there is a sizable subpopulation of individuals whom we may invite to participate in our research.
+Even if only a few thousand individuals can be sampled from [see @stewartAverageLaboratorySamples2015], this can still be helpful for organizational scholarship (e.g., measurement refinement).
+It might even be useful for examining understudied phenomena or populations of workers [e.g., job search behavior, underemployment, unemployed; see @roulinDonThrowBaby2015].
+
+By using MTurk to sample workers from a wide range of occupational settings, it has widely been believed that scholars' ability to generate inferences with greater external validity from sample data has increased [@aguinisConductingFieldExperiments2012; @highhouseNewFruitFly2015; @smithConvenientSolutionUsing2015].
+MTurk's diversity on variables such as age, ethnicity, education, employment status, job experience, profession, nationality, and personality [@behrendViabilityCrowdsourcingSurvey2011] is commonly cited as a strength that sets it apart from other commonly studied populations (e.g., university students, community samples), making it an attractive subject pool for organizational scholars to draw upon [@buhrmesterAmazonMechanicalTurk2011; @erikssonWhatAmericansKnow2012; @paolacciRunningExperimentsAmazon2010].
+
+While several studies have examined the attributes of the MTurk population [e.g., demographic, occupational, psychographic, etc.; see @behrendViabilityCrowdsourcingSurvey2011; @michelAmazonMechanicalTurk2018], only one has compared the occupational makeup of MTurk [i.e., @michelAmazonMechanicalTurk2018].
+By comparing the occupational makeup (or occupational heterogeneity or diversity) of a sample of U.S.
+MTurk respondents to the labor force, @michelAmazonMechanicalTurk2018 inferred that MTurk workers are broadly sampled from various occupational areas.
+For instance, they noted that the largest MTurk subpopulation was from the "Education and Training" career cluster, comprising approximately 13% of responses.
+They point out that a majority of the career clusters were within a 5% difference range when compared with corresponding career clusters as defined by the Bureau of Labor Statistics.
+They also point out that the most undersampled population was "Business Management and Administration."
+
+Michel et al.'s (2018) study is important for prompting conversation about how the occupational diversity of MTurk compares to the broader labor force.
+However, while informative, Michel et al.'s (2018) study has notable shortcomings that we sought to overcome.
+First, Michel et al.
+sought to determine if MTurk workers are broadly distributed across the labor market.
+While they did indeed answer this question, a statistical test would challenge a key assumption that might be adopted (implicitly or explicitly) by organizational researchers who use MTurk; namely, that the labor force accessed through MTurk is comparable to the broader labor force.
+Examining this assumption statistically is important because if we cannot assume that MTurk gives us a comparable cross section of the labor force, then our conclusions will be biased in favor of over- or under-sampled sampled areas.
+It is also worth pointing that that, since we have data spread across multiple years (2015 and 2017), we have an opportunity to examine the pervasiveness of trends in occupational and demographic makeup of the workforce that is accessed via MTurk.
+If MTurk has a particular and pervasive bias in favor of certain occupational areas, then increasing our reliance on MTurk might will not bring about the purported benefits.
+Rather, such a growing reliance will prevent us from overcoming concerns that our knowledge base applies only to certain kinds of workers [e.g., core, salaried, managerial; @bergmanWhereHaveAll2016].
+
+Second, Michel et al.
+relied on labor force descriptions from 2013.
+If we assume that Michel et al.'s data were also gathered in the same year, then - given that roughly half of the workers leave MTurk within each year [@difallahDemographicsDynamicsMechanical2018; @stewartAverageLaboratorySamples2015] - Michel et al.'s conclusions may no longer accurately describe the labor force that is accessible via MTurk.
+Having some idea regarding the composition of the labor force that is accessible via MTurk can inform sampling practices.
+For instance, if a researcher hopes to examine sales professionals, then knowing whether or not this population is historically underrepresented by MTurk can be useful for deciding whether or not to sample workers from MTurk.
+
+In sum, though prior work suggests that the labor force that is accessible via MTurk is quite diverse in terms of occupations, our work expands the literature by (1) clarifying the extent to which this heterogeneity aligns with the broader and indirectly sampled labor force and (2) showing the pervasiveness of these trends.
+If the occupational diversity of the broader U.S.
+population is indeed reflected by MTurk, then findings from MTurk's labor force should better generalize across occupations.
+Alternatively, if MTurk’s occupational diversity consistently over- or under-represents certain occupations, then the generalizability of findings from MTurk may be more limited than has been appreciated.
+Therefore, we begin our investigation by clarifying our focal research question.
+
+*Research Question 1: Does the occupational diversity of the labor force that is accessible via MTurk adequately represent the broader U.S. labor force?*
+
+In addition to examining the occupational makeup of the labor force that is accessible via MTurk, we examine other demographic attributes, focusing in on age, gender, ethnicity, and education, as these are commonly studied in the organizational sciences [e.g., @berryInterpersonalDevianceOrganizational2007; @collinsRaceJobApplicants1998; @dalalMetaAnalysisRelationshipOrganizational2005].
+While there is much prior research on MTurk, it describes broad trends associated with the MTurk population in general, which may or may not generalize to the subpopulation that is also part of the labor force.
+For the U.S., the general MTurk population seems to be younger and slightly female-biased [@difallahDemographicsDynamicsMechanical2018].
+Compared to college students and community samples, it is more diverse in terms of education [@behrendViabilityCrowdsourcingSurvey2011; @goodmanDataCollectionFlat2013].
+In comparing MTurk samples to nationally representative samples (e.g., U.S.
+Census, Survey USA), @keithSystemsPerspectiveAmazon2017 also note that MTurk samples are younger, more educated.
+Knowing the extent to which the labor force that is accessible via MTurk mirrors the broader labor force, demographically speaking, would also be informative for the same reasons noted for RQ1.
+Given that no prior work has conducted this comparison, we sought to answer a second research question.
+
+*Research Question 2: Does the demographic diversity (age, gender, ethnicity, and education) of the labor force that is accessible via MTurk adequately represent of the broader U.S. labor force?*
 
@@
 
-## US Population Occupational Summary Statistics
-
-Occupational Employment Statistics were obtained from the United States Bureau of Labor Statistics (BLS) both from years 2015 and 2017.
-These data are released annually in the spring and describe the previous year.
-Statistics from these reports allowed us to define expectations regarding the proportion of workers falling into a particular intermediate occupational category.
-We adopted the Intermediate Aggregation and Standard Occupational Classification (SOC) used by the Bureau of Labor Statistics (BLS) for this study to ease our analysis.
+## U.S. Population Occupational Information
+
+Occupational Employment Statistics were obtained from the BLS (BLS) both from years 2015 and 2017 to correspond with the MTurk samples, which were also gathered from the same years.
+These years for chosen because those are the years for which we have relevant data on MTurk.
+The BLS data are released annually in the spring and describe the previous year.
+Statistics from these reports allowed us to define expectations regarding the proportion of workers falling into a particular occupational category.
+For the sake of consistency, we adopted the Intermediate Aggregation and Standard Occupational Classification (SOC) used by the BLS for this study.
 
@@
 # unzip("BLS2015.zip")
-BLS <- read_excel("oesm15nat/national_M2015_dl.xlsx")
+BLS <- read_excel("Data/oesm15nat/national_M2015_dl.xlsx")
 BLS <- BLS[c(2,4)]
@@
 
-# Delete unneeded data.
+# Delete unneeded variables.
 LATech <- LATech[c(1:3)]
@@
 
+# Filter out cases from foreign countries and questionable IP addresses.
+# Conditionally delete cases that were flagged for being either out of the country (C) or blocked B (B).
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Co-FOunder"),] # C
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="senior analyst"),] # C
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Supply Chain Cordinator"),] # C
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Assistant Manager" & LATech$`O*NET Occupation Title` =="First-Line Supervisors of Food Preparation and Serving Workers"),] # C
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="residential care aide"),] # C
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Receptionist"),] # C
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Global Training Lead"),] # C
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="residential care worker"),] # C
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Navigation Officer"),] # C
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Assembly Supervisor"),] # C
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="x-ray tech"),] # C
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Financial Analyst"),] # C
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Financial Advisor" & LATech$`O*NET Occupation Title` =="Financial Managers, Branch or Department"),] # C
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Project Manager" & LATech$`O*NET Occupation Title` =="Information Technology Project Managers"),] # C
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Manufacturing Engineer"),] # C
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Computer Programmer"),] # C
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Staff Assistant"),] # C
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Communications Engineer"),] # C
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="engineering apprentice"),] # C
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="IT specialist"),] # C
+LATech <-LATech[-c(511),] # C Deleting a random cashier because we cannot identify which cashier was from Nepal. 
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Telephone systems analyst"),] # C
+LATech <-LATech[-c(697),] # C Deleting a random plumber because we cannot identify which plumber was from the Philippines. 
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="photo editor"),] # C
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Hydro-Tech III"),] # C
+LATech <-LATech[-c(147),] # C Deleting a random software engineer because we cannot identify which software engineer was from Sweeden.
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Carpenter" & LATech$`O*NET Occupation Title` =="Carpenter"),] # C
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Retail Sales Associate"),] # C
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Manufacturing Producer"),] # B
+LATech <-LATech[-c(488),] # B Deleting a random nanny because we cannot identify which nanny was questionable
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Process Engineer"),] # B
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Account Manager"),] # B
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="engineer" & LATech$`O*NET Occupation Title` =="media engineer"),] # B
+LATech <-LATech[-c(538),] # B Deleting a random sales associate because we cannot identify which sales associate was questionable.
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Social Worker"),] # B
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="producer"),] # B
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Stock Clerk"),] # B
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="therapist"),] # B
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Stockboy"),] # B
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Production engineer Lead"),] # B
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="TSO"),] # B
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Multimedia Animator"),] # B
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Assistant Seafood Manager"),] # B
+LATech <-LATech[-c(147),] # B Deleting a random software engineer because we cannot identify which software engineer was questionable.
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Accounts Payable clerk"),] # B
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Customer Service Staff"),] # B
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="PSD"),] # B
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Special Education"),] # B
+LATech <-LATech[!(LATech$`Self-Reported Job Title`=="Pharmacisy technician"),] # B
+
 # Remove unemployed cases.
@@
 # UGA data
-UGA <- read_excel("Data/Rachel's Data from 2015.xlsx")
+UGA <- read_csv("Data/Rachel's Data from 2015.csv")
+
+# Filter out cases from foreign countries and questionable IP addresses.
+UGA <- filter(UGA, countryName == "United States") # Results in a loss of 46 cases.
+According to the Mechanical Turk Worker Website FAQ, US citizens are not allowed to work on MTurk.
+We therefore deemed cases falling outside the US as questionable and ommitted them from our studies.
+UGA <- filter(UGA, block == "0") # Results in a loss of 22 cases (though 25 cases were flagged for questionable IP addresses).
+# retain only needed variables
 UGA <- UGA[c(2,21)] 
@@
 x15.1[["stdres"]]
-# Significantly over-represented: (i) 11-13 Management, Business, and Financial (6.94), (ii) 15-19 Computer, Engineering, and Science (11.97), and (iii) 21-27 Education, Legal, Community Service, Arts, and Media (8.17).
-# Conforming with expectations: (i) 29 Healthcare Practitioners and Technical (0.58), (ii) 41 Sales and Related (-2.47), (iii) 43 Office and Administrative Support (1.15), (iv) 45 Farming, Fishing, and Forestry (-0.22), and (v) 55 Military Specific (-1.37).
-# Significantly under-represented: (i) 31-39 Service (-6.33), (ii) 47 Construction and Extraction (-3.40), (iii) 49 Installation, Maintenance, and Repair (-4.51), (iv) 51 Production (-5.47), and (v) 53 Transportion and Material Moving (-5.69).
 
@@
 x15.2[["stdres"]]
-# Significantly over-represented: (i) 11-13 Management, Business, and Financial (14.76), (ii) 15-19 Computer, Engineering, and Science (8.52), and (iii) 21-27 Education, Legal, Community Service, Arts, and Media (7.30).
-# Conforming with expectations: (i) 41 Sales and Related (-1.70), (ii) 43 Office and Administrative Support (1.17), (iii) 45 Farming, Fishing, and Forestry (0.43), and (iv) 55 Military Specific (-1.76).
-# Significantly under-represented: (i) 29 Healthcare Practitioners and Technical (-3.32), (ii) 31-39 Service (-5.57), (iii) 47 Construction and Extraction (-4.72), (iv) 49 Installation, Maintenance, and Repair (-5.98), (v) 51 Production (-5.44), and (vi) 53 Transportion and Material Moving (-7.29).
 
@@
 
-# C217 data
-C217 <- read_excel("2017 Data.xls")
-
-# Delete unneeded data.
-C217 <- C217[c(12, 20:21)]
-names(C217) <- c("Self-Reported Job Title", "O*NET Occupation Title", "O*NET Job Code")
-
-# Edit data. Some participants provided incorrect codes or no codes.
-C217[153, 3] = "43-3011.00" 
-C217[412, 3] = "43-5081.03" # Provided two codes; picked the first code.
-C217[612, 3] = "43-3031.00"
-C217[644, 3] = "41-9031.00"
+# 2017 data
+C217 <- read_csv("Data/C217.csv")
+C217 <- C217[c(12, 20:21, 258, 259)]
+names(C217) <- c("Self-Reported Job Title", "O*NET Occupation Title", "O*NET Job Code", "countryName", "block")
+C217$`O*NET Job Code`[C217$`O*NET Job Code` == "43-3011.00	Bill and Account Collectors"] = "43-3011.00" 
+C217$`O*NET Job Code`[C217$`O*NET Job Code` == "43-5081.03 and 41-4012.00"] = "43-5081.03" # Provided two codes; picked the first code.
+C217$`O*NET Job Code`[C217$`O*NET Job Code` == "43-3031.00 - Bookkeeping, Accounting, and Auditing Clerks"] = "43-3031.00"
+C217$`O*NET Job Code`[C217$`O*NET Job Code` == "42-9031.00"] = "41-9031.00"
+
+# Filter out cases from foreign countries and questionable IP addresses.
+C217 <- filter(C217, countryName == "United States") # Results in a loss of 30 cases.
+According to the Mechanical Turk Worker Website FAQ, US citizens are not allowed to work on MTurk.
+We therefore deemed cases falling outside the US as questionable and ommitted them from our studies.
+C217 <- filter(C217, block == "0") # Results in a loss of 21 cases (though 25 cases were flagged for questionable IP addresses).
+# drop the two auxiliary variables
+C217 <- C217[c(-4,-5)]
+
+# Address missing data for one case.
 C217[274,] = c("analyst", "analyst", "13-0000.00")
-
-# Remove unemployed cases.
-C217 <- completeFun(C217, "O*NET Job Code")
 
@@
 x17.1[["stdres"]]
-# Significantly over-represented: (i) 11-13 Management, Business, and Financial (8.23), (ii) 15-19 Computer, Engineering, and Science (9.56), and (iii) 21-27 Education, Legal, Community Service, Arts, and Media (6.30).
-# Conforming with expectations: (i) 29 Healthcare Practitioners and Technical (-2.52), (ii) 41 Sales and Related (-2.23), (iii) 43 Office and Administrative Support (2.36), (iv) 45 Farming, Fishing, and Forestry (1.42), (v) 49 Installation and Maintenance (-2.10), and (vi) 55 Military Specific (-1.02).
-# Significantly under-represented: (i) 31-39 Service (-6.05), (ii) 47 Construction and Extraction (-4.68), (iii) 51 Production (-4.47), and (iv) 53 Transportion and Material Moving (-5.57).
 ```
-
-## MTurk Occupational Summary Statistics
-
-In 2015, participants’ data were collected from two independently conducted studies (n~1~ = `r nrow(LATech)`; n~2~ = `r nrow(UGA)`) for purposes that were not directly related to the purpose of this study (i.e., investigating psychological phenomena in organizational life).
-Data collected in 2017 (n~3~ = `r nrow(C217)`) can be similarly described.
-For two samples (2015; n~1~ =`r nrow(LATech)`; 2017; n~3~ =`r nrow(C217)`), occupational data were self-reported by participants who were asked to described their job title.
-They were then brought to ONET online and asked to retrieve the six-digit occupational classification code that most closely corresponded to their job title.
-In another sample (n~2~ = `r nrow(UGA)`), participants again self-reported their job title.
-However, the six-digit occupational classification codes were obtained by training research assistants to match the self-reported job titles to those in the ONET database.
-Using this data, we described the occupational diversity of each sample using relative frequencies of occupational category representation.
-Table 1 contains statistics for 2015.
-Table 2 contains statistics for 2017.
-
-```{r Table 1, results="asis"}
-papaja::apa_table(table, 
-                  caption = "Proportions of individuals sampled from each intermediate occupational category in 2015.",
-                  landscape = TRUE,
-                  note = "n = sample; 1 or 2 = sample 1 or 2, accordingly; LL = lower 95% confidence limit; Obs = observed proportion; UL = upper 95% confidence limit.")
-```
-```{r Table 2, results="asis"}
-papaja::apa_table(table3, 
-                  caption = "Proportions of individuals sampled from each intermediate occupational category in 2017",
-                  landscape = TRUE,
-                  note = "n = sample; 3 = sample 3, accordingly; LL = lower 95% confidence limit; Obs = observed proportion; UL = upper 95% confidence limit.")
-```
-
-## Analytical Approach
-
-A chi-square test of goodness-of-fit was used to determine whether observed proportions from MTurk samples deviated from expected proportions as derived from the BLS.
-Specifically, we tested whether MTurk’s occupational diversity deviated (p < .05) from that expected if we assume the BLS population parameters generalize to the MTurk population.
-Gender, ethnicity, and education were examined in the same fashion.
-Given that multiple occupational and ethnic groups were examined, significant tests were followed by a post-hoc test.
-More specifically, we examined the standardized residuals from our chi-square tests [see @agrestiIntroductionCategoricalData2007], which in this context defines occupations that in our view were over-represented (values > +3), under-represented (values < -3), or consistent with expectations (< or = |3|).
-To facilitate interpretation, we also calculated 95% confidence intervals for our sample proportions and plotted these values (see Figure 1 for 2015 and Figure 2 for 2017).
-Age differences were examined used a one-sample t-test.
-Overall, our approach tests several distinct yet related null hypotheses; namely that the MTurk and broader US labor force contain similar proportions of individuals from (i) occupational areas, (ii) gender, (iii) ethnic, (iv) education, and (v) are of comparable age.
-[^p]
-
-[^p]: Analysis of the occupational diversity of MTurk was conducted on the 2015 samples and were not pre-registered.
-However, analysis of the occupational diversity of the 2017 sample were pre-registered on the Open Science Framework.
-It is worth pointing out hat ost-hoc testing was not pre-registered nor were the analyses regarding gender, ethnicity, education, and age.
-
-# Results
-
-## Occupational Diversity (2015)
-
-Chi-square tests indicate that MTurk’s occupational diversity does not align with expectations in both sample 1 (*X*^2^(`r x15.1[["parameter"]]`) = `r x15.1$statistic`, *p* `r myround2(x15.1$p.value)`) and sample 2, (*X*^2^(`r x15.2[["parameter"]]`)= `r x15.2$statistic`, *p* `r myround2(x15.2$p.value)`).
-Therefore, both samples deviate from expectations.
-
-```{r Barplot 1, echo = FALSE, warning = FALSE, fig.cap = "Comparing the occupational diversity of two MTurk samples with expecations based on the Bureau of Labor Statistics"}
-# Bar Plot with error bars
-Values <- c(table[1:13,2], table[1:13, 5], table[1:13, 9])
-Group <- c("BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2")
-Occupations <- c(as.character(table[1:13, 1]))
-Occ_Nums <- sapply(strsplit(Occupations, " "), "[[", 1)
-barplot_data <- data.frame(as.character(Values), as.character(Occupations),as.character(Group))
-names(barplot_data) <- c("Frequency", "Occupations","Group")
-dodge <- position_dodge(width = .9)
-
-# Define Error Bar limits.
-upperB <- c(0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
-upperM <- c(table[1:13, 6], table[1:13, 10])
-upper <-c(upperB, upperM)
-lowerB <- c(0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
-lowerM <- c(table[1:13, 4], table[1:13,8])
-lower <- c(lowerB, lowerM)
-se <- data.frame(upper, lower)
-
-# Merge data
-df <- cbind(se,barplot_data)
-
-# Plot data
-ggplot(barplot_data, aes(Occupations, Values, fill = Group, ymax = upper, ymin = lower)) + 
-  geom_bar(stat="identity", position = "dodge", width = 0.7) +
-  geom_bar(stat="identity", position = "dodge", 
-                colour = "black", width = 0.7, 
-                show.legend = TRUE) +
-  scale_y_continuous(breaks = seq(0, 0.30, 0.1), 
-                limits = c(0, 0.30), 
-                expand = c(0, 0)) +
-  scale_fill_manual(name = "Groups" , 
-                 values = c('grey30', 'grey60', 'grey 80'), 
-                 labels = c("BLS 2015", "Sample 1", "Sample 2")) +
-  geom_errorbar(position=position_dodge(width=0.7), 
-                     width=0.0, size=0.5, color="black") +
-  #ggtitle("Occupational Diversity of MTurk") +
-  labs(x = element_blank(), y = "Proportions") +
-  theme(legend.position = c(.8,.8), 
-        #plot.title = element_text(hjust = 0), 
-        text=element_text(family="serif")) +
-  coord_flip()
-```
-
-Across both samples, over-represented occupations included (i) 11-13 Management, Business, and Financial (study 1 = `r x15.1[["stdres"]][1]`; study 2 = `r x15.2[["stdres"]][1]`), (ii) 15-19 Computer, Engineering, and Science (study 1 = `r x15.1[["stdres"]][2]`; study 2 = `r x15.2[["stdres"]][2]`), and (iii) 21-27 Education, Legal, Community Service, Arts, and Media (study 1 = `r x15.1[["stdres"]][3]`; study 2 = `r x15.2[["stdres"]][3]`).
-Occupations that were consistently under-represented included (i) 31-39 Service (study 1 = `r x15.1[["stdres"]][5]`; study 2 = `r x15.2[["stdres"]][5]`), (ii) 47 Construction and Extraction (study 1 = `r x15.1[["stdres"]][9]`; study 2 = `r x15.2[["stdres"]][9]`), (iii) 49 Installation, Maintenance, and Repair (study 1 = `r x15.1[["stdres"]][10]`; study 2 = `r x15.2[["stdres"]][10]`), (iv) 51 Production (study 1 = `r x15.1[["stdres"]][11]`; study 2 = `r x15.2[["stdres"]][11]`), and (v) 53 Transportation and Material Moving (study 1 = `r x15.1[["stdres"]][12]`; study 2 = `r x15.2[["stdres"]][12]`).
-Lastly, occupations that consistently appeared in a proportion that conformed with expectations included (i) 41 Sales and Relateed (study 1 = `r x15.1[["stdres"]][6]`; study 2 = `r x15.2[["stdres"]][6]`), (ii) 43 Office and Administrative Support (study 1 = `r x15.1[["stdres"]][7]`; study 2 = `r x15.2[["stdres"]][7]`), (iii) 45 Farming, Fishing, and Forestry (study 1 = `r x15.1[["stdres"]][8]`; study 2 = `r x15.2[["stdres"]][8]`), and (iv) 55 Military Specific (study 1 = `r x15.1[["stdres"]][13]`; study 2 = `r x15.2[["stdres"]][13]`).
-Overall, these results suggests that the MTurk population contains a disproportionate share of white-collar occupations relative to blue-collar occupations.
-For intermediate occupational group 29 (Healthcare Practitioners and Technical), sample one suggests that these occupations are represented as expected (study 1 = `r x15.1[["stdres"]][4]`).
-However, this group was under-represented in sample 2 (study 2 = `r x15.2[["stdres"]][3]`).
-Given that the confidence intervals from our two samples overlap (albeit very weakly), we tentatively conclude that this group appears adequately represented.
-
-## Demographic Diversity (2015) 
-```{r Exploratory Analysis with Demographics, warning = FALSE, echo = FALSE, include = FALSE}
+```{r 2015 Demographic Analysis, warning = FALSE, echo = FALSE, include = FALSE}
 # Age
-BLS_age_15 <- read_excel("BLS.Age.2015.xlsx")
+BLS_age_15 <- read_excel("Data/BLS.Age.2015.xlsx")
 
@@
 # Run one-samplet test and estimate Cohen's D for Rachel's data.
-MTurk15_R <- read_excel("Data/Rachel's Data from 2015.xlsx")
+MTurk15_R <- read_csv("Data/Rachel's Data from 2015.csv")
 t15.2 <- oneSampleTTest(x = MTurk15_R$Age, mu = pop_mean_15)
@@
 # Gender
-BLS_2015_doc <- read_excel("bls.gender.2015.xlsx")
+BLS_2015_doc <- read_excel("Data/bls.gender.2015.xlsx")
 
@@
 gender_table_15 <- cbind(MTurk_gender_15, gCI_15, BLS_gender_15)
-names(gender_table_15) <- c("gender", "n", "o", "LL_g", "UL_g", "e")
-gender_table_15 <- gender_table_15[, c(1, 3, 2, 4, 6, 5)]
+gender_table_15 <- gender_table_15[, c(1, 6, 2, 4, 3, 5)]
+names(gender_table_15) <- c("Characteristic", "Expected", "n1", "LL1", "Obs1", "UL1")
+gender_table_15$Expected <- round(gender_table_15$Expected, 2)
+gender_table_15$n1 <- round(gender_table_15$n1, 2)
+gender_table_15$LL1 <- round(gender_table_15$LL1, 2)
+gender_table_15$Obs1 <- round(gender_table_15$Obs1, 2)
+gender_table_15$UL1 <- round(gender_table_15$UL1, 2)
 
 # Run chi-square test for gender
-x15.3 <- chisq.test(gender_table_15$n, p = round(gender_table_15$e,3))
+x15.3 <- chisq.test(gender_table_15$n1, p = round(gender_table_15$Expected,3))
 
@@
 gender_table_15_R <- cbind(MTurk_gender_15_R, gCI_15_R, BLS_gender_15)
-names(gender_table_15_R) <- c("gender", "n", "o", "LL_g", "UL_g", "e")
-gender_table_15_R <- gender_table_15_R[, c(1, 3, 2, 4, 6, 5)]
+gender_table_15_R <- gender_table_15_R[, c(1, 6, 2, 4, 3, 5)]
+names(gender_table_15_R) <- c("Characteristic", "Expected", "n2", "LL2", "Obs2", "UL2")
+gender_table_15_R$Expected <- round(gender_table_15_R$Expected, 2)
+gender_table_15_R$n2 <- round(gender_table_15_R$n2, 2)
+gender_table_15_R$LL2 <- round(gender_table_15_R$LL2, 2)
+gender_table_15_R$Obs2 <- round(gender_table_15_R$Obs2, 2)
+gender_table_15_R$UL2 <- round(gender_table_15_R$UL2, 2)
 
 #Gender chi square test
-x15.4 <- chisq.test(gender_table_15_R$n, p = round(gender_table_15_R$e,3))
+x15.4 <- chisq.test(gender_table_15_R$n2, p = round(gender_table_15_R$Expected,3))
 
@@
 MTurk15$ethnicity[MTurk15$ethnicity==7] <- "Other"
-MTurk_eth_15 <- count(MTurk15, ethnicity)
+MTurk_eth_15 <- MTurk15 %>%
+  count(ethnicity)
 MTurk_eth_15 <- MTurk_eth_15[c(4,2,1,3),]
@@
 ethnicity_table_15 <- cbind(MTurk_eth_15, ethCI_15, BLS15_eth_prop)
-names(ethnicity_table_15) <- c("ethnicity", "n", "o", "LL", "UL", "e")
 eth_table_15 <- ethnicity_table_15[ , c(1, 6, 2, 4, 3, 5)]
+names(eth_table_15) <- c("Characteristic", "Expected", "n1", "LL1", "Obs1", "UL1")
+eth_table_15$Expected <- round(eth_table_15$Expected, 2)
+eth_table_15$n1 <- round(eth_table_15$n1, 2)
+eth_table_15$LL1 <- round(eth_table_15$LL1, 2)
+eth_table_15$Obs1 <- round(eth_table_15$Obs1, 2)
+eth_table_15$UL1 <- round(eth_table_15$UL1, 2)
 
 # Ethnicity chi squared test for Chris's data
-x15.5 <- chisq.test(eth_table_15$n, p = round(eth_table_15$e,3))
+x15.5 <- chisq.test(eth_table_15$n1, p = round(eth_table_15$Expected,3))
 
@@
 ethnicity_table_15_R$e[4] <- "Other"
-eth_table_15_R <- ethnicity_table_15_R[1:4, c(1, 2, 3, 5, 6, 7)]
-names(eth_table_15_R) <- c("ethnicity", "n", "o", "LL", "UL", "e")
+eth_table_15_R <- ethnicity_table_15_R[1:4, c(1, 7, 2, 5, 4, 6)]
+names(eth_table_15_R) <- c("Characteristic", "Expected", "n2", "LL2", "Obs2", "UL2")
+eth_table_15_R$Expected <- round(eth_table_15_R$Expected, 2)
+eth_table_15_R$n2 <- round(eth_table_15_R$n2, 2)
+eth_table_15_R$LL2 <- round(eth_table_15_R$LL2, 2)
+eth_table_15_R$Obs2 <- round(eth_table_15_R$Obs2, 2)
+eth_table_15_R$UL2 <- round(eth_table_15_R$UL2, 2)
 
 # Ethnicity chi squared test for Rachel's data
-x15.6 <- chisq.test(eth_table_15_R$n, p = round(eth_table_15_R$e,3))
+x15.6 <- chisq.test(eth_table_15_R$n2, p = round(eth_table_15_R$Expected,3))
 
@@
 education_table_15_R <- cbind(MTurk15_R_edu, eduCI_15_R, BLS_edu_15)
-names(education_table_15_R) <- c("education level", "n", "o", "LL_eth", "UL_eth", "e")
 education_table_15_R <- education_table_15_R[ , c(1, 6, 2, 4, 3, 5)]
-education_table_15_R$e <- round(education_table_15_R$e,2)
+names(education_table_15_R) <- c("Characteristic", "Expected", "n2", "LL2", "Obs2", "UL2")
+education_table_15_R$Expected <- round(education_table_15_R$Expected, 2)
+education_table_15_R$n2 <- round(education_table_15_R$n2, 2)
+education_table_15_R$LL2 <- round(education_table_15_R$LL2, 2)
+education_table_15_R$Obs2 <- round(education_table_15_R$Obs2, 2)
+education_table_15_R$UL2 <- round(education_table_15_R$UL2, 2)
 
 # Chi-square test
-x15.7 <- chisq.test(education_table_15_R$n, p = round(education_table_15_R$e,3))
+x15.7 <- chisq.test(education_table_15_R$n2, p = round(education_table_15_R$Expected,3))
 
@@
 x15.7[["stdres"]]
-# Under-represented: (i) no high school (-9.06) and (ii) some college (-11.51).
-# Expected: (i) 2 year degree (2.12).
-# Over-represented: (i) some college (5.60) and (ii) bachelors or higher (9.77). 
 ```
-The average worker in 2015 was `r t15.1[["mu"]]` years of age, which was significantly older than the average MTurk worker across both samples (n~1~: M = `r round(t15.1[["mean"]],2)`, SD = `r round(t15.1[["sd"]],2)`, *t*(`r t15.1[["df"]]`) = `r round(t15.1[["t.statistic"]],2)`, *p* `r myround2(t15.1[["p.value"]])`, *d* = `r t15.1[["effect.size"]]`; n~2~: M = `r round(t15.2[["mean"]],2)`, SD = `r round(t15.1[["sd"]],2)`, *t*(`r t15.2[["df"]]`) = `r round(t15.1[["t.statistic"]],2)`, *p* `r myround2(t15.1[["p.value"]])`, *d* = `r t15.1[["effect.size"]]`).
-
-With regard to gender, the BLS suggests that labor force was slightly male-dominated (Male = `r percent(gender_table_15$e[2])`; Female = `r percent(gender_table_15$e[1])`).
-The opposite was the case for both MTurk samples (n~1~: Male = `r percent(gender_table_15$o[2])`; Female = `r percent(gender_table_15$o[1])`; n~2~: Male = `r percent(gender_table_15_R$o[2])`; Female = `r percent(gender_table_15_R$o[1])`).
-These differences were statistically significant in both cases (n~1~: *X*^2^(`r x15.3[["parameter"]]`) = `r x15.3$statistic`, *p* `r myround2(x15.3$p.value)`; n~2~:*X*^2^(`r x15.4[["parameter"]]`) = `r x15.4$statistic`, *p* `r myround2(x15.4$p.value)`, suggests that MTurk is over-represented by females (standardized residuals: n~1~ = `r  round(x15.3[["stdres"]][1],2)`; n~2~ = `r round(x15.4[["stdres"]][1],2)`).
-
-With regard to ethnicity, we examined only the published proportions for Caucasians, African Americans, and Asians.[^p] BLS summary statistics suggest that the labor force was composed of approximately `r percent(BLS_cauc)` Caucasians, `r percent(BLS_AfAm)` African Americans, and `r percent(BLS_Asn)` Asians.
-This distribution deviated significantly from both of our MTurk samples (n~1~: *X*^2^(`r x15.5[["parameter"]]`) = `r x15.5$statistic`, *p* `r myround2(x15.5$p.value)`; n~2~:*X*^2^(`r x15.6[["parameter"]]`) = `r x15.6$statistic`, *p* `r myround2(x15.6$p.value)`.
-Post-hoc testing revealed that African Americans (n~1~ = `r percent(eth_table_15$o[3])`; n~2~ `r percent(eth_table_15_R$o[3])`) were significantly under-represented (standardized residuals: n~1~ = `r round(x15.5[["stdres"]][2],2)`; n~2~ = `r round(x15.6[["stdres"]][2],2)`).
-Additionally, the "other" category (n~1~ = `r percent(eth_table_15$o[4])`; n~2~ `r percent(eth_table_15_R$o[4])`) was over-represented by MTurk (standardized residuals: n~1~ = `r round(x15.5[["stdres"]][4],2)`; n~2~ = `r round(x15.6[["stdres"]][4],2)`).
-The remaining categories were represented in a manner that was consistent with expectations.
-
-[^p]: An "other" category was created as the remainder of these three categories.
-
-With regard to education, due to a scaling issue with sample 1, we were only able to examine sample 2.[^p] We detected a significant overall deviation from expectations (n~2~:*X*^2^(`r x15.7[["parameter"]]`) = `r x15.7$statistic`, *p* `r myround2(x15.7$p.value)`).
-Specifically, both the "no high school" (MTurk = `r percent(education_table_15_R$o[1])`; BLS = `r percent(education_table_15_R$e[1])`; standardized residual = `r round(x15.7[["stdres"]][1],2)`) and the "high school diploma/GED" groups (MTurk = `r percent(education_table_15_R$o[2])`; BLS = `r percent(education_table_15_R$e[2])`; standardized residual = `r round(x15.7[["stdres"]][2],2)`) were under-represented in the MTurk sample.
-Two education levels were over-represented (4-year degree: MTurk = `r percent(education_table_15_R$o[3])`, BLS = `r percent(education_table_15_R$e[3])`, standardized residual = `r round(x15.7[["stdres"]][3])`; advanced degree: MTurk = `r percent(education_table_15_R$o[5])`; BLS = `r percent(education_table_15_R$e[5])`, standardized residual = `r round(x15.7[["stdres"]][5],2)`).
-The "2 year degree" conformed to expectations (MTurk = `r percent(education_table_15_R$o[4])`, BLS = `r percent(education_table_15_R$e[4])`, standardized residual = `r round(x15.7[["stdres"]][4],2)`).
-This overall pattern suggests that MTurk may contain more highly educated individuals than the general population.
-
-[^p]: Additionally, to be consistent with the BLS, only individuals of age 25 or older were analyzed.
-
-## Occupational Diversity (2017)
-
-Chi-square tests indicate that MTurk’s occupational diversity does not align with expectations in (*X*^2^(`r x17.1[["parameter"]]`) = `r x17.1$statistic`, *p* `r myround2(x17.1$p.value)`).
-
-```{r Barplot 2, echo = FALSE, warning = FALSE, fig.cap = "Comparing the occupational diversity of two MTurk samples with expecations based on the Bureau of Labor Statistics"}
+```{r 2017 Demographic Analyses, echo = FALSE, include = FALSE}
+#Age Analysis T- Test
+#Load Dataset
+age_demo <- read_excel("Data/age_demo.xlsx")
+
+# Define population mean. In this case it was already calculated in the dataset. 
+pop_mean <- as.numeric(age_demo[6 , 10])
+
+# Define sample 
+MTurk17 <- read_csv("Data/C217.csv")
+
+# Run one-samplet test and estimate Cohen's D.
+t <- oneSampleTTest(x = MTurk17$What.is.your.age., mu = pop_mean)
+tvalue <- t$t.statistic %>%
+  formatC(digits = 2, format = "f")
+if (t$p.value < 0.0005) {
+  pvalue <- " < 0.001"
+} else {
+  if (t$p.value < 0.005)
+      pvalue <- paste0(" = ",t$p.value %>% formatC(digits = 3, format = "f"))
+    else 
+      pvalue <- paste0(" = ",t$p.value %>% formatC(digits = 2, format = "f")) 
+  }
+df <- t$df
+d <- round((t$effect.size),2)
+# MTurk participants are significantly younger than labor force at large. Moderate effect according to Cohen's criteria.
+
+## Gender Analysis
+BLS_data <- read_excel("Data/employment_demo.xlsx")
+
+# Get BLS gender data (expected value)
+BLS_women <- as.numeric(BLS_data[7,3])/100
+BLS_other <- 1.000 - BLS_women
+BLS_gender <- c(BLS_women, BLS_other)
+
+# Get MTurk gender data (observed value)
+MTurk17$What.is.your.gender.[MTurk17$What.is.your.gender.=="Male"] <- "Other"
+MTurk_gender <- MTurk17 %>%
+  count(What.is.your.gender.)
+
+# Define confidence intervals
+gCI <- binom.confint(x = MTurk_gender$n, n = sum(MTurk_gender$n), conf.level = 0.95, methods = "exact")
+gCI <- gCI[ , 4:6]
+
+# Build Gender table with gender, expected value, n, LL, observed, UL
+gender_table <- cbind(MTurk_gender, gCI, BLS_gender)
+gender_table <- gender_table[ , c(1, 6, 2, 4, 3, 5)]
+names(gender_table) <- c("Characteristic", "Expected", "n3", "LL3", "Obs3", "UL3")
+gender_table$Expected <- round(gender_table$Expected, 2)
+gender_table$n3 <- round(gender_table$n3, 2)
+gender_table$LL3 <- round(gender_table$LL3, 2)
+gender_table$Obs3 <- round(gender_table$Obs3, 2)
+gender_table$UL3 <- round(gender_table$UL3, 2)
+# Run chi-square test for gender
+x17.3 <- chisq.test(gender_table$n3, p = round(gender_table$Expected,3))
+
+# Result is significant.
+
+# Ethnicity Analysis [Note: Numbers taken from Table 1 of this webpage: https://www.bls.gov/opub/reports/race-and-ethnicity/2017/home.htm)]
+BLS_cauc_17 <- as.numeric(120176/153337)
+BLS_AfAm_17 <- as.numeric(18587/153337)
+BLS_Asn_17 <- as.numeric(9448/153337)
+BLS_other_17 <- as.numeric(1-sum(BLS_cauc_17,BLS_AfAm_17,BLS_Asn_17))
+BLS_eth <- c(BLS_AfAm_17, BLS_Asn_17, BLS_cauc_17, BLS_other_17)
+
+# Get MTurk ethnicity data (observed value)
+MTurk17$With.which.ethnicity.do.you.most.identify.[MTurk17$With.which.ethnicity.do.you.most.identify.=="Hispanic"] <- "Other"
+MTurk17$With.which.ethnicity.do.you.most.identify.[MTurk17$With.which.ethnicity.do.you.most.identify.=="Indian"] <- "Other"
+MTurk17$With.which.ethnicity.do.you.most.identify.[MTurk17$With.which.ethnicity.do.you.most.identify.=="Native American"] <- "Other"
+MTurk17$With.which.ethnicity.do.you.most.identify.[MTurk17$With.which.ethnicity.do.you.most.identify.=="Other:"] <- "Other"
+MTurk_eth <- MTurk17 %>%
+  count(MTurk17$With.which.ethnicity.do.you.most.identify.)
+
+# Define confidence intervals 
+ethCI <- binom.confint(x = MTurk_eth$n, n = sum(MTurk_eth$n), conf.level = 0.95, methods = "exact")
+ethCI <- ethCI[ , 4:6]
+
+# Build Ethnicity table 
+ethnicity_table <- cbind(MTurk_eth, ethCI, BLS_eth)
+ethnicity_table <- ethnicity_table[ , c(1, 6, 2, 4, 3, 5)]
+names(ethnicity_table) <- c("Characteristic", "Expected", "n3", "LL3", "Obs3", "UL3")
+ethnicity_table$Expected <- round(ethnicity_table$Expected, 3)
+ethnicity_table$n3 <- round(ethnicity_table$n3, 3)
+ethnicity_table$LL3 <- round(ethnicity_table$LL3, 3)
+ethnicity_table$Obs3 <- round(ethnicity_table$Obs3, 3)
+ethnicity_table$UL3 <- round(ethnicity_table$UL3, 3)
+
+# Ethnicity chi squared test
+x17.4 <- chisq.test(ethnicity_table$n3, p = round(ethnicity_table$Expected,3))
+
+# Adjust values to be consistent with two decimal places. 
+ethnicity_table$Expected <- round(ethnicity_table$Expected, 2)
+ethnicity_table$n3 <- round(ethnicity_table$n3, 2)
+ethnicity_table$LL3 <- round(ethnicity_table$LL3, 2)
+ethnicity_table$Obs3 <- round(ethnicity_table$Obs3, 2)
+ethnicity_table$UL3 <- round(ethnicity_table$UL3, 2)
+
+# Result is significant. Run post-hoc pairwise comparisons. 
+x17.4[["stdres"]]
+
+# MTurk is under-represented by African Americans, Asians, and other ethnicities. However, it does appear to be slightly over-represented by Caucasians.
+
+#Education Analysis 
+#Clean BLS Data. Get totals.  
+#BLS_education_original <- read_excel("Data/education_demo.xlsx")
+#BLS_education <- as.data.frame(BLS_education_original[8:14, ])
+#BLS_education <- BLS_education[1, c(-2, -3, -6)]
+#names(BLS_education) <- c("category", "High school graduates, no college(1)", "Some college, no degree", "Associate degree", "Bachelor's degree only", "Advanced degree")
+
+# Combine categories as necessary. Get proportions.  
+#highschool_ged <- c(as.numeric(BLS_education$`High school graduates, no college(1)`) + #as.numeric(BLS_education$`Some college, no degree`))
+#two_year_deg <- as.numeric(BLS_education$`Associate degree`)
+#four_year_deg <- as.numeric(BLS_education$`Bachelor's degree only`)
+#advanaced_deg <- as.numeric(BLS_education$`Advanced degree`)
+#BLS_education <- c(highschool_ged, two_year_deg, four_year_deg, advanaced_deg)
+#names(BLS_education) <- c("high school/GED" , "2 year degree", "4 year degree", "advanced degree")
+#BLS_total <- as.numeric(sum(BLS_education))
+
+# Function to find proportion for each iteration of the vector. 
+#e_prop <- function(x) {
+#  e <- x/BLS_total
+#}
+
+# Use vapply and the above function to get expected proportions from BLS data
+#BLS_edu <- sapply(BLS_education, e_prop)
+
+#Use vapply and the above function to get expected proportions from BLS data
+#BLS_edu <- sapply(BLS_education, function(x) {x/BLS_total})
+
+# Clean MTurk Data [Note: Due to scaling issues, we cannot analyze the education data for 2017]
+#MTurk_education <- MTurk17 %>%
+#  count(MTurk17$What.level.of.education.have.you.completed.)
+#colnames(MTurk_education) <- c("education level", "n")
+#advanced_deg <- as.numeric(MTurk_education[4,2]) + as.numeric(MTurk_education[5,2])
+#MTurk_education <- rbind(MTurk_education, advanced_deg)
+#MTurk_education[6,1] <- "advanced degree"
+#MTurk_edu <- MTurk_education[c(-4, -5), ]
+
+# Define confidence intervals 
+#eduCI <- binom.confint(x = MTurk_edu$n, n = sum(MTurk_edu$n), conf.level = 0.95, methods = "exact")
+#eduCI <- eduCI[ , 4:6]
+
+# Build Education table 
+#education_table <- cbind(MTurk_edu, eduCI, BLS_edu)
+#names(education_table) <- c("education level", "n", "o", "LL_eth", "UL_eth", "e")
+#education_table <- education_table[ , c(1, 6, 2, 4, 3, 5)]
+
+# Education chi squared test
+#x17.5 <- chisq.test(education_table$n, p = round(education_table$e,3))
+# Result is  significant. MTurk contains an unexpected proportion of education.
+```
+
+## MTurk Sample Information
+
+In 2015, participants’ data were collected from two independently conducted studies (n~1~ = `r nrow(LATech)`; n~2~ = `r formatC(nrow(UGA), big.mark = ",")`) for purposes that were not directly related to the purpose of this study (i.e., investigating psychological phenomena in organizational life).
+Data collected in 2017 (n~3~ = `r nrow(C217)`) can be similarly described.
+[^1] For each sample, data collection was restricted to employed individuals in the United States.
+Small monetary incentives were used ($.75-$1.30) to encourage participation.
+Following guidance from the literature, we used worker reputation to pre-screen individuals prior to granting them access to our surveys [e.g., approval ratings greater than 90%; @peerReputationSufficientCondition2014].
+For all samples, participants self-reported their job titles.
+For two samples (n~1~ = `r nrow(LATech)`; n~2~ = `r formatC(nrow(UGA), big.mark = ",")`), the six-digit standard occupational classification (SOC) codes were obtained by utilizing trained research assistants, who matched the self-reported job titles to those in the ONET database.
+In a third sample, (n~3~ = `r nrow(C217)`) participants were then brought to the Occupation Network Online (ONET) website (www.onetonline.org) and asked to retrieve the six-digit occupational classification code that most closely corresponded to their job title.
+[^2] Only individuals who could be classified using the Intermediate Aggregation were included in our analyses.
+Using this data, we described the occupational and demographic diversity of each MTurk sample using proportions of category representation.
+We also estimated 95% confidence intervals to allow ease of plotting and analysis.
+
+[^1]: Our samples are what remained after filtering out inattentive responders [see @meadeIdentifyingCarelessResponses2012], individuals who were outside of the target population (that is, the labor force that is accessible via MTurk), completing MTurk work while located outside of the U.S.
+(and therefore being of questionable origin), and for using a questionable IP address [@kennedyShapeSolutionsMTurk2018].
+
+[^2]: To conserve resources, future researcher wishing to replicate our results should consider using the "ONETr" package for this purpose.
+
+## Analytical Approach
+
+A chi-square test of goodness-of-fit was used to determine whether proportions observed from MTurk samples deviated from expected proportions as derived from the BLS.
+Specifically, we tested whether MTurk’s occupational diversity deviated significantly from that expected if we assume the BLS population parameters generalize to the MTurk population.
+Gender, ethnicity, and education were examined in the same fashion.
+Given that multiple occupational and ethnic groups were examined, significant tests were followed by a post-hoc test.
+More specifically, we examined the standardized residuals (std.
+res.) from our chi-square tests [see @agrestiIntroductionCategoricalData2007], which in this context defines occupations that were overrepresented (values $\ge$ 3), underrepresented (values $\le$ 3), or consistent with expectations ($\le$ |2.99|).
+To facilitate interpretation, we also calculated 95% confidence intervals for our sample proportions and plotted these values (see Figure 1 for 2015 and Figure 2 for 2017).
+Age differences were examined used a one-sample t-test with BLS data defining the average age of the labor force (the sample standard deviations were used to estimate the population standard deviation).
+[^3]
+
+[^3]: Analysis of the occupational diversity of MTurk was conducted on the 2015 samples and were not pre-registered.
+However, analysis of the occupational diversity of the 2017 sample were pre-registered on the Open Science Framework.
+It is worth pointing out that post-hoc testing was not pre-registered nor were the analyses regarding gender, ethnicity, education, and age.
+
+# Results
+
+## Occupational Diversity of the Broader Labor Force Accessible via MTurk in 2015
+
+All relevant statistics are described by Tables 1 through 4.
+Alternatively, Figures 1 (2015) and 2 (2017) plot these occupational diversity for ease of analysis.
+Chi-square testing indicated that MTurk’s occupational diversity does not consistently align with expectations in both sample 1 ($\chi$^2^(`r x15.1[["parameter"]]`) = `r x15.1$statistic`, *p* `r myround2(x15.1$p.value)`) and sample 2, ($\chi$^2^(`r x15.2[["parameter"]]`)= `r x15.2$statistic`, *p* `r myround2(x15.2$p.value)`).
+Therefore, both samples deviate from expectations.
+Across both samples, overrepresented occupations included (i) 11-13 Management, Business, and Financial (std.
+res.: study 1 = `r x15.1[["stdres"]][1]`; study 2 = `r x15.2[["stdres"]][1]`), (ii) 15-19 Computer, Engineering, and Science (std.
+res.: study 1 = `r x15.1[["stdres"]][2]`; study 2 = `r x15.2[["stdres"]][2]`), and (iii) 21-27 Education, Legal, Community Service, Arts, and Media (std.
+res.: study 1 = `r x15.1[["stdres"]][3]`; study 2 = `r x15.2[["stdres"]][3]`).
+Occupations that were consistently under-represented included (i) 31-39 Service (std.
+res.: study 1 = `r x15.1[["stdres"]][5]`; study 2 = `r x15.2[["stdres"]][5]`), (ii) 47 Construction and Extraction (std.
+res.: study 1 = `r x15.1[["stdres"]][9]`; study 2 = `r x15.2[["stdres"]][9]`), (iii) 49 Installation, Maintenance, and Repair (std.
+res.: study 1 = `r x15.1[["stdres"]][10]`; study 2 = `r x15.2[["stdres"]][10]`), (iv) 51 Production (std.
+res.: study 1 = `r x15.1[["stdres"]][11]`; study 2 = `r x15.2[["stdres"]][11]`), and (v) 53 Transportation and Material Moving (std.
+res.: study 1 = `r x15.1[["stdres"]][12]`; study 2 = `r x15.2[["stdres"]][12]`).
+Lastly, occupations that consistently appeared in a proportion that conformed with expectations included (i) 41 Sales and Related (std.
+res.: study 1 = `r x15.1[["stdres"]][6]`; study 2 = `r x15.2[["stdres"]][6]`), (ii) 43 Office and Administrative Support (std.
+res.: study 1 = `r x15.1[["stdres"]][7]`; study 2 = `r x15.2[["stdres"]][7]`), (iii) 45 Farming, Fishing, and Forestry (std.
+res.: study 1 = `r x15.1[["stdres"]][8]`; study 2 = `r x15.2[["stdres"]][8]`), and (iv) 55 Military Specific (std.
+res.: study 1 = `r x15.1[["stdres"]][13]`; study 2 = `r x15.2[["stdres"]][13]`).
+For 29 Healthcare Practitioners and Technical, sample 1 suggests that these occupations are represented as expected (std.
+res.: study 1 = `r x15.1[["stdres"]][4]`).
+However, this group was under-represented in sample 2 (std.
+res.: study 2 = `r x15.2[["stdres"]][3]`).
+
+# ---------------
+# Insert Table 1, Table 2, and Figure 1 about here
+# ---------------
+```{r Table 1, results="asis"}
+papaja::apa_table(table, 
+                  caption = "Proportions of individuals sampled from each intermediate occupational category (2015).",
+                  landscape = TRUE,
+                  note = "LL = lower 95% confidence limit; Obs = observed proportion; UL = upper 95% confidence limit.")
+```
+```{r Table 2, results="asis"}
+# cBind 2015 tables
+gdadd <- rep("",10)
+ethadd <- rep("",10)
+table4.1 <- cbind(gender_table_15,gender_table_15_R)
+table4.1 <- table4.1[c(-7,-8)]
+table4.2 <- cbind(eth_table_15, eth_table_15_R)
+table4.2 <- table4.2[c(-7,-8)]
+table4.3 <- rbind(gdadd,table4.1,ethadd,table4.2)
+table4.3[1,] <- c("Gender","", "", "", "", "","","","","")
+table4.3[4,] <- c("Ethnicity","", "", "", "", "","","","","")
+
+# Format education table for integration
+education_table_15 <- education_table_15_R
+colnames(education_table_15)[3] <- "n1"
+education_table_15$n1 <- ""
+colnames(education_table_15)[4] <- "LL1"
+education_table_15$LL1 <- ""
+colnames(education_table_15)[5] <- "Obs1"
+education_table_15$Obs1 <- ""
+colnames(education_table_15)[6] <- "UL1"
+education_table_15$UL1 <- ""
+education_table_15_Rach <- education_table_15_R[c(3,4,5,6)]
+education_table <- cbind(education_table_15,education_table_15_Rach)
+rownames(education_table) <- NULL
+eddadd <- rep("",10)
+table4.4 <- rbind(eddadd,education_table)
+table4.4[1,] <- c("Education","", "", "", "", "","","","","")
+table4.4$Characteristic <- as.character(table4.4$Characteristic)
+
+# Merge gender and ethnicity tables
+table4 <- rbind(table4.3, table4.4)
+
+# Build table
+papaja::apa_table(table4, 
+                  caption = "Demograhpic distribution (gender, ethnicity, and education) of labor force sampled indirectly from MTurk (2015).",
+                  landscape = FALSE,
+                  note = "LL = lower 95% confidence limit; Obs = observed proportion; UL = upper 95% confidence limit.")
+```
+```{r, echo = FALSE, warning = FALSE, fig.cap = "Comparing the occupational diversity of two MTurk samples (2015) with expecations based on the Bureau of Labor Statistics."}
+# Bar Plot with error bars
+Values <- c(table[1:13,2], table[1:13, 5], table[1:13, 9])
+Group <- c("BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 1", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2", "Sample 2")
+Occupations <- c(as.character(table[1:13, 1]))
+Occ_Nums <- sapply(strsplit(Occupations, " "), "[[", 1)
+barplot_data <- data.frame(as.character(Values), as.character(Occupations),as.character(Group))
+names(barplot_data) <- c("Frequency", "Occupations","Group")
+dodge <- position_dodge(width = .9)
+
+# Define Error Bar limits.
+upperB <- c(0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
+upperM <- c(table[1:13, 6], table[1:13, 10])
+upper <-c(upperB, upperM)
+lowerB <- c(0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
+lowerM <- c(table[1:13, 4], table[1:13,8])
+lower <- c(lowerB, lowerM)
+se <- data.frame(upper, lower)
+
+# Merge data
+df <- cbind(se,barplot_data)
+
+# Plot data
+ggplot(barplot_data, aes(Occupations, Values, fill = Group, ymax = upper, ymin = lower)) + 
+  geom_bar(stat="identity", position = "dodge", width = 0.7) +
+  geom_bar(stat="identity", position = "dodge", 
+                colour = "black", width = 0.7, 
+                show.legend = TRUE) +
+  scale_y_continuous(breaks = seq(0, 0.30, 0.1), 
+                limits = c(0, 0.30), 
+                expand = c(0, 0)) +
+  scale_fill_manual(name = "Groups" , 
+                 values = c('grey30', 'grey60', 'grey 80'), 
+                 labels = c("BLS 2015", "Sample 1", "Sample 2")) +
+  geom_errorbar(position=position_dodge(width=0.7), 
+                     width=0.0, size=0.5, color="black") +
+  #ggtitle("Occupational Diversity of MTurk") +
+  labs(x = element_blank(), y = "Proportions") +
+  theme(legend.position = c(.8,.8), 
+        #plot.title = element_text(hjust = 0), 
+        text=element_text(family="serif")) +
+  coord_flip()
+```
+
+## Demographic Diversity of the Broader Labor Force Accessible via MTurk in 2015
+
+The average worker in 2015 was `r t15.1[["mu"]]` years of age, which was significantly older than the average MTurk worker across both samples (n~1~: M = `r round(t15.1[["mean"]],2)`, SD = `r round(t15.1[["sd"]],2)`, *t*(`r t15.1[["df"]]`) = `r round(t15.1[["t.statistic"]],2)`, *p* `r myround2(t15.1[["p.value"]])`, *d* = -`r t15.1[["effect.size"]]`; n~2~: M = `r round(t15.2[["mean"]],2)`, SD = `r round(t15.1[["sd"]],2)`, *t*(`r t15.2[["df"]]`) = `r round(t15.1[["t.statistic"]],2)`, *p* `r myround2(t15.1[["p.value"]])`, *d* = -`r t15.1[["effect.size"]]`).
+
+With regard to gender, the BLS suggests a male-biased labor force (Male = `r percent(gender_table_15$Expected[2])`; Female = `r percent(gender_table_15$Expected[1])`).
+The opposite was the case for both MTurk samples (n~1~: Male = `r percent(gender_table_15$Obs1[2])`; Female = `r percent(gender_table_15$Obs1[1])`; n~2~: Male = `r percent(gender_table_15_R$Obs2[2])`; Female = `r percent(gender_table_15_R$Obs2[1])`).
+These differences were statistically significant in both cases (n~1~: $\chi$^2^(`r x15.3[["parameter"]]`) = `r x15.3$statistic`, *p* `r myround2(x15.3$p.value)`; n~2~: $\chi$^2^(`r x15.4[["parameter"]]`) = `r x15.4$statistic`, *p* `r myround2(x15.4$p.value)`), which suggests that MTurk is overrepresented by females (std.
+res.: n~1~ = `r  round(x15.3[["stdres"]][1],2)`; n~2~ = `r round(x15.4[["stdres"]][1],2)`).
+
+With regard to ethnicity, we examined only the published proportions for Caucasians, African Americans, and Asians.[^4] BLS summary statistics suggest that the labor force was composed of approximately `r percent(BLS_cauc)` Caucasians, `r percent(BLS_AfAm)` African Americans, and `r percent(BLS_Asn)` Asians.
+This distribution deviated significantly from both of our MTurk samples (n~1~: $\chi$^2^(`r x15.5[["parameter"]]`) = `r x15.5$statistic`, *p* `r myround2(x15.5$p.value)`; n~2~: $\chi$^2^(`r x15.6[["parameter"]]`) = `r x15.6$statistic`, *p* `r myround2(x15.6$p.value)`).
+Post-hoc testing revealed that African Americans (n~1~ = `r percent(eth_table_15$Obs1[2])`; n~2~ `r percent(eth_table_15_R$Obs2[2])`) were consistently under-represented (std.
+res.: n~1~ = `r round(x15.5[["stdres"]][2],2)`; n~2~ = `r round(x15.6[["stdres"]][2],2)`).
+Additionally, the "other" category (n~1~ = `r percent(eth_table_15$Obs1[4])`; n~2~ `r percent(eth_table_15_R$Obs2[4])`) was consistently overrepresented by MTurk (std.
+res.: n~1~ = `r round(x15.5[["stdres"]][4],2)`; n~2~ = `r round(x15.6[["stdres"]][4],2)`).
+Caucasians (n~1~ = `r percent(eth_table_15$Obs1[1])`, std.
+res.: n~1~ = `r round(x15.5[["stdres"]][1],2)`; n~2~ `r percent(eth_table_15_R$Obs2[1])`; std.
+res.
+= `r round(x15.6[["stdres"]][1],2)`) and Asians (n~1~ = `r percent(eth_table_15$Obs1[3])`, std.
+res.: n~1~ = `r round(x15.5[["stdres"]][3],2)`; n~2~ `r percent(eth_table_15_R$Obs2[3])`; std.
+res.
+= `r round(x15.6[["stdres"]][3],2)`) were represented in a manner that was consistent with expectations.
+
+[^4]: An "other" category was created as the remainder of these three categories, which contained Hispanics and other ethnic groups.
+
+With regard to education, due to a scaling issue with sample 1, we were only able to examine sample 2.
+Furthermore, to be consistent with the BLS, only a subset of individuals of age 25 or older were analyzed.
+Nevertheless, we detected a significant overall deviation from expectations (n~2~: $\chi$^2^(`r x15.7[["parameter"]]`) = `r x15.7$statistic`, *p* `r myround2(x15.7$p.value)`).
+Specifically, both the "no high school" (MTurk = `r percent(education_table_15_R$Obs2[1])`; BLS = `r percent(education_table_15_R$Expected[1])`; std.
+res.
+= `r round(x15.7[["stdres"]][1],2)`) and the "high school diploma/GED" groups (MTurk = `r percent(education_table_15_R$Obs2[2])`; BLS = `r percent(education_table_15_R$Expected[2])`; std.
+res.
+= `r round(x15.7[["stdres"]][2],2)`) were under-represented in the MTurk sample.
+Two education levels were overrepresented: specifically, individuals with some college (MTurk = `r percent(education_table_15_R$Obs[3])`, BLS = `r percent(education_table_15_R$Expected[3])`, std.
+res.
+= `r round(x15.7[["stdres"]][3], 2)`) and individuals with a bachelors degree or higher (MTurk = `r percent(education_table_15_R$Obs2[5])`; BLS = `r percent(education_table_15_R$Expected[5])`, std.
+res.
+= `r round(x15.7[["stdres"]][5],2)`).
+Individuals holding a 2 year degree emerged in a manner that was consistent with expectations (MTurk = `r percent(education_table_15_R$Obs2[4])`, BLS = `r percent(education_table_15_R$Expected[4])`, std.
+res.
+= `r round(x15.7[["stdres"]][4],2)`).
+
+## Occupational Diversity of the Broader Labor Force Accessible via MTurk in 2017
+
+Many of our findings regarding the occupational diversity of the 2017 sample mirrored those from 2015.
+Chi-square testing indicated that MTurk’s occupational diversity does not consistently align with expectations ($\chi$^2^(`r x17.1[["parameter"]]`) = `r x17.1$statistic`, *p* `r myround2(x17.1$p.value)`).
+Overrepresented occupations included (i) 11-13 Management, Business, and Financial (std.
+res.
+= `r x17.1[["stdres"]][1]`), (ii) 15-19 Computer, Engineering, and Science (std.
+res.
+= `r x17.1[["stdres"]][2]`), and (iii) 21-27 Education, Legal, Community Service, Arts, and Media (std.
+res.
+= `r x17.1[["stdres"]][3]`).
+Occupations that were underrepresented included (i) 31-39 Service (std.
+res.
+= `r x17.1[["stdres"]][5]`), (ii) 47 Construction and Extraction (std.
+res.
+= `r x17.1[["stdres"]][9]`), (iii) 49 Installation, Maintenance, and Repair, (iv) 51 Production (std.
+res.
+= `r x17.1[["stdres"]][11]`), and (v) 53 Transportation and Material Moving (std.
+res.
+= `r x17.1[["stdres"]][12]`).
+Lastly, occupations that appeared in a proportion that conformed with expectations included (i) 29 Healthcare Practitioners and Technical (std.
+res.
+= `r x17.1[["stdres"]][4]`), (ii) 41 Sales and Related (std.
+res.
+= `r x17.1[["stdres"]][6]`), (iii) 43 Office and Administrative Support (std.
+res.
+= `r x17.1[["stdres"]][7]`), (iv) 45 Farming, Fishing, and Forestry (std.
+res.
+= `r x17.1[["stdres"]][8]`), and (v) 55 Military Specific (std.
+res.
+= `r x17.1[["stdres"]][13]`).
+
+# ---------------
+# Insert Table 3, Table 4, and Figure 2 about here
+# ---------------
+```{r Table 3, results="asis"}
+papaja::apa_table(table3, 
+                  caption = "Proportions of individuals sampled from each intermediate occupational category (2017).",
+                  landscape = TRUE,
+                  note = "LL = lower 95% confidence limit; Obs = observed proportion; UL = upper 95% confidence limit.")
+```
+```{r Table 4, results="asis"}
+# Merge gender and ethnicity tables
+gdadd <- rep("",6)
+ethadd <- rep("",6)
+table2 <- rbind(gdadd,gender_table,ethadd,ethnicity_table)
+table2[1,] <- c("Gender","", "", "", "", "")
+table2[3,] <- c("Male",0.53, 226, 0.30, 0.34, 0.38)
+table2[4,] <- c("Ethnicity","", "", "", "", "")
+
+# Build table
+papaja::apa_table(table2, 
+                  caption = "Demograhpic distribution (gender and ethnicity) of labor force sampled indirectly from MTurk (2017).",
+                  landscape = FALSE,
+                  note = "LL = lower 95% confidence limit; Obs = observed proportion; UL = upper 95% confidence limit.")
+```
+```{r, echo = FALSE, warning = FALSE, fig.cap = "Comparing the occupational diversity of one MTurk sample (2017) with expecations based on the Bureau of Labor Statistics."}
 # Bar Plot with error bars
@@
 
-Many of our findings from the 2017 sample mirrored those from 2015.
-Over-represented occupations again included (i) 11-13 Management, Business, and Financial (`r x17.1[["stdres"]][1]`), (ii) 15-19 Computer, Engineering, and Science (`r x17.1[["stdres"]][2]`), and (iii) 21-27 Education, Legal, Community Service, Arts, and Media (`r x17.1[["stdres"]][3]`).
-Occupations that were under-represented again included (i) 31-39 Service (`r x17.1[["stdres"]][5]`), (ii) 47 Construction and Extraction (`r x17.1[["stdres"]][9]`), (iii) 51 Production (`r x17.1[["stdres"]][11]`), and (iv) 53 Transportation and Material Moving (`r x17.1[["stdres"]][12]`).
-Lastly, occupations that appeared in a proportion that conformed with expectations included (i) 41 Sales and Related (`r x17.1[["stdres"]][6]`), (ii) 43 Office and Administrative Support (`r x17.1[["stdres"]][7]`), (iii) 45 Farming, Fishing, and Forestry (`r x17.1[["stdres"]][8]`), and (iv) 55 Military Specific (`r x17.1[["stdres"]][13]`).
-Again, these results suggests that the MTurk population contains a disproportionate share of white-collar occupations relative to blue-collar occupations.
-However, certain results deviated from the 2015 samples: (i) 49 Installation, Maintenance, and Repair (`r x17.1[["stdres"]][10]`) and (ii) 29 (Healthcare Practitioners and Technical).
-Both groups conformed with expectations in our 2017 sample.
-
-## Demographic Diversity (2017)
-
-```{r 2017 Demographic Analyses, echo = FALSE, include = FALSE}
-#Age Analysis T- Test
-#Load Dataset
-age_demo <- read_excel("age_demo.xlsx")
-
-# Define population mean. In this case it was already calculated in the dataset. 
-pop_mean <- as.numeric(age_demo[6 , 10])
-
-# Define sample 
-MTurk17 <- read_excel("2017 Data.xls")
-
-# Run one-samplet test and estimate Cohen's D.
-t <- oneSampleTTest(x = MTurk17$What.is.your.age., mu = pop_mean)
-tvalue <- t$t.statistic %>%
-  formatC(digits = 2, format = "f")
-if (t$p.value < 0.0005) {
-  pvalue <- " < 0.001"
-} else {
-  if (t$p.value < 0.005)
-      pvalue <- paste0(" = ",t$p.value %>% formatC(digits = 3, format = "f"))
-    else 
-      pvalue <- paste0(" = ",t$p.value %>% formatC(digits = 2, format = "f")) 
-  }
-df <- t$df
-d <- round((t$effect.size),2)
-# MTurk participants are significantly younger than labor force at large. Moderate effect according to Cohen's criteria.
-
-## Gender Analysis
-BLS_data <- read_excel("employment_demo.xlsx")
-
-# Get BLS gender data (expected value)
-BLS_women <- as.numeric(BLS_data[7,3])/100
-BLS_other <- 1.000 - BLS_women
-BLS_gender <- c(BLS_women, BLS_other)
-
-# Get MTurk gender data (observed value)
-MTurk17$What.is.your.gender.[MTurk17$What.is.your.gender.=="Male"] <- "Other"
-MTurk_gender <- MTurk17 %>%
-  count(What.is.your.gender.)
-
-# Define confidence intervals
-gCI <- binom.confint(x = MTurk_gender$n, n = sum(MTurk_gender$n), conf.level = 0.95, methods = "exact")
-gCI <- gCI[ , 4:6]
-
-# Build Gender table with gender, expected value, n, LL, observed, UL
-gender_table <- cbind(MTurk_gender, gCI, BLS_gender)
-names(gender_table) <- c("gender", "n", "o", "LL_g", "UL_g", "e")
-gender_table <- gender_table[ , c(1, 6, 2, 4, 3, 5)]
-
-# Run chi-square test for gender
-x17.3 <- chisq.test(gender_table$n, p = round(gender_table$e,3))
-
-# Result is significant.
-
-# Ethnicity Analysis [Note: Numbers taken from Table 1 of this webpage: https://www.bls.gov/opub/reports/race-and-ethnicity/2017/home.htm)]
-BLS_cauc_17 <- as.numeric(120176/153337)
-BLS_AfAm_17 <- as.numeric(18587/153337)
-BLS_Asn_17 <- as.numeric(9448/153337)
-BLS_other_17 <- as.numeric(1-sum(BLS_cauc_17,BLS_AfAm_17,BLS_Asn_17))
-BLS_eth <- c(BLS_AfAm_17, BLS_Asn_17, BLS_cauc_17, BLS_other_17)
-
-# Get MTurk ethnicity data (observed value)
-MTurk17$With.which.ethnicity.do.you.most.identify.[MTurk17$With.which.ethnicity.do.you.most.identify.=="Hispanic"] <- "Other"
-MTurk17$With.which.ethnicity.do.you.most.identify.[MTurk17$With.which.ethnicity.do.you.most.identify.=="Indian"] <- "Other"
-MTurk17$With.which.ethnicity.do.you.most.identify.[MTurk17$With.which.ethnicity.do.you.most.identify.=="Native American"] <- "Other"
-MTurk17$With.which.ethnicity.do.you.most.identify.[MTurk17$With.which.ethnicity.do.you.most.identify.=="Other:"] <- "Other"
-MTurk_eth <- MTurk17 %>%
-  count(MTurk17$With.which.ethnicity.do.you.most.identify.)
-
-# Define confidence intervals 
-ethCI <- binom.confint(x = MTurk_eth$n, n = sum(MTurk_eth$n), conf.level = 0.95, methods = "exact")
-ethCI <- ethCI[ , 4:6]
-
-# Build Ethnicity table 
-ethnicity_table <- cbind(MTurk_eth, ethCI, BLS_eth)
-names(ethnicity_table) <- c("ethnicity", "n", "o", "LL_eth", "UL_eth", "e")
-ethnicity_table <- ethnicity_table[ , c(1, 6, 2, 4, 3, 5)]
-
-# Ethnicity chi squared test
-x17.4 <- chisq.test(ethnicity_table$n, p = round(ethnicity_table$e,3))
-
-# Result is significant. Run post-hoc pairwise comparisons. 
-x17.4[["stdres"]]
-
-# MTurk is under-represented by African Americans, Asians, and other ethnicities. However, it does appear to be slightly over-represented by Caucasians.
-
-#Education Analysis 
-#Clean BLS Data. Get totals.  
-BLS_education_original <- read_excel("education_demo.xlsx")
-BLS_education <- as.data.frame(BLS_education_original[8:14, ])
-BLS_education <- BLS_education[1, c(-2, -3, -6)]
-names(BLS_education) <- c("category", "High school graduates, no college(1)", "Some college, no degree", "Associate degree", "Bachelor's degree only", "Advanced degree")
-
-# Combine categories as necessary. Get proportions.  
-highschool_ged <- c(as.numeric(BLS_education$`High school graduates, no college(1)`) + as.numeric(BLS_education$`Some college, no degree`))
-two_year_deg <- as.numeric(BLS_education$`Associate degree`)
-four_year_deg <- as.numeric(BLS_education$`Bachelor's degree only`)
-advanaced_deg <- as.numeric(BLS_education$`Advanced degree`)
-BLS_education <- c(highschool_ged, two_year_deg, four_year_deg, advanaced_deg)
-names(BLS_education) <- c("high school/GED" , "2 year degree", "4 year degree", "advanced degree")
-BLS_total <- as.numeric(sum(BLS_education))
-
-# Function to find proportion for each iteration of the vector. 
-e_prop <- function(x) {
-  e <- x/BLS_total
-}
-
-# Use vapply and the above function to get expected proportions from BLS data
-BLS_edu <- sapply(BLS_education, e_prop)
-
-#Use vapply and the above function to get expected proportions from BLS data
-BLS_edu <- sapply(BLS_education, function(x) {x/BLS_total})
-
-# Clean MTurk Data [Note: Due to scaling issues, we cannot analyze the education data for 2017]
-#MTurk_education <- MTurk17 %>%
-#  count(MTurk17$What.level.of.education.have.you.completed.)
-#colnames(MTurk_education) <- c("education level", "n")
-#advanced_deg <- as.numeric(MTurk_education[4,2]) + as.numeric(MTurk_education[5,2])
-#MTurk_education <- rbind(MTurk_education, advanced_deg)
-#MTurk_education[6,1] <- "advanced degree"
-#MTurk_edu <- MTurk_education[c(-4, -5), ]
-
-# Define confidence intervals 
-#eduCI <- binom.confint(x = MTurk_edu$n, n = sum(MTurk_edu$n), conf.level = 0.95, methods = "exact")
-#eduCI <- eduCI[ , 4:6]
-
-# Build Education table 
-#education_table <- cbind(MTurk_edu, eduCI, BLS_edu)
-#names(education_table) <- c("education level", "n", "o", "LL_eth", "UL_eth", "e")
-#education_table <- education_table[ , c(1, 6, 2, 4, 3, 5)]
-
-# Education chi squared test
-#x17.5 <- chisq.test(education_table$n, p = round(education_table$e,3))
-# Result is  significant. MTurk contains an unexpected proportion of education.
-```
-The average worker in 2017 was `r t[["mu"]]` years of age, which again was significantly older than the average MTurk worker (M = `r round(t[["mean"]],2)`, SD = `r round(t[["sd"]],2)`, *t*(`r t[["df"]]`) = `r round(t[["t.statistic"]],2)`, *p* `r myround2(t[["p.value"]])`, *d* = `r round(t[["effect.size"]],2)`).
-
-With regard to gender, the BLS suggests that labor force was slightly male-dominated (Male = `r percent(gender_table$e[2])`; Female = `r percent(gender_table$e[1])`).
-Again, the opposite was the case for the MTurk sample (Male = `r percent(gender_table$o[2])`; Female = `r percent(gender_table$o[2])`.
-This difference was statistically significant in (*X*^2^(`r x17.3[["parameter"]]`) = `r round(x17.3$statistic,2)`, *p* `r myround2(x17.3$p.value)`), again suggesting that MTurk is over-represented by females (standardized residual = `r  round(x17.3[["stdres"]][1],2)`).
-
-With regard to ethnicity, again we examined only the published proportions for Caucasians, African Americans, and Asians.
+## Demographic Diversity of the Broader Labor Force Accessible via MTurk in 2017
+
+Many of our findings regarding the demographic diversity of the 2017 sample (n~3~) mirrored those from 2015.
+The average worker in 2017 was `r t[["mu"]]` years of age, which was significantly older than the average MTurk worker (M = `r round(t[["mean"]],2)`, SD = `r round(t[["sd"]],2)`, *t*(`r t[["df"]]`) = `r round(t[["t.statistic"]],2)`, *p* `r myround2(t[["p.value"]])`, *d* = -`r round(t[["effect.size"]],2)`).
+
+With regard to gender, the BLS suggests a male-biased labor force (Male = `r percent(gender_table$Expected[2])`; Female = `r percent(gender_table$Expected[1])`).
+The opposite was the case for the MTurk sample (Male = `r percent(gender_table$Obs[2])`; Female = `r percent(gender_table$Obs[2])`).
+This difference was statistically significant in ($\chi$^2^(`r x17.3[["parameter"]]`) = `r round(x17.3$statistic,2)`, *p* `r myround2(x17.3$p.value)`), suggesting that MTurk is overrepresented by females (std.
+res.
+= `r  round(x17.3[["stdres"]][1],2)`).
+
+With regard to ethnicity, we examined only the published proportions for Caucasians, African Americans, and Asians.
 BLS summary statistics suggest that the labor force was composed of approximately `r percent(BLS_cauc_17)` Caucasians, `r percent(BLS_AfAm_17)` African Americans, and `r percent(BLS_Asn_17)` Asians.
-Again, this distribution deviated significantly from our our MTurk sample (*X*^2^(`r x17.4[["parameter"]]`) = `r round(x17.4$statistic,2)`, *p* `r myround2(x17.4$p.value)`.
-Post-hoc testing revealed that, again, African Americans (MTurk = `r percent(ethnicity_table$o[1])`) were significantly under-represented (BLS = `r percent(ethnicity_table$e[1])`; standardized residual = `r round(x17.4[["stdres"]][1],2)`).
-Additionally, the "other" category `r percent(ethnicity_table$o[4])` was over-represented by MTurk (standardized residual = `r round(x17.4[["stdres"]][4],2)`).
-The remaining categories conformed to expectations.[^p]
-
-[^p]: Again, education was not analyzed due to a scaling issue.
+This distribution deviated significantly from our our MTurk sample ($\chi$^2^(`r x17.4[["parameter"]]`) = `r round(x17.4$statistic,2)`, *p* `r myround2(x17.4$p.value)`).
+Post-hoc testing revealed that African Americans (MTurk = `r percent(ethnicity_table$Obs[1])`) were significantly underrepresented (std.
+res.
+= `r round(x17.4[["stdres"]][1],2)`).
+Additionally, the "other" category (MTurk = `r percent(ethnicity_table$Obs[4])`) was overrepresented by MTurk (std.
+res.
+= `r round(x17.4[["stdres"]][4],2)`).
+Caucasians (MTurk: `r percent(ethnicity_table$Obs[3])`; std.
+res.: `r round(x17.4[["stdres"]][3],2)`) and Asians (MTurk: `r percent(ethnicity_table$o[2])`; std.
+res.: `r round(x17.4[["stdres"]][2],2)`) were represented in a manner that was consistent with expectations.
 
@@
 
-What started our investigation was a simple research question: is the occupational diversity of the MTurk population representative of the broader US population?
-While our data suggest that the answer is not consistently so, it is nevertheless striking how the diversity of MTurk nevertheless mirrors that of the broader labor force (albeit, imperfectly).
-Though MTurk over-represents certain white-collar occupations and under-represent blue collar occupations, the overall pattern does mirror the broader labor force.
-This is important because of questions concerning the work settings from which these individuals are sampled.
-Nevertheless, while sampling from MTurk does give researchers an useful cross-section of labor force, this cross-section is not ideal and so adjustments may be needed [e.g., respondent weighting; @simonsCommonMisBeliefs2012], particularly when drawing inferences to the larger labor force.
-
-## Recommendations for Researchers Using MTurk
-
-Given that organizational researchers will likely wish to continue using MTurk as a means of gathering diverse, convenient, and low-cost survey sample data, researchers should consider how differences in the occupational diversity observed among MTurk workers relative to the US population might impinge upon the generalizability of their findings [@newmanExternalValidityMultiorganization2015].
-Specifically, given the over-representation of workers from (1) Management, Business, and Financial, (2) Computer, Engineering, and Science, and (3) Education, Legal, Community Service, Arts, and Media occupations, we might safely assume that many of our findings from MTurk will generalize across jobs classified under these broader over-represented occupational categories.
-However, as many occupations were under-represented [e.g., (1) Service, (2) Construction and Extraction, (3) Installation, Maintenance, and Repair, (4) Production; and (5) Transportation and Material Moving], questions may arise as to whether findings will generalize to jobs falling under these broad classifications.
-
-To address this issue, researchers should consider capturing occupational data and modeling theoretically derived moderators.
-Person-environment (P-E) fit theories should help guide researchers in proposing how certain occupational groupings might influence individual-level relationships, lending to more nuanced and contextualized results [@meadeDrStrangeLOVEHow2009].
-Further, O*NET might be useful in this regard as it provides researchers a means for quantifying key occupational differences (e.g., level of competition requirements, social skills requirements) and thereby testing P-E fit hypotheses pertaining to occupational group differences [see @judgePersonSituationDebate2015].
+Consistent with the broader literature on MTurk demographics [@behrendViabilityCrowdsourcingSurvey2011; @berinskyEvaluatingOnlineLabor2012; @difallahDemographicsDynamicsMechanical2018; @keithSystemsPerspectiveAmazon2017; @levayDemographicPoliticalComposition2016], we identified consistent trends in the occupational makeup of MTurk, which suggest that the labor force available for study via MTurk does not mirror the broader labor force.
+Rather, the labor force that is accessible via MTurk contains a disproportionate share of certain white-collar occupations and a dearth of blue-collar occupations.
+Specifically, MTurk workers were consistently more likely to come from occupational areas related to (i) Management, Business, and Financial, (ii) Computer, Engineering, and Science, and (iii) Education, Legal, Community Service, Arts, and Media occupations.
+They were also less likely to come from occupational areas related to (i) Service, (ii) Construction and Extraction, (iii) Installation, Maintenance, and Repair, (iv) Production, and (v) Transportation and Material Moving.
+The remaining occupations were consistent with expectations.
+One exception applies Healthcare Practitioners and Technical occupations, where one 2015 sample suggested that these occupations were underrepresented.
+However, the confidence intervals for the two 2015 samples overlapped, and so we suspect that this was a sampling error.
+Demographically, the labor force that is available through MTurk is younger, female-biased, less likely to contain African Americans, overrepresented by other ethnic groups (likely Hispanics), and more likely to contain highly educated members of the labor force [these trends mirror prior research on the MTurk population as a whole; see @keithSystemsPerspectiveAmazon2017].
+Nevertheless, our study thus contributes to the literature on the demographics of the MTurk population and on the generalizability of social science research that relies on MTurk [e.g., @paolacciRunningExperimentsAmazon2010; @henrichWeirdestPeopleWorld2010].
+
+Given recent claims that the organizational science literature holds greater relevance for certain kinds of workers [e.g., core, salaried, managerial; @bergmanWhereHaveAll2016] and that scholars have increasingly relied upon MTurk for reasons that include enhancing generalizability [@keithSystemsPerspectiveAmazon2017; @landersInconvenientTruthArbitrary2015], our findings regarding the occupational diversity of MTurk appear troubling.
+Overall, these findings suggest that, by increasingly relying upon MTurk, we may simply be more easily sampling from a population that we have historically overstudied [e.g., core, salaried, and managerial workers; @bergmanWhereHaveAll2016].
+For instance, the most consistently sampled group of individuals worked in Management, Business, and Financial occupations, which are groups that we have long studied [@bergmanWhereHaveAll2016].
+If so, then organizational scholars may be overstating conclusions generated using MTurk samples, particularly when the occupational characteristics matter [as they often do; see @johnsEssentialImpactContext2006; @newmanExternalValidityMultiorganization2015].
+Therefore, we hope to caution future researchers against assuming that MTurk samples adequately sample from the broader labor force.
+For researchers using MTurk in their research, we have the following recommendations, thus contributing to the behavioral research methods literature on the proper use of MTurk [e.g., @cheungAmazonMechanicalTurk2017; @keithSystemsPerspectiveAmazon2017; @landersInconvenientTruthArbitrary2015]
+
+## Recommendations for Organizational Scholars Using MTurk for Research Purposes
+
+Despite the concerns we have raised regarding the occupational diversity of the labor force that is accessible through MTurk, it is nevertheless striking how the distribution mirrors that of the broader labor force (albeit, imperfectly).
+Though MTurk overrepresents certain white-collar occupations and underrepresents blue collar occupations, the overall pattern does mirror the broader labor force.
+While this does echo the claim made by @michelAmazonMechanicalTurk2018, namely that the labor force that is accessible via MTurk is diverse, if researchers hope to generalize across the workforce while using MTurk, then other methodological choices must be made [e.g., stratified sampling, respondent weighting; for examples, see @simonsCommonMisBeliefs2012; @levayDemographicPoliticalComposition2016].
+
+While scholars studying organizational phenomena may consider pre-screening for employment, this action could backfire.
+A recent observation has been made suggesting that roughly 20% of participants will lie to gain access to a study [@chandlerLieDimeWhen].
+It does not appear as though we encountered this problem because we informed our participants that, while we were interested in studying members of the labor force via MTurk, we would still allow non-labor force members to participate (they were given access to generic individual difference measures).
+We do not have experimental evidence demonstrating that this messaging had the desired effect, however.
+Future researchers drawing on MTurk may wish to test this.
+In the interim, scholars drawing on MTurk might consider adopting our messaging strategy to sample labor force participants through MTurk.
+
+Another way for scholars studying organizational phenomena is to leverage what diversity the MTurk population does have to, for instance, form more precise predictions of organizational phenomena.
+Consider that, in testing a unified model of person-situation interactionism, @judgePersonSituationDebate2015 predicted both the extent to which personality traits as a whole relate to performance (e.g., traits are more predictive in weak work situations, such as those granting decision making authority) and how strongly certain traits would relate to performance (e.g., conscientiousness is more predictive for occupations that require independence and strong attention-to-detail requirements).
+While they did not rely on MTurk (Judge and Zapata drew upon available data from the BLS as well as published meta-analyses), one could adapt their approach for studying the MTurk population by using multi-level modeling techniques [@kozlowskiMultilevelApproachTheory2000; @newmanExternalValidityMultiorganization2015].
+By joining BLS data with data collected from MTurk, researchers might enhance their predictions of workplace outcomes, such as counterproductive behavior and citizenship behavior [@judgeBrightDarkSides2007; @kish-gephartBadApplesBad2010; @oboyleMetaanalysisDarkTriad2012].
+Doing so can facilitate theory testing in ways that may not have been considered previously [e.g., comparing objective vs.
+subjective situations; see @tettPersonalityTraitbasedInteractionist2003].
 
@@
 
-One key limitation is that we assumed that O*NET’s classification system perfectly captured all occupations during 2015.
-Additionally, as both studies involved convenient sampling procedures, it remains uncertain the extent to which these samples adequately reflect the larger MTurk population.
-Still, the consistency of our findings should be considered by future OB/HR researchers hoping to draw on MTurk for their research with the hopes of generalizing to the larger (or a specific) working US population.
-Additionally, as our studies were conducted in the US, it remains unclear how other MTurk populations might reflect (however imperfectly) their respective broader labor force.
+As all our samples were obtained via convenient sampling procedures, it remains uncertain the extent to which these samples adequately reflect the larger MTurk population.
+There are a variety of reasons why this could be the case [e.g., participants' use of message boards to identify our study; see @keithSystemsPerspectiveAmazon2017].
+Nevertheless, the consistency of our findings across our samples should be considered by organizational scholars hoping to draw on MTurk for their research with the hopes of generalizing to the larger labor force population.
+Additionally, as our studies were conducted in the U.S., it remains unclear how other MTurk populations might reflect (however imperfectly) their respective broader labor force.
 Future larger scale studies should also consider lower levels of BLS occupational classification to examine the extent to which narrower occupations might not be represented by MTurk.
-Lastly, examining diversity in other respects (age, ethnic, income, education, etc.) should also be considered.
-Though MTurk offers a practically feasible method of attaining high quality data, future research will be needed to understand the limitations of this tool.
+
+Given that roughly half of MTurk workers might be Turking while working [@offermannWhatOweMy2015], future research should examine the occupational features that motivate such behavior.
+For instance, in responding to the question "Does your job make a meaningful contribution to the world?", roughly 40% of individuals answer no [see @graeberBullshitJobs2018].
+Examining the occupational characteristics (e.g., job characteristics) that relate to questions via MTurk would be interesting for cultivating a deeper understanding about the nature of work for the labor force participants who are available via MTurk.
 
 Given that our data were gathered and analyzed in 2015 and 2017, it might be insightful to have our procedures replicated annually to examine how the demographics of MTurk, specifically occupational characteristics, change over time, especially as access to technology becomes even easier and more commonplace.
-Thus, we encourage researchers to continue examining the occupational diversity of MTurk relative to the US labor force.
-We also encourage researchers to consider novel ways of approximating the occupational diversity of both the US labor force and MTurk because the currently existing taxonomies that we have used (i.e., BLS-based) probably do not capture all occupations.
-Lastly, our results raise a new and interesting research question: Why might MTurk possess the occupational diversity makeup that it does (i.e., why are some occupations over-represented while others are under-represented)?
+Thus, we encourage researchers to continue examining the occupational diversity of MTurk relative to the U.S.
+labor force.
+We also encourage researchers to consider novel ways of approximating the occupational diversity of both the U.S.
+labor force and MTurk as the currently existing taxonomies that we have used (i.e., BLS-based) probably do not capture all occupations.
+Lastly, our results raise a new and interesting research question: Why might MTurk possess the occupational diversity makeup that it does (i.e., why are some occupations overrepresented while others are under-represented)?
 Similarly, what factors (e.g., access to technology, interest in psychology) might make it easier for workers coming from certain occupations to participate in OB studies hosted on MTurk?
